### 2021-11-30 Fish Data Analysis/Figure_Duplication.Rmd
Working on code to analyze data.

---
title: "Figure Duplication"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(car)
library(viridis)
library(boot)
```

### Katz, Y., Tunstrom, K., Ioannou, C. C., Huepe, C., & Couzin, I. D. (2011). Inferring the structure and dynamics of interactions in schooling fish. Proceedings of the National Academy of Sciences, 108(46), 18720–18725. https://doi.org/10.1073/pnas.1107583108

![Katz Figure 1](Figures/Katz_2011_Fig1.png)

```{r}

```

### Chicoli, A., Butail, S., Lun, Y., Bak-Coleman, J., Coombs, S., & Paley, D. A. (2014). The effects of flow on schooling Devario aequipinnatus: School structure, startle response and information transmission. Journal of Fish Biology, 84(5), 1401–1421. https://doi.org/10.1111/jfb.12365

![Chicoli Figure 3](Figures/Chicoli_2014_Fig3.png)

```{r}

```

### McKee, A., Soto, A. P., Chen, P., & McHenry, M. J. (2020). The sensory basis of schooling by intermittent swimming in the rummy-nose tetra ( Hemigrammus rhodostomus ). Proceedings of the Royal Society B: Biological Sciences, 287(1937), 20200568. https://doi.org/10.1098/rspb.2020.0568

![McKee Figure 3](Figures/McKee_2020_Fig3.png)

```{r}

```

### 2021-11-30 Fish Data Analysis/Ji_Zhou_Data.Rmd
Working on code to analyze data.

---
title: "Fish Data For Ji Zhou"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(car)
library(viridis)
library(boot)
```

```{r}
comp_data <- read.csv("Fish_Comp_Values.csv")
comp_data <- na.omit(comp_data)

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           filter(Distance <= 4) %>%
                           filter(Speed_Diff <= 6) %>% 
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))

indiv_data <- indiv_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark"))

```

Tank Size: 60cm long and 25cm wide

Fish Size:

  Small Fish: 
    Length: 
    Width:
    Height:

  Big Fish: 
    Length: 
    Width:
    Height:

Flow: 10.16 cm/s

```{r}
comp_data %>% group_by(Flow, Ablation, Darkness) %>% summarise(mean_Dist = round(mean(Distance),2), 
                                                                sd_Dist = round(sd(Distance),2))
```

NND:
  Still Mean: 1.87
  Still SD:   0.89

  Flow Mean:  1.90
  Flow SD:    1.00

```{r}
indiv_data %>% group_by(Flow, Ablation, Darkness) %>% summarise(mean_Dist = round(mean(Speed),2), 
                                                                sd_Dist = round(sd(Speed),2))
```

Speed:
  Still Mean: 1.42
  Still SD:   0.83

  Flow Mean:  2.38
  Flow SD:    0.66

```{r}
indiv_data %>% group_by(Flow, Ablation, Darkness) %>% summarise(mean_Dist = round(mean(TB_Frequency),2), 
                                                                sd_Dist = round(sd(TB_Frequency),2))
```

Tailbeat Frequency:
  Still Mean: 2.29
  Still SD:   1.15

  Flow Mean:  2.82
  Flow SD:    1.43

### 2021-11-30 Fish Data Analysis/comp_fish.Rmd
Working on code to analyze data.

---
title: "Fish Comparisons"
output: html_notebook
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(car)
library(mgcv)
library(viridis)
```

Sets up the functions that will be used later 
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan(mean(sin(deg2rad(x)))/mean(cos(deg2rad(x)))))}
```

```{r}
max_x <- 2
min_x <- 2

max_y <- 2
min_y <- 0

max_d <- 2
```

#Reads in the data and alters it as needed 
```{r}
comp_data <- read.csv("Fish_Comp_Values.csv")
comp_data <- na.omit(comp_data)

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           filter(Speed_Diff <= 6) %>% 
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))

sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
                               summarise(Speed_Diff = mean(Speed_Diff),
                                         Heading_Diff = ang_mean(Heading_Diff),
                                         Sync = mean(Sync),
                                         Quarter_Heading_Diff = mean(quarter_heading_diff),
                                         Is_Aligned = mean(Is_Aligned),
                                         Is_Reversed = mean(Is_Reversed))
```

Graphs the density of the fish 
```{r}
ggplot(comp_data , aes(x = X_Distance, y = abs(Y_Distance)))+
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  xlim(-3,3) + 
  ylim(0,3) +
  theme_light()
```
This creates a dataframe that is used for making model predictions and graphing them
```{r}
#Dataframe for Predictions

d <- seq(from = 0, to = 2, by = 0.1)
a <- seq(from = 0, to = 180, by = 10)

x <- seq(from = -sqrt(2), to = sqrt(2), by = 0.1)
y <- seq(from = 0, to = sqrt(2), by = 0.1)

flows <- c("Flow 0", "Flow 2")
ablation <- c("No Ablation", "Ablated")
dark <- c("Light","Dark")

#predict_df <- expand.grid(Distance = d, Angle = a, Flow = flows, Ablation = ablation, Darkness = dark)
#predict_df <- predict_df %>% mutate(X_Distance = Distance*(cos(deg2rad(Angle))), Y_Distance = Distance*(sin(deg2rad(Angle))))

predict_df <- expand.grid(X_Distance = x, Y_Distance = y, Flow = flows, Ablation = ablation, Darkness = dark)
predict_df <- predict_df %>% mutate(Distance = sqrt(X_Distance**2 + Y_Distance**2), Angle = rad2deg(atan(Y_Distance/X_Distance)))

predict_df <- predict_df %>% filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
predict_df <- na.omit(predict_df)

```

## Speed Differences

First we make a GAM based on the speed data
```{r}
# speed_gam <- gam(Speed_Diff ~ s(Distance)+s(Angle)+s(Distance,Angle)+
#                               Flow+s(Distance,by=Flow)+s(Angle,by=Flow)+s(Distance,Angle,by=Flow)+
#                               Darkness+s(Distance,by=Darkness)+s(Angle,by=Darkness)+s(Distance,Angle,by=Darkness)+
#                               Ablation+s(Distance,by=Ablation)+s(Angle,by=Ablation)+s(Distance,Angle,by=Ablation),
#                               data = comp_data %>% mutate(Flow = as.factor(Flow),
#                                                           Darkness = as.factor(Darkness),
#                                                           Ablation = as.factor(Ablation)))
```

```{r}
summary(speed_gam)
speed_pred <- predict_df %>% mutate(Speed_Diff = predict.gam(speed_gam,predict_df))
```

Next we plot speed difference vs distance and angle
```{r}
ggplot(speed_pred, aes(x = Distance, y = Speed_Diff))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(speed_pred, aes(x = Angle, y = Speed_Diff))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()
```
Now we plot the modeled data as well as the actual summarized data
```{r}
ggplot(speed_pred, aes(x = X_Distance, y = Y_Distance, fill = Speed_Diff))+
  geom_tile()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(sum_comp_data , aes(x = X_Distance, y = Y_Distance, fill = Speed_Diff))+
  geom_tile() +
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  xlim(-2,2) + 
  ylim(0,2) +
  theme_light()
```

## Heading Differences

```{r}
comp_data <- comp_data %>% mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))
```

Next we make a GAM based on the heading data
```{r}
# heading_gam <- gam(Heading_Diff ~ s(Distance)+s(Angle)+s(Distance,Angle)+
#                               Flow+s(Distance,by=Flow)+s(Angle,by=Flow)+s(Distance,Angle,by=Flow)+
#                               Darkness+s(Distance,by=Darkness)+s(Angle,by=Darkness)+s(Distance,Angle,by=Darkness)+
#                               Ablation+s(Distance,by=Ablation)+s(Angle,by=Ablation)+s(Distance,Angle,by=Ablation),
#                               data = comp_data %>% mutate(Flow = as.factor(Flow),
#                                                           Darkness = as.factor(Darkness),
#                                                           Ablation = as.factor(Ablation)))
```

```{r}
summary(heading_gam)
heading_pred <- predict_df %>% mutate(Heading_Diff = predict.gam(heading_gam,predict_df))
```

Then we plot the heading differences vs distance and angle
```{r}
ggplot(heading_pred, aes(x = Distance, y = Heading_Diff))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(heading_pred, aes(x = Angle, y = Heading_Diff))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()
```
And then we plot heading differnces on the 2D plane to compare with the actual data
```{r}
# ggplot(heading_pred, aes(x = X_Distance, y = Y_Distance, fill = Heading_Diff))+
#   geom_tile()+
#   scale_fill_viridis() +
#   facet_wrap(~ Flow + Ablation + Darkness) +
#   theme_light()

ggplot(sum_comp_data, aes(x = X_Distance, y = Y_Distance, fill = Quarter_Heading_Diff)) +
  geom_tile()+
  xlim(-2,2) +
  ylim(0,2) +
  facet_wrap(~ Flow + Ablation + Darkness) +
  scale_fill_viridis() +
  theme_light()

ggplot(sum_comp_data, aes(x = X_Distance, y = Y_Distance, fill = Is_Aligned)) +
  geom_tile()+
  xlim(-2,2) +
  ylim(0,2) +
  facet_wrap(~ Flow + Ablation + Darkness) +
  scale_fill_gradient(low = "#EEEEEE",high = "#FF0000") +
  theme_light()

ggplot(sum_comp_data, aes(x = X_Distance, y = Y_Distance, fill = Is_Reversed)) +
  geom_tile()+
  xlim(-2,2) +
  ylim(0,2) +
  facet_wrap(~ Flow + Ablation + Darkness) +
  scale_fill_gradient(low = "#EEEEEE",high = "#0000FF") +
  theme_light()

```
##Sync Differences

```{r}
# sync_gam <- gam(Sync ~ s(Distance)+s(Angle)+s(Distance,Angle)+
#                               Flow+s(Distance,by=Flow)+s(Angle,by=Flow)+s(Distance,Angle,by=Flow)+
#                               Darkness+s(Distance,by=Darkness)+s(Angle,by=Darkness)+s(Distance,Angle,by=Darkness)+
#                               Ablation+s(Distance,by=Ablation)+s(Angle,by=Ablation)+s(Distance,Angle,by=Ablation),
#                               data = comp_data %>% mutate(Flow = as.factor(Flow),
#                                                           Darkness = as.factor(Darkness),
#                                                           Ablation = as.factor(Ablation)))
```

```{r}
summary(sync_gam)
sync_pred <- predict_df %>% mutate(Sync = predict.gam(sync_gam,predict_df))
```

Trying to do different non-gam models
```{r}

#All variables
#speed_m_all = lm(crim~.,data = Boston)

#No variables
#m0 = lm(crim~1,data = Boston)

```

```{r}
ggplot(sync_pred, aes(x = Distance, y = Sync))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(sync_pred, aes(x = Angle, y = Sync))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()
```

```{r}
ggplot(sync_pred, aes(x = X_Distance, y = Y_Distance, fill = Sync))+
  geom_tile()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(sum_comp_data , aes(x = X_Distance, y = Y_Distance, fill = abs(Sync)))+
  geom_tile() +
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  xlim(-3,3) + 
  ylim(0,3) +
  theme_light()
```

### 2021-11-30 Fish Data Analysis/comp_fish_simple_models.Rmd
Working on code to analyze data.

---
title: "Fish Comparisons Simple Models"
output: html_notebook
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(car)
library(viridis)
library(boot)
```

So here we're going to do some simpler model selection things with the data using GLMs instead of GAMs

Sets up the functions that will be used later 
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan(mean(sin(deg2rad(x)))/mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}
```

Reads in the data and alters it as needed 
```{r}
comp_data <- read.csv("Fish_Comp_Values.csv")
comp_data <- na.omit(comp_data)

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           filter(Distance <= 4) %>%
                           filter(Speed_Diff <= 6) %>% 
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))

sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
                               summarise(Speed_Diff = mean(Speed_Diff),
                                         Heading_Diff = ang_mean(Heading_Diff),
                                         Sync = mean(Sync),
                                         Quarter_Heading_Diff = mean(quarter_heading_diff),
                                         Is_Aligned = mean(Is_Aligned),
                                         Is_Reversed = mean(Is_Reversed))

```

#Basic Stats

```{r}
speed_anova <- glm(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(speed_anova)

heading_anova <- glm(quarter_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(heading_anova)

sync_anova <- glm(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(sync_anova)

dist_anova <- glm(Distance ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(dist_anova)
```

```{r}
ggplot(comp_data, aes(x = Flow, y = Speed_Diff, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,3) +
  theme_light()

ggplot(comp_data, aes(x = Flow, y = quarter_heading_diff, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,90) +
  theme_light()

ggplot(comp_data, aes(x = Flow, y = Sync, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,1) +
  theme_light()

ggplot(comp_data, aes(x = Flow, y = Distance, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,4) +
  theme_light()
```

Now we add in distance and angle

```{r}
speed_anova_da <- glm(Speed_Diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)

Anova(speed_anova_da)

heading_anova_da <- glm(quarter_heading_diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)

Anova(heading_anova_da)

sync_anova_da <- glm(Sync ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)

Anova(sync_anova_da)
```

```{r}
ggplot(comp_data, aes(x = Distance, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Distance, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Distance, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()
```
```{r}
ggplot(comp_data, aes(x = Angle, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()
```

This creates a dataframe that is used for making model predictions and graphing them
```{r}
d <- seq(from = 0, to = 4, by = 0.1)
a <- seq(from = 0, to = 180, by = 10)

flows <- c("Flow 0", "Flow 2")
ablation <- c("No Ablation", "Ablated")
dark <- c("Light","Dark")

predict_df_da <- expand.grid(Distance = d, Angle = a, Flow = flows, Ablation = ablation, Darkness = dark)
predict_df_da <- predict_df_da %>% mutate(X_Distance = Distance*(cos(deg2rad(Angle))), Y_Distance = Distance*(sin(deg2rad(Angle))))

predict_df_da <- predict_df_da %>% filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
predict_df_da <- na.omit(predict_df_da)
```

### Speed Models

So I want to make a model that tries to include both distance and angle. What I really need is to figure out what power works best for angle and distance, and then include that. The issue is stepwise selection can just remove one of them entirely. So I'm going to use cross validation to select the power for both of them, and then use that. I will also calculate the AICs to help in this decision making process

```{r, warnings=F}
set.seed(7)

comp_data_speed_model <- comp_data %>% select(c(Flow,Darkness,Ablation,Angle,Distance,Speed_Diff))

max_poly <- 10

speed_dist_cv_error_10 <- rep(0,max_poly)
speed_dist_AIC_10 <- rep(0,max_poly)

for (i in 1:max_poly){
  speed_dist_fit <- glm(Speed_Diff ~ poly(Distance,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                        data = comp_data_speed_model)
  speed_dist_cv_error_10[i] <- cv.glm(comp_data_speed_model, speed_dist_fit, K = 10)$delta[1]
  speed_dist_AIC_10[i] <- AIC(speed_dist_fit)
}

speed_angle_cv_error_10 <- rep(0,max_poly)
speed_angle_AIC_10 <- rep(0,max_poly)

for (i in 1:max_poly){
  speed_angle_fit <- glm(Speed_Diff ~ poly(Angle,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                         data = comp_data_speed_model)
  speed_angle_cv_error_10[i] <- cv.glm(comp_data_speed_model, speed_angle_fit, K = 10)$delta[1]
  speed_angle_AIC_10[i] <- AIC(speed_angle_fit)
}

speed_poly_plot_df <- data.frame(c(seq(max_poly),seq(max_poly)),
                                 c(speed_dist_cv_error_10,speed_angle_cv_error_10),
                                 c(speed_dist_AIC_10,speed_angle_AIC_10),
                                 c(rep("Distance",max_poly),rep("Angle",max_poly)))

colnames(speed_poly_plot_df) <- c("Degree","Error","AIC","Predictor")

speed_poly_plot_df <- speed_poly_plot_df %>% group_by(Predictor) %>%
                                             mutate(minError = min(Error),minAIC = min(AIC)) %>%
                                             ungroup() %>%
                                             mutate(isMinEror = ifelse(Error == minError,3,1),isMinAIC = ifelse(AIC == minAIC,3,1))

ggplot(speed_poly_plot_df, aes(x = Degree, y = Error, color = Predictor))+
  geom_point(size = speed_poly_plot_df$isMinEror)+
  geom_line()+
  theme_light()+
  facet_wrap(~ Predictor, scales = "free") +
  scale_size(guide = "none")

ggplot(speed_poly_plot_df, aes(x = Degree, y = AIC, color = Predictor))+
  geom_point(size = speed_poly_plot_df$isMinAIC)+
  geom_line()+
  theme_light()+
  facet_wrap(~ Predictor, scales = "free") +
  scale_size(guide = "none")
```
Now let's use those polynomials to create the actual model

While they not be the lowest, the big improvements happen at 4 for Distance, and 2 for Angle

```{r}
speed_diff_glm <- glm(Speed_Diff ~ poly(Distance,4)*poly(Angle,2)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                        data = comp_data_speed_model)

summary(speed_diff_glm)
```

Now let's make some predictions

```{r}
speed_pred <- predict_df_da %>% mutate(Speed_Diff = predict(speed_diff_glm,predict_df_da))

comp_data <- comp_data %>% mutate(Round_Dist = as.factor(round_any(Distance,1)), Round_Angle = as.factor(round_any(Angle,30)))

ggplot()+
  geom_boxplot(data = comp_data, aes(x = Round_Dist, y = Speed_Diff))+
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

round_dist_aov <- aov(Speed_Diff ~ Round_Dist*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
Anova(round_dist_aov)

ggplot()+
  geom_boxplot(data = comp_data, aes(x = Round_Angle, y = Speed_Diff))+
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

round_angle_aov <- aov(Speed_Diff ~ Round_Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
Anova(round_angle_aov)

# ggplot()+
#   geom_point(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Distance, y = Speed_Diff), alpha = 0.1)+
#   geom_smooth(data = speed_pred, aes(x = Distance, y = Speed_Diff))+
#   facet_wrap(~ Flow + Ablation + Darkness) +
#   theme_light()

# ggplot()+
#   geom_density_2d_filled(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Distance, y = Speed_Diff), contour_var = "ndensity")+
#   geom_smooth(data = speed_pred, aes(x = Distance, y = Speed_Diff, color = "red"))+
#   facet_wrap(~ Flow + Ablation + Darkness) +
#   theme_light()

# ggplot()+
#   geom_point(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Angle, y = Speed_Diff), alpha = 0.1)+
#   geom_smooth(data = speed_pred, aes(x = Angle, y = Speed_Diff))+
#   facet_wrap(~ Flow + Ablation + Darkness) +
#   theme_light()

# ggplot()+
#   geom_density_2d_filled(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Angle, y = Speed_Diff), contour_var = "ndensity")+
#   geom_smooth(data = speed_pred, aes(x = Angle, y = Speed_Diff, color = "red"))+
#   facet_wrap(~ Flow + Ablation + Darkness) +
#   theme_light()

ggplot(data = comp_data, aes(x = Angle, y = Distance, z = Speed_Diff))+
  stat_summary_2d() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  scale_fill_viridis(direction = -1) +
  theme_light()
```
You know let's just try stepwise as well. There's jsut way too many thing in that possible model

```{r}

speed_m_all <- glm(Speed_Diff ~ Distance*Angle*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow) +
                                I(Distance^2)*I(Angle^2)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow)+
                                I(Distance^3)*I(Angle^3)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow)+
                                I(Distance^4)*I(Angle^4)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                        data = comp_data_speed_model)

speed_m_none <- glm(Speed_Diff ~ 1, data = comp_data_speed_model)

speed_m_both <- step(speed_m_none, direction = "both", scope = formula(speed_m_all), trace = F)

summary(speed_m_both)
```

### Sync Models

Now let's try the same thing for sync values (Rayleigh's R)

```{r, warnings=F}
set.seed(7)

comp_data_sync_model <- comp_data %>% select(c(Flow,Darkness,Ablation,Angle,Distance,Sync))

max_poly <- 10

sync_dist_cv_error_10 <- rep(0,max_poly)
sybc_dist_AIC_10 <- rep(0,max_poly)

for (i in 1:max_poly){
  sync_dist_fit <- glm(Sync ~ poly(Distance,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                        data = comp_data_sync_model)
  sync_dist_cv_error_10[i] <- cv.glm(comp_data_sync_model, sync_dist_fit, K = 10)$delta[1]
  sybc_dist_AIC_10[i] <- AIC(sync_dist_fit)
}

sync_angle_cv_error_10 <- rep(0,max_poly)
sync_angle_AIC_10 <- rep(0,max_poly)

for (i in 1:max_poly){
  sync_angle_fit <- glm(Sync ~ poly(Angle,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                         data = comp_data_sync_model)
  sync_angle_cv_error_10[i] <- cv.glm(comp_data_sync_model, sync_angle_fit, K = 10)$delta[1]
  sync_angle_AIC_10[i] <- AIC(sync_angle_fit)
}

sync_poly_plot_df <- data.frame(c(seq(max_poly),seq(max_poly)),
                                 c(speed_dist_cv_error_10,speed_angle_cv_error_10),
                                 c(speed_dist_AIC_10,speed_angle_AIC_10),
                                 c(rep("Distance",max_poly),rep("Angle",max_poly)))

colnames(sync_poly_plot_df) <- c("Degree","Error","AIC","Predictor")

sync_poly_plot_df <- sync_poly_plot_df %>% group_by(Predictor) %>%
                                             mutate(minError = min(Error),minAIC = min(AIC)) %>%
                                             ungroup() %>%
                                             mutate(isMinEror = ifelse(Error == minError,3,1),isMinAIC = ifelse(AIC == minAIC,3,1))

ggplot(sync_poly_plot_df, aes(x = Degree, y = Error, color = Predictor))+
  geom_point(size = sync_poly_plot_df$isMinEror)+
  geom_line()+
  theme_light()+
  facet_wrap(~ Predictor, scales = "free") +
  scale_size(guide = "none")

ggplot(sync_poly_plot_df, aes(x = Degree, y = AIC, color = Predictor))+
  geom_point(size = sync_poly_plot_df$isMinAIC)+
  geom_line()+
  theme_light()+
  facet_wrap(~ Predictor, scales = "free") +
  scale_size(guide = "none")
```
Now let's use those polynomials to create the actual model

While they not be the lowest, the big improvements happen at 2 for Distance, and 2 for Angle

```{r}
sync_diff_glm <- glm(Sync ~ I(Distance^2)*I(Angle^2)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
                        data = comp_data_sync_model)

summary(sync_diff_glm)
```

Now let's make some predictions

```{r}
sync_pred <- predict_df_da %>% mutate(Sync = predict(sync_diff_glm,predict_df_da))

ggplot(comp_data, aes(x = Distance, y = Sync))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = lm, formula = y ~ poly(x, 2)) +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = Sync))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = glm, formula = y ~ poly(x, 2))+
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(sync_pred, aes(x = Distance, y = Sync))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()

ggplot(sync_pred, aes(x = Angle, y = Sync))+
  geom_smooth()+
  scale_fill_viridis() +
  facet_wrap(~ Flow + Ablation + Darkness) +
  theme_light()
```

### 2021-11-30 Fish Data Analysis/comp_fish.R

@@ -50,10 +50,22 @@ predict_df <- na.omit(predict_df)
 
 ## Speed Differences
 
-speed_gam <- gam(Speed_Diff ~ s(Distance)+s(Angle)+Flow+Darkness+Ablation, data = comp_data)
+speed_gam <- gam(Speed_Diff ~ s(Distance)+s(Angle)+s(Distance,Angle)+Flow+Darkness+Ablation, data = comp_data)
 summary(speed_gam)
 plot(speed_gam,pages=1,residuals=TRUE)
 speed_pred <- predict_df %>% mutate(Speed_Diff = predict.gam(speed_gam,predict_df))
+
+ggplot(speed_pred, aes(x = Distance, y = Speed_Diff))+
+  geom_smooth()+
+  scale_fill_viridis() +
+  facet_wrap(~ Flow + Ablation + Darkness) +
+  theme_light()
+
+ggplot(speed_pred, aes(x = Angle, y = Speed_Diff))+
+  geom_smooth()+
+  scale_fill_viridis() +
+  facet_wrap(~ Flow + Ablation + Darkness) +
+  theme_light()
 
 ggplot(speed_pred, aes(x = X_Distance, y = Y_Distance, fill = Speed_Diff))+
   geom_tile()+
@@ -71,10 +83,22 @@ ggplot(sum_comp_data , aes(x = X_Distance, y = Y_Distance, fill = Speed_Diff))+
 
 ## Heading Differences
 
-heading_gam <- gam(Heading_Diff ~ s(Distance)+s(Angle)+Flow+Darkness+Ablation, data = comp_data)
+heading_gam <- gam(Heading_Diff ~ s(Distance)+s(Angle)+s(Distance,Angle)+Flow+Darkness+Ablation, data = comp_data)
 summary(heading_gam)
 plot(heading_gam,pages=1,residuals=TRUE)
 heading_pred <- predict_df %>% mutate(Heading_Diff = predict.gam(heading_gam,predict_df))
+
+ggplot(heading_pred, aes(x = Distance, y = Heading_Diff))+
+  geom_smooth()+
+  scale_fill_viridis() +
+  facet_wrap(~ Flow + Ablation + Darkness) +
+  theme_light()
+
+ggplot(heading_pred, aes(x = Angle, y = Heading_Diff))+
+  geom_smooth()+
+  scale_fill_viridis() +
+  facet_wrap(~ Flow + Ablation + Darkness) +
[…]

### 2021-11-30 Fish Data Analysis/individual_fish.R

@@ -7,11 +7,10 @@ indiv_data <- read.csv("Fish_Individual_Values.csv")
 indiv_data <- na.omit(indiv_data)
 
 indiv_data <- indiv_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
-                             mutate(Abalation = ifelse(Abalation == "N", "No Ablation", "Ablated")) %>%
-                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                             rename(Ablation = Abalation)
+                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark"))
 
-m_speed <- aov(Speed ~ Flow + Ablation + Darkness + Flow*Ablation + Flow*Darkness, data = indiv_data)
+m_speed <- aov(Speed ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = indiv_data)
 Anova(m_speed)
 TukeyHSD(m_speed)
 

### 2021-11-30 data_files_to_csv_4P.py

@@ -17,6 +17,7 @@ import matplotlib as mpl
 from matplotlib import gridspec 
 import pandas as pd
 import numpy as np
+import random
 import math
 import os
 
@@ -108,7 +109,7 @@ def x_intercept(x1,y1,x2,y2):
     return intercept
 
 class fish_data:
-    def __init__(self, name, data, scorer):
+    def __init__(self, name, data, scorer, flow):
         #This sets up all of the datapoints that I will need from this fish
         self.name = name
         self.head_x = data[scorer][name]["head"]["x"].to_numpy() 
@@ -123,6 +124,8 @@ class fish_data:
         self.tailtip_x = data[scorer][name]["tailtip"]["x"].to_numpy() 
         self.tailtip_y = data[scorer][name]["tailtip"]["y"].to_numpy()
         self.tailtip_perp = [] 
+
+        self.flow = flow
         
         #These are all blank and will be used for graphing
         self.normalized_tailtip = []
@@ -152,16 +155,26 @@ class fish_data:
         vec_y = head_y_next - self.head_y
 
         #Then we use arctan to calculate the heading based on the x and y point vectors
-        self.heading = np.rad2deg(np.arctan2(vec_y,vec_x))
+        #Becasue of roll we don't want to the last value since it will be wrong
+        self.heading = np.rad2deg(np.arctan2(vec_y,vec_x))[:-1]
 
     def calc_speed(self):
         #First we get the next points on the fish
         head_x_next = np.roll(self.head_x, -1)
         head_y_next = np.roll(self.head_y, -1)
 
-        #You exclude the last value becuase of how it gets rolled over
+        #Then we create a vector of the future point minus the last one
+        vec_x = head_x_next - self.head_x
+        vec_y = head_y_next - self.head_y
+
+        #Then we add the flow to the x value
+        #Since (0,0) is in the upper left a positive vec_x value value means it is moving downstream
+        #so I should subtract the flow value 
+        #The flow value is mutliplied by the fish length since the vec_x values are in pixels, but it is in BLS so divide by fps
+        vec_x_flow = vec_x - (self.flow*fish_len)/fps
+
         #It is divided in order to get it in body lengths and then times fps to get BL/s
-        self.speed = get_dist_np(self.head_x,self.head_y,head_x_next,head_y_next)[:-1]/fish_len * fps
[…]

### 2021-12-13 Fish Data Analysis/Old Code.Rmd
Back before adding roup level features

--- 2021-11-30 Fish Data Analysis/comp_fish_simple_models.Rmd
@@
 ---
-title: "Fish Comparisons Simple Models"
+title: "R Notebook"
 output: html_notebook
@@
 
-```{r setup, include=FALSE}
-library(tidyverse)
-library(ggplot2)
-library(car)
-library(viridis)
-library(boot)
-```
-
-So here we're going to do some simpler model selection things with the data using GLMs instead of GAMs
-
-Sets up the functions that will be used later 
-```{r}
-rad2deg <- function(rad) {(rad * 180) / (pi)}
-deg2rad <- function(deg) {(deg * pi) / (180)}
-round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
-ang_mean <- function(x){rad2deg(atan(mean(sin(deg2rad(x)))/mean(cos(deg2rad(x)))))}
-
-fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}
-```
-
-Reads in the data and alters it as needed 
-```{r}
-comp_data <- read.csv("Fish_Comp_Values.csv")
-comp_data <- na.omit(comp_data)
-
-comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
-                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
-                           filter(Distance <= 4) %>%
-                           filter(Speed_Diff <= 6) %>% 
-                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
-                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
-                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
-                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))
-
-sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
-                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
-                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
-                               summarise(Speed_Diff = mean(Speed_Diff),
-                                         Heading_Diff = ang_mean(Heading_Diff),
-                                         Sync = mean(Sync),
-                                         Quarter_Heading_Diff = mean(quarter_heading_diff),
-                                         Is_Aligned = mean(Is_Aligned),
-                                         Is_Reversed = mean(Is_Reversed))
-
-```
-
-#Basic Stats
-
-```{r}
-speed_anova <- glm(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
-
-Anova(speed_anova)
-
-heading_anova <- glm(quarter_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
-
-Anova(heading_anova)
-
-sync_anova <- glm(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
-
-Anova(sync_anova)
-
-dist_anova <- glm(Distance ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
-
-Anova(dist_anova)
-```
-
-```{r}
-ggplot(comp_data, aes(x = Flow, y = Speed_Diff, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,3) +
-  theme_light()
-
-ggplot(comp_data, aes(x = Flow, y = quarter_heading_diff, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,90) +
-  theme_light()
-
-ggplot(comp_data, aes(x = Flow, y = Sync, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,1) +
-  theme_light()
-
-ggplot(comp_data, aes(x = Flow, y = Distance, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,4) +
-  theme_light()
-```
-
-Now we add in distance and angle
-
-```{r}
-speed_anova_da <- glm(Speed_Diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-
-Anova(speed_anova_da)
-
-heading_anova_da <- glm(quarter_heading_diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-
-Anova(heading_anova_da)
-
-sync_anova_da <- glm(Sync ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-
-Anova(sync_anova_da)
-```
-
 ```{r}
 ggplot(comp_data, aes(x = Distance, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
+  geom_smooth(method = "gam", formula = y ~ s(x))+
   facet_wrap(~ Flow) +
@@
 ggplot(comp_data, aes(x = Distance, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
+  geom_smooth(method = "gam", formula = y ~ s(x))+
   facet_wrap(~ Flow) +
@@
 ggplot(comp_data, aes(x = Distance, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
+  geom_smooth(method = "gam", formula = y ~ s(x))+
   facet_wrap(~ Flow) +
@@
 ggplot(comp_data, aes(x = Angle, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
+  geom_smooth(method = "gam", formula = y ~ s(x))+
   facet_wrap(~ Flow) +
@@
 ggplot(comp_data, aes(x = Angle, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
+  geom_smooth(method = "gam", formula = y ~ s(x))+
   facet_wrap(~ Flow) +
@@
 ggplot(comp_data, aes(x = Angle, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
+  geom_smooth(method = "gam", formula = y ~ s(x))+
   facet_wrap(~ Flow) +

### 2021-12-13 Fish Data Analysis/comp_fish_simple_models.Rmd
Back before adding roup level features

@@
 library(boot)
+library(mgcv)
+library(forcats)
+library(ggpubr)
 ```
 
-So here we're going to do some simpler model selection things with the data using GLMs instead of GAMs
+Alright, so from all of this what do I know?
+
+Speed Differences:
+  Flow increases speed differences
+  Ablation decreases speed differences
+  Darkness increases speed differences
+  Distance increases speed differences
+  Angles around 90 degrees have a bigger difference in speed
+
+Heading Differences:
+  Fish are more aligned when they are around 90 degrees, slightly less in ablated fish
+
+Synchronization:
+  Darkness increases synchronization
+
+NND:
+  Darkness increases NND
+  Flow decreases NND
+
+Nearest Neighbor Bearing:
+  In darkness fish are more in front or behind
+  In flow fish are more in positioned alongside each other
 
@@
 fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}
+
+fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}
+
+min_n <- function(x,n){sort(x)[1:n]}
+max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}
 ```
@@
                            mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                            filter(Distance <= 4) %>%
-                           filter(Speed_Diff <= 6) %>% 
-                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
+                           filter(abs(Speed_Diff) <= 6) %>% 
+                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
+                           mutate(fold_heading_diff = abs(fold_angle_neg_180_180_to_neg_90_90(Heading_Diff))) %>%
                            mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                            mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
-                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Flow 0","Flow 2"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(rad_Angle = Angle) %>%
+                           mutate(sin_Angle = sin(rad_Angle), cos_Angle = cos(rad_Angle)) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))
+
+                           #mutate(Angle = fold_angle_0_360_to_0_180(Angle))
 
@@
                                          Sync = mean(Sync),
-                                         Quarter_Heading_Diff = mean(quarter_heading_diff),
+                                         Fold_Heading_Diff = mean(fold_heading_diff),
                                          Is_Aligned = mean(Is_Aligned),
@@
 
+comp_data_switch_fish <- comp_data %>% mutate(Fish3 = Fish1) %>%
+                                       mutate(Fish1 = Fish2) %>%
+                                       mutate(Fish2 = Fish3) %>%
+                                       select(-c(Fish3))
+
+comp_data_NND <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
+                                                                 filter(Distance == min(Distance)) %>%
+                                                                 ungroup()
+
+comp_data_near_3 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
+                                                                 slice_min(Distance, n = 3) %>%
+                                                                 ungroup() %>%
+                                                                 distinct(Distance, .keep_all= TRUE)
 ```
@@
 ```{r}
-speed_anova <- glm(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
+speed_anova <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
 
@@
 
-heading_anova <- glm(quarter_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
+heading_anova <- aov(fold_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
 
@@
 
-sync_anova <- glm(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
+sync_anova <- aov(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
 
@@
 
-dist_anova <- glm(Distance ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)
+dist_anova <- aov(Distance ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
+
+Anova(dist_anova)
+
+angle_anova <- aov(Angle ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
 
@@
 ```{r}
-ggplot(comp_data, aes(x = Flow, y = Speed_Diff, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,3) +
-  theme_light()
+ggplot(comp_data_near_3, aes(x = cos(deg2rad(Angle))))+
+  geom_histogram()+
+  facet_wrap(~ Flow + Ablation + Darkness)
 
-ggplot(comp_data, aes(x = Flow, y = quarter_heading_diff, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,90) +
-  theme_light()
-
-ggplot(comp_data, aes(x = Flow, y = Sync, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,1) +
-  theme_light()
-
-ggplot(comp_data, aes(x = Flow, y = Distance, fill = paste(Ablation,Darkness,sep="-")))+
-  geom_boxplot(outlier.shape = NA) +
-  ylim(0,4) +
-  theme_light()
-```
-
-Now we add in distance and angle
-
-```{r}
-speed_anova_da <- glm(Speed_Diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-
-Anova(speed_anova_da)
-
-heading_anova_da <- glm(quarter_heading_diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-
-Anova(heading_anova_da)
-
-sync_anova_da <- glm(Sync ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-
-Anova(sync_anova_da)
+ggplot(comp_data_near_3, aes(x = sin(deg2rad(Angle))))+
+  geom_histogram()+
+  facet_wrap(~ Flow + Ablation + Darkness)
 ```
@@
 ```{r}
-ggplot(comp_data, aes(x = Distance, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
-  facet_wrap(~ Flow) +
+ggplot(comp_data_near_3, aes(x = Flow, y = Speed_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Speed Difference") +
+  xlab("") +
+  ylab("Speed Difference (BL/s)") +
+  ylim(-0.1,2.5) +
   theme_light()
 
-ggplot(comp_data, aes(x = Distance, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
-  facet_wrap(~ Flow) +
+ggplot(comp_data_near_3, aes(x = Flow, y = fold_heading_diff, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Heading Difference") +
+  xlab("") +
+  ylab("Heading Difference (Degrees)") +
   theme_light()
 
-ggplot(comp_data, aes(x = Distance, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
-  facet_wrap(~ Flow) +
-  theme_light()
-```
-```{r}
-ggplot(comp_data, aes(x = Angle, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
-  facet_wrap(~ Flow) +
+ggplot(comp_data_near_3, aes(x = Flow, y = Sync, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Tailbeat Synchonization") +
+  xlab("") +
+  ylab("Syncronization") +
   theme_light()
 
-ggplot(comp_data, aes(x = Angle, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
-  facet_wrap(~ Flow) +
+ggplot(comp_data_near_3, aes(x = Flow, y = Distance, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
+  xlab("") +
+  ylab("NND (BL)") +
   theme_light()
 
-ggplot(comp_data, aes(x = Angle, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
-  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
-  facet_wrap(~ Flow) +
+ggplot(comp_data_near_3, aes(x = Flow, y = Angle, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Nearest Neighbor Bearing") +
+  xlab("") +
+  ylab("Nearest Neighbor Bearing (Degrees)") +
+  scale_y_continuous(breaks = c(30,60,90,120,150)) +
   theme_light()
+
 ```
 
-This creates a dataframe that is used for making model predictions and graphing them
+Trying GAMs
+
 ```{r}
-d <- seq(from = 0, to = 4, by = 0.1)
+speed_gam <- gam(Speed_Diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
+                              data = comp_data_near_3)
+
+summary(speed_gam)
+
+heading_gam <- gam(fold_heading_diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
+                              data = comp_data_near_3)
+
+summary(heading_gam)
+
+sync_gam <- gam(Sync ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
+                              data = comp_data_near_3)
+
+summary(sync_gam)
+```
+
+Now we make some predictions for this.
+```{r}
+d <- seq(from = 0, to = 3, by = 0.1)
 a <- seq(from = 0, to = 180, by = 10)
@@
 
-predict_df_da <- expand.grid(Distance = d, Angle = a, Flow = flows, Ablation = ablation, Darkness = dark)
-predict_df_da <- predict_df_da %>% mutate(X_Distance = Distance*(cos(deg2rad(Angle))), Y_Distance = Distance*(sin(deg2rad(Angle))))
+predict_df <- expand.grid(Distance = d, Angle = a, Flow = flows, Ablation = ablation, Darkness = dark)
 
-predict_df_da <- predict_df_da %>% filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
-predict_df_da <- na.omit(predict_df_da)
+predict_df <- predict_df %>% mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>% 
+                            filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
+
+predict_df <- predict_df %>% mutate(pred_speed_diff = predict.gam(speed_gam,predict_df),
+                                    pred_heading_diff = predict.gam(heading_gam,predict_df),
+                                    pred_sync = predict.gam(sync_gam,predict_df))
+
+predict_df <- predict_df %>% group_by(Distance,Flow,Ablation,Darkness) %>%
+                             mutate(mean_Speed_Distance = mean(pred_speed_diff), sd_Speed_Distance = sd(pred_speed_diff),
+                                    mean_Heading_Distance = mean(pred_heading_diff), sd_Heading_Distance = sd(pred_heading_diff),
+                                    mean_Sync_Distance = mean(pred_sync), sd_Sync_Distance = sd(pred_sync)) %>%
+                             ungroup() %>%
+                             group_by(Angle,Flow,Ablation,Darkness) %>%
+                             mutate(mean_Speed_Angle = mean(pred_speed_diff), sd_Speed_Angle = sd(pred_speed_diff),
+                                    mean_Heading_Angle = mean(pred_heading_diff), sd_Heading_Angle = sd(pred_heading_diff),
+                                    mean_Sync_Angle = mean(pred_sync), sd_Sync_Angle = sd(pred_sync)) %>%
+                             ungroup()
 ```
 
-### Speed Models
-
-So I want to make a model that tries to include both distance and angle.
-What I really need is to figure out what power works best for angle and distance, and then include that.
-The issue is stepwise selection can just remove one of them entirely.
-So I'm going to use cross validation to select the power for both of them, and then use that.
-I will also calculate the AICs to help in this decision making process
-
-```{r, warnings=F}
-set.seed(7)
-
-comp_data_speed_model <- comp_data %>% select(c(Flow,Darkness,Ablation,Angle,Distance,Speed_Diff))
-
-max_poly <- 10
-
-speed_dist_cv_error_10 <- rep(0,max_poly)
-speed_dist_AIC_10 <- rep(0,max_poly)
-
-for (i in 1:max_poly){
-  speed_dist_fit <- glm(Speed_Diff ~ poly(Distance,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                        data = comp_data_speed_model)
-  speed_dist_cv_error_10[i] <- cv.glm(comp_data_speed_model, speed_dist_fit, K = 10)$delta[1]
-  speed_dist_AIC_10[i] <- AIC(speed_dist_fit)
-}
-
-speed_angle_cv_error_10 <- rep(0,max_poly)
-speed_angle_AIC_10 <- rep(0,max_poly)
-
-for (i in 1:max_poly){
-  speed_angle_fit <- glm(Speed_Diff ~ poly(Angle,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                         data = comp_data_speed_model)
-  speed_angle_cv_error_10[i] <- cv.glm(comp_data_speed_model, speed_angle_fit, K = 10)$delta[1]
-  speed_angle_AIC_10[i] <- AIC(speed_angle_fit)
-}
-
-speed_poly_plot_df <- data.frame(c(seq(max_poly),seq(max_poly)),
-                                 c(speed_dist_cv_error_10,speed_angle_cv_error_10),
-                                 c(speed_dist_AIC_10,speed_angle_AIC_10),
-                                 c(rep("Distance",max_poly),rep("Angle",max_poly)))
-
-colnames(speed_poly_plot_df) <- c("Degree","Error","AIC","Predictor")
-
-speed_poly_plot_df <- speed_poly_plot_df %>% group_by(Predictor) %>%
-                                             mutate(minError = min(Error),minAIC = min(AIC)) %>%
-                                             ungroup() %>%
-                                             mutate(isMinEror = ifelse(Error == minError,3,1),isMinAIC = ifelse(AIC == minAIC,3,1))
-
-ggplot(speed_poly_plot_df, aes(x = Degree, y = Error, color = Predictor))+
-  geom_point(size = speed_poly_plot_df$isMinEror)+
-  geom_line()+
-  theme_light()+
-  facet_wrap(~ Predictor, scales = "free") +
-  scale_size(guide = "none")
-
-ggplot(speed_poly_plot_df, aes(x = Degree, y = AIC, color = Predictor))+
-  geom_point(size = speed_poly_plot_df$isMinAIC)+
-  geom_line()+
-  theme_light()+
-  facet_wrap(~ Predictor, scales = "free") +
-  scale_size(guide = "none")
-```
-Now let's use those polynomials to create the actual model
-
-While they not be the lowest, the big improvements happen at 4 for Distance, and 2 for Angle
+And now we graph those?
 
 ```{r}
-speed_diff_glm <- glm(Speed_Diff ~ poly(Distance,4)*poly(Angle,2)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                        data = comp_data_speed_model)
+ggplot(predict_df, aes(x = Distance, y = mean_Speed_Distance, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=" "))) +
+  geom_line() +
+  #geom_point(data=predict_df, aes(x = Distance, y = pred_speed_diff, alpha = 0.15)) +
+  geom_ribbon(aes(ymin = mean_Speed_Distance-sd_Speed_Distance, ymax = mean_Speed_Distance+sd_Speed_Distance),
+              linetype = 0,
+              alpha = 0.1) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Distance and Senses on Speed Difference") +
+  xlab("Distance (BL)") +
+  ylab("Speed Difference (BL/s)") +
+  ylim(0,1.5) +
+  theme_light()
 
-summary(speed_diff_glm)
+ggplot(predict_df, aes(x = Distance, y = mean_Heading_Distance, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  #geom_point(data=predict_df, aes(x = Distance, y = pred_heading_diff, alpha = 0.15)) +
+  geom_ribbon(aes(ymin = mean_Heading_Distance-sd_Heading_Distance, ymax = mean_Heading_Distance+sd_Heading_Distance),
+              linetype = 0,
+              alpha = 0.1) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Distance and Senses on Heading Difference") +
+  xlab("Distance (BL)") +
+  ylab("Heading Difference (Degrees)") +
+  ylim(0,50) +
+  theme_light()
+
+ggplot(predict_df, aes(x = Distance, y = mean_Sync_Distance, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  #geom_point(data=predict_df, aes(x = Distance, y = pred_sync, alpha = 0.15)) +
+  geom_ribbon(aes(ymin = mean_Sync_Distance-sd_Sync_Distance, ymax = mean_Sync_Distance+sd_Sync_Distance),
+              linetype = 0,
+              alpha = 0.1) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Distance and Senses on Synchonization") +
+  xlab("Distance (BL)") +
+  ylab("Synchonization") +
+  ylim(0,1)+
+  theme_light()
+```
+```{r}
+ggplot(predict_df, aes(x = Angle, y = mean_Speed_Angle, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  #geom_point(data=predict_df, aes(x = Angle, y = pred_speed_diff, alpha = 0.15)) +
+  geom_ribbon(aes(ymin = mean_Speed_Angle-sd_Speed_Angle, ymax = mean_Speed_Angle+sd_Speed_Angle),
+              linetype = 0,
+              alpha = 0.1) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Bearing and Senses on Speed Difference") +
+  xlab("Bearing (Degrees)") +
+  ylab("Speed Difference (BL/s)") +
+  ylim(0,1.5) +
+  theme_light()
+
+ggplot(predict_df, aes(x = Angle, y = mean_Heading_Angle, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  #geom_point(data=predict_df, aes(x = Angle, y = pred_heading_diff, alpha = 0.15)) +
+  geom_ribbon(aes(ymin = mean_Heading_Angle-sd_Heading_Angle, ymax = mean_Heading_Angle+sd_Heading_Angle),
+              linetype = 0,
+              alpha = 0.1) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Bearing and Senses on Heading Difference") +
+  xlab("Angle (Degrees)") +
+  ylab("Heading Difference (Degrees)") +
+  ylim(0,50) +
+  theme_light()
+
+ggplot(predict_df, aes(x = Angle, y = mean_Sync_Angle, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+ #geom_point(data=predict_df, aes(x = Angle, y = pred_sync, alpha = 0.15)) +
+  geom_ribbon(aes(ymin = mean_Sync_Angle-sd_Sync_Angle, ymax = mean_Sync_Angle+sd_Sync_Angle),
+              linetype = 0,
+              alpha = 0.1) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Bearing and Senses on Synchonization") +
+  xlab("Bearing (Degrees)") +
+  ylab("Synchonization") +
+  ylim(0,1)+
+  theme_light()
+```
+Density vs Things
+
+```{r}
+dist_bin_size <- 1
+angle_bin_size <- 30
+
+comp_data_freqs <- comp_data_near_3 %>% mutate(Dist_bin = round_any(Distance, dist_bin_size), 
+                                               Angle_bin = round_any(Angle, angle_bin_size)) %>%
+                                        group_by(Flow,Darkness,Ablation, Dist_bin, Angle_bin,Flow_Ablation_Darkness) %>%
+                                        mutate(Count = n()) %>%
+                                        ungroup() %>%
+                                        group_by(Flow,Darkness,Ablation,Flow_Ablation_Darkness) %>%
+                                        mutate(Freq = Count/n()) %>%
+                                        ungroup() %>%
+                                        group_by(Flow,Darkness,Ablation,Dist_bin,Angle_bin,Flow_Ablation_Darkness) %>%
+                                        summarise(Speed_Diff = mean(Speed_Diff),
+                                                  Fold_Heading_Diff = ang_mean(fold_heading_diff),
+                                                  Sync = mean(Sync),
+                                                  Freq = mean(Freq))
+
 ```
 
-Now let's make some predictions
+```{r}
+freq_speed_glm <- glm(Speed_Diff ~ Freq*(Flow+Darkness+Ablation+Flow:Ablation+Flow:Darkness), data = comp_data_freqs)
+
+summary(freq_speed_glm)
+
+freq_heading_glm <- glm(Fold_Heading_Diff ~ Freq*(Flow+Darkness+Ablation+Flow:Ablation+Flow:Darkness), data = comp_data_freqs)
+
+summary(freq_heading_glm)
+
+freq_sync_glm <- glm(Sync ~ Freq*(Flow+Darkness+Ablation+Flow:Ablation+Flow:Darkness), data = comp_data_freqs)
+
+summary(freq_sync_glm)
+
+freq_speed_gam <- gam(Speed_Diff ~ s(Freq,by=Flow_Ablation_Darkness),
+                              data = comp_data_freqs)
+
+summary(freq_speed_gam)
+
+freq_heading_gam <- gam(Fold_Heading_Diff ~ s(Freq,by=Flow_Ablation_Darkness),
+                              data = comp_data_freqs)
+
+summary(freq_heading_gam)
+
+freq_sync_gam <- gam(Sync ~ s(Freq,by=Flow_Ablation_Darkness),
+                              data = comp_data_freqs)
+
+summary(freq_sync_gam)
+```
+
+Now we make some predictions for this.
+```{r}
+f <- seq(from = 0.005, to = 0.07, by = 0.001)
+
+flows <- c("Flow 0", "Flow 2")
+ablation <- c("No Ablation", "Ablated")
+dark <- c("Light","Dark")
+
+freq_predict_df <- expand.grid(Freq = f, Flow = flows, Ablation = ablation, Darkness = dark)
+
+freq_predict_df <- freq_predict_df %>% mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>% 
+                            filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
+
+freq_predict_df <- freq_predict_df %>% mutate(pred_speed_diff = predict.gam(freq_speed_gam,freq_predict_df),
+                                    pred_heading_diff = predict.gam(freq_heading_gam,freq_predict_df),
+                                    pred_sync = predict.gam(freq_sync_gam,freq_predict_df))
+
+```
 
 ```{r}
-speed_pred <- predict_df_da %>% mutate(Speed_Diff = predict(speed_diff_glm,predict_df_da))
-
-comp_data <- comp_data %>% mutate(Round_Dist = as.factor(round_any(Distance,1)), Round_Angle = as.factor(round_any(Angle,30)))
-
-ggplot()+
-  geom_boxplot(data = comp_data, aes(x = Round_Dist, y = Speed_Diff))+
-  facet_wrap(~ Flow + Ablation + Darkness) +
+ggplot(comp_data_freqs, aes(x = Freq, y = Speed_Diff, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Preference and Senses on Speed Difference") +
+  xlab("Frequency of Observations") +
+  ylab("Speed Difference (BL/s)") +
   theme_light()
 
-round_dist_aov <- aov(Speed_Diff ~ Round_Dist*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-Anova(round_dist_aov)
-
-ggplot()+
-  geom_boxplot(data = comp_data, aes(x = Round_Angle, y = Speed_Diff))+
-  facet_wrap(~ Flow + Ablation + Darkness) +
+ggplot(comp_data_freqs, aes(x = Freq, y = Fold_Heading_Diff, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Preference and Senses on Heading Difference") +
+  xlab("Frequency of Observations") +
+  ylab("Heading Difference (Degrees)") +
   theme_light()
 
-round_angle_aov <- aov(Speed_Diff ~ Round_Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)
-Anova(round_angle_aov)
-
-# ggplot()+
-#   geom_point(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Distance, y = Speed_Diff), alpha = 0.1)+
-#   geom_smooth(data = speed_pred, aes(x = Distance, y = Speed_Diff))+
-#   facet_wrap(~ Flow + Ablation + Darkness) +
-#   theme_light()
-
-# ggplot()+
-#   geom_density_2d_filled(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Distance, y = Speed_Diff), contour_var = "ndensity")+
-#   geom_smooth(data = speed_pred, aes(x = Distance, y = Speed_Diff, color = "red"))+
-#   facet_wrap(~ Flow + Ablation + Darkness) +
-#   theme_light()
-
-# ggplot()+
-#   geom_point(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Angle, y = Speed_Diff), alpha = 0.1)+
-#   geom_smooth(data = speed_pred, aes(x = Angle, y = Speed_Diff))+
-#   facet_wrap(~ Flow + Ablation + Darkness) +
-#   theme_light()
-
-# ggplot()+
-#   geom_density_2d_filled(data = comp_data %>% filter(Speed_Diff <= 2), aes(x = Angle, y = Speed_Diff), contour_var = "ndensity")+
-#   geom_smooth(data = speed_pred, aes(x = Angle, y = Speed_Diff, color = "red"))+
-#   facet_wrap(~ Flow + Ablation + Darkness) +
-#   theme_light()
-
-ggplot(data = comp_data, aes(x = Angle, y = Distance, z = Speed_Diff))+
-  stat_summary_2d() +
-  facet_wrap(~ Flow + Ablation + Darkness) +
-  scale_fill_viridis(direction = -1) +
+ggplot(comp_data_freqs, aes(x = Freq, y = Sync, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Preference and Senses on Synchonization") +
+  xlab("Frequency of Observations") +
+  ylab("Synchonization") +
   theme_light()
 ```
-You know let's just try stepwise as well. There's jsut way too many thing in that possible model
 
 ```{r}
-
-speed_m_all <- glm(Speed_Diff ~ Distance*Angle*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow) +
-                                I(Distance^2)*I(Angle^2)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow)+
-                                I(Distance^3)*I(Angle^3)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow)+
-                                I(Distance^4)*I(Angle^4)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                        data = comp_data_speed_model)
-
-speed_m_none <- glm(Speed_Diff ~ 1, data = comp_data_speed_model)
-
-speed_m_both <- step(speed_m_none, direction = "both", scope = formula(speed_m_all), trace = F)
-
-summary(speed_m_both)
-```
-
-### Sync Models
-
-Now let's try the same thing for sync values (Rayleigh's R)
-
-```{r, warnings=F}
-set.seed(7)
-
-comp_data_sync_model <- comp_data %>% select(c(Flow,Darkness,Ablation,Angle,Distance,Sync))
-
-max_poly <- 10
-
-sync_dist_cv_error_10 <- rep(0,max_poly)
-sybc_dist_AIC_10 <- rep(0,max_poly)
-
-for (i in 1:max_poly){
-  sync_dist_fit <- glm(Sync ~ poly(Distance,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                        data = comp_data_sync_model)
-  sync_dist_cv_error_10[i] <- cv.glm(comp_data_sync_model, sync_dist_fit, K = 10)$delta[1]
-  sybc_dist_AIC_10[i] <- AIC(sync_dist_fit)
-}
-
-sync_angle_cv_error_10 <- rep(0,max_poly)
-sync_angle_AIC_10 <- rep(0,max_poly)
-
-for (i in 1:max_poly){
-  sync_angle_fit <- glm(Sync ~ poly(Angle,i)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                         data = comp_data_sync_model)
-  sync_angle_cv_error_10[i] <- cv.glm(comp_data_sync_model, sync_angle_fit, K = 10)$delta[1]
-  sync_angle_AIC_10[i] <- AIC(sync_angle_fit)
-}
-
-sync_poly_plot_df <- data.frame(c(seq(max_poly),seq(max_poly)),
-                                 c(speed_dist_cv_error_10,speed_angle_cv_error_10),
-                                 c(speed_dist_AIC_10,speed_angle_AIC_10),
-                                 c(rep("Distance",max_poly),rep("Angle",max_poly)))
-
-colnames(sync_poly_plot_df) <- c("Degree","Error","AIC","Predictor")
-
-sync_poly_plot_df <- sync_poly_plot_df %>% group_by(Predictor) %>%
-                                             mutate(minError = min(Error),minAIC = min(AIC)) %>%
-                                             ungroup() %>%
-                                             mutate(isMinEror = ifelse(Error == minError,3,1),isMinAIC = ifelse(AIC == minAIC,3,1))
-
-ggplot(sync_poly_plot_df, aes(x = Degree, y = Error, color = Predictor))+
-  geom_point(size = sync_poly_plot_df$isMinEror)+
-  geom_line()+
-  theme_light()+
-  facet_wrap(~ Predictor, scales = "free") +
-  scale_size(guide = "none")
-
-ggplot(sync_poly_plot_df, aes(x = Degree, y = AIC, color = Predictor))+
-  geom_point(size = sync_poly_plot_df$isMinAIC)+
-  geom_line()+
-  theme_light()+
-  facet_wrap(~ Predictor, scales = "free") +
-  scale_size(guide = "none")
-```
-Now let's use those polynomials to create the actual model
-
-While they not be the lowest, the big improvements happen at 2 for Distance, and 2 for Angle
-
-```{r}
-sync_diff_glm <- glm(Sync ~ I(Distance^2)*I(Angle^2)*(Ablation+Flow+Darkness+Ablation:Flow+Darkness:Flow),
-                        data = comp_data_sync_model)
-
-summary(sync_diff_glm)
-```
-
-Now let's make some predictions
-
-```{r}
-sync_pred <- predict_df_da %>% mutate(Sync = predict(sync_diff_glm,predict_df_da))
-
-ggplot(comp_data, aes(x = Distance, y = Sync))+
-  geom_point(alpha = 0.1)+
-  geom_smooth(method = lm, formula = y ~ poly(x, 2)) +
-  facet_wrap(~ Flow + Ablation + Darkness) +
+ggplot(freq_predict_df, aes(x = Freq, y = pred_speed_diff, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Frequency of Observations on Speed Difference") +
+  xlab("Frequency (%)") +
+  ylab("Speed Difference (BL/s)") +
   theme_light()
 
-ggplot(comp_data, aes(x = Angle, y = Sync))+
-  geom_point(alpha = 0.1)+
-  geom_smooth(method = glm, formula = y ~ poly(x, 2))+
-  facet_wrap(~ Flow + Ablation + Darkness) +
+ggplot(freq_predict_df, aes(x = Freq, y = pred_heading_diff, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Frequency of Observations on Heading Difference") +
+  xlab("Frequency (%)") +
+  ylab("Heading Difference (Degrees)") +
   theme_light()
 
-ggplot(sync_pred, aes(x = Distance, y = Sync))+
-  geom_smooth()+
-  scale_fill_viridis() +
-  facet_wrap(~ Flow + Ablation + Darkness) +
-  theme_light()
-
-ggplot(sync_pred, aes(x = Angle, y = Sync))+
-  geom_smooth()+
-  scale_fill_viridis() +
-  facet_wrap(~ Flow + Ablation + Darkness) +
+ggplot(freq_predict_df, aes(x = Freq, y = pred_sync, color = interaction(Ablation,Darkness,sep=", "),
+                       fill = interaction(Ablation,Darkness,sep=", "))) +
+  geom_line() +
+  facet_wrap(~ Flow) +
+  guides(fill = "none", color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Frequency of Observations on Synchonization") +
+  xlab("Frequency (%)") +
+  ylab("Synchonization") +
   theme_light()

### 2021-12-13 data_files_to_csv_4P.py

@@ -230,7 +230,9 @@ class fish_data:
 
         ax0 = plt.subplot(gs[:,0])
         ax0.plot(self.head_x, self.head_y)
+        ax0.scatter(self.head_x[0], self.head_y[0])
         ax0.plot(self.tailtip_x, self.tailtip_y)
+        ax0.scatter(self.tailtip_x[0], self.tailtip_y[0])
         ax0.set_title("Fish Path (Blue = Head, Orange = Tailtip)")
 
         ax1 = plt.subplot(gs[0,1])
@@ -285,19 +287,21 @@ class fish_comp:
 
     def calc_angle(self):
         #Calculate the angle of the x and y difference in degrees
-        anglee_diff = np.rad2deg(np.arctan2(self.y_diff,self.x_diff))
+        angle_diff = np.rad2deg(np.arctan2(self.y_diff,self.x_diff))
         #This makes it from 0 to 360
-        angles_diff_360 = np.mod(abs(anglee_diff-360),360)
+        #angle_diff_360 = np.mod(abs(angle_diff-360),360)
         #This rotates it so that 0 is at the top and 180 is below the fish for a sideways swimming fish model
-        self.angle = np.mod(angles_diff_360+90,360)
+        #self.angle = np.mod(angle_diff_360+90,360)
+
+        #12/1/21: Back to making change notes. Now keeping it as the raw -180 to 180
+        self.angle = angle_diff
 
     def calc_heading_diff(self):
-        self.heading_diff = np.rad2deg(np.arctan2(np.sin(self.f1.heading-self.f2.heading),
-                                                  np.cos(self.f1.heading-self.f2.heading)))
+        self.heading_diff = np.rad2deg(np.arctan2(np.sin(np.deg2rad(self.f1.heading-self.f2.heading)),
+                                                  np.cos(np.deg2rad(self.f1.heading-self.f2.heading))))
 
     def calc_speed_diff(self):
-        #I want to absolute value so that -1 and 1 average to 1, not 0
-        self.speed_diff = abs(self.f1.speed - self.f2.speed)
+        self.speed_diff = self.f1.speed - self.f2.speed
 
     def calc_tailbeat_offset(self):
         #Setup an array to hold all the zero crossing differences
@@ -440,6 +444,8 @@ class fish_comp:
         ax0 = plt.subplot(gs[:,0])
         ax0.plot(self.f1.head_x, self.f1.head_y)
[…]

### 2021-12-14 Fish Data Analysis/whole_school_data.Rmd
Added in full school processing code in python

--- 2021-12-13 Fish Data Analysis/comp_fish_simple_models.Rmd
@@
 ---
-title: "Fish Comparisons Simple Models"
+title: "Fish Whole School Data"
 output: html_notebook
@@
 ```
-
-Alright, so from all of this what do I know?
-
-Speed Differences:
-  Flow increases speed differences
-  Ablation decreases speed differences
-  Darkness increases speed differences
-  Distance increases speed differences
-  Angles around 90 degrees have a bigger difference in speed
-
-Heading Differences:
-  Fish are more aligned when they are around 90 degrees, slightly less in ablated fish
-
-Synchronization:
-  Darkness increases synchronization
-
-NND:
-  Darkness increases NND
-  Flow decreases NND
-
-Nearest Neighbor Bearing:
-  In darkness fish are more in front or behind
-  In flow fish are more in positioned alongside each other
 
@@
 ```
-
-#Basic Stats
-
-```{r}
-speed_anova <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
-
-Anova(speed_anova)
-
-heading_anova <- aov(fold_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
-
-Anova(heading_anova)
-
-sync_anova <- aov(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
-
-Anova(sync_anova)
-
-dist_anova <- aov(Distance ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
-
-Anova(dist_anova)
-
-angle_anova <- aov(Angle ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
-
-Anova(dist_anova)
-```
-
-```{r}
-ggplot(comp_data_near_3, aes(x = cos(deg2rad(Angle))))+
-  geom_histogram()+
-  facet_wrap(~ Flow + Ablation + Darkness)
-
-ggplot(comp_data_near_3, aes(x = sin(deg2rad(Angle))))+
-  geom_histogram()+
-  facet_wrap(~ Flow + Ablation + Darkness)
-```
-
-```{r}
-ggplot(comp_data_near_3, aes(x = Flow, y = Speed_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Available Senses on Speed Difference") +
-  xlab("") +
-  ylab("Speed Difference (BL/s)") +
-  ylim(-0.1,2.5) +
-  theme_light()
-
-ggplot(comp_data_near_3, aes(x = Flow, y = fold_heading_diff, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Available Senses on Heading Difference") +
-  xlab("") +
-  ylab("Heading Difference (Degrees)") +
-  theme_light()
-
-ggplot(comp_data_near_3, aes(x = Flow, y = Sync, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Available Senses on Tailbeat Synchonization") +
-  xlab("") +
-  ylab("Syncronization") +
-  theme_light()
-
-ggplot(comp_data_near_3, aes(x = Flow, y = Distance, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
-  xlab("") +
-  ylab("NND (BL)") +
-  theme_light()
-
-ggplot(comp_data_near_3, aes(x = Flow, y = Angle, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Available Senses on Nearest Neighbor Bearing") +
-  xlab("") +
-  ylab("Nearest Neighbor Bearing (Degrees)") +
-  scale_y_continuous(breaks = c(30,60,90,120,150)) +
-  theme_light()
-
-```
-
-Trying GAMs
-
-```{r}
-speed_gam <- gam(Speed_Diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
-                              data = comp_data_near_3)
-
-summary(speed_gam)
-
-heading_gam <- gam(fold_heading_diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
-                              data = comp_data_near_3)
-
-summary(heading_gam)
-
-sync_gam <- gam(Sync ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
-                              data = comp_data_near_3)
-
-summary(sync_gam)
-```
-
-Now we make some predictions for this.
-```{r}
-d <- seq(from = 0, to = 3, by = 0.1)
-a <- seq(from = 0, to = 180, by = 10)
-
-flows <- c("Flow 0", "Flow 2")
-ablation <- c("No Ablation", "Ablated")
-dark <- c("Light","Dark")
-
-predict_df <- expand.grid(Distance = d, Angle = a, Flow = flows, Ablation = ablation, Darkness = dark)
-
-predict_df <- predict_df %>% mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>% 
-                            filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
-
-predict_df <- predict_df %>% mutate(pred_speed_diff = predict.gam(speed_gam,predict_df),
-                                    pred_heading_diff = predict.gam(heading_gam,predict_df),
-                                    pred_sync = predict.gam(sync_gam,predict_df))
-
-predict_df <- predict_df %>% group_by(Distance,Flow,Ablation,Darkness) %>%
-                             mutate(mean_Speed_Distance = mean(pred_speed_diff), sd_Speed_Distance = sd(pred_speed_diff),
-                                    mean_Heading_Distance = mean(pred_heading_diff), sd_Heading_Distance = sd(pred_heading_diff),
-                                    mean_Sync_Distance = mean(pred_sync), sd_Sync_Distance = sd(pred_sync)) %>%
-                             ungroup() %>%
-                             group_by(Angle,Flow,Ablation,Darkness) %>%
-                             mutate(mean_Speed_Angle = mean(pred_speed_diff), sd_Speed_Angle = sd(pred_speed_diff),
-                                    mean_Heading_Angle = mean(pred_heading_diff), sd_Heading_Angle = sd(pred_heading_diff),
-                                    mean_Sync_Angle = mean(pred_sync), sd_Sync_Angle = sd(pred_sync)) %>%
-                             ungroup()
-```
-
-And now we graph those?
-
-```{r}
-ggplot(predict_df, aes(x = Distance, y = mean_Speed_Distance, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=" "))) +
-  geom_line() +
-  #geom_point(data=predict_df, aes(x = Distance, y = pred_speed_diff, alpha = 0.15)) +
-  geom_ribbon(aes(ymin = mean_Speed_Distance-sd_Speed_Distance, ymax = mean_Speed_Distance+sd_Speed_Distance),
-              linetype = 0,
-              alpha = 0.1) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Distance and Senses on Speed Difference") +
-  xlab("Distance (BL)") +
-  ylab("Speed Difference (BL/s)") +
-  ylim(0,1.5) +
-  theme_light()
-
-ggplot(predict_df, aes(x = Distance, y = mean_Heading_Distance, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  #geom_point(data=predict_df, aes(x = Distance, y = pred_heading_diff, alpha = 0.15)) +
-  geom_ribbon(aes(ymin = mean_Heading_Distance-sd_Heading_Distance, ymax = mean_Heading_Distance+sd_Heading_Distance),
-              linetype = 0,
-              alpha = 0.1) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Distance and Senses on Heading Difference") +
-  xlab("Distance (BL)") +
-  ylab("Heading Difference (Degrees)") +
-  ylim(0,50) +
-  theme_light()
-
-ggplot(predict_df, aes(x = Distance, y = mean_Sync_Distance, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  #geom_point(data=predict_df, aes(x = Distance, y = pred_sync, alpha = 0.15)) +
-  geom_ribbon(aes(ymin = mean_Sync_Distance-sd_Sync_Distance, ymax = mean_Sync_Distance+sd_Sync_Distance),
-              linetype = 0,
-              alpha = 0.1) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Distance and Senses on Synchonization") +
-  xlab("Distance (BL)") +
-  ylab("Synchonization") +
-  ylim(0,1)+
-  theme_light()
-```
-```{r}
-ggplot(predict_df, aes(x = Angle, y = mean_Speed_Angle, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  #geom_point(data=predict_df, aes(x = Angle, y = pred_speed_diff, alpha = 0.15)) +
-  geom_ribbon(aes(ymin = mean_Speed_Angle-sd_Speed_Angle, ymax = mean_Speed_Angle+sd_Speed_Angle),
-              linetype = 0,
-              alpha = 0.1) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Bearing and Senses on Speed Difference") +
-  xlab("Bearing (Degrees)") +
-  ylab("Speed Difference (BL/s)") +
-  ylim(0,1.5) +
-  theme_light()
-
-ggplot(predict_df, aes(x = Angle, y = mean_Heading_Angle, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  #geom_point(data=predict_df, aes(x = Angle, y = pred_heading_diff, alpha = 0.15)) +
-  geom_ribbon(aes(ymin = mean_Heading_Angle-sd_Heading_Angle, ymax = mean_Heading_Angle+sd_Heading_Angle),
-              linetype = 0,
-              alpha = 0.1) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Bearing and Senses on Heading Difference") +
-  xlab("Angle (Degrees)") +
-  ylab("Heading Difference (Degrees)") +
-  ylim(0,50) +
-  theme_light()
-
-ggplot(predict_df, aes(x = Angle, y = mean_Sync_Angle, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
- #geom_point(data=predict_df, aes(x = Angle, y = pred_sync, alpha = 0.15)) +
-  geom_ribbon(aes(ymin = mean_Sync_Angle-sd_Sync_Angle, ymax = mean_Sync_Angle+sd_Sync_Angle),
-              linetype = 0,
-              alpha = 0.1) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Bearing and Senses on Synchonization") +
-  xlab("Bearing (Degrees)") +
-  ylab("Synchonization") +
-  ylim(0,1)+
-  theme_light()
-```
-Density vs Things
-
-```{r}
-dist_bin_size <- 1
-angle_bin_size <- 30
-
-comp_data_freqs <- comp_data_near_3 %>% mutate(Dist_bin = round_any(Distance, dist_bin_size), 
-                                               Angle_bin = round_any(Angle, angle_bin_size)) %>%
-                                        group_by(Flow,Darkness,Ablation, Dist_bin, Angle_bin,Flow_Ablation_Darkness) %>%
-                                        mutate(Count = n()) %>%
-                                        ungroup() %>%
-                                        group_by(Flow,Darkness,Ablation,Flow_Ablation_Darkness) %>%
-                                        mutate(Freq = Count/n()) %>%
-                                        ungroup() %>%
-                                        group_by(Flow,Darkness,Ablation,Dist_bin,Angle_bin,Flow_Ablation_Darkness) %>%
-                                        summarise(Speed_Diff = mean(Speed_Diff),
-                                                  Fold_Heading_Diff = ang_mean(fold_heading_diff),
-                                                  Sync = mean(Sync),
-                                                  Freq = mean(Freq))
-
-```
-
-```{r}
-freq_speed_glm <- glm(Speed_Diff ~ Freq*(Flow+Darkness+Ablation+Flow:Ablation+Flow:Darkness), data = comp_data_freqs)
-
-summary(freq_speed_glm)
-
-freq_heading_glm <- glm(Fold_Heading_Diff ~ Freq*(Flow+Darkness+Ablation+Flow:Ablation+Flow:Darkness), data = comp_data_freqs)
-
-summary(freq_heading_glm)
-
-freq_sync_glm <- glm(Sync ~ Freq*(Flow+Darkness+Ablation+Flow:Ablation+Flow:Darkness), data = comp_data_freqs)
-
-summary(freq_sync_glm)
-
-freq_speed_gam <- gam(Speed_Diff ~ s(Freq,by=Flow_Ablation_Darkness),
-                              data = comp_data_freqs)
-
-summary(freq_speed_gam)
-
-freq_heading_gam <- gam(Fold_Heading_Diff ~ s(Freq,by=Flow_Ablation_Darkness),
-                              data = comp_data_freqs)
-
-summary(freq_heading_gam)
-
-freq_sync_gam <- gam(Sync ~ s(Freq,by=Flow_Ablation_Darkness),
-                              data = comp_data_freqs)
-
-summary(freq_sync_gam)
-```
-
-Now we make some predictions for this.
-```{r}
-f <- seq(from = 0.005, to = 0.07, by = 0.001)
-
-flows <- c("Flow 0", "Flow 2")
-ablation <- c("No Ablation", "Ablated")
-dark <- c("Light","Dark")
-
-freq_predict_df <- expand.grid(Freq = f, Flow = flows, Ablation = ablation, Darkness = dark)
-
-freq_predict_df <- freq_predict_df %>% mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>% 
-                            filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
-
-freq_predict_df <- freq_predict_df %>% mutate(pred_speed_diff = predict.gam(freq_speed_gam,freq_predict_df),
-                                    pred_heading_diff = predict.gam(freq_heading_gam,freq_predict_df),
-                                    pred_sync = predict.gam(freq_sync_gam,freq_predict_df))
-
-```
-
-```{r}
-ggplot(comp_data_freqs, aes(x = Freq, y = Speed_Diff, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Preference and Senses on Speed Difference") +
-  xlab("Frequency of Observations") +
-  ylab("Speed Difference (BL/s)") +
-  theme_light()
-
-ggplot(comp_data_freqs, aes(x = Freq, y = Fold_Heading_Diff, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Preference and Senses on Heading Difference") +
-  xlab("Frequency of Observations") +
-  ylab("Heading Difference (Degrees)") +
-  theme_light()
-
-ggplot(comp_data_freqs, aes(x = Freq, y = Sync, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Preference and Senses on Synchonization") +
-  xlab("Frequency of Observations") +
-  ylab("Synchonization") +
-  theme_light()
-```
-
-```{r}
-ggplot(freq_predict_df, aes(x = Freq, y = pred_speed_diff, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Frequency of Observations on Speed Difference") +
-  xlab("Frequency (%)") +
-  ylab("Speed Difference (BL/s)") +
-  theme_light()
-
-ggplot(freq_predict_df, aes(x = Freq, y = pred_heading_diff, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Frequency of Observations on Heading Difference") +
-  xlab("Frequency (%)") +
-  ylab("Heading Difference (Degrees)") +
-  theme_light()
-
-ggplot(freq_predict_df, aes(x = Freq, y = pred_sync, color = interaction(Ablation,Darkness,sep=", "),
-                       fill = interaction(Ablation,Darkness,sep=", "))) +
-  geom_line() +
-  facet_wrap(~ Flow) +
-  guides(fill = "none", color = guide_legend(title = "Condition")) +
-  scale_color_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  scale_fill_manual(values=c("#000000", "#4CB944", "#00A7E1")) +
-  ggtitle("Effect of Frequency of Observations on Synchonization") +
-  xlab("Frequency (%)") +
-  ylab("Synchonization") +
-  theme_light()
-```

### 2021-12-14 data_files_to_csv_4P.py

@@ -108,6 +108,30 @@ def x_intercept(x1,y1,x2,y2):
 
     return intercept
 
+#Calculates the uniformity of a distribution of phases or angles as a dimensionless number from 0 to 1
+#Data must be given already normalized between 0 and 2pi
+
+def rayleigh_cor(data):
+    #Make an empy array the length of long axis of data
+    out_cor = np.zeros(data.shape[0])
+
+    #Get each time point as an array
+    for i,d in enumerate(data):
+        #Calcualte the x and y coordinates on the unit circle from the angle
+        xs = np.cos(d)
+        ys = np.sin(d)
+
+        #Take the mean of x and of y
+        mean_xs = np.nanmean(xs)
+        mean_ys = np.nanmean(ys)
+
+        #Find the magnitude of this new vector
+        magnitude = np.sqrt(mean_xs**2 + mean_ys**2)
+
+        out_cor[i] = magnitude
+
+    return out_cor
+
 class fish_data:
     def __init__(self, name, data, scorer, flow):
         #This sets up all of the datapoints that I will need from this fish
@@ -183,7 +207,7 @@ class fish_data:
 
         out_tailtip_perps = []
 
-        #My old code does this frame by frame. THere may be a way to vectorize it, but I'm not sure about that yet
+        #My old code does this frame by frame. There may be a way to vectorize it, but I'm not sure about that yet
         for i in range(total_frames):
             #Create a vector from the head to the tailtip and from the head to the midline
             tailtip_vec = np.asarray([self.head_x[i]-self.tailtip_x[i],self.head_y[i]-self.tailtip_y[i],0])
@@ -220,8 +244,13 @@ class fish_data:
         tb_freq = 60/np.diff(self.zero_crossings)
 
         #Then we repeat it to match the length of the tailbeats
-        tailbeat_lengths = abs(np.diff(np.append(self.zero_crossings,len(self.tailtip_zero_centered))))
-        self.tb_freq_reps = np.repeat(tb_freq,tailbeat_lengths[:len(tb_freq)])
+        tailbeat_lengths = np.diff(np.append(self.zero_crossings,len(self.tailtip_zero_centered)))
+        #This is so that if the first one does start at zero, a bit gets added on so that they all end up the same length
+        #Some fish are gone entirely, and this breaks if I call an index when the fish don't have any points
[…]

### 2022-05-18 Fish Data Analysis/Data_For_Eric.Rmd
Update before I do my work making the 3D processor

---
title: "Data For Eric"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
tailbeat_len = 19

round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
```

```{r}
raw_school_data <- read.csv("Fish_Raw_Comp_Values.csv")
raw_school_data <- na.omit(raw_school_data)

raw_school_data <- raw_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x")

raw_school_data_fish_switch <- raw_school_data %>% mutate(Fish3 = Fish1) %>%
                                                   mutate(Fish1 = Fish2) %>%
                                                   mutate(Fish2 = Fish3) %>%
                                                   select(-c(Fish3))

raw_school_data_both_fish <- bind_rows(raw_school_data, raw_school_data_fish_switch)
```

```{r}
count_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                ungroup() %>%
                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                ungroup()
```

```{r}
ggplot(count_within_2, 
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
           fill = interaction(Ablation,Darkness,sep=", "), color = interaction(Year,Month,Day,Trial,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Mean size of group within 2BL") +
  xlab("") +
  ylab("Mean size of group within 2BL (# of Fish)") +
  ylim(0,9) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  scale_y_continuous(breaks=c(0,2,4,6,8))
```
So from this the Light & Still groups with the best values are:
7/28/20 - 10
3/25/21 - 1

So from this the Dark & Still groups with the best values are:
10/8/21 - 15
7/7/21 - 19
7/7/21 - 21

```{r}
raw_school_data_both_fish %>% group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness) %>% summarise(count = n()) %>% ungroup() %>% arrange(-count) %>% filter(Ablation == "No Ablation" & Flow == "Still Water")
```

Of these 7/28/20 - 10 has the most for light and 7/7/21 - 19 has the most for darkness

Getting Light CSV

```{r}
eric_light_data <- raw_school_data %>% filter(Year == 2020 & Month == 7 & Day == 28 & Trial == 10) %>% 
                                        mutate(Tailbeat_Num = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness,
                                                 Tailbeat_Num, Frame_Num, Fish1) %>%
                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2),
                                                  Speed_Diff = mean(Speed_Diff),
                                                  Distance = mean(Distance)) %>%
                                        ungroup() %>%
                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat_Num) %>%
                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL),
                                                  Speed_Diff = mean(Speed_Diff),
                                                  Distance = mean(Distance)) %>%
                                        ungroup()

eric_school_data <- read.csv("Fish_School_Values.csv")
eric_school_data <- na.omit(eric_school_data)

eric_school_data <- eric_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           filter(Year == 2020 & Month == 7 & Day == 28 & Trial == 10)

eric_light_data <- eric_light_data %>% inner_join(eric_school_data %>% select(Tailbeat_Num, Area))

###

eric_dark_data <- raw_school_data %>% filter(Year == 2021 & Month == 7 & Day == 7 & Trial == 19) %>% 
                                        mutate(Tailbeat_Num = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness,
                                                 Tailbeat_Num, Frame_Num, Fish1) %>%
                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2),
                                                  Speed_Diff = mean(Speed_Diff),
                                                  Distance = mean(Distance)) %>%
                                        ungroup() %>%
                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat_Num) %>%
                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL),
                                                  Speed_Diff = mean(Speed_Diff),
                                                  Distance = mean(Distance)) %>%
                                        ungroup()

eric_school_data <- read.csv("Fish_School_Values.csv")
eric_school_data <- na.omit(eric_school_data)

eric_school_data <- eric_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           filter(Year == 2021 & Month == 7 & Day == 7 & Trial == 19)

eric_dark_data <- eric_dark_data %>% inner_join(eric_school_data %>% select(Tailbeat_Num, Area))

eric_data <- eric_dark_data %>% full_join(eric_light_data)

write.csv(eric_data, file = "Eric_Light_Dark_Data.csv")

```

Eric Fish Tracks

```{r}
fish_tracks_2020_07_28_10 <- read.csv("2020_07_28_10_TN_DN_F0_V1DLC_resnet50_L8FV4PFeb22shuffle1_100000_bx_filtered.csv")

fish_tracks_2020_07_28_10 <- fish_tracks_2020_07_28_10 %>% pivot_longer(Fish1_X:Fish8_Y,
                                                                        names_to = c("Fish",".value"),
                                                                        names_pattern = "(.)_(.)") %>%
                                                           mutate(Year = 2020, Month = 7, Day = 28, Trial = 10,
                                                                  Flow = "Still Water", Ablation = "No Ablation",
                                                                  Darkness = "Light") %>%
                                                          relocate(Frame:Y, .after = Darkness)

fish_tracks_2021_07_07_21 <- read.csv("2021_07_07_21_TN_DY_F0_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv")

fish_tracks_2021_07_07_21 <- fish_tracks_2021_07_07_21 %>% pivot_longer(Fish1_X:Fish8_Y,
                                                                        names_to = c("Fish",".value"),
                                                                        names_pattern = "(.)_(.)") %>%
                                                           mutate(Year = 2021, Month = 7, Day = 7, Trial = 21,
                                                                  Flow = "Still Water", Ablation = "No Ablation",
                                                                  Darkness = "Dark") %>%
                                                          relocate(Frame:Y, .after = Darkness)

Eric_Light_Dark_Fish_Tracks <- fish_tracks_2020_07_28_10 %>% full_join(fish_tracks_2021_07_07_21) %>%
                                                             mutate(BL_X = X / 193,
                                                                    BL_Y = Y / 193)

write.csv(Eric_Light_Dark_Fish_Tracks, file = "Eric_Light_Dark_Fish_Tracks.csv")                                                      
```

### 2022-05-18 Fish Data Analysis/Final_Plots.Rmd
Update before I do my work making the 3D processor

---
title: "Finalized Plots"
output: html_notebook
---

```{r}
library(tidyverse) #For dplyr and data sorting
library(ggplot2) #For plotting
library(bbmle) #For ICtab
library(car) #For Anova
library(forcats) #For Factor Work
library(ggpubr) #For the significance bars
```

### Functions and Varibles I need
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#E71D36"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")
```

### NND

```{r}
school_data <- read.csv("Fish_School_Values.csv")
school_data <- na.omit(school_data)

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           filter(Flow %in% allowed_flow_type)
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = NND, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(2.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggsave("Final Graphs/School_NND.png")
```

### Num fish Within 2 BL

```{r}
raw_school_data <- read.csv("Fish_Raw_Comp_Values.csv")
raw_school_data <- na.omit(raw_school_data)

raw_school_data <- raw_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%
                           filter(Flow %in% allowed_flow_type)

raw_school_data_fish_switch <- raw_school_data %>% mutate(Fish3 = Fish1) %>%
                                                   mutate(Fish1 = Fish2) %>%
                                                   mutate(Fish2 = Fish3) %>%
                                                   select(-c(Fish3))

raw_school_data_both_fish <- bind_rows(raw_school_data, raw_school_data_fish_switch)

count_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                ungroup() %>%
                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                ungroup()
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )

ggplot(count_within_2, 
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Mean size of group within 2BL") +
  xlab("") +
  ylab("Mean size of group within 2BL (# of Fish)") +
  ylim(0,9) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  scale_y_continuous(breaks=c(0,2,4,6,8))

ggsave("Final Graphs/Mean_Group_Size.png")
```

### Polarization

```{r}
school_data <- read.csv("Fish_School_Values.csv")
school_data <- na.omit(school_data)

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>% 
                           filter(Flow %in% allowed_flow_type)
```

```{r}
ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on School Polarization") +
  xlab("") +
  ylab("Polarization") +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1, 1.25), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggsave("Final Graphs/Polarization.png")
```

### Number of fish aligned within 2 BL

```{r}
count_within_2_aligned <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                        filter(Heading_Diff > -30 & Heading_Diff < 30) %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                        ungroup() %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                        ungroup()
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )

ggplot(count_within_2_aligned, 
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Mean size of group within 2BL") +
  xlab("") +
  ylab("Number of Aligned Fish within 2BL (# of Fish)") +
  ylim(0,5) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(3.5,4.25), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  scale_y_continuous(breaks=c(0,2,4,6,8))

ggsave("Final Graphs/Num_Aligned_Fish_2BL.png")

```

### Speed Ratio

```{r}
speed_whole_school <- school_data

indiv_data <- read.csv("Fish_Individual_Values.csv")
indiv_data <- na.omit(indiv_data)

indiv_data <- indiv_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           filter(Flow %in% allowed_flow_type)

indiv_data_4_speed <- indiv_data %>% group_by(Year, Month, Day, Trial, Tailbeat_Num) %>%
                                     summarise(Mean_Speed = mean(Speed))

fish_speed_division <- speed_whole_school %>% inner_join(indiv_data_4_speed, by = c("Year", "Month", "Day", "Trial", "Tailbeat_Num")) %>%
                                              mutate(Divided_Speed = School_Speed/Mean_Speed)
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )

ggplot(fish_speed_division, aes(x = interaction(Ablation,Darkness,sep=", "), y = Divided_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on School Speed") +
  xlab("") +
  ylab("Speed (BL/s)") +
  ylim(0,8) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(6.5,7.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggsave("Final Graphs/School_Speed_Over_Indiv_Speed.png")

```

### Turning Bias

```{r}
turning_data <- read.csv("Annushka_Turning_Data_Wall.csv") %>%
                           filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>%
                           filter(Flow %in% allowed_flow_type)

turning_data_sum <- turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               n = n()) %>%
                                     ungroup()

turning_data_sum_one <- turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               n = n()) %>%
                                     ungroup()
```

```{r}
ggplot(turning_data_sum, aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ggsave("Final Graphs/Right_Turn_Prob.png")
```

```{r}
#mi_fr_d <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data, family = binomial)

mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)

ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Ablation))+
  geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ggsave("Final Graphs/Best_Model_Right_Turn_Prob.png")

```

### Simulated # of fish within 2 BL

```{r}
raw_school_data_simul <- rbind(read.csv("Fish_Raw_Comp_Values.csv"),
                               read.csv("Data Sim/Fish_Raw_Comp_Values_Random.csv"))
raw_school_data_simul <- na.omit(raw_school_data_simul) %>% filter(Flow == "0")

raw_school_data_simul <- raw_school_data_simul %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", ifelse(Ablation == "Y","Ablated","Simulated"))) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", ifelse(Darkness == "Y", "Dark", "Simulated"))) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x")

raw_school_data_simul_fish_switch <- raw_school_data_simul %>% mutate(Fish3 = Fish1) %>%
                                                   mutate(Fish1 = Fish2) %>%
                                                   mutate(Fish2 = Fish3) %>%
                                                   select(-c(Fish3))

raw_school_data_simul_both_fish <- bind_rows(raw_school_data_simul, raw_school_data_simul)

count_within_2_simul <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                ungroup() %>%
                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                ungroup()
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
                        c("No Ablation, Light", "Ablated, Light"),
                        c("No Ablation, Dark", "Simulated, Simulated"))

ggplot(count_within_2_simul %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
  ggtitle("Mean size of group within 2BL") +
  xlab("") +
  ylab("Mean size of group within 2BL (# of Fish)") +
  ylim(0,9) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5,6), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  scale_y_continuous(breaks=c(0,2,4,6,8))

ggsave("Final Graphs/Simmed_Group_Num_in_2_BL.png")

```

### Simluated Data Aligned within 2BL

```{r}

max_offset <- 15

count_within_2_simul_aligned <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                        filter(abs(Heading_Diff) < max_offset) %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                        ungroup() %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                        ungroup()
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
                        c("No Ablation, Light", "Ablated, Light"),
                        c("No Ablation, Dark", "Simulated, Simulated"))

ggplot(count_within_2_simul_aligned %>% filter(Flow == "Still Water"), 
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL,
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
  ggtitle("Mean size of group within 2BL") +
  xlab("") +
  ylab("Number of Aligned Fish within 2BL (# of Fish)") +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(4.5,3.5,4), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  ylim(0,7) +
  scale_y_continuous(breaks=c(0,2,4,6,8))

ggsave("Final Graphs/Simmed_Aligned_Group_Num_in_2_BL.png")

```

### Simulated Turning Bias

```{r}
turning_data_sim <- read.csv("Annushka_Turning_Data_Simmed.csv") %>% 
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", ifelse(Ablation == "LY","Ablated",Ablation))) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", ifelse(Darkness == "DY", "Dark", Darkness))) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0))

turning_data_sim_sum <- turning_data_sim %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               n = n()) %>%
                                     ungroup()

turning_data_sim_sum_one <- turning_data_sim %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               n = n()) %>%
                                     ungroup()
```

```{r}

mi_fr_d_sim <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data_sim, family = binomial)

ggplot(turning_data_sim, aes(x = Fish_Num_Ratio, y = turn_bool, color = Darkness))+
  geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d_sim, type="response"), color = Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d_sim, type="response"), color = Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,sim_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ggsave("Final Graphs/Simmed_Right_Turn_Best_Model.png")

```

### 2022-05-18 Fish Data Analysis/Individual Fish.Rmd
Update before I do my work making the 3D processor

---
title: "Individual Fish"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(car)
library(forcats)
library(ggpubr)
library(rstatix)
```

```{r}
indiv_data <- read.csv("Fish_Individual_Values.csv")
indiv_data <- na.omit(indiv_data)

indiv_data <- indiv_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))

indiv_data_4_speed <- indiv_data %>% group_by(Year, Month, Day, Trial, Tailbeat_Num) %>%
                                     summarise(Mean_Speed = mean(Speed))
```

```{r}
m_speed <- aov(Speed ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = indiv_data)
Anova(m_speed)
TukeyHSD(m_speed)

ggplot(indiv_data,aes(x=Speed))+
  geom_histogram() +
  facet_wrap(~ Flow + Ablation + Darkness, scales="free") +
  xlim(0,6) +
  theme_light()

ggplot(indiv_data %>% filter(Speed < 5), aes(x = Flow, y = Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Fish Speed") +
  xlab("") +
  #ylim(0,5) +
  ylab("Speed (BL/s)") +
  theme_light()

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )

ggplot(indiv_data %>% filter(Speed < 5), aes(x = interaction(Ablation,Darkness,sep=", "), y = Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Fish Speed") +
  xlab("") +
  ylab("Speed (BL/s)") +
  ylim(0,6) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(4.5, 5.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

```{r}
m_heading <- aov(Heading ~ Flow + Ablation + Darkness + Flow*Ablation + Flow*Darkness, data = indiv_data)
Anova(m_heading)
TukeyHSD(m_heading)

ggplot(indiv_data, aes(x = Flow, y = rad2deg(atan(sin(deg2rad(Heading))/cos(deg2rad(Heading)))), fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Fish Heading") +
  xlab("") +
  ylab("Heading (Degrees)") +
  theme_light()
```

```{r}
m_tailbeats <- aov(TB_Frequency ~ Flow + Ablation + Darkness + Flow*Ablation + Flow*Darkness, data = indiv_data)
Anova(m_tailbeats)
TukeyHSD(m_tailbeats)

ggplot(indiv_data, aes(x = Flow, y = TB_Frequency, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Fish Tailbeat Frequency") +
  xlab("") +
  ylim(0,7) +
  ylab("Tailbeat Frequency (Beats/s)") +
  theme_light()

my_comparisons <- list(c("Still Water", "Flowing Water (2 BL/s)"))

ggplot(indiv_data, aes(x = Flow, y = TB_Frequency, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Fish Tailbeat Frequency") +
  xlab("") +
  ylab("Tailbeat Frequency (Beats/s)") +
  theme_light() +
  facet_wrap(~ interaction(Ablation,Darkness,sep=", "), strip.position = "bottom")+
   ylim(0,10) +
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(9), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggplot(indiv_data, aes(x = Flow, y = TB_Frequency))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Fish Tailbeat Frequency") +
  xlab("") +
  ylab("Tailbeat Frequency (Beats/s)") +
  theme_light() +
  facet_wrap(~ interaction(Ablation,Darkness,sep=", "), strip.position = "bottom")+
   ylim(0,10) +
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(9), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

### 2022-05-18 Fish Data Analysis/Ji_Zhou_Data.Rmd
Back before adding roup level features
Update before I do my work making the 3D processor

@@
 
-comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
-                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
-                           filter(Distance <= 4) %>%
-                           filter(Speed_Diff <= 6) %>% 
-                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
-                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
-                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
-                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))
+indiv_data <- read.csv("Fish_Individual_Values.csv")
+indiv_data <- na.omit(indiv_data)
+
+# comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
+#                            mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+#                            mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+#                            mutate(Heading_Diff = abs(Heading_Diff)) %>%
+#                            filter(Distance <= 4) %>%
+#                            filter(Speed_Diff <= 6) %>% 
+#                            mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
+#                            mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
+#                            mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
+#                            mutate(Angle = fold_angle_0_360_to_0_180(Angle))
 
@@
 
-Fish Size:
+Fish Size (cm):
 
-  Small Fish: 
-    Length: 
-    Width:
-    Height:
+  Fish 1: 
+    Length: 8.2
+    Width:  0.8
+    Height: 1.8
 
-  Big Fish: 
-    Length: 
-    Width:
-    Height:
+  Fish 2: 
+    Length: 6.7
+    Width:  0.8
+    Height: 1.7
+
+  Fish 3: 
+    Length: 7.3
+    Width:  0.7
+    Height: 1.6
+
+  Fish 4: 
+    Length: 6.6
+    Width:  0.7
+    Height: 1.4
 
@@
   Flow SD:    1.43
+
+```{r}
+ggplot(indiv_data, aes(X, Y) ) +
+  geom_bin2d(bins = 15) +
+  facet_wrap(~ Flow + Ablation + Darkness) +
+  scale_fill_continuous(type = "viridis") +
+  theme_light()
+```

### 2022-05-18 Fish Data Analysis/comp_fish_simple_models.Rmd
Update before I do my work making the 3D processor

@@
 library(ggpubr)
+library(mgcViz)
 ```
@@
 round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
-ang_mean <- function(x){rad2deg(atan(mean(sin(deg2rad(x)))/mean(cos(deg2rad(x)))))}
+ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}
 
@@
 
-comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
+comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                            mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
@@
                            filter(abs(Speed_Diff) <= 6) %>% 
-                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
-                           mutate(fold_heading_diff = abs(fold_angle_neg_180_180_to_neg_90_90(Heading_Diff))) %>%
+                           #mutate(Speed_Diff = abs(Speed_Diff)) %>%
+                           mutate(rad_Heading = deg2rad(Heading_Diff)) %>%
+                           mutate(sin_Heading = sin(rad_Heading), cos_Heading = cos(rad_Heading)) %>%
+                           #mutate(fold_heading_diff = abs(fold_angle_neg_180_180_to_neg_90_90(Heading_Diff))) %>%
                            mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
@@
                            mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Flow 0","Flow 2"))) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                            mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                            mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(rad_Angle = Angle) %>%
+                           mutate(rad_Angle = deg2rad(Angle)) %>%
                            mutate(sin_Angle = sin(rad_Angle), cos_Angle = cos(rad_Angle)) %>%
+                           mutate(Flow_Ablation = factor(paste(Flow,Ablation,sep=", "))) %>%
+                           mutate(Flow_Darkness = factor(paste(Flow,Darkness,sep=", "))) %>%
                            mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))
@@
                                          Sync = mean(Sync),
-                                         Fold_Heading_Diff = mean(fold_heading_diff),
+                                         #Fold_Heading_Diff = mean(fold_heading_diff),
                                          Is_Aligned = mean(Is_Aligned),
@@
 
-comp_data_NND <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
+comp_data_NND <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat_Num) %>%
                                                                  filter(Distance == min(Distance)) %>%
@@
 
-comp_data_near_3 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
+comp_data_near_3 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat_Num) %>%
                                                                  slice_min(Distance, n = 3) %>%
@@
 ```{r}
-speed_anova <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
+speed_anova <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
 
@@
 
-heading_anova <- aov(fold_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
+heading_anova <- aov(Heading_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
 
@@
 
-sync_anova <- aov(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)
+sync_anova <- aov(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)
 
@@
 
-Anova(dist_anova)
-```
-
-```{r}
-ggplot(comp_data_near_3, aes(x = cos(deg2rad(Angle))))+
-  geom_histogram()+
-  facet_wrap(~ Flow + Ablation + Darkness)
-
-ggplot(comp_data_near_3, aes(x = sin(deg2rad(Angle))))+
-  geom_histogram()+
-  facet_wrap(~ Flow + Ablation + Darkness)
+Anova(angle_anova)
 ```
@@
   ylab("Speed Difference (BL/s)") +
-  ylim(-0.1,2.5) +
+  #ylim(-0.1,2.5) +
   theme_light()
 
-ggplot(comp_data_near_3, aes(x = Flow, y = fold_heading_diff, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
+#rad2deg(atan(sin_Heading/cos_Heading))
+
+ggplot(comp_data_near_3, aes(x = Flow, y = Heading_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_violin(outlier.shape = NA) +
   guides(fill = guide_legend(title = "Condition")) +
@@
   ylab("Heading Difference (Degrees)") +
+  #scale_y_continuous(breaks = c(-90,-60,-30,0,30,60,90)) +
   theme_light()
@@
 
+#rad2deg(atan2(sin_Angle,cos_Angle))
+
 ggplot(comp_data_near_3, aes(x = Flow, y = Angle, fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
+  geom_violin(outlier.shape = NA) +
   guides(fill = guide_legend(title = "Condition")) +
@@
   ylab("Nearest Neighbor Bearing (Degrees)") +
-  scale_y_continuous(breaks = c(30,60,90,120,150)) +
+  #scale_y_continuous(breaks = c(-90,-60,-30,0,30,60,90)) +
   theme_light()
@@
 ```
-
-Trying GAMs
+ Just nearest Fish Speed Diff
 
 ```{r}
-speed_gam <- gam(Speed_Diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
-                              data = comp_data_near_3)
+comp_data_near_1 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat_Num) %>%
+                                                                 slice_max(Distance, n = 1) %>%
+                                                                 ungroup() %>%
+                                                                 distinct(Distance, .keep_all= TRUE)
 
+speed_anova_nn <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_1)
+
+Anova(speed_anova_nn)
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+ggplot(comp_data_near_1, aes(x = interaction(Ablation,Darkness,sep=", "), y = Speed_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_violin(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Nearest Speed Diff") +
+  xlab("") +
+  ylab("Speed Difference (BL/s)") +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  #stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+```
+
+Trying ggpubr
+
+```{r}
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark") )
+
+ggplot(comp_data_near_3, aes(x = interaction(Ablation,Darkness,sep=", "), y = Distance, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
+  xlab("") +
+  ylab("NND (BL)") +
+  theme_light() +
+  facet_wrap(~ Flow)+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(4.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+```
+
+So we need to make all the possible GLMs for these variables and then compare them in order to see which model does best in order to see what actually has effects
+```{r}
+# speed_gam_d <- gam(Speed_Diff ~ s(Distance), data = comp_data_near_3)
+# speed_gam_d_f <- gam(Speed_Diff ~ s(Distance,by=Flow), data = comp_data_near_3)
+# speed_gam_d_a <- gam(Speed_Diff ~ s(Distance,by=Ablation), data = comp_data_near_3)
+# speed_gam_d_d <- gam(Speed_Diff ~ s(Distance,by=Darkness), data = comp_data_near_3)
+# speed_gam_d_fa <- gam(Speed_Diff ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
+# speed_gam_d_fd <- gam(Speed_Diff ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
+# speed_gam_d_fda <- gam(Speed_Diff ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# speed_gam_ca <- gam(Speed_Diff ~ s(cos_Angle), data = comp_data_near_3)
+# speed_gam_ca_f <- gam(Speed_Diff ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
+# speed_gam_ca_a <- gam(Speed_Diff ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
+# speed_gam_ca_d <- gam(Speed_Diff ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
+# speed_gam_ca_fa <- gam(Speed_Diff ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# speed_gam_ca_fd <- gam(Speed_Diff ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# speed_gam_ca_fda <- gam(Speed_Diff ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# speed_gam_sa <- gam(Speed_Diff ~ s(sin_Angle), data = comp_data_near_3)
+# speed_gam_sa_f <- gam(Speed_Diff ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
+# speed_gam_sa_a <- gam(Speed_Diff ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
+# speed_gam_sa_d <- gam(Speed_Diff ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
+# speed_gam_sa_fa <- gam(Speed_Diff ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# speed_gam_sa_fd <- gam(Speed_Diff ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# speed_gam_sa_fda <- gam(Speed_Diff ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# speed_gam_dca <- gam(Speed_Diff ~ s(Distance,cos_Angle), data = comp_data_near_3)
+# speed_gam_dca_f <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
+# speed_gam_dca_a <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
+# speed_gam_dca_d <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
+# speed_gam_dca_fa <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# speed_gam_dca_fd <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# speed_gam_dca_fda <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# speed_gam_dsa <- gam(Speed_Diff ~ s(Distance,sin_Angle), data = comp_data_near_3)
+# speed_gam_dsa_f <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
+# speed_gam_dsa_a <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
+# speed_gam_dsa_d <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
+# speed_gam_dsa_fa <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# speed_gam_dsa_fd <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# speed_gam_dsa_fda <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# speed_gam_dcasa <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle), data = comp_data_near_3)
+# speed_gam_dcasa_f <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow), data = comp_data_near_3)
+# speed_gam_dcasa_a <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Ablation), data = comp_data_near_3)
+# speed_gam_dcasa_d <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Darkness), data = comp_data_near_3)
+# speed_gam_dcasa_fa <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# speed_gam_dcasa_fd <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# speed_gam_dcasa_fda <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+
+speed_AIC <- AIC(speed_gam_d,speed_gam_d_f,speed_gam_d_a,speed_gam_d_d,speed_gam_d_fa,speed_gam_d_fd,speed_gam_d_fda,
+                 speed_gam_ca,speed_gam_ca_f,speed_gam_ca_a,speed_gam_ca_d,speed_gam_ca_fa,speed_gam_ca_fd,speed_gam_ca_fda,
+                 speed_gam_sa,speed_gam_sa_f,speed_gam_sa_a,speed_gam_sa_d,speed_gam_sa_fa,speed_gam_sa_fd,speed_gam_sa_fda,
+                 speed_gam_dca,speed_gam_dca_f,speed_gam_dca_a,speed_gam_dca_d,speed_gam_dca_fa,speed_gam_dca_fd,speed_gam_dca_fda,
+                 speed_gam_dsa,speed_gam_dsa_f,speed_gam_dsa_a,speed_gam_dsa_d,speed_gam_dsa_fa,speed_gam_dsa_fd,speed_gam_dsa_fda,
+                 speed_gam_dcasa,speed_gam_dcasa_f,speed_gam_dcasa_a,speed_gam_dcasa_d,speed_gam_dcasa_fa,speed_gam_dcasa_fd,speed_gam_dcasa_fda)
+
+speed_AIC <- tibble::rownames_to_column(speed_AIC, "Model_Name")
+
+speed_AIC <- speed_AIC %>% mutate(Model_Name = fct_reorder(Model_Name, -AIC)) %>% arrange(AIC)
+
+ggplot(speed_AIC, aes(x = Model_Name, y = AIC)) +
+  geom_point(color = "blue") +
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  theme_light()+
+  scale_y_reverse() +
+  coord_flip()
+
+speed_AIC
+```
+
+How we do that for the cosine of the headings
+
+```{r}
+# cos_heading_gam_d <- gam(cos_Heading ~ s(Distance), data = comp_data_near_3)
+# cos_heading_gam_d_f <- gam(cos_Heading ~ s(Distance,by=Flow), data = comp_data_near_3)
+# cos_heading_gam_d_a <- gam(cos_Heading ~ s(Distance,by=Ablation), data = comp_data_near_3)
+# cos_heading_gam_d_d <- gam(cos_Heading ~ s(Distance,by=Darkness), data = comp_data_near_3)
+# cos_heading_gam_d_fa <- gam(cos_Heading ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
+# cos_heading_gam_d_fd <- gam(cos_Heading ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
+# cos_heading_gam_d_fda <- gam(cos_Heading ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# cos_heading_gam_ca <- gam(cos_Heading ~ s(cos_Angle), data = comp_data_near_3)
+# cos_heading_gam_ca_f <- gam(cos_Heading ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
+# cos_heading_gam_ca_a <- gam(cos_Heading ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
+# cos_heading_gam_ca_d <- gam(cos_Heading ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
+# cos_heading_gam_ca_fa <- gam(cos_Heading ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# cos_heading_gam_ca_fd <- gam(cos_Heading ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# cos_heading_gam_ca_fda <- gam(cos_Heading ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# cos_heading_gam_sa <- gam(cos_Heading ~ s(sin_Angle), data = comp_data_near_3)
+# cos_heading_gam_sa_f <- gam(cos_Heading ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
+# cos_heading_gam_sa_a <- gam(cos_Heading ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
+# cos_heading_gam_sa_d <- gam(cos_Heading ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
+# cos_heading_gam_sa_fa <- gam(cos_Heading ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# cos_heading_gam_sa_fd <- gam(cos_Heading ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# cos_heading_gam_sa_fda <- gam(cos_Heading ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# cos_heading_gam_dca <- gam(cos_Heading ~ s(Distance,cos_Angle), data = comp_data_near_3)
+# cos_heading_gam_dca_f <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
+# cos_heading_gam_dca_a <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
+# cos_heading_gam_dca_d <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
+# cos_heading_gam_dca_fa <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# cos_heading_gam_dca_fd <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# cos_heading_gam_dca_fda <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# cos_heading_gam_dsa <- gam(cos_Heading ~ s(Distance,sin_Angle), data = comp_data_near_3)
+# cos_heading_gam_dsa_f <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
+# cos_heading_gam_dsa_a <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
+# cos_heading_gam_dsa_d <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
+# cos_heading_gam_dsa_fa <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# cos_heading_gam_dsa_fd <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# cos_heading_gam_dsa_fda <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# cos_heading_gam_dcasa <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle), data = comp_data_near_3)
+# cos_heading_gam_dcasa_f <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow), data = comp_data_near_3)
+# cos_heading_gam_dcasa_a <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Ablation), data = comp_data_near_3)
+# cos_heading_gam_dcasa_d <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Darkness), data = comp_data_near_3)
+# cos_heading_gam_dcasa_fa <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# cos_heading_gam_dcasa_fd <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# cos_heading_gam_dcasa_fda <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+
+cos_heading_AIC <- AIC(cos_heading_gam_d,cos_heading_gam_d_f,cos_heading_gam_d_a,cos_heading_gam_d_d,cos_heading_gam_d_fa,cos_heading_gam_d_fd,cos_heading_gam_d_fda,
+                 cos_heading_gam_ca,cos_heading_gam_ca_f,cos_heading_gam_ca_a,cos_heading_gam_ca_d,cos_heading_gam_ca_fa,cos_heading_gam_ca_fd,cos_heading_gam_ca_fda,
+                 cos_heading_gam_sa,cos_heading_gam_sa_f,cos_heading_gam_sa_a,cos_heading_gam_sa_d,cos_heading_gam_sa_fa,cos_heading_gam_sa_fd,cos_heading_gam_sa_fda,
+                 cos_heading_gam_dca,cos_heading_gam_dca_f,cos_heading_gam_dca_a,cos_heading_gam_dca_d,cos_heading_gam_dca_fa,cos_heading_gam_dca_fd,cos_heading_gam_dca_fda,
+                 cos_heading_gam_dsa,cos_heading_gam_dsa_f,cos_heading_gam_dsa_a,cos_heading_gam_dsa_d,cos_heading_gam_dsa_fa,cos_heading_gam_dsa_fd,cos_heading_gam_dsa_fda,
+                 cos_heading_gam_dcasa,cos_heading_gam_dcasa_f,cos_heading_gam_dcasa_a,cos_heading_gam_dcasa_d,cos_heading_gam_dcasa_fa,cos_heading_gam_dcasa_fd,cos_heading_gam_dcasa_fda)
+
+cos_heading_AIC <- tibble::rownames_to_column(cos_heading_AIC, "Model_Name")
+
+cos_heading_AIC <- cos_heading_AIC %>% mutate(Model_Name = fct_reorder(Model_Name, -AIC)) %>% arrange(AIC)
+
+ggplot(cos_heading_AIC %>% arrange(AIC), aes(x = Model_Name, y = AIC)) +
+  geom_point(color = "blue") +
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  theme_light() +
+  scale_y_reverse() +
+  coord_flip()
+
+cos_heading_AIC
+```
+
+Now with the sin of the Headings
+```{r}
+# sin_heading_gam_d <- gam(sin_Heading ~ s(Distance), data = comp_data_near_3)
+# sin_heading_gam_d_f <- gam(sin_Heading ~ s(Distance,by=Flow), data = comp_data_near_3)
+# sin_heading_gam_d_a <- gam(sin_Heading ~ s(Distance,by=Ablation), data = comp_data_near_3)
+# sin_heading_gam_d_d <- gam(sin_Heading ~ s(Distance,by=Darkness), data = comp_data_near_3)
+# sin_heading_gam_d_fa <- gam(sin_Heading ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
+# sin_heading_gam_d_fd <- gam(sin_Heading ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
+# sin_heading_gam_d_fda <- gam(sin_Heading ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sin_heading_gam_ca <- gam(sin_Heading ~ s(cos_Angle), data = comp_data_near_3)
+# sin_heading_gam_ca_f <- gam(sin_Heading ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
+# sin_heading_gam_ca_a <- gam(sin_Heading ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
+# sin_heading_gam_ca_d <- gam(sin_Heading ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
+# sin_heading_gam_ca_fa <- gam(sin_Heading ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sin_heading_gam_ca_fd <- gam(sin_Heading ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sin_heading_gam_ca_fda <- gam(sin_Heading ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sin_heading_gam_sa <- gam(sin_Heading ~ s(sin_Angle), data = comp_data_near_3)
+# sin_heading_gam_sa_f <- gam(sin_Heading ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
+# sin_heading_gam_sa_a <- gam(sin_Heading ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
+# sin_heading_gam_sa_d <- gam(sin_Heading ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
+# sin_heading_gam_sa_fa <- gam(sin_Heading ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sin_heading_gam_sa_fd <- gam(sin_Heading ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sin_heading_gam_sa_fda <- gam(sin_Heading ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sin_heading_gam_dca <- gam(sin_Heading ~ s(Distance,cos_Angle), data = comp_data_near_3)
+# sin_heading_gam_dca_f <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
+# sin_heading_gam_dca_a <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
+# sin_heading_gam_dca_d <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
+# sin_heading_gam_dca_fa <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sin_heading_gam_dca_fd <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sin_heading_gam_dca_fda <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sin_heading_gam_dsa <- gam(sin_Heading ~ s(Distance,sin_Angle), data = comp_data_near_3)
+# sin_heading_gam_dsa_f <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
+# sin_heading_gam_dsa_a <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
+# sin_heading_gam_dsa_d <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
+# sin_heading_gam_dsa_fa <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sin_heading_gam_dsa_fd <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sin_heading_gam_dsa_fda <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sin_heading_gam_dcasa <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle), data = comp_data_near_3)
+# sin_heading_gam_dcasa_f <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow), data = comp_data_near_3)
+# sin_heading_gam_dcasa_a <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Ablation), data = comp_data_near_3)
+# sin_heading_gam_dcasa_d <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Darkness), data = comp_data_near_3)
+# sin_heading_gam_dcasa_fa <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sin_heading_gam_dcasa_fd <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sin_heading_gam_dcasa_fda <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+
+sin_Heading_AIC <- AIC(sin_heading_gam_d,sin_heading_gam_d_f,sin_heading_gam_d_a,sin_heading_gam_d_d,sin_heading_gam_d_fa,sin_heading_gam_d_fd,sin_heading_gam_d_fda,
+                 sin_heading_gam_ca,sin_heading_gam_ca_f,sin_heading_gam_ca_a,sin_heading_gam_ca_d,sin_heading_gam_ca_fa,sin_heading_gam_ca_fd,sin_heading_gam_ca_fda,
+                 sin_heading_gam_sa,sin_heading_gam_sa_f,sin_heading_gam_sa_a,sin_heading_gam_sa_d,sin_heading_gam_sa_fa,sin_heading_gam_sa_fd,sin_heading_gam_sa_fda,
+                 sin_heading_gam_dca,sin_heading_gam_dca_f,sin_heading_gam_dca_a,sin_heading_gam_dca_d,sin_heading_gam_dca_fa,sin_heading_gam_dca_fd,sin_heading_gam_dca_fda,
+                 sin_heading_gam_dsa,sin_heading_gam_dsa_f,sin_heading_gam_dsa_a,sin_heading_gam_dsa_d,sin_heading_gam_dsa_fa,sin_heading_gam_dsa_fd,sin_heading_gam_dsa_fda,
+                 sin_heading_gam_dcasa,sin_heading_gam_dcasa_f,sin_heading_gam_dcasa_a,sin_heading_gam_dcasa_d,sin_heading_gam_dcasa_fa,sin_heading_gam_dcasa_fd,sin_heading_gam_dcasa_fda)
+
+sin_Heading_AIC <- tibble::rownames_to_column(sin_Heading_AIC, "Model_Name")
+
+sin_Heading_AIC <- sin_Heading_AIC %>% mutate(Model_Name = fct_reorder(Model_Name, -AIC)) %>% arrange(AIC)
+
+ggplot(sin_Heading_AIC %>% arrange(AIC), aes(x = Model_Name, y = AIC)) +
+  geom_point(color = "blue") +
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  theme_light()+
+  scale_y_reverse() +
+  coord_flip()
+
+sin_Heading_AIC
+```
+
+And now with Sync
+
+```{r}
+# sync_gam_d <- gam(Sync ~ s(Distance), data = comp_data_near_3)
+# sync_gam_d_f <- gam(Sync ~ s(Distance,by=Flow), data = comp_data_near_3)
+# sync_gam_d_a <- gam(Sync ~ s(Distance,by=Ablation), data = comp_data_near_3)
+# sync_gam_d_d <- gam(Sync ~ s(Distance,by=Darkness), data = comp_data_near_3)
+# sync_gam_d_fa <- gam(Sync ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
+# sync_gam_d_fd <- gam(Sync ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
+# sync_gam_d_fda <- gam(Sync ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sync_gam_ca <- gam(Sync ~ s(cos_Angle), data = comp_data_near_3)
+# sync_gam_ca_f <- gam(Sync ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
+# sync_gam_ca_a <- gam(Sync ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
+# sync_gam_ca_d <- gam(Sync ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
+# sync_gam_ca_fa <- gam(Sync ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sync_gam_ca_fd <- gam(Sync ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sync_gam_ca_fda <- gam(Sync ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sync_gam_sa <- gam(Sync ~ s(sin_Angle), data = comp_data_near_3)
+# sync_gam_sa_f <- gam(Sync ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
+# sync_gam_sa_a <- gam(Sync ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
+# sync_gam_sa_d <- gam(Sync ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
+# sync_gam_sa_fa <- gam(Sync ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sync_gam_sa_fd <- gam(Sync ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sync_gam_sa_fda <- gam(Sync ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sync_gam_dca <- gam(Sync ~ s(Distance,cos_Angle), data = comp_data_near_3)
+# sync_gam_dca_f <- gam(Sync ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
+# sync_gam_dca_a <- gam(Sync ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
+# sync_gam_dca_d <- gam(Sync ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
+# sync_gam_dca_fa <- gam(Sync ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sync_gam_dca_fd <- gam(Sync ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sync_gam_dca_fda <- gam(Sync ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sync_gam_dsa <- gam(Sync ~ s(Distance,sin_Angle), data = comp_data_near_3)
+# sync_gam_dsa_f <- gam(Sync ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
+# sync_gam_dsa_a <- gam(Sync ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
+# sync_gam_dsa_d <- gam(Sync ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
+# sync_gam_dsa_fa <- gam(Sync ~ s(Distance,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sync_gam_dsa_fd <- gam(Sync ~ s(Distance,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sync_gam_dsa_fda <- gam(Sync ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+# 
+# sync_gam_dcasa <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle), data = comp_data_near_3)
+# sync_gam_dcasa_f <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Flow), data = comp_data_near_3)
+# sync_gam_dcasa_a <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Ablation), data = comp_data_near_3)
+# sync_gam_dcasa_d <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Darkness), data = comp_data_near_3)
+# sync_gam_dcasa_fa <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
+# sync_gam_dcasa_fd <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
+# sync_gam_dcasa_fda <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+
+Sync_AIC <- AIC(sync_gam_d,sync_gam_d_f,sync_gam_d_a,sync_gam_d_d,sync_gam_d_fa,sync_gam_d_fd,sync_gam_d_fda,
+                 sync_gam_ca,sync_gam_ca_f,sync_gam_ca_a,sync_gam_ca_d,sync_gam_ca_fa,sync_gam_ca_fd,sync_gam_ca_fda,
+                 sync_gam_sa,sync_gam_sa_f,sync_gam_sa_a,sync_gam_sa_d,sync_gam_sa_fa,sync_gam_sa_fd,sync_gam_sa_fda,
+                 sync_gam_dca,sync_gam_dca_f,sync_gam_dca_a,sync_gam_dca_d,sync_gam_dca_fa,sync_gam_dca_fd,sync_gam_dca_fda,
+                 sync_gam_dsa,sync_gam_dsa_f,sync_gam_dsa_a,sync_gam_dsa_d,sync_gam_dsa_fa,sync_gam_dsa_fd,sync_gam_dsa_fda,
+                 sync_gam_dcasa,sync_gam_dcasa_f,sync_gam_dcasa_a,sync_gam_dcasa_d,sync_gam_dcasa_fa,sync_gam_dcasa_fd,sync_gam_dcasa_fda)
+
+Sync_AIC <- tibble::rownames_to_column(Sync_AIC, "Model_Name")
+
+Sync_AIC <- Sync_AIC %>% mutate(Model_Name = fct_reorder(Model_Name, -AIC)) %>% arrange(AIC)
+
+ggplot(Sync_AIC %>% arrange(AIC), aes(x = Model_Name, y = AIC)) +
+  geom_point(color = "blue") +
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  theme_light()+
+  scale_y_reverse() +
+  coord_flip()
+
+Sync_AIC
+```
+
+Now we use the best of those
+```{r}
+speed_gam <- speed_gam_dsa_fda <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
 summary(speed_gam)
+vis.gam(speed_gam)
+# speed_gam_viz <- getViz(speed_gam)
+# plotRGL(sm(speed_gam_viz, 1))
 
-heading_gam <- gam(fold_heading_diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
-                              data = comp_data_near_3)
+cos_heading_gam <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+summary(cos_heading_gam)
+vis.gam(cos_heading_gam)
+# cos_heading_gam_viz <- getViz(cos_heading_gam)
+# plotRGL(sm(cos_heading_gam_viz, 1), fix = c("Distance" = 0))
 
-summary(heading_gam)
+sin_heading_gam <- gam(sin_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
+summary(sin_heading_gam)
+vis.gam(sin_heading_gam)
+# sin_heading_gam_viz <- getViz(sin_heading_gam)
+# plotRGL(sm(sin_heading_gam_viz, 1), fix = c("Distance" = 0))
 
-sync_gam <- gam(Sync ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
-                              data = comp_data_near_3)
-
+sync_gam <- gam(Sync ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
 summary(sync_gam)
+vis.gam(sync_gam)
+# sync_gam_viz <- getViz(sync_gam)
+# plotRGL(sm(sync_gam_viz, 1), fix = c("Distance" = 0))
 ```
@@
 d <- seq(from = 0, to = 3, by = 0.1)
-a <- seq(from = 0, to = 180, by = 10)
+a <- seq(from = 0, to = 180, by = 5)
 
@@
 predict_df <- predict_df %>% mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>% 
-                            filter(!(Ablation == "Ablated" & Darkness == 'Dark'))
+                             filter(!(Ablation == "Ablated" & Darkness == 'Dark')) %>%
+                             mutate(rad_Angle = deg2rad(Angle)) %>%
+                             mutate(sin_Angle = sin(rad_Angle), cos_Angle = cos(rad_Angle))
 
 predict_df <- predict_df %>% mutate(pred_speed_diff = predict.gam(speed_gam,predict_df),
-                                    pred_heading_diff = predict.gam(heading_gam,predict_df),
-                                    pred_sync = predict.gam(sync_gam,predict_df))
+                                    pred_cos_heading_diff = predict.gam(cos_heading_gam,predict_df),
+                                    pred_sin_heading_diff = predict.gam(sin_heading_gam,predict_df),
+                                    pred_sync = predict.gam(sync_gam,predict_df)) %>%
+                                    mutate(Angle = rad2deg(atan2(sin_Angle,cos_Angle))) %>%
+                                    mutate(pred_heading_diff = rad2deg(atan2(pred_sin_heading_diff,pred_cos_heading_diff)))
 
-predict_df <- predict_df %>% group_by(Distance,Flow,Ablation,Darkness) %>%
+predict_df_sum <- predict_df %>% group_by(Distance,Flow,Ablation,Darkness) %>%
                              mutate(mean_Speed_Distance = mean(pred_speed_diff), sd_Speed_Distance = sd(pred_speed_diff),
@@
                              mutate(mean_Speed_Angle = mean(pred_speed_diff), sd_Speed_Angle = sd(pred_speed_diff),
-                                    mean_Heading_Angle = mean(pred_heading_diff), sd_Heading_Angle = sd(pred_heading_diff),
+                                    mean_Heading_Angle = rad2deg(atan(mean(pred_sin_heading_diff)/mean(pred_cos_heading_diff))),
+                                    sd_Heading_Angle = rad2deg(atan(sd(pred_sin_heading_diff)/sd(pred_cos_heading_diff))),
                                     mean_Sync_Angle = mean(pred_sync), sd_Sync_Angle = sd(pred_sync)) %>%
@@
 ```{r}
-ggplot(predict_df, aes(x = Distance, y = mean_Speed_Distance, color = interaction(Ablation,Darkness,sep=", "),
+ggplot(predict_df_sum, aes(x = Distance, y = mean_Speed_Distance, color = interaction(Ablation,Darkness,sep=", "),
                        fill = interaction(Ablation,Darkness,sep=" "))) +
@@
   ylab("Speed Difference (BL/s)") +
-  ylim(0,1.5) +
+  #ylim(0,1.5) +
   theme_light()
 
-ggplot(predict_df, aes(x = Distance, y = mean_Heading_Distance, color = interaction(Ablation,Darkness,sep=", "),
+ggplot(predict_df_sum, aes(x = Distance, y = mean_Heading_Distance, color = interaction(Ablation,Darkness,sep=", "),
                        fill = interaction(Ablation,Darkness,sep=", "))) +
@@
   ylab("Heading Difference (Degrees)") +
-  ylim(0,50) +
+  #ylim(0,50) +
   theme_light()
 
-ggplot(predict_df, aes(x = Distance, y = mean_Sync_Distance, color = interaction(Ablation,Darkness,sep=", "),
+ggplot(predict_df_sum, aes(x = Distance, y = mean_Sync_Distance, color = interaction(Ablation,Darkness,sep=", "),
                        fill = interaction(Ablation,Darkness,sep=", "))) +
@@
   ylab("Synchonization") +
-  ylim(0,1)+
+  #ylim(0,1)+
   theme_light()
@@
 ```{r}
-ggplot(predict_df, aes(x = Angle, y = mean_Speed_Angle, color = interaction(Ablation,Darkness,sep=", "),
+ggplot(predict_df_sum, aes(x = Angle, y = mean_Speed_Angle, color = interaction(Ablation,Darkness,sep=", "),
                        fill = interaction(Ablation,Darkness,sep=", "))) +
@@
   ylab("Speed Difference (BL/s)") +
-  ylim(0,1.5) +
   theme_light()
 
-ggplot(predict_df, aes(x = Angle, y = mean_Heading_Angle, color = interaction(Ablation,Darkness,sep=", "),
+ggplot(predict_df_sum, aes(x = Angle, y = mean_Heading_Angle, color = interaction(Ablation,Darkness,sep=", "),
                        fill = interaction(Ablation,Darkness,sep=", "))) +
@@
   ylab("Heading Difference (Degrees)") +
-  ylim(0,50) +
   theme_light()
 
-ggplot(predict_df, aes(x = Angle, y = mean_Sync_Angle, color = interaction(Ablation,Darkness,sep=", "),
+ggplot(predict_df_sum, aes(x = Angle, y = mean_Sync_Angle, color = interaction(Ablation,Darkness,sep=", "),
                        fill = interaction(Ablation,Darkness,sep=", "))) +
@@
   ylab("Synchonization") +
-  ylim(0,1)+
   theme_light()

### 2022-05-18 Fish Data Analysis/turning_fish_bias.Rmd
Update before I do my work making the 3D processor

---
title: "Turning Fish Bias"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
```

```{r}
turning_data <- read.csv("Annushka_Turning_Data_Wall.csv") %>%
                           filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0))

turning_data_sum <- turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()

turning_data_sum_one <- turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()

turning_data_count <- turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                     summarize(count_per = n()) %>%
                                     ungroup()
```

```{r}
ggplot(turning_data_sum, aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  # geom_errorbar(aes(ymin=mean_right_turn-se_right_turn,
  #                   ymax=mean_right_turn+se_right_turn),
  #               alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c("Dark Grey","Blue")) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ggplot(turning_data_sum_one, aes(x = Fish_Num_Ratio, y = mean_right_turn))+
  geom_point()+
  geom_line(alpha = 0.25) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ggplot(turning_data_count, aes(x = Fish_Num_Ratio, y = count_per, fill = Flow))+
  geom_col(position = "dodge")+
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Count for Each Condition") +
  #scale_colour_manual(values = c("Dark Grey","Blue")) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))
```

```{r}
m0 <- glm(turn_bool ~ 1, data = turning_data, family = binomial)
m_fr <- glm(turn_bool ~ Fish_Num_Ratio, data = turning_data, family = binomial)
m_fl <- glm(turn_bool ~ Flow, data = turning_data, family = binomial)
m_a <- glm(turn_bool ~ Ablation, data = turning_data, family = binomial)
m_d <- glm(turn_bool ~ Darkness, data = turning_data, family = binomial)
ma_fr_fl <- glm(turn_bool ~ Fish_Num_Ratio + Flow, data = turning_data, family = binomial)
ma_fr_a <- glm(turn_bool ~ Fish_Num_Ratio + Ablation, data = turning_data, family = binomial)
ma_fr_d <- glm(turn_bool ~ Fish_Num_Ratio + Darkness, data = turning_data, family = binomial)
ma_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio + Flow + Ablation, data = turning_data, family = binomial)
ma_fr_fl_d <- glm(turn_bool ~ Fish_Num_Ratio + Flow + Darkness, data = turning_data, family = binomial)
ma_fr_a_d <- glm(turn_bool ~ Fish_Num_Ratio + Ablation + Darkness, data = turning_data, family = binomial)
ma_fr_fl_a_d <- glm(turn_bool ~ Fish_Num_Ratio + Flow + Ablation + Darkness, data = turning_data, family = binomial)
mi_fr_fl <- glm(turn_bool ~ Fish_Num_Ratio * Flow, data = turning_data, family = binomial)
mi_fr_a <- glm(turn_bool ~ Fish_Num_Ratio * Ablation, data = turning_data, family = binomial)
mi_fr_d <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data, family = binomial)
mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Ablation, data = turning_data, family = binomial)
mi_fr_fl_d <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Darkness, data = turning_data, family = binomial)
mi_fr_a_d <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, data = turning_data, family = binomial)
mi_fr_fl_a_d <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Ablation * Darkness, data = turning_data, family = binomial)

ICtab(m0,m_fr,m_fl,m_a,m_d,
      ma_fr_fl,ma_fr_a,ma_fr_d,ma_fr_fl_a,ma_fr_fl_d,ma_fr_a_d,ma_fr_fl_a_d,
      mi_fr_fl,mi_fr_a,mi_fr_d,mi_fr_fl_a,mi_fr_fl_d,mi_fr_a_d,mi_fr_fl_a_d)

Anova(mi_fr_fl_a)

```

```{r}

#turning_data_graph <- turning_data %>% mutate(predicted = predict(mi_fr_d, newdata=turning_data, type="response"))

ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow))+
  geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(ma_fr_fl_a, type="response"), color = Flow, shape = Ablation)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(ma_fr_fl_a, type="response"), color = Flow, shape = Ablation)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c("#FF483E","#0C17A1")) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

```

### NOW WITH SIMULATED DATA!

```{r}
turning_data_sim <- read.csv("Annushka_Turning_Data_Simmed.csv") %>% 
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", ifelse(Ablation == "LY","Ablated",Ablation))) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", ifelse(Darkness == "DY", "Dark", Darkness))) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0))

turning_data_sim_sum <- turning_data_sim %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               n = n()) %>%
                                     ungroup()

turning_data_sim_sum_one <- turning_data_sim %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               n = n()) %>%
                                     ungroup()
```

```{r}
ggplot(turning_data_sim_sum, aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  # geom_errorbar(aes(ymin=mean_right_turn-sd_right_turn,
  #                   ymax=mean_right_turn+sd_right_turn),
  #               alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c("Dark Grey","Blue")) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ggplot(turning_data_sum_one, aes(x = Fish_Num_Ratio, y = mean_right_turn))+
  geom_point()+
  geom_line(alpha = 0.25) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))
```

```{r}
m0 <- glm(turn_bool ~ 1, data = turning_data_sim, family = binomial)
m_fr <- glm(turn_bool ~ Fish_Num_Ratio, data = turning_data_sim, family = binomial)
m_fl <- glm(turn_bool ~ Flow, data = turning_data_sim, family = binomial)
m_a <- glm(turn_bool ~ Ablation, data = turning_data_sim, family = binomial)
m_d <- glm(turn_bool ~ Darkness, data = turning_data_sim, family = binomial)
ma_fr_fl <- glm(turn_bool ~ Fish_Num_Ratio + Flow, data = turning_data_sim, family = binomial)
ma_fr_a <- glm(turn_bool ~ Fish_Num_Ratio + Ablation, data = turning_data_sim, family = binomial)
ma_fr_d <- glm(turn_bool ~ Fish_Num_Ratio + Darkness, data = turning_data_sim, family = binomial)
ma_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio + Flow + Ablation, data = turning_data_sim, family = binomial)
ma_fr_fl_d <- glm(turn_bool ~ Fish_Num_Ratio + Flow + Darkness, data = turning_data_sim, family = binomial)
ma_fr_a_d <- glm(turn_bool ~ Fish_Num_Ratio + Ablation + Darkness, data = turning_data_sim, family = binomial)
ma_fr_fl_a_d <- glm(turn_bool ~ Fish_Num_Ratio + Flow + Ablation + Darkness, data = turning_data_sim, family = binomial)
mi_fr_fl <- glm(turn_bool ~ Fish_Num_Ratio * Flow, data = turning_data_sim, family = binomial)
mi_fr_a <- glm(turn_bool ~ Fish_Num_Ratio * Ablation, data = turning_data_sim, family = binomial)
mi_fr_d <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data_sim, family = binomial)
mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Ablation, data = turning_data_sim, family = binomial)
mi_fr_fl_d <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Darkness, data = turning_data_sim, family = binomial)
mi_fr_a_d <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, data = turning_data_sim, family = binomial)
mi_fr_fl_a_d <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Ablation * Darkness, data = turning_data_sim, family = binomial)

ICtab(m0,m_fr,m_fl,m_a,m_d,
      ma_fr_fl,ma_fr_a,ma_fr_d,ma_fr_fl_a,ma_fr_fl_d,ma_fr_a_d,ma_fr_fl_a_d,
      mi_fr_fl,mi_fr_a,mi_fr_d,mi_fr_fl_a,mi_fr_fl_d,mi_fr_a_d,mi_fr_fl_a_d)

Anova(m_fr)
Anova(mi_fr_d)

```

```{r}

#turning_data_graph <- turning_data %>% mutate(predicted = predict(mi_fr_d, newdata=turning_data, type="response"))

ggplot(turning_data_sim, aes(x = Fish_Num_Ratio, y = turn_bool, color = Darkness))+
  geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d, type="response"), color = Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d, type="response"), color = Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c("#FF483E","#0C17A1", "#777777")) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

```

### 2022-05-18 Fish Data Analysis/whole_school_data.Rmd
Update before I do my work making the 3D processor

@@
 library(ggpubr)
+library(splancs)
+library(bbmle)
+library(car)
 ```
@@
 max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}
+
+substrRight <- function(x, n){
+  substr(x, nchar(x)-n+1, nchar(x))
+}
+
+tailbeat_len = 19
+
 ```
@@
 ```{r}
-comp_data <- read.csv("Fish_Comp_Values.csv")
-comp_data <- na.omit(comp_data)
+school_data <- read.csv("Fish_School_Values.csv")
+school_data <- na.omit(school_data)
 
-comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
+school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                            mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                            mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           filter(Distance <= 4) %>%
-                           filter(abs(Speed_Diff) <= 6) %>% 
-                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
-                           mutate(fold_heading_diff = abs(fold_angle_neg_180_180_to_neg_90_90(Heading_Diff))) %>%
-                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
-                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
-                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%
+                           filter(School_Speed < 7) %>%
                            mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Flow 0","Flow 2"))) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                            mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                            mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(rad_Angle = Angle) %>%
-                           mutate(sin_Angle = sin(rad_Angle), cos_Angle = cos(rad_Angle)) %>%
                            mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))
+```
 
-                           #mutate(Angle = fold_angle_0_360_to_0_180(Angle))
+Let's make some models
+```{r}
+school_speed_anova <- aov(School_Speed ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = school_data)
 
-sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
-                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
-                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
-                               summarise(Speed_Diff = mean(Speed_Diff),
-                                         Heading_Diff = ang_mean(Heading_Diff),
-                                         Sync = mean(Sync),
-                                         Fold_Heading_Diff = mean(fold_heading_diff),
-                                         Is_Aligned = mean(Is_Aligned),
-                                         Is_Reversed = mean(Is_Reversed))
+Anova(school_speed_anova)
 
-comp_data_switch_fish <- comp_data %>% mutate(Fish3 = Fish1) %>%
+school_tbf_anova <- aov(School_TB_Freq ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = school_data)
+
+Anova(school_tbf_anova)
+
+school_polar_anova <- aov(School_Polar ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = school_data)
+
+Anova(school_polar_anova)
+
+school_nnd_anova <- aov(NND ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = school_data)
+
+Anova(school_nnd_anova)
+
+school_area_anova <- aov(Area ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = school_data)
+
+Anova(school_area_anova)
+```
+
+Now let's make some plots
+
+```{r}
+ggplot(school_data, aes(x = Flow, y = School_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Speed") +
+  xlab("") +
+  ylab("Speed (BL/s)") +
+  theme_light()
+
+ggplot(school_data, aes(x = Flow, y = School_TB_Freq, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Tailbeat Frequency") +
+  xlab("") +
+  ylab("Tailbeat Frequency (Beats/s)") +
+  theme_light()
+
+ggplot(school_data, aes(x = Flow, y = School_Polar, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Polarization") +
+  xlab("") +
+  ylab("Polarization") +
+  theme_light()
+
+ggplot(school_data, aes(x = Flow, y = NND, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
+  xlab("") +
+  ylab("NND (BL)") +
+  theme_light()
+
+ggplot(school_data, aes(x = Flow, y = Area, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Area") +
+  xlab("") +
+  ylab("School Area (BL^2)") +
+  theme_light()
+```
+```{r}
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Speed") +
+  xlab("") +
+  ylab("Speed (BL/s)") +
+  ylim(0,8) +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )
+
+ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = School_TB_Freq, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Tailbeat Frequency") +
+  xlab("") +
+  ylab("Tailbeat Frequency (Beats/s)") +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(5,6), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )
+
+ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Polarization") +
+  xlab("") +
+  ylab("Polarization") +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  #stat_compare_means(comparisons = my_comparisons, label.y = c(1, 1.25), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = NND, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
+  xlab("") +
+  ylab("NND (BL)") +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(2.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+ggplot(school_data, aes(x = interaction(Ablation,Darkness,sep=", "), y = Area, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Area") +
+  xlab("") +
+  ylab("School Area (BL^2)") +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(17), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+```
+
+```{r}
+n = 100
+
+school_sum <- school_data %>% group_by(Flow,Darkness,Ablation) %>%
+                              summarise(x_sd = mean(X_SD), y_sd = mean(Y_SD)) %>% 
+                              ungroup()
+
+school_sum_rep <- school_data %>% group_by(Flow,Darkness,Ablation) %>%
+                              summarise(x_sd = mean(X_SD), y_sd = mean(Y_SD)) %>% 
+                              ungroup() %>%
+                              slice(rep(1:n(), each = n)) %>%
+                              group_by(Flow,Darkness,Ablation) %>%
+                              mutate(angle = seq(0,2*pi,length.out=n)) %>%
+                              ungroup() %>%
+                              mutate(oval_x = x_sd*cos(angle), oval_y = y_sd*sin(angle))
+
+ggplot(data = school_sum_rep,  aes(x = oval_x, y = oval_y, color = Flow))+
+  geom_path() +
+  facet_wrap(~Darkness + Ablation) +
+  xlim(-2.1,2.1) +
+  ylim(-2.1,2.1) +
+  theme_light() +
+  coord_equal()
+
+```
+
+So now we're reading in the raw between fish comparisons in order to do the binning of polarization and speed diffs by distance
+```{r}
+raw_school_data <- read.csv("Fish_Raw_Comp_Values.csv")
+raw_school_data <- na.omit(raw_school_data)
+
+raw_school_data <- raw_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x")
+
+raw_school_data_fish_switch <- raw_school_data %>% mutate(Fish3 = Fish1) %>%
                                                    mutate(Fish1 = Fish2) %>%
@@
 
-comp_data_NND <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
-                                                                 filter(Distance == min(Distance)) %>%
+raw_school_data_both_fish <- bind_rows(raw_school_data, raw_school_data_fish_switch)
+```
+
+Now let's do the actually binning, mutating, and calculations
+
+```{r}
+
+raw_school_binned <- raw_school_data %>% mutate(Round_Dist = round_any(Distance, 1)) %>%
+                                         group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Frame_Num, Round_Dist) %>%
+                                         summarise(Mean_Speed_Diff = mean(Speed_Diff),
+                                                   Polarization = (1/(2*n()))*sqrt(sum(sin(deg2rad(c(Fish1_Heading,Fish2_Heading))))**2 + 
+                                                                               sum(cos(deg2rad(c(Fish1_Heading,Fish2_Heading))))**2 ),
+                                                   Count = n()) %>%
+                                         ungroup() %>%
+                                         mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                         group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Round_Dist) %>%
+                                         summarise(Mean_Speed_Diff = mean(Mean_Speed_Diff),
+                                                   Polarization = mean(Polarization),
+                                                   Count = sum(Count)) %>%
+                                         ungroup() %>%
+                                         filter(Round_Dist <= 3) %>%
+                                         mutate(Round_Dist = as.factor(Round_Dist))
+```
+
+```{r}
+binned_speed_dist_aov <- aov(Mean_Speed_Diff ~ Round_Dist*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = raw_school_binned)
+
+Anova(binned_speed_dist_aov)
+
+binned_polar_dist_aov <- aov(Polarization ~ Round_Dist*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = raw_school_binned)
+
+Anova(binned_polar_dist_aov)
+```
+
+```{r}
+ggplot(raw_school_binned, aes(x = Round_Dist, y = Polarization, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Distance and Available Senses on Polarization") +
+  facet_wrap(~ Flow) +
+  xlab("") +
+  ylab("Polarization (BL)") +
+  ylim(0,1) +
+  theme_light()
+
+ggplot(raw_school_binned, aes(x = Round_Dist, y = abs(Mean_Speed_Diff), fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Distance and Available Senses on Speed Difference") +
+  facet_wrap(~ Flow + Ablation + Darkness) +
+  xlab("") +
+  ylab("Speed Difference (BL/s)") +
+  ylim(0,2) +
+  theme_light()
+```
+
+Let's look at polarization just less than 2 BL away
+
+```{r}
+raw_school_less_2BL <- raw_school_data %>% filter(Distance <= 2) %>%
+                                         group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Frame_Num) %>%
+                                         summarise(Mean_Speed_Diff = mean(Speed_Diff),
+                                                   Polarization = (1/(2*n()))*sqrt(sum(sin(deg2rad(c(Fish1_Heading,Fish2_Heading))))**2 + 
+                                                                               sum(cos(deg2rad(c(Fish1_Heading,Fish2_Heading))))**2 ),
+                                                   Count = n()) %>%
+                                         ungroup() %>%
+                                         mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                         group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                         summarise(Mean_Speed_Diff = mean(Mean_Speed_Diff),
+                                                   Polarization = mean(Polarization),
+                                                   Count = sum(Count)) %>%
+                                         ungroup()
+```
+
+```{r}
+school_polar_anova_2BL <- aov(Polarization ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = raw_school_less_2BL)
+
+Anova(school_polar_anova_2BL)
+
+ggplot(raw_school_less_2BL, aes(x = Flow, y = Polarization, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Polarization") +
+  xlab("") +
+  ylab("Polarization") +
+  theme_light()
+```
+
+Okay so now we'll do the proportion of fish in each condition that are farther than some distance away
+
+```{r}
+school_dist_props <- raw_school_data %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                         group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                         summarise(P_LE_1 = sum(Distance <= 1) / n() * 100,
+                                                   P_LE_2 = sum(Distance <= 2) / n() * 100,
+                                                   P_LE_3 = sum(Distance <= 3) / n() * 100)
+
+ggplot(school_dist_props, aes(x = Flow, y = P_LE_1, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Percent of Fish Within 1 BL") +
+  xlab("") +
+  ylab("Percent (%)") +
+  theme_light()
+
+ggplot(school_dist_props, aes(x = Flow, y = P_LE_2, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Percent of Fish Within 2 BL") +
+  xlab("") +
+  ylab("Percent (%)") +
+  theme_light()
+
+ggplot(school_dist_props, aes(x = Flow, y = P_LE_3, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Percent of Fish Within 3 BL") +
+  xlab("") +
+  ylab("Percent (%)") +
+  theme_light()
+
+```
+Now let's try and show if they form small groupings, or if they are just spaced out more
+We're going to plot distance to each neighbor on average
+
+```{r}
+d_to_each_neighbor <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                          group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Frame_Num, Fish1) %>%
+                                          mutate(Neighbor_Num = min_rank(Distance)) %>%
+                                          ungroup() %>%
+                                          group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Neighbor_Num) %>%
+                                          summarise(Neighbor_Dist = mean(Distance))
+```
+
+```{r}
+ggplot(d_to_each_neighbor %>% filter(Neighbor_Num <= 3), aes(x = as.factor(Neighbor_Num), y = Neighbor_Dist, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  facet_wrap(~ Flow) + 
+  ggtitle("Distance to Each Neighboring Fish") +
+  xlab("") +
+  ylab("Distance (BL)") +
+  theme_light()
+```
+Okay.
+Better idea.
+Let's see where the biggest distance difference is between fish!
+So if they are all evenly spaced you would see that the largest difference would be randomly between any of them.
+If they tend to be between the second closest and third then you'll see it skewed smaller.
+
+```{r}
+min_diff_dist_neighbor <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                              group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Frame_Num, Fish1) %>%
+                                              arrange(Distance) %>%
+                                              mutate(Neighbor_Dist_Diff = lead(Distance) - Distance) %>%
+                                              slice_max(order_by = Neighbor_Dist_Diff) %>%
+                                              ungroup() %>%
+                                              mutate(Biggest_Diff_Neighbor = as.numeric(substrRight(Fish2,1))) %>%
+                                              group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                              summarise(Biggest_Diff_Neighbor_Mean_Log = exp(mean(log(Biggest_Diff_Neighbor), na.rm = TRUE))) %>%
+                                              ungroup()
+```
+
+```{r}
+ggplot(min_diff_dist_neighbor, aes(x = Flow, y = Biggest_Diff_Neighbor_Mean_Log, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_violin() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Average Neighbor with the Largest Difference in Distance") +
+  xlab("") +
+  ylab("Neighbor Number") +
+  theme_light()
+```
+In the end this has not been helpful.
+Or they are all the same, but I think the bounded data makes this difficult.
+I'm not sure what this really shows in the end.
+I thought it would show a clearer pattern, but they all seem to be about the same.
+So this says that most often the largest jump is between the 4th and 5th.
+But how can that go both ways?
+
+What if instead we look at the percent of time there is only 1, 2 etc fish within 2 BL?
+
+```{r}
+count_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
+                                                summarise(Only_2_Fish_in_2BL = ifelse(sum(Distance <= 2) <= 1, 1, 0)) %>%
+                                                ungroup() %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                                summarise(Percent_Only_2_Fish_in_2BL = sum(Only_2_Fish_in_2BL)/n() * 100) %>%
+                                                ungroup()
+```
+
+```{r}
+percent_with_2BL_aov <- aov(Percent_Only_2_Fish_in_2BL ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = count_within_2)
+Anova(percent_with_2BL_aov)
+
+ggplot(count_within_2, aes(x = Flow, y = Percent_Only_2_Fish_in_2BL, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Percent of time there are one or less fish with 2 BL") +
+  xlab("") +
+  ylab("Percent of time there are one or less fish within 2 BL (%)") +
+  ylim(-5,105) +
+  theme_light()
+```
+
+Now we are looking at the percent of time there is just 1 fish within 2 BL
+
+```{r}
+only_1_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
+                                                summarise(Only_1_Fish_in_2BL = ifelse(sum(Distance <= 2) == 1, 1, 0)) %>%
+                                                ungroup() %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                                summarise(Percent_Only_1_Fish_in_2BL = sum(Only_1_Fish_in_2BL)/n() * 100) %>%
                                                 ungroup()
 
-comp_data_near_3 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
-                                                                 slice_min(Distance, n = 3) %>%
+only_1_within_2_aov <- aov(Percent_Only_1_Fish_in_2BL ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = only_1_within_2)
+Anova(only_1_within_2_aov)
+
+ggplot(only_1_within_2, aes(x = Flow, y = Percent_Only_1_Fish_in_2BL, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Percent of time there is just one other fish within 2 BL") +
+  xlab("") +
+  ylab("Percent of time there is just one other fish within 2 BL(%)") +
+  ylim(-5,105) +
+  theme_light()
+
+only_0_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
+                                                summarise(Only_0_Fish_in_2BL = ifelse(sum(Distance <= 2) == 0, 1, 0)) %>%
                                                 ungroup() %>%
-                                                                 distinct(Distance, .keep_all= TRUE)
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                                summarise(Percent_Only_0_Fish_in_2BL = sum(Only_0_Fish_in_2BL)/n() * 100) %>%
+                                                ungroup()
+
+only_0_within_2_aov <- aov(Percent_Only_0_Fish_in_2BL ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = only_0_within_2)
+Anova(only_0_within_2_aov)
+
+ggplot(only_0_within_2, aes(x = Flow, y = Percent_Only_0_Fish_in_2BL, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Percent of time there are one or less fish with 2 BL") +
+  xlab("") +
+  ylab("Percent of time there are one or less fish within 2 BL (%)") +
+  ylim(-5,105) +
+  theme_light()
 ```
+
+```{r}
+count_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
+                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
+                                                ungroup() %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
+                                                ungroup()
+
+ggplot(count_within_2, aes(x = Flow, y = Mean_Count_Fish_in_2BL, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Number of Fish within 2 BL") +
+  xlab("") +
+  ylab("Number of Fish within 2 BL") +
+  theme_light()
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )
+
+ggplot(count_within_2, 
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Mean size of group within 2BL") +
+  xlab("") +
+  ylab("Mean size of group within 2BL (# of Fish)") +
+  ylim(0,9) +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+  scale_y_continuous(breaks=c(0,2,4,6,8))
+```
+
+```{r}
+only_n_within_2 <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
+                                                summarise(Only_0_Fish_in_2BL = ifelse(sum(Distance <= 2) == 0, 1, 0),
+                                                          Only_1_Fish_in_2BL = ifelse(sum(Distance <= 2) == 1, 1, 0),
+                                                          Only_2_Fish_in_2BL = ifelse(sum(Distance <= 2) == 2, 1, 0),
+                                                          Only_3_Fish_in_2BL = ifelse(sum(Distance <= 2) == 3, 1, 0),
+                                                          Only_4_Fish_in_2BL = ifelse(sum(Distance <= 2) == 4, 1, 0),
+                                                          Only_5_Fish_in_2BL = ifelse(sum(Distance <= 2) == 5, 1, 0),
+                                                          Only_6_Fish_in_2BL = ifelse(sum(Distance <= 2) == 6, 1, 0),
+                                                          Only_7_Fish_in_2BL = ifelse(sum(Distance <= 2) == 6, 1, 0)) %>%
+                                                ungroup() %>%
+                                                pivot_longer(c(Only_0_Fish_in_2BL,Only_1_Fish_in_2BL,Only_2_Fish_in_2BL,Only_3_Fish_in_2BL,
+                                                               Only_4_Fish_in_2BL,Only_5_Fish_in_2BL,Only_6_Fish_in_2BL,Only_7_Fish_in_2BL),
+                                                             names_to = "Num_Fish_In_2_BL", values_to = "count") %>%
+                                                mutate(Num_Fish_In_2_BL = gsub('Only_', '', gsub('_Fish_in_2BL', '', Num_Fish_In_2_BL))) %>%
+                                                group_by(Flow, Ablation, Darkness, Num_Fish_In_2_BL) %>%
+                                                summarise(Percent = sum(count)/n() * 100) %>%
+                                                ungroup() %>%
+                                                mutate(Num_Fish_In_2_BL = fct_rev(Num_Fish_In_2_BL))
+
+ggplot(only_n_within_2, aes(y=Percent, x=interaction(Ablation,Darkness,sep=", "), fill = Num_Fish_In_2_BL)) + 
+    geom_bar(position="fill", stat="identity") + 
+    facet_wrap(~ Flow) +
+    theme_light() +
+    xlab("")
+```
+
+Calculating Group Speed over Individual Speed
+
+```{r}
+speed_whole_school <- school_data %>% rename(Tailbeat_Num = X)
+
+fish_speed_division <- speed_whole_school %>% inner_join(indiv_data_4_speed, by = c("Year", "Month", "Day", "Trial", "Tailbeat_Num")) %>%
+                                              mutate(Divided_Speed = School_Speed/Mean_Speed)
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light") )
+
+ggplot(fish_speed_division, aes(x = interaction(Ablation,Darkness,sep=", "), y = Divided_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
+  ggtitle("Effect of Available Senses on School Speed") +
+  xlab("") +
+  ylab("Speed (BL/s)") +
+  ylim(0,8) +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(6.5,7.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+```
+
+How many nearest neighbors do they have in one trial?
+
+```{r}
+num_neighbors_df <- raw_school_data_both_fish %>% select(-c(X,Angle,Fish1_Heading,Fish2_Heading,Heading_Diff,Speed_Diff,Sync)) %>%
+                                                  mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                  group_by(Year, Month, Day, Trial, Tailbeat, Fish1, Fish2,
+                                                           Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
+                                                  summarise(Distance = mean(Distance)) %>%
+                                                  ungroup() %>%
+                                                  group_by(Year, Month, Day, Trial, Tailbeat, Fish1) %>%
+                                                  filter(Distance == min(Distance)) %>%
+                                                  ungroup() %>%
+                                                  group_by(Year, Month, Day, Trial, Fish1, Fish2) %>%
+                                                  mutate(n_encounters = n()) %>%
+                                                  ungroup() %>%
+                                                  group_by(Year, Month, Day, Trial, Fish1) %>%
+                                                  mutate(prop_encounters = n_encounters/n(),
+                                                         n_neightbors = length(unique(Fish2))) %>%
+                                                  ungroup()
+
+num_neighbors_df_model_hist <- num_neighbors_df %>% group_by(Year, Month, Day, Trial, Fish1,
+                                                             Flow, Ablation, Darkness, Flow_Ablation_Darkness,) %>%
+                                                    summarize(n_neightbors = mean(n_neightbors))
+
+num_neighbors_for_bar_df <- num_neighbors_df %>% group_by(Flow, Ablation, Darkness,n_neightbors) %>%
+                                                  mutate(Count_N_Neighbors = n()) %>%
+                                                  ungroup() %>%
+                                                  group_by(Flow, Ablation, Darkness) %>%
+                                                  mutate(total = n()) %>%
+                                                  ungroup() %>%
+                                                  group_by(Flow, Ablation, Darkness, Flow_Ablation_Darkness,n_neightbors) %>%
+                                                  summarise(Percent = mean(Count_N_Neighbors/total)) %>%
+                                                  ungroup() %>%
+                                                  group_by(Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
+                                                  mutate(group_p_total = sum(Percent),
+                                                         n_neightbors = fct_rev(factor(n_neightbors)))
+
+```
+
+```{r}
+ggplot(num_neighbors_df_model_hist, aes(x = n_neightbors, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_histogram() + 
+  scale_fill_manual(values=c("#AAAAAA", "#4CB944", "#00A7E1")) +
+  facet_wrap(~ Flow_Ablation_Darkness, strip.position = "bottom")+
+  theme_light()
+
+ggplot(num_neighbors_for_bar_df, aes(y = Percent, x=interaction(Ablation,Darkness,sep=", "), fill = n_neightbors)) + 
+    geom_bar(position="fill", stat="identity") + 
+    facet_wrap(~ Flow) +
+    theme_light() +
+    xlab("")
+```
+model time?
+
+```{r}
+m0 <- glm(n_neightbors ~ 1, data = num_neighbors_df_model_hist)
+m_f <- glm(n_neightbors ~ Flow, data = num_neighbors_df_model_hist)
+m_a <- glm(n_neightbors ~ Ablation, data = num_neighbors_df_model_hist)
+m_d <- glm(n_neightbors ~ Darkness, data = num_neighbors_df_model_hist)
+m_f_a <- glm(n_neightbors ~ Flow*Ablation, data = num_neighbors_df_model_hist)
+m_f_d <- glm(n_neightbors ~ Flow*Darkness, data = num_neighbors_df_model_hist)
+m_a_d <- glm(n_neightbors ~ Ablation*Darkness, data = num_neighbors_df_model_hist)
+m_f_a_d <- glm(n_neightbors ~ Flow*Ablation*Darkness, data = num_neighbors_df_model_hist)
+best_groups <- glm(n_neightbors ~ 0+Flow:Ablation, data = num_neighbors_df_model_hist)
+
+ICtab(m0,m_f,m_a,m_d,m_f_a,m_f_d,m_a_d,m_f_a_d)
+
+summary(m_f_a)
+summary(best_groups)
+Anova(m_f_a)
+
+```
+
+Now 2BL with Simulated Data!
+
+```{r}
+raw_school_data_simul <- read.csv("Fish_Raw_Comp_Values_Plus_Simul.csv") %>% select(-c(X.1,X.2,X.3,X.4,X.5))
+raw_school_data_simul <- na.omit(raw_school_data_simul)
+
+raw_school_data_simul <- raw_school_data_simul %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", ifelse(Ablation == "Y","Ablated",Ablation))) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", ifelse(Darkness == "Y", "Dark", Darkness))) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x")
+
+raw_school_data_simul_fish_switch <- raw_school_data_simul %>% mutate(Fish3 = Fish1) %>%
+                                                   mutate(Fish1 = Fish2) %>%
+                                                   mutate(Fish2 = Fish3) %>%
+                                                   select(-c(Fish3))
+
+raw_school_data_simul_both_fish <- bind_rows(raw_school_data_simul, raw_school_data_simul)
+
+count_within_2_simul <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
+                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
+                                                ungroup() %>%
+                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
+                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
+                                                ungroup()
+
+ggplot(count_within_2_simul, aes(x = Flow, y = Mean_Count_Fish_in_2BL, fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot() +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1", "#777777")) +
+  ggtitle("Number of Fish within 2 BL") +
+  xlab("") +
+  ylab("Number of Fish within 2 BL") +
+  theme_light()
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
+                        c("No Ablation, Light", "Ablated, Light"),
+                        c("No Ablation, Dark", "Simulated, Simulated"))
+
+ggplot(count_within_2_simul %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1","#777777")) +
+  ggtitle("Mean size of group within 2BL") +
+  xlab("") +
+  ylab("Mean size of group within 2BL (# of Fish)") +
+  ylim(0,9) +
+  theme_light() +
+  facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5,6), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) +
+  scale_y_continuous(breaks=c(0,2,4,6,8))
+
+anova_model <- aov(Mean_Count_Fish_in_2BL+1 ~ Flow * Ablation * Darkness, data = count_within_2_simul)
+anova(anova_model)
+
+TukeyHSD(anova_model)
+
+t_test_data <- count_within_2_simul %>% filter(Flow == "Still Water" & Darkness %in% c("Dark", "Simulated"))
+t.test(Mean_Count_Fish_in_2BL ~ Darkness, data = t_test_data)
+```
+
+#### Now trying to see how long fish stay within 2 BL in the different conditions.
+
+```{r}
+raw_school_data_simul <- rbind(read.csv("Fish_Raw_Comp_Values_Plus_Simul.csv") %>% select(-c(X.1)),
+                               read.csv("Data Sim/Fish_Raw_Comp_Values_Sim.csv"))
+raw_school_data_simul <- na.omit(raw_school_data_simul) %>% filter(Flow == "0")
+
+raw_school_data_simul <- raw_school_data_simul %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", ifelse(Ablation == "Y","Ablated",Ablation))) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", ifelse(Darkness == "Y", "Dark", Darkness))) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                          mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x")
+
+raw_school_data_simul_fish_switch <- raw_school_data_simul %>% mutate(Fish3 = Fish1) %>%
+                                                   mutate(Fish1 = Fish2) %>%
+                                                   mutate(Fish2 = Fish3) %>%
+                                                   select(-c(Fish3))
+
+raw_school_data_simul_both_fish <- bind_rows(raw_school_data_simul, raw_school_data_simul) %>% distinct()
+
+subset_data <- raw_school_data_simul_both_fish %>% filter(Year == 1995 & Month == 9 & Day == 7 & Trial == 1 & Fish1 == "individual7" & Fish2 == "individual2")
+
+time_within_2_simul <- raw_school_data_simul_both_fish %>% filter(Distance <= 2) %>%
+                                                           group_by(Year, Month, Day, Trial, Fish1, Fish2) %>%
+                                                           mutate(frame_diff = Frame_Num - lag(Frame_Num)) %>%
+                                                           mutate(frame_diff = ifelse(is.na(frame_diff), 1, frame_diff)) %>%
+                                                           #This next line adds a grouping variable by keeping all the values after a jump in frame
+                                                           # larger, and the same as each other
+                                                           mutate(frame_grouper = cumsum(frame_diff) - 0:(n()-1)) %>%
+                                                           group_by(Year, Month, Day, Trial, Ablation, Darkness, Fish1, Fish2, frame_grouper) %>%
+                                                           #mutate(Together_Secs = max(Frame_Num) - min(Frame_Num))
+                                                           #group_by(Year, Month, Day, Trial, Ablation, Darkness, Fish1, Fish2, frame_grouper) %>%
+                                                           #The mean is just to make it into one number, it's all the same
+                                                           summarize(Together_Secs = max((max(Frame_Num) - min(Frame_Num))/60))
+
+```
+
+```{r}
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
+                        c("No Ablation, Light", "Ablated, Light"),
+                        c("No Ablation, Dark", "Simulated, Simulated"))
+
+ggplot(time_within_2_simul,
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Together_Secs,
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_boxplot(outlier.shape = NA) +
+  #guides(fill = guide_legend(title = "Condition")) +
+  #scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
+  ggtitle("Mean size of group within 2BL") +
+  xlab("") +
+  ylab("Mean size of group within 2BL (# of Fish)") +
+  #sylim(0,9) +
+  theme_light() +
+  #facet_wrap(~ Flow, strip.position = "bottom")+
+  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
+  #stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5,6), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) +
+  scale_y_continuous(breaks=c(0,2,4,6,8))
+```

### 2022-05-18 2Dto3D/DLT_Converter.py

@@ -1,0 +1,132 @@
+import os
+import numpy as np
+import pandas as pd
+import math
+import plotly.express as px
+from scipy import linalg
+
+#Header list for reading the raw location CSVs
+header = list(range(4))
+
+#Get all te files
+v1_files = os.listdir("V1 CSVs")
+v2_files = os.listdir("V2 CSVs")
+dlt_coef_files = os.listdir("DLT Coefs")
+
+num_fish = 8
+body_parts = ["head","midline2","tailbase","tailtip"]
+
+def DLTdvRecon(Ls, uvs):
+
+    #uvs are in format [[v1_xs,v1_ys],[v2_xs,v2_ys]]
+
+    Ls = np.array(Ls)
+    uvs = np.array(uvs)
+
+    #http://kwon3d.com/theory/dlt/dlt.html#3d
+
+    #https://github.com/tlhedrick/dltdv/blob/master/DLTdv8a_internal/dlt_reconstruct_v2.m
+
+    m1 = np.zeros((4,3))
+    m2 = np.zeros((4,1))
+
+    m1[0:3:2,0] = uvs[:,0] * Ls[:,8] - Ls[:,0]
+    m1[0:3:2,1] = uvs[:,0] * Ls[:,9] - Ls[:,1]
+    m1[0:3:2,2] = uvs[:,0] * Ls[:,10] - Ls[:,2]
+
+    m1[1:4:2,0] = uvs[:,1] * Ls[:,8] - Ls[:,4]
+    m1[1:4:2,1] = uvs[:,1] * Ls[:,9] - Ls[:,5]
+    m1[1:4:2,2] = uvs[:,1] * Ls[:,10] - Ls[:,6]
+
+    m2[0:3:2,0] = Ls[:,3] - uvs[:,0]
+    m2[1:4:2,0] = Ls[:,7] - uvs[:,1]
+
+    xyz = linalg.lstsq(m1, m2, lapack_driver = "gelsy")[0]
+
+    return xyz
+
+
+single_file =  "" #"2021_10_08_26_LN_DY_F0_V2DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered"
+
+# We have more v1 files than v2, so we do this for every v2 file
+for v2f in v2_files:
+    if v2f.endswith(".csv") and single_file in v2f:
+
+        #Get a long ID for the matching V1, short ID for the DLT
+        file_id = v2f[0:22]
+        short_id = v2f[0:10]
+
[…]

### 2022-05-18 2Dto3D/DLT_Plotter.py

@@ -1,0 +1,61 @@
+import os
+import numpy as np
+import pandas as pd
+import math
+import plotly.express as px
+from scipy import linalg
+
+#Header list for reading the raw location CSVs
+header = list(range(4))
+
+num_fish = 8
+body_parts = ["head","midline2","tailbase","tailtip"]
+
+file_folder = "Final 3D/"
+
+three_d_files = os.listdir("Final 3D")
+
+for file_name in three_d_files:
+    if file_name.endswith(".csv"):
+
+        file_path = file_folder+file_name
+
+        fish_raw_data = pd.read_csv(file_path, index_col=0, header=header)
+
+        #They asked me why by god would I ever do this in pandas and not dplyr like I ACTUALLY KNOW HOW TO DO
+        # but plotly is better and I have code for that, and by god I will learn how to use pandas
+
+        #So first we melt it to make all the column names into rows
+        #This is great! Other than we still want x, y, and z to be their own columns and not just labeled
+        df = pd.melt(fish_raw_data)
+
+        #Let's rename things to what they actually are
+        df = df.rename(columns={"variable_0": "Scorer", "variable_1": "Fish", "variable_2": "BodyPart", "variable_3": "Point"})
+
+        #So now I add the Frame to this because I will need to group by that otherwise there is overlap between labels
+        df['Frame'] = df.groupby(['Scorer','Fish','BodyPart','Point']).cumcount()+1
+
+        #So now we pivot from the Point column, into seperate ones for x, y, and z
+        df = df.pivot(index = ['Scorer','Fish','BodyPart','Frame'], columns='Point', values='value')
+
+        #Then we have to reset the index so that we can use 'Scorer','Fish','BodyPart','Frame' as data columns
+        df = df.reset_index()
+
+        #THANKS STACK EXCHANGE WOOOOOOO
+
+        #Now we graph it, nice and easy
+
+        #Though the axies keep shifting weirdly so not my fave
+        fig = px.scatter_3d(df,x="x", y="y", z="z", color="Fish", animation_frame="Frame", hover_data = ["BodyPart"],
+                               range_x=[df["x"].min()-0.05,df["x"].max()+0.05],
+                               range_y=[df["y"].min()-0.05,df["y"].max()+0.05],
+                               range_z=[df["z"].min()-0.05,df["z"].max()+0.05],
+                               color_continuous_scale = "rainbow")
+
[…]

### 2022-05-18 2Dto3D/DLTrecon.py

@@ -1,270 +1,0 @@
-import numpy as np
-import pandas as pd
-import math
-import plotly.express as px
-from scipy import linalg
-
-def DLC_CSV_to_dict(num_fish,fish_parts,file):
-	data_points = ["x","y","prob"]
-		
-	fish_dict = {}
-
-	for i in range(num_fish):
-		fish_dict[i] = {}
-		for part in fish_parts:
-			fish_dict[i][part] = {}
-			for point in data_points:
-				fish_dict[i][part][point] = []
-		
-	# To open Workbook 
-	fish_data = pd.read_csv(file)
-
-	cols = fish_data.columns
-	time_points = len(fish_data[cols[1]])
-
-	for i in range(0,len(cols)-1):
-		#Every 3 [x,y,p] times number of body parts columns we move onto a new fish
-		fish_num = math.floor(i/(n_b_parts*3))
-		#Every 3 [x,y,p] columns we move to a new body part, and we rotate through all
-		fish_part = fish_parts[int(math.floor(i/3)%n_b_parts)]
-		#rotate through the 3 [x,y,p] data type columns
-		data_point = data_points[i%3]
-		#Store the column data in the dict
-		#Ignore the first 3 rows as those are column labels
-		#print(fish_num,fish_part,data_point)
-
-		fish_dict[fish_num][fish_part][data_point] = fish_data[cols[i+1]][3:time_points].astype(float).to_numpy()
-
-	return(fish_dict,time_points-3)
-
-#This only does one point at a time!!!
-def DLTrecon(Ls, uvs):
-	'''
-	From: https://github.com/Fishified/Tracker3D/blob/master/DLT.py
-	Reconstruction of object point from image point(s) based on the DLT parameters.
-	This code performs 2D or 3D DLT point reconstruction with any number of views (cameras).
-	For 3D DLT, at least two views (cameras) are necessary.
-	Inputs:
-	 nd is the number of dimensions of the object space: 3 for 3D DLT and 2 for 2D DLT. (for me nd is always 3)
[…]

### 2022-05-18 3D_data_files_to_csv_4P.py

@@ -1,0 +1,948 @@
+#This is in effect the same code as before, but now in 3D!
+
+#This is the new code that will process all the CSVs of points into twos CSVs for R
+# One will have fish summary stats, while the other will have the fish comparison values
+#For the fish one the columns will be:
+# Year, Month, Day, Trial, Abalation, Darkness, Flow, Fish, Tailbeat Num, Heading, Speed, TB Frequency
+
+# For the between fish comparisons the columns will be: 
+# Year, Month, Day, Trial, Abalation, Darkness, Flow, Fishes, Tailbeat Num, X Distance, Y Distance, Distance, Angle, Heading Diff, Speed Diff, Synchonization
+
+#This is a lot of columns. But now instead of having multiple .npy files this will create an object for each of the positional data
+# CSVs and then add them all together in the end. This will ideally make things easier to graph for testing, and not require so many 
+# nested for loops. Fish may be their own objects inside of the trial objects so that they can be quickly compared. Which may mean that I need to 
+# take apart fish_core_4P.py. In the end I think a lot of this will be easier to do with pandas and objects instead of reading line by line.
+
+from scipy.signal import hilbert, savgol_filter
+from scipy.spatial import ConvexHull
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+from matplotlib import gridspec 
+import pandas as pd
+import numpy as np
+import random
+import math
+import os, sys
+
+#Matplotlib breaks with Qt now in big sur :(
+mpl.use('tkagg')
+
+fps = 60
+
+#The moving average window is more of a guess tbh
+moving_average_n = 35
+
+#Tailbeat len is the median of all frame distances between tailbeats
+tailbeat_len = 19
+
+#Fish len is the median of all fish lengths in pixels
+fish_len = 193
+
+#Header list for reading the raw location CSVs
+header = list(range(4))
+
+def get_dist_np(x1s,y1s,x2s,y2s):
+    dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2)
+    return dist
+
+def get_fish_length(fish):
+    return get_dist_np(fish.head_x,fish.head_y,fish.midline_x,fish.midline_y) + get_dist_np(fish.midline_x,fish.midline_y,fish.tailbase_x,fish.tailbase_y) + get_dist_np(fish.tailbase_x,fish.tailbase_y,fish.tailtip_x,fish.tailtip_y)
+
[…]

### 2022-05-18 Fish Data Analysis/Data Sim/data_randomizer.py

@@ -1,0 +1,38 @@
+import pandas as pd
+
+#Header list for reading the raw location CSVs
+header = list(range(4))
+
+#Fish 1 is columns 0 to 11
+#Fish 2 is columns 12 to 23
+#Fish 3 is columns 24 to 35
+#Fish 4 is columns 36 to 47
+#Fish 5 is columns 48 to 59
+#Fish 6 is columns 60 to 71
+#Fish 7 is columns 72 to 83
+#Fish 8 is columns 84 to 95
+
+data_folder = "Finished_Fish_Data_4P_gaps_randomized/"
+
+files = ["2020_06_29_20_TN_DN_F0_VDLC_resnet50_L8FV4PFeb22shuffle1_100000_bx_filtered.csv",
+"2020_07_28_10_TN_DN_F0_V1DLC_resnet50_L8FV4PFeb22shuffle1_100000_bx_filtered.csv",
+"2020_07_28_11_TN_DN_F0_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv",
+"2020_07_28_24_TN_DN_F0_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv",
+"2021_03_25_01_TN_DN_F0_V1DLC_resnet50_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv",
+"2021_03_25_10_TN_DN_F0_V1DLC_resnet50_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv",
+"2021_03_25_12_TN_DN_F0_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv",
+"2021_03_25_22_TN_DN_F0_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv",
+"2021_03_25_24_TN_DN_F0_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv"]
+
+data_to_fill = pd.read_csv(data_folder+files[0], index_col=0, header=header)
+
+all_data_arr = [pd.read_csv(data_folder+f, index_col=0, header=header) for f in files]
+
[…]

### 2022-05-18 data_files_to_csv_4P.py

@@ -12,6 +12,7 @@
 # take apart fish_core_4P.py. In the end I think a lot of this will be easier to do with pandas and objects instead of reading line by line.
 
 from scipy.signal import hilbert, savgol_filter
+from scipy.spatial import ConvexHull
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 from matplotlib import gridspec 
@@ -19,7 +20,7 @@ import pandas as pd
 import numpy as np
 import random
 import math
-import os
+import os, sys
 
 #Matplotlib breaks with Qt now in big sur :(
 mpl.use('tkagg')
@@ -329,6 +330,20 @@ class fish_comp:
         self.heading_diff = np.rad2deg(np.arctan2(np.sin(np.deg2rad(self.f1.heading-self.f2.heading)),
                                                   np.cos(np.deg2rad(self.f1.heading-self.f2.heading))))
 
+    def calc_heading_diff_filtered(self):
+        #Makes sure that head wiggle doesn't mess up polarization
+        f1_heading_og = self.f1.heading
+        f2_heading_og = self.f2.heading
+
+        self.f1.heading = savgol_filter(self.f1.heading,tailbeat_len,1)
+        self.f2.heading = savgol_filter(self.f2.heading,tailbeat_len,1)
+
+        self.heading_diff = np.rad2deg(np.arctan2(np.sin(np.deg2rad(self.f1.heading-self.f2.heading)),
+                                                  np.cos(np.deg2rad(self.f1.heading-self.f2.heading))))
+
+        for i in range(len(self.f1.heading)):
+            print(f1_heading_og[i],f2_heading_og[i],self.f1.heading[i],self.f2.heading[i],self.heading_diff[i])
+
     def calc_speed_diff(self):
         self.speed_diff = self.f1.speed - self.f2.speed
 
@@ -546,12 +561,15 @@ class school_comps:
         self.nearest_neighbor_distance = []
         self.group_tailbeat_cor = []
 
+        self.school_areas = []
+
         self.calc_school_pos_stats()
         self.calc_school_speed()
         self.calc_school_tb_freq()
         self.calc_school_polarization()
         self.calc_nnd()
         self.calc_tailbeat_cor()
+        self.calc_school_area()
 
     def calc_school_pos_stats(self):
         school_xs = [fish.head_x for fish in self.fishes]
@@ -560,8 +578,8 @@ class school_comps:
[…]

### 2022-05-18 Fish Data Analysis/Final_Plots_3D.Rmd
Still some bugs in distance, but it all runs

--- 2022-05-18 Fish Data Analysis/Final_Plots.Rmd
@@
 ```{r}
-school_data <- read.csv("Fish_School_Values.csv")
+school_data <- read.csv("Fish_School_Values_3D.csv")
 school_data <- na.omit(school_data)
@@
 
-ggsave("Final Graphs/School_NND.png")
+ggsave("Final Graphs/School_NND_3D.png")
 ```
@@
 ```{r}
-raw_school_data <- read.csv("Fish_Raw_Comp_Values.csv")
+raw_school_data <- read.csv("Fish_Raw_Comp_Values_3D.csv")
 raw_school_data <- na.omit(raw_school_data)
@@
 
-ggsave("Final Graphs/Mean_Group_Size.png")
+ggsave("Final Graphs/Mean_Group_Size_3D.png")
 ```
@@
 
-ggsave("Final Graphs/Polarization.png")
+ggsave("Final Graphs/Polarization_3D.png")
 ```
@@
 
-ggsave("Final Graphs/Num_Aligned_Fish_2BL.png")
+ggsave("Final Graphs/Num_Aligned_Fish_2BL_3D.png")
 
@@
 
-indiv_data <- read.csv("Fish_Individual_Values.csv")
+indiv_data <- read.csv("Fish_Individual_Values_3D.csv")
 indiv_data <- na.omit(indiv_data)
@@
 
-ggsave("Final Graphs/School_Speed_Over_Indiv_Speed.png")
+ggsave("Final Graphs/School_Speed_Over_Indiv_Speed_3D.png")
 
 ```
-
-### Turning Bias
-
-```{r}
-turning_data <- read.csv("Annushka_Turning_Data_Wall.csv") %>%
-                           filter(Next.to.Wall == 0) %>%
-                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
-                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>%
-                           filter(Flow %in% allowed_flow_type)
-
-turning_data_sum <- turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-
-turning_data_sum_one <- turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-```
-
-```{r}
-ggplot(turning_data_sum, aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
-  geom_point()+
-  geom_line(alpha = 0.25) +
-  facet_wrap(~ Darkness + Ablation) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
-
-ggsave("Final Graphs/Right_Turn_Prob.png")
-```
-
-```{r}
-#mi_fr_d <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data, family = binomial)
-
-mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)
-
-ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Ablation))+
-  geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
-
-ggsave("Final Graphs/Best_Model_Right_Turn_Prob.png")
-
-```
-
-### Simulated # of fish within 2 BL
-
-```{r}
-raw_school_data_simul <- rbind(read.csv("Fish_Raw_Comp_Values.csv"),
-                               read.csv("Data Sim/Fish_Raw_Comp_Values_Random.csv"))
-raw_school_data_simul <- na.omit(raw_school_data_simul) %>% filter(Flow == "0")
-
-raw_school_data_simul <- raw_school_data_simul %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", ifelse(Ablation == "Y","Ablated","Simulated"))) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", ifelse(Darkness == "Y", "Dark", "Simulated"))) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           separate(Fish, c("Fish1", "Fish2"),sep="x")
-
-raw_school_data_simul_fish_switch <- raw_school_data_simul %>% mutate(Fish3 = Fish1) %>%
-                                                   mutate(Fish1 = Fish2) %>%
-                                                   mutate(Fish2 = Fish3) %>%
-                                                   select(-c(Fish3))
-
-raw_school_data_simul_both_fish <- bind_rows(raw_school_data_simul, raw_school_data_simul)
-
-count_within_2_simul <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
-                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
-                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
-                                                ungroup() %>%
-                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
-                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
-                                                ungroup()
-```
-
-```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
-                        c("No Ablation, Light", "Ablated, Light"),
-                        c("No Ablation, Dark", "Simulated, Simulated"))
-
-ggplot(count_within_2_simul %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
-  ggtitle("Mean size of group within 2BL") +
-  xlab("") +
-  ylab("Mean size of group within 2BL (# of Fish)") +
-  ylim(0,9) +
-  theme_light() +
-  facet_wrap(~ Flow, strip.position = "bottom")+
-  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
-  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5,6), label = "p.signif", hide.ns = TRUE) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) +
-  scale_y_continuous(breaks=c(0,2,4,6,8))
-
-ggsave("Final Graphs/Simmed_Group_Num_in_2_BL.png")
-
-```
-
-### Simluated Data Aligned within 2BL
-
-```{r}
-
-max_offset <- 15
-
-count_within_2_simul_aligned <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
-                                                        filter(abs(Heading_Diff) < max_offset) %>%
-                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
-                                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
-                                                        ungroup() %>%
-                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
-                                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
-                                                        ungroup()
-```
-
-```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
-                        c("No Ablation, Light", "Ablated, Light"),
-                        c("No Ablation, Dark", "Simulated, Simulated"))
-
-ggplot(count_within_2_simul_aligned %>% filter(Flow == "Still Water"), 
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL,
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
-  ggtitle("Mean size of group within 2BL") +
-  xlab("") +
-  ylab("Number of Aligned Fish within 2BL (# of Fish)") +
-  theme_light() +
-  facet_wrap(~ Flow, strip.position = "bottom")+
-  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
-  stat_compare_means(comparisons = my_comparisons, label.y = c(4.5,3.5,4), label = "p.signif", hide.ns = TRUE) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-  ylim(0,7) +
-  scale_y_continuous(breaks=c(0,2,4,6,8))
-
-ggsave("Final Graphs/Simmed_Aligned_Group_Num_in_2_BL.png")
-
-```
-
-### Simulated Turning Bias
-
-```{r}
-turning_data_sim <- read.csv("Annushka_Turning_Data_Simmed.csv") %>% 
-                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", ifelse(Ablation == "LY","Ablated",Ablation))) %>%
-                           mutate(Darkness = ifelse(Darkness == "DN", "Light", ifelse(Darkness == "DY", "Dark", Darkness))) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
-                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0))
-
-turning_data_sim_sum <- turning_data_sim %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-
-turning_data_sim_sum_one <- turning_data_sim %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-```
-
-```{r}
-
-mi_fr_d_sim <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data_sim, family = binomial)
-
-ggplot(turning_data_sim, aes(x = Fish_Num_Ratio, y = turn_bool, color = Darkness))+
-  geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d_sim, type="response"), color = Darkness)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d_sim, type="response"), color = Darkness)) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,sim_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
-
-ggsave("Final Graphs/Simmed_Right_Turn_Best_Model.png")
-
-```

### 2022-05-18 2Dto3D/DLT_Converter.py

@@ -121,7 +121,7 @@ for v2f in v2_files:
 
         fish_out_df = pd.DataFrame.from_dict(fish_data_out_dict)
         #Replace to make new file name
-        new_file_name = v2f.replace("V2 CSVs/","").replace("V2","3D")
+        new_file_name = v2f.replace("V2 CSVs/","").replace("V2","3D_")
         fish_out_df.to_csv("/Users/Ben/Desktop/Fish Midline Processer/2Dto3D/Final 3D/"+new_file_name)
 
 

### 2022-05-18 3D_data_files_to_csv_4P.py

@@ -36,13 +36,18 @@ moving_average_n = 35
 tailbeat_len = 19
 
 #Fish len is the median of all fish lengths in pixels
-fish_len = 193
+#Scale is different becasue of calibration
+fish_len = 0.07195
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
 
 def get_dist_np(x1s,y1s,x2s,y2s):
     dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2)
+    return dist
+
+def get_dist_np_3D(x1s,y1s,z1s,x2s,y2s,z2s):
+    dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2+(z1s-z2s)**2)
     return dist
 
 def get_fish_length(fish):
@@ -141,15 +146,25 @@ class fish_data:
         self.name = name
         self.head_x = data[scorer][name]["head"]["x"].to_numpy() 
         self.head_y = data[scorer][name]["head"]["y"].to_numpy() 
+        self.head_z = data[scorer][name]["head"]["z"].to_numpy() 
 
         self.midline_x = data[scorer][name]["midline2"]["x"].to_numpy() 
         self.midline_y = data[scorer][name]["midline2"]["y"].to_numpy() 
+        self.midline_z = data[scorer][name]["midline2"]["z"].to_numpy() 
 
         self.tailbase_x = data[scorer][name]["tailbase"]["x"].to_numpy() 
         self.tailbase_y = data[scorer][name]["tailbase"]["y"].to_numpy() 
+        self.tailbase_z = data[scorer][name]["tailbase"]["z"].to_numpy()
 
         self.tailtip_x = data[scorer][name]["tailtip"]["x"].to_numpy() 
         self.tailtip_y = data[scorer][name]["tailtip"]["y"].to_numpy()
+        self.tailtip_z = data[scorer][name]["tailtip"]["z"].to_numpy()
+
+        self.vec_x = []
+        self.vec_y = []
+        self.vec_z = []
+        self.vec_xy = []
+
         self.tailtip_perp = [] 
 
         self.flow = flow
@@ -160,48 +175,69 @@ class fish_data:
         self.tailtip_zero_centered = []
 
         #These are the summary stats for the fish 
-        self.heading = []
+        self.yaw_heading = []
+        self.pitch_heading = []
         self.speed = []
         self.zero_crossings = []
         self.tb_freq_reps = []
 
         #This calcualtes the summary stats
[…]

### 2022-05-18 data_files_to_csv_4P.py

@@ -169,15 +169,13 @@ class fish_data:
         self.calc_tailtip_perp()
         self.calc_tb_freq()
 
-    #This function clacualtes the heading of the fish at each timepoint
+    #This function calcualtes the pitch heading of the fish at each timepoint
+    #We are using body heading now, so midline to head, not head to next head
     def calc_heading(self):
-        #First we get the next points on the fish
-        head_x_next = np.roll(self.head_x, -1)
-        head_y_next = np.roll(self.head_y, -1)
 
-        #Then we create a vector of the future point minus the last one
-        vec_x = head_x_next - self.head_x
-        vec_y = head_y_next - self.head_y
+        #Then we create a vector of the head minus the midline 
+        vec_x = self.head_x - self.midline_x
+        vec_y = self.head_y - self.midline_y
 
         #Then we use arctan to calculate the heading based on the x and y point vectors
         #Becasue of roll we don't want to the last value since it will be wrong

### 2022-05-27 Fish Data Analysis/Final_Plots_3D.Rmd
Fixed issue with 3D school NND, 999s didn't leave

@@
 count_within_2_aligned <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
-                                                        filter(Heading_Diff > -30 & Heading_Diff < 30) %>%
+                                                        filter(Yaw_Heading_Diff > -30 & Yaw_Heading_Diff < 30) %>%
                                                         group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%

### 2022-05-27 2Dto3D/DLT_Converter.py

@@ -64,7 +64,7 @@ for v2f in v2_files:
         #Add the filepath on here as well
         v1f = "V1 CSVs/" + v1f
         v2f = "V2 CSVs/" + v2f
-        dlt_coefs_file = "DLT_Coefs/" + dlt_coefs_file
+        dlt_coefs_file = "DLT Coefs/" + dlt_coefs_file
 
         print(v1f,v2f,dlt_coefs_file)
 
@@ -122,7 +122,7 @@ for v2f in v2_files:
         fish_out_df = pd.DataFrame.from_dict(fish_data_out_dict)
         #Replace to make new file name
         new_file_name = v2f.replace("V2 CSVs/","").replace("V2","3D_")
-        fish_out_df.to_csv("/Users/Ben/Desktop/Fish Midline Processer/2Dto3D/Final 3D/"+new_file_name)
+        fish_out_df.to_csv("/Users/Ben/Desktop/Fish-Midline-Processer/2Dto3D/Final 3D/"+new_file_name)
 
 
 

### 2022-05-27 2Dto3D/DLT_Plotter.py

@@ -36,7 +36,7 @@ for file_name in three_d_files:
         df['Frame'] = df.groupby(['Scorer','Fish','BodyPart','Point']).cumcount()+1
 
         #So now we pivot from the Point column, into seperate ones for x, y, and z
-        df = df.pivot(index = ['Scorer','Fish','BodyPart','Frame'], columns='Point', values='value')
+        df = df.pivot_table(index = ['Scorer','Fish','BodyPart','Frame'], columns='Point', values='value')
 
         #Then we have to reset the index so that we can use 'Scorer','Fish','BodyPart','Frame' as data columns
         df = df.reset_index()

### 2022-05-27 3D_data_files_to_csv_4P.py

@@ -552,10 +552,9 @@ class fish_comp:
         gs = gridspec.GridSpec(ncols = 5, nrows = 3) 
 
         ax0 = plt.subplot(gs[:,0])
-        ax0.plot(self.f1.head_x, self.f1.head_y)
-        ax0.plot(self.f2.head_x, self.f2.head_y)
-        ax0.scatter(self.f1.head_x[0], self.f1.head_y[0])
-        ax0.scatter(self.f2.head_x[0], self.f2.head_y[0])
+
+        ax0.scatter(self.f1.head_x, self.f1.head_y, c = np.linspace(0,1,num = len(self.f1.head_x)), s = 2)
+        ax0.scatter(self.f2.head_x, self.f2.head_y, c = np.linspace(0,1,num = len(self.f2.head_x)), s = 2)
         ax0.set_title("Fish Path (Blue = Fish 1, Orange = Fish 2)")
 
         ax1 = plt.subplot(gs[0,1])
@@ -579,15 +578,15 @@ class fish_comp:
         ax5.set_title("Speed Difference")
 
         ax6 = plt.subplot(gs[0,3])
-        ax6.plot(range(len(self.f1.heading)), self.f1.heading)
+        ax6.plot(range(len(self.f1.yaw_heading)), self.f1.yaw_heading)
         ax6.set_title("Fish 1 Heading")
 
         ax7 = plt.subplot(gs[1,3])
-        ax7.plot(range(len(self.f2.heading)), self.f2.heading)
+        ax7.plot(range(len(self.f2.yaw_heading)), self.f2.yaw_heading)
         ax7.set_title("Fish 2 Heading")
 
         ax8 = plt.subplot(gs[2,3])
-        ax8.plot(range(len(self.heading_diff)), self.heading_diff)
+        ax8.plot(range(len(self.yaw_heading_diff)), self.yaw_heading_diff)
         ax8.set_title("Heading Difference")
 
         ax9 = plt.subplot(gs[0,4])
@@ -638,6 +637,8 @@ class school_comps:
         self.calc_nnd()
         self.calc_tailbeat_cor()
         self.calc_school_area()
+
+        #self.graph_values()
 
     def calc_school_pos_stats(self):
         school_xs = [fish.head_x for fish in self.fishes]
@@ -692,9 +693,7 @@ class school_comps:
 
     def calc_nnd(self):
         #first we make an array to fill with the NNDs 
[…]

### 2022-05-27 data_files_to_csv_4P.py

@@ -174,12 +174,12 @@ class fish_data:
     def calc_heading(self):
 
         #Then we create a vector of the head minus the midline 
-        vec_x = self.head_x - self.midline_x
-        vec_y = self.head_y - self.midline_y
+        self.vec_x = self.head_x - self.midline_x
+        self.vec_y = self.head_y - self.midline_y
 
         #Then we use arctan to calculate the heading based on the x and y point vectors
         #Becasue of roll we don't want to the last value since it will be wrong
-        self.heading = np.rad2deg(np.arctan2(vec_y,vec_x))[:-1]
+        self.heading = np.rad2deg(np.arctan2(self.vec_y,self.vec_x))[:-1]
 
     def calc_speed(self):
         #First we get the next points on the fish
@@ -325,8 +325,17 @@ class fish_comp:
         self.angle = angle_diff
 
     def calc_heading_diff(self):
-        self.heading_diff = np.rad2deg(np.arctan2(np.sin(np.deg2rad(self.f1.heading-self.f2.heading)),
-                                                  np.cos(np.deg2rad(self.f1.heading-self.f2.heading))))
+        f1_vector = np.asarray([self.f1.vec_x,self.f1.vec_y]).transpose()
+        #print(f1_vector)
+        f2_vector = np.asarray([self.f2.vec_x,self.f2.vec_y]).transpose()
+
+        self.heading_diff = np.zeros(len(self.f1.vec_x))
+
+        for i in range(len(self.f1.vec_x)):
+            dot_product = np.dot(f1_vector[i], f2_vector[i])
+
+            prod_of_norms = np.linalg.norm(f1_vector[i]) * np.linalg.norm(f2_vector[i])
+            self.heading_diff[i] = np.degrees(np.arccos(dot_product / prod_of_norms))
 
     def calc_heading_diff_filtered(self):
         #Makes sure that head wiggle doesn't mess up polarization

### 2022-06-29 Fish Data Analysis/Final_Plots.Rmd
Adding 3D Data

@@
 ```{r}
-school_data <- read.csv("Fish_School_Values.csv")
+school_data <- read.csv("Data/Fish_School_Values.csv")
 school_data <- na.omit(school_data)
@@
 ```{r}
-raw_school_data <- read.csv("Fish_Raw_Comp_Values.csv")
+raw_school_data <- read.csv("Data/Fish_Raw_Comp_Values.csv")
 raw_school_data <- na.omit(raw_school_data)
@@
 
-indiv_data <- read.csv("Fish_Individual_Values.csv")
+indiv_data <- read.csv("Data/Fish_Individual_Values.csv")
 indiv_data <- na.omit(indiv_data)
@@
 ```{r}
-turning_data <- read.csv("Annushka_Turning_Data_Wall.csv") %>%
+turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
                            filter(Next.to.Wall == 0) %>%
@@
 ```{r}
-raw_school_data_simul <- rbind(read.csv("Fish_Raw_Comp_Values.csv"),
+raw_school_data_simul <- rbind(read.csv("Data/Fish_Raw_Comp_Values.csv"),
                                read.csv("Data Sim/Fish_Raw_Comp_Values_Random.csv"))
@@
 ```{r}
-turning_data_sim <- read.csv("Annushka_Turning_Data_Simmed.csv") %>% 
+turning_data_sim <- read.csv("Data/Annushka_Turning_Data_Simmed.csv") %>% 
                            mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%

### 2022-06-29 Fish Data Analysis/Final_Plots_Same_3D.Rmd
Adding 3D Data

--- 2022-05-18 Fish Data Analysis/Final_Plots.Rmd
@@
 ```{r}
-school_data <- read.csv("Fish_School_Values.csv")
+school_data <- read.csv("Data/Fish_School_Values_Same_3D.csv")
 school_data <- na.omit(school_data)
@@
 
-ggsave("Final Graphs/School_NND.png")
+ggsave("Final Graphs/School_NND_Same_3D.png")
 ```
@@
 ```{r}
-raw_school_data <- read.csv("Fish_Raw_Comp_Values.csv")
+raw_school_data <- read.csv("Data/Fish_Raw_Comp_Values_Same_3D.csv")
 raw_school_data <- na.omit(raw_school_data)
@@
 
-ggsave("Final Graphs/Mean_Group_Size.png")
+ggsave("Final Graphs/Mean_Group_Size_Same_3D.png")
 ```
@@
 
-ggsave("Final Graphs/Polarization.png")
+ggsave("Final Graphs/Polarization_Same_3D.png")
 ```
@@
 
-ggsave("Final Graphs/Num_Aligned_Fish_2BL.png")
+ggsave("Final Graphs/Num_Aligned_Fish_2BL_Same_3D.png")
 
@@
 
-indiv_data <- read.csv("Fish_Individual_Values.csv")
+indiv_data <- read.csv("Data/Fish_Individual_Values_Same_3D.csv")
 indiv_data <- na.omit(indiv_data)
@@
 
-ggsave("Final Graphs/School_Speed_Over_Indiv_Speed.png")
+ggsave("Final Graphs/School_Speed_Over_Indiv_Speed_Same_3D.png")
 
 ```
-
-### Turning Bias
-
-```{r}
-turning_data <- read.csv("Annushka_Turning_Data_Wall.csv") %>%
-                           filter(Next.to.Wall == 0) %>%
-                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
-                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>%
-                           filter(Flow %in% allowed_flow_type)
-
-turning_data_sum <- turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-
-turning_data_sum_one <- turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-```
-
-```{r}
-ggplot(turning_data_sum, aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
-  geom_point()+
-  geom_line(alpha = 0.25) +
-  facet_wrap(~ Darkness + Ablation) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
-
-ggsave("Final Graphs/Right_Turn_Prob.png")
-```
-
-```{r}
-#mi_fr_d <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data, family = binomial)
-
-mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)
-
-ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Ablation))+
-  geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
-
-ggsave("Final Graphs/Best_Model_Right_Turn_Prob.png")
-
-```
-
-### Simulated # of fish within 2 BL
-
-```{r}
-raw_school_data_simul <- rbind(read.csv("Fish_Raw_Comp_Values.csv"),
-                               read.csv("Data Sim/Fish_Raw_Comp_Values_Random.csv"))
-raw_school_data_simul <- na.omit(raw_school_data_simul) %>% filter(Flow == "0")
-
-raw_school_data_simul <- raw_school_data_simul %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", ifelse(Ablation == "Y","Ablated","Simulated"))) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", ifelse(Darkness == "Y", "Dark", "Simulated"))) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           separate(Fish, c("Fish1", "Fish2"),sep="x")
-
-raw_school_data_simul_fish_switch <- raw_school_data_simul %>% mutate(Fish3 = Fish1) %>%
-                                                   mutate(Fish1 = Fish2) %>%
-                                                   mutate(Fish2 = Fish3) %>%
-                                                   select(-c(Fish3))
-
-raw_school_data_simul_both_fish <- bind_rows(raw_school_data_simul, raw_school_data_simul)
-
-count_within_2_simul <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
-                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
-                                                summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
-                                                ungroup() %>%
-                                                group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
-                                                summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
-                                                ungroup()
-```
-
-```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
-                        c("No Ablation, Light", "Ablated, Light"),
-                        c("No Ablation, Dark", "Simulated, Simulated"))
-
-ggplot(count_within_2_simul %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL+1,
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
-  ggtitle("Mean size of group within 2BL") +
-  xlab("") +
-  ylab("Mean size of group within 2BL (# of Fish)") +
-  ylim(0,9) +
-  theme_light() +
-  facet_wrap(~ Flow, strip.position = "bottom")+
-  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
-  stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5,6), label = "p.signif", hide.ns = TRUE) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) +
-  scale_y_continuous(breaks=c(0,2,4,6,8))
-
-ggsave("Final Graphs/Simmed_Group_Num_in_2_BL.png")
-
-```
-
-### Simluated Data Aligned within 2BL
-
-```{r}
-
-max_offset <- 15
-
-count_within_2_simul_aligned <- raw_school_data_simul_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
-                                                        filter(abs(Heading_Diff) < max_offset) %>%
-                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
-                                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
-                                                        ungroup() %>%
-                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
-                                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
-                                                        ungroup()
-```
-
-```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),
-                        c("No Ablation, Light", "Ablated, Light"),
-                        c("No Ablation, Dark", "Simulated, Simulated"))
-
-ggplot(count_within_2_simul_aligned %>% filter(Flow == "Still Water"), 
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Count_Fish_in_2BL,
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_boxplot(outlier.shape = NA) +
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color,sim_color)) +
-  ggtitle("Mean size of group within 2BL") +
-  xlab("") +
-  ylab("Number of Aligned Fish within 2BL (# of Fish)") +
-  theme_light() +
-  facet_wrap(~ Flow, strip.position = "bottom")+
-  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
-  stat_compare_means(comparisons = my_comparisons, label.y = c(4.5,3.5,4), label = "p.signif", hide.ns = TRUE) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-  ylim(0,7) +
-  scale_y_continuous(breaks=c(0,2,4,6,8))
-
-ggsave("Final Graphs/Simmed_Aligned_Group_Num_in_2_BL.png")
-
-```
-
-### Simulated Turning Bias
-
-```{r}
-turning_data_sim <- read.csv("Annushka_Turning_Data_Simmed.csv") %>% 
-                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", ifelse(Ablation == "LY","Ablated",Ablation))) %>%
-                           mutate(Darkness = ifelse(Darkness == "DN", "Light", ifelse(Darkness == "DY", "Dark", Darkness))) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated","Simulated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark","Simulated"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
-                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0))
-
-turning_data_sim_sum <- turning_data_sim %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-
-turning_data_sim_sum_one <- turning_data_sim %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               n = n()) %>%
-                                     ungroup()
-```
-
-```{r}
-
-mi_fr_d_sim <- glm(turn_bool ~ Fish_Num_Ratio * Darkness, data = turning_data_sim, family = binomial)
-
-ggplot(turning_data_sim, aes(x = Fish_Num_Ratio, y = turn_bool, color = Darkness))+
-  geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d_sim, type="response"), color = Darkness)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_d_sim, type="response"), color = Darkness)) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,sim_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
-
-ggsave("Final Graphs/Simmed_Right_Turn_Best_Model.png")
-
-```

### 2022-06-29 2D_3D_Compare_Plotter.py

@@ -1,0 +1,90 @@
+import os
+import numpy as np
+import pandas as pd
+import math
+import plotly.express as px
+from scipy import linalg
+import sys
+
+#Header list for reading the raw location CSVs
+header = list(range(4))
+
+num_fish = 8
+body_parts = ["head","midline2","tailbase","tailtip"]
+
+files_3D = os.listdir("3D_Finished_Fish_Data_4P_gaps")
+files_2D = os.listdir("Finished_Fish_Data_4P_gaps_Same_3D")
+
+for file_3D in files_3D:
+
+    if file_3D.endswith(".csv"):
+        file_id = file_3D[0:22]
+        short_id = file_3D[0:10]
+
+        #Get the v1 file that matches, and the dlt coefs that go with them both
+        file_2D = [f for f in files_2D if file_id in f][0]
+
+        file_3D = "3D_Finished_Fish_Data_4P_gaps/" + file_3D
+        file_2D = "Finished_Fish_Data_4P_gaps_Same_3D/" + file_2D
+
+        files_to_do = [file_2D,file_3D]
+
+        for data_file in files_to_do:
+            fish_raw_data = pd.read_csv(data_file, index_col=0, header=header)
+
+            df = pd.melt(fish_raw_data)
+
+            #Let's rename things to what they actually are
+            df = df.rename(columns={"variable_0": "Scorer", "variable_1": "Fish", "variable_2": "BodyPart", "variable_3": "Point"})
+
+            #So now I add the Frame to this because I will need to group by that otherwise there is overlap between labels
+            df['Frame'] = df.groupby(['Scorer','Fish','BodyPart','Point']).cumcount()+1
+
+            #So now we pivot from the Point column, into seperate ones for x, y, and z
+            df = df.pivot_table(index = ['Scorer','Fish','BodyPart','Frame'], columns='Point', values='value')
+
+            #Then we have to reset the index so that we can use 'Scorer','Fish','BodyPart','Frame' as data columns
+            df = df.reset_index()
+
+            df = df[df['BodyPart'] == "head"]
+
+            if "3D_DLC" in data_file:
+                df_3D = df
+                df_3D["Fish"] = df_3D["Fish"] + "_3D"
+
+                max_x_3D = max(df_3D["x"])
[…]

### 2022-06-29 2Dto3D/DLT_Plotter.py

@@ -4,6 +4,7 @@ import pandas as pd
 import math
 import plotly.express as px
 from scipy import linalg
+import sys
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
@@ -47,17 +48,23 @@ for file_name in three_d_files:
 
         #Now we graph it, nice and easy
 
-        #Though the axies keep shifting weirdly so not my fave
-        fig = px.scatter_3d(df,x="x", y="y", z="z", color="Fish", animation_frame="Frame", hover_data = ["BodyPart"],
-                               range_x=[df["x"].min()-0.05,df["x"].max()+0.05],
-                               range_y=[df["y"].min()-0.05,df["y"].max()+0.05],
-                               range_z=[df["z"].min()-0.05,df["z"].max()+0.05],
-                               color_continuous_scale = "rainbow")
+        print(df)
 
-        fig.layout.scene.aspectratio = {'x':1, 'y':1, 'z':1}
+        df.to_csv()
 
-        #fig.show()
+        sys.exit()
 
-        file_id = file_name[0:22]
+        # #Though the axies keep shifting weirdly so not my fave
+        # fig = px.scatter_3d(df,x="x", y="y", z="z", color="Fish", animation_frame="Frame", hover_data = ["BodyPart"],
+        #                        range_x=[df["x"].min()-0.05,df["x"].max()+0.05],
+        #                        range_y=[df["y"].min()-0.05,df["y"].max()+0.05],
+        #                        range_z=[df["z"].min()-0.05,df["z"].max()+0.05],
+        #                        color_continuous_scale = "rainbow")
 
-        fig.write_html("Saved 3D Plots/{name}.html".format(name = file_id), auto_play=False)
+        # fig.layout.scene.aspectratio = {'x':1, 'y':1, 'z':1}
+
+        # #fig.show()
+
+        # file_id = file_name[0:22]
+
+        # fig.write_html("Saved 3D Plots/{name}.html".format(name = file_id), auto_play=False)

### 2022-06-29 data_files_to_csv_4P.py

@@ -899,11 +899,11 @@ class trial:
 
         return(out_data)
 
-data_folder = "Finished_Fish_Data_4P_gaps/"
+data_folder = "Finished_Fish_Data_4P_gaps_Same_3D/"
 
 trials = []
 
-single_file = "" #"2021_08_03_11_LY_DN_F2_V1DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv"
+single_file = ""
 
 for file_name in os.listdir(data_folder):
     if file_name.endswith(".csv") and single_file in file_name:
@@ -931,10 +931,10 @@ for trial in trials:
         fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
         fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
 
-fish_sigular_dataframe.to_csv("Fish_Individual_Values.csv")
-fish_comp_dataframe.to_csv("Fish_Comp_Values.csv")
-fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values.csv")
-fish_school_dataframe.to_csv("Fish_School_Values.csv")
+fish_sigular_dataframe.to_csv("Fish_Individual_Values_Same_3D.csv")
+fish_comp_dataframe.to_csv("Fish_Comp_Values_Same_3D.csv")
+fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_Same_3D.csv")
+fish_school_dataframe.to_csv("Fish_School_Values_Same_3D.csv")
 
 #Recalculate when new data is added
 # all_trials_tailbeat_lens = []

### 2022-07-01 Fish Data Analysis/Final_Plots_3D.Rmd
Added Single Fish Data

@@
 ```{r}
-school_data <- read.csv("Fish_School_Values_3D.csv")
+school_data <- read.csv("Data/Fish_School_Values_3D.csv")
 school_data <- na.omit(school_data)
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
+  ggtitle("3D Data: Effect of Available Senses on Nearest Neighbor Distance (NND)") +
   xlab("") +
@@
 ```{r}
-raw_school_data <- read.csv("Fish_Raw_Comp_Values_3D.csv")
+raw_school_data <- read.csv("Data/Fish_Raw_Comp_Values_3D.csv")
 raw_school_data <- na.omit(raw_school_data)
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Mean size of group within 2BL") +
+  ggtitle("3D Data: Mean size of group within 2BL") +
   xlab("") +
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on School Polarization") +
+  ggtitle("3D Data: Effect of Available Senses on School Polarization") +
   xlab("") +
@@
 
-indiv_data <- read.csv("Fish_Individual_Values_3D.csv")
+indiv_data <- read.csv("Data/Fish_Individual_Values_3D.csv")
 indiv_data <- na.omit(indiv_data)
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on School Speed") +
+  ggtitle("3D Data: Effect of Available Senses on School Speed") +
   xlab("") +

### 2022-07-01 Fish Data Analysis/Final_Plots_Single_Fish.Rmd
Added Single Fish Data

--- 2022-06-29 Fish Data Analysis/Final_Plots_Same_3D.Rmd
@@
 ```{r}
-school_data <- read.csv("Data/Fish_School_Values_Same_3D.csv")
+school_data <- read.csv("Data/Fish_School_Values_Single_Fish.csv")
 school_data <- na.omit(school_data)
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
+  ggtitle("Single Fish: Effect of Available Senses on Nearest Neighbor Distance (NND)") +
   xlab("") +
@@
 
-ggsave("Final Graphs/School_NND_Same_3D.png")
+ggsave("Final Graphs/School_NND_Single_Fish.png")
 ```
@@
 ```{r}
-raw_school_data <- read.csv("Data/Fish_Raw_Comp_Values_Same_3D.csv")
+raw_school_data <- read.csv("Data/Fish_Raw_Comp_Values_Single_Fish.csv")
 raw_school_data <- na.omit(raw_school_data)
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Mean size of group within 2BL") +
+  ggtitle("Single Fish: Mean size of group within 2BL") +
   xlab("") +
@@
 
-ggsave("Final Graphs/Mean_Group_Size_Same_3D.png")
+ggsave("Final Graphs/Mean_Group_Size_Single_Fish.png")
 ```
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on School Polarization") +
+  ggtitle("Single Fish: Effect of Available Senses on School Polarization") +
   xlab("") +
@@
 
-ggsave("Final Graphs/Polarization_Same_3D.png")
+ggsave("Final Graphs/Polarization_Single_Fish.png")
 ```
@@
 
-ggsave("Final Graphs/Num_Aligned_Fish_2BL_Same_3D.png")
+ggsave("Final Graphs/Num_Aligned_Fish_2BL_Single_Fish.png")
 
@@
 
-indiv_data <- read.csv("Data/Fish_Individual_Values_Same_3D.csv")
+indiv_data <- read.csv("Data/Fish_Individual_Values_Single_Fish.csv")
 indiv_data <- na.omit(indiv_data)
@@
   scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on School Speed") +
+  ggtitle("Single Fish: Effect of Available Senses on School Speed") +
   xlab("") +
@@
 
-ggsave("Final Graphs/School_Speed_Over_Indiv_Speed_Same_3D.png")
+ggsave("Final Graphs/School_Speed_Over_Indiv_Speed_Single_Fish.png")
 

### 2022-07-01 Fish Data Analysis/Data Sim/data_randomizer.py

@@ -35,4 +35,10 @@ for i in range(8):
         #print(i,j,j*12,(j+1)*12-1)
         data_to_fill.iloc[: , j*12:(j+1)*12-1] = all_data_arr[(j+i)%8].iloc[: , j*12:(j+1)*12-1]
 
-    data_to_fill.to_csv(data_folder+"1995_09_07_0{i}_TS_DS_F0_VDLC_resnet50_L8FV4PFeb22shuffle1_100000_bx_filtered.csv".format(i=i+1))  
+    data_to_fill.to_csv(data_folder+"1995_09_07_0{i}_TS_DS_F0_VDLC_resnet50_L8FV4PFeb22shuffle1_100000_bx_filtered.csv".format(i=i+1)) 
+
+
+
+
+
+     

### 2022-07-01 data_files_to_csv_4P.py

@@ -899,7 +899,7 @@ class trial:
 
         return(out_data)
 
-data_folder = "Finished_Fish_Data_4P_gaps_Same_3D/"
+data_folder = "Single Fish Combiner/Multi Data/"
 
 trials = []
 
@@ -931,10 +931,10 @@ for trial in trials:
         fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
         fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
 
-fish_sigular_dataframe.to_csv("Fish_Individual_Values_Same_3D.csv")
-fish_comp_dataframe.to_csv("Fish_Comp_Values_Same_3D.csv")
-fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_Same_3D.csv")
-fish_school_dataframe.to_csv("Fish_School_Values_Same_3D.csv")
+fish_sigular_dataframe.to_csv("Fish_Individual_Values_Single_Fish.csv")
+fish_comp_dataframe.to_csv("Fish_Comp_Values_Single_Fish.csv")
+fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_Single_Fish.csv")
+fish_school_dataframe.to_csv("Fish_School_Values_Single_Fish.csv")
 
 #Recalculate when new data is added
 # all_trials_tailbeat_lens = []

### 2022-08-24 Single Fish Turning Processor/get_turn_bias.py
Added turning processing

@@ -1,0 +1,142 @@
+import matplotlib.pyplot as plt
+from matplotlib import gridspec 
+from scipy.signal import savgol_filter
+from scipy.signal import find_peaks
+import pandas
+import os
+import numpy as np
+
+header = list(range(4))
+
+fish_names = ["individual1","individual2",
+              "individual3","individual4",
+              "individual5","individual6",
+              "individual7","individual8"]
+
+csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Turn_Dir},{Fish_Left},{Fish_Right}\n"
+
+def turn_frames(x_data,y_data):
+    diff_needed = 15
+    smooth_window_size = 41
+
+    x_data_smooth = savgol_filter(x_data, smooth_window_size, 3)
+    y_data_smooth = savgol_filter(y_data, smooth_window_size, 3)
+
+    x_data_rolled = np.roll(x_data_smooth, 5)
+    y_data_rolled = np.roll(y_data_smooth, 5)
+
+    x_diff = x_data_smooth - x_data_rolled
+    y_diff = y_data_smooth - y_data_rolled
+
+    angle = np.rad2deg(np.arctan2(y_diff,x_diff))
+
+    angle_diff = angle - np.roll(angle, 1)
+
+    angle_diff = (angle_diff + 180) % 360 - 180
+
+    angle_diff = savgol_filter(angle_diff, smooth_window_size, 3)
+
+    angle_diff_windowed = abs(np.convolve(angle_diff,np.ones(10,dtype=int),'valid'))
+
+    peaks, _  = find_peaks(angle_diff_windowed, prominence = diff_needed)
+
+    #-1 = Right, 1 = Left
+    turn_dirs = np.sign(angle_diff[peaks])
+
+    return(peaks,turn_dirs)
+
+def is_point_LR(mid_to_head,mid_to_other):
+    cross_prod = np.cross(mid_to_head,mid_to_other)
+
+    if cross_prod[2] <= 0:
+        return 0
+
+    elif cross_prod[2] > 0:
+        return 1
+
+def get_num_LR(frame,main_fish,fish_df,scorerer):
+    #index 0 is Right, index 1 is Left
+    lr_out = [0,0]
+
+    # print(frame)
+    # print(fish_df[scorerer][main_fish]["head"]["x"])
+
+    try:
[…]

### 2022-08-24 Single Fish Turning Processor/turn_finder.py

@@ -1,0 +1,73 @@
+import matplotlib.pyplot as plt
+from matplotlib import gridspec 
+from scipy.signal import savgol_filter
+from scipy.signal import find_peaks
+import pandas
+import os
+import numpy as np
+
+header = list(range(4))
+diff_needed = 15
+
+smooth_window_size = 41
+
+fish_data = pandas.read_csv("Data/2022_06_10_01_LN_DN_F0_V1_02_03_08_17_33_38_44_45.csv",index_col=0, header=header)
+
+scorerer = fish_data.keys()[0][0]
+
+#print(fish_data[scorerer]["individual1"])
+
+x_data = fish_data[scorerer]["individual2"]["head"]["x"]
+y_data = fish_data[scorerer]["individual2"]["head"]["y"]
+
+x_data_smooth = savgol_filter(x_data, smooth_window_size, 3)
+y_data_smooth = savgol_filter(y_data, smooth_window_size, 3)
+
+x_data_rolled = np.roll(x_data_smooth, 5)
+y_data_rolled = np.roll(y_data_smooth, 5)
+
+x_diff = x_data_smooth - x_data_rolled
+y_diff = y_data_smooth - y_data_rolled
+
+angle = np.rad2deg(np.arctan2(y_diff,x_diff))
+angle_diff = angle - np.roll(angle, 1)
+angle_diff = (angle_diff + 180) % 360 - 180
+
+angle_diff = savgol_filter(angle_diff, smooth_window_size, 3)
+
+angle_diff_windowed = abs(np.convolve(angle_diff,np.ones(10,dtype=int),'valid'))
+
+fig = plt.figure(figsize=(8, 6))
+
+gs = gridspec.GridSpec(ncols = 3, nrows = 3) 
+
+peaks, _  = find_peaks(angle_diff_windowed, prominence = diff_needed)
+
+x_data = x_data[:len(angle_diff_windowed)]
+y_data = y_data[:len(angle_diff_windowed)]
+
+ax0 = plt.subplot(gs[0,0])
+ax0.plot(x_data, y_data)
+ax0.plot(x_data_smooth, y_data_smooth)
+ax0.scatter(x_data[0], y_data[0])
+ax0.plot(x_data[peaks], y_data[peaks], "x")
[…]

### 2022-08-24 Fish Data Analysis/turning_fish_bias.Rmd
Analyzed Single Fish Turning Data

@@
 mi_fr_fl_a_d <- glm(turn_bool ~ Fish_Num_Ratio * Flow * Ablation * Darkness, data = turning_data, family = binomial)
+mi_fl_a_d <- glm(turn_bool ~ Flow * Ablation * Darkness, data = turning_data, family = binomial)
 
@@
       ma_fr_fl,ma_fr_a,ma_fr_d,ma_fr_fl_a,ma_fr_fl_d,ma_fr_a_d,ma_fr_fl_a_d,
-      mi_fr_fl,mi_fr_a,mi_fr_d,mi_fr_fl_a,mi_fr_fl_d,mi_fr_a_d,mi_fr_fl_a_d)
+      mi_fr_fl,mi_fr_a,mi_fr_d,mi_fr_fl_a,mi_fr_fl_d,mi_fr_a_d,mi_fr_fl_a_d,mi_fl_a_d)
 
@@
 ```
+
+# Uses Single Fish Data
+
+```{r}
+turning_data <- read.csv("Data/single_fish_turning.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
+                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
+                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
+                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
+                                                           c("7:0","6:1","5:2","4:3",
+                                                             "3:4","2:5","1:6","0:7"))) %>%
+                           mutate(turn_bool = ifelse(Turn_Dir == -1,1,0))
+
+turning_data_sum <- turning_data %>% na.omit %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                     summarize(mean_right_turn = mean(turn_bool),
+                                               sd_right_turn = sd(turn_bool),
+                                               se_right_turn = sd_right_turn/sqrt(n()),
+                                               n = n()) %>%
+                                     ungroup()
+
+turning_data_sum_one <- turning_data %>% na.omit %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio) %>%
+                                     summarize(mean_right_turn = mean(turn_bool),
+                                               sd_right_turn = sd(turn_bool),
+                                               se_right_turn = sd_right_turn/sqrt(n()),
+                                               n = n()) %>%
+                                     ungroup()
+
+turning_data_count <- turning_data %>% na.omit %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                     summarize(count_per = n()) %>%
+                                     ungroup()
+```
+
+```{r}
+light_no_ab_color = "#d4d7dd"
+light_ab_color = "#f5ba9e"
+dark_no_ab_color = "#5e94d4"
+sim_color = "#777777"
+
+flow_split_still = "#F59DE2"
+flow_split_flow = "#5DD492"
+
+dark_split_light = "#E71D36"
+dark_split_dark = "#011627"
+
+ggplot(turning_data_sum, aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
+  geom_point()+
+  geom_line(alpha = 0.25) +
+  facet_wrap(~ Darkness + Ablation) +
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))
+
+ggsave("Final Graphs/Single_Fish_Right_Turn_Prob.png")
+```
+```{r}
+mi_fr_a_d <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, data = turning_data, family = binomial)
+
+ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Ablation))+
+  geom_jitter(alpha = 0.1, height = 0.025)+
+  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_a_d, type="response"), color = Ablation, shape = Darkness)) +
+  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_a_d, type="response"), color = Ablation, shape = Darkness)) +
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))
+```

### 2022-10-17 Fish Data Analysis/Final_Plots.Rmd
Added new plots and added code for analysis

@@
 library(ggpubr) #For the significance bars
+library(report) #For the reports
+library(emmeans) #For reporting
 ```
@@
 ggsave("Final Graphs/School_NND.png")
+
+nnd_glm <- glm(NND ~ 0 + Ablation + Darkness + Flow, data = school_data)s
+Anova(nnd_glm)
+
+#report(nnd_glm)
+
+emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness:Flow)
+emmeans(nnd_glm, specs = pairwise ~ Flow)
 ```
@@
 ggsave("Final Graphs/Mean_Group_Size.png")
+
 ```
@@
 ggsave("Final Graphs/Polarization.png")
+
+polar_glm <- glm(School_Polar ~ 0 + Ablation + Darkness + Flow, data = school_data)
+Anova(polar_glm)
+
+emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness:Flow)
+emmeans(polar_glm, specs = pairwise ~ Flow)
 ```
@@
 fish_speed_division <- speed_whole_school %>% inner_join(indiv_data_4_speed, by = c("Year", "Month", "Day", "Trial", "Tailbeat_Num")) %>%
-                                              mutate(Divided_Speed = School_Speed/Mean_Speed)
+                                              mutate(Divided_Speed = School_Speed/Mean_Speed,
+                                                     Sub_Speed = ifelse(Flow == "Flowing Water (2 BL/s)", School_Speed - 2, School_Speed))
 ```
@@
 
-ggplot(fish_speed_division, aes(x = interaction(Ablation,Darkness,sep=", "), y = Divided_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
+ggplot(fish_speed_division, aes(x = interaction(Ablation,Darkness,sep=", "), y = Sub_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
   geom_boxplot(outlier.shape = NA) +
@@
 ggsave("Final Graphs/School_Speed_Over_Indiv_Speed.png")
+
+speed_glm <- glm(Divided_Speed ~ 0 + Ablation + Darkness + Flow, data = fish_speed_division)
+Anova(speed_glm)
+
+emmeans(speed_glm, specs = pairwise ~ Ablation*Darkness*Flow - Ablation:Darkness)
+emmeans(speed_glm, specs = pairwise ~ Flow)
 
@@
 
-mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)
+#mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)
 
-ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Ablation))+
+mi_fr_fl <- glm(turn_bool ~ Fish_Num_Ratio*Flow, data = turning_data, family = binomial)
+
+ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow))+
   geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
+  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl, type="response"), color = Flow)) +
+  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl, type="response"), color = Flow)) +
   theme_classic() +
@@
   ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
+  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
 ggsave("Final Graphs/Best_Model_Right_Turn_Prob.png")
+
+turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*(Flow+Darkness+Ablation), data = turning_data, family = binomial)
+Anova(turning_glm)
+
+report(turning_glm)
+emmeans(turning_glm, specs = pairwise ~ Flow)
 
@@
 ```
+#Demo graph for startle experiments
+```{r}
+
+startle_data <- tibble(Darkness = rep(c("Light","Dark"), each = 100),
+                       Trial = rep(rep(c("1","10","20","30"), each = 25), 2),
+                       NND = c(rnorm(100,1,0.1),
+                               rnorm(25,1.5,0.25),rnorm(25,1.33,0.2),rnorm(25,1.16,0.15),rnorm(25,1,0.1)))
+
+ggplot(startle_data, aes(x = Trial, y = NND, fill = Darkness))+
+  geom_boxplot(outlier.shape = NA) +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color)) +
+  ggtitle("Effect of Startle Trial Number (NND)") +
+  xlab("Startles #") +
+  ylab("NND (BL)") +
+  theme_light()
+
+```

### 2022-11-07 Single Fish Turning Processor/new_turn_finder.py
Calculating Based on Midline to Head

@@ -33,8 +33,13 @@ scorerer = fish_data.keys()[0][0]
 
 #print(fish_data[scorerer]["individual1"])
 
-x_data = fish_data[scorerer]["individual5"]["head"]["x"].to_numpy()
-y_data = fish_data[scorerer]["individual5"]["head"]["y"].to_numpy()
+fish = "individual5"
+
+head_x_data = fish_data[scorerer][fish]["head"]["x"].to_numpy()
+head_y_data = fish_data[scorerer][fish]["head"]["y"].to_numpy()
+
+mid_x_data = fish_data[scorerer][fish]["midline2"]["x"].to_numpy()
+mid_y_data = fish_data[scorerer][fish]["midline2"]["y"].to_numpy()
 
 #x_data = savgol_filter(x_data, smooth_window_size, 3)
 #y_data = savgol_filter(y_data, smooth_window_size, 3)
@@ -45,38 +50,54 @@ y_data = fish_data[scorerer]["individual5"]["head"]["y"].to_numpy()
 #print(x_data)
 #print(len(x_data))
 
-point_data = np.column_stack((x_data, y_data))
+head_point_data = np.column_stack((head_x_data, head_y_data))
+mid_point_data = np.column_stack((mid_x_data, mid_y_data))
 
 #print(point_data)
 
 #offset = 10
 
-common_peaks = dict()
+#common_peaks = dict()
 
 #Lower offsets find smaller turns
 #Higher offsets find bigger turns
 
 #maxoffset = 20 
 
-dot_prods = np.zeros(len(point_data))+1
+dot_prods = np.zeros(len(head_point_data))+1
 
-#for offset in range(2,maxoffset):
+#Now with midlines!
 
 offset = 20
 
-for i in range(offset,len(point_data)-offset-1):
+for i in range(len(head_point_data)-offset-1):
 
-    #print(i)
-
-    vec1 = (point_data[i] - point_data[i-offset]) / calc_mag(point_data[i],point_data[i-offset])
-    vec2 = (point_data[i+offset] - point_data[i]) / calc_mag(point_data[i+offset],point_data[i])
+    vec1 = (head_point_data[i] - mid_point_data[i]) / calc_mag(head_point_data[i],mid_point_data[i])
[…]

### 2022-11-10 Fish Data Analysis/Paper_Figures.qmd
Added code to make grouped paper graphs

---
title: "Paper Figures and Text"
format: html
editor: visual
---

## Loading in the Libraries for Everything

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
```

## Functions and Variables

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")
```

## Fish Turning Graphs

```{r}
annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
                           #filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
                           rename("Turn_Dir" = "Turn.Direction")  %>%
                           rename("Fish_Left" = "No..Fish.Left")  %>%
                           rename("Fish_Right" = "No..Fish.Right")  %>%
                           mutate(Type = "Eight Fish")

single_fish_turning_data <- read.csv("Data/single_fish_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           select(-c("Singles")) %>%
                           mutate(Type = "Combined Single")

all_turning_data <- rbind(annushka_turning_data,single_fish_turning_data)

turning_data_sum <- all_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()
```

### All the Plots of Eight Fish in Flow and Still, Raw and GLM

```{r}
eight_fish_all_cond <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

only_still_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
                 data = eight_fish_turning_data %>% filter(Flow == "Still Water"), 
                 family = binomial)

eight_fish_still_model <- ggplot(eight_fish_turning_data %>% filter(Flow == "Still Water"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

only_flow_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
                 data = eight_fish_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), 
                 family = binomial)

eight_fish_flow_model <- ggplot(eight_fish_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

eight_fish_all_cond
eight_fish_still_model
eight_fish_flow_model
```

### All the Plots of Eight Fish vs Single in Still Water

```{r}

dark_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
                 data = all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark"), 
                 family = binomial)

dark_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(dark_eight_and_single_model, type="response"), color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(dark_eight_and_single_model, type="response"), color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

ablation_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
                 data = all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated"), 
                 family = binomial)

ablation_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(ablation_eight_and_single_model, type="response"), color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(ablation_eight_and_single_model, type="response"), color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

light_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
                 data = all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"), 
                 family = binomial)

light_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(light_eight_and_single_model, type="response"), color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(light_eight_and_single_model, type="response"), color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph
```

### Now we combine it all

```{r}
turning_mega_plot <- ggarrange(eight_fish_all_cond, eight_fish_still_model, eight_fish_flow_model,
          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2)

ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)
```

## School Summary Stats

```{r}
school_data <- read.csv("Data/Fish_School_Values.csv")
school_data <- na.omit(school_data)

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed)) %>%
                           ungroup()
```

### NND Plot

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both") +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both") +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

nnd_still
nnd_flow
```
### Polarization

```{r}

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both") +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both") +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

polar_still
polar_flow
```

### Speed

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both") +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both") +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

speed_still
speed_flow
```
### Now we combine them

```{r}
school_stats_mega_plot <- ggarrange(nnd_still, nnd_flow, 
                                    polar_still, polar_flow,
                                    speed_still, speed_flow,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 2, nrow = 3)

ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 20)
```

### 2022-11-10 Fish Data Analysis/turning_fish_bias.Rmd
Added code to make grouped paper graphs

@@
 ```{r}
-turning_data <- read.csv("Data/single_fish_turning.csv") %>%
+turning_data <- read.csv("Data/eight_fish_turning.csv") %>%
                            mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
@@
                                                              "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn_Dir == -1,1,0))
+                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0))
 
@@
   ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
+  scale_colour_manual(values = c(dark_no_ab_color,light_ab_color)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,

### 2022-11-10 Single Fish Turning Processor/get_turn_bias_midline.py

@@ -1,0 +1,188 @@
+import matplotlib.pyplot as plt
+from matplotlib import gridspec 
+from scipy.signal import savgol_filter
+from scipy.signal import find_peaks
+import pandas
+import os
+import numpy as np
+import math
+
+header = list(range(4))
+
+fish_names = ["individual1","individual2",
+              "individual3","individual4",
+              "individual5","individual6",
+              "individual7","individual8"]
+
+csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Turn_Dir},{Fish_Left},{Fish_Right}\n"
+
+def calc_mag(p1,p2):
+    return math.sqrt((p1[0]-p2[0])**2 + (p1[1]-p2[1])**2)
+
+def moving_average(x, w):
+    return np.convolve(x, np.ones(w), 'valid') / w
+
+def turn_frames(head_x_data,head_y_data,mid_x_data,mid_y_data):
+
+    #Get the head and midline data in a form that is easy to subtract
+    head_point_data = np.column_stack((head_x_data, head_y_data))
+    mid_point_data = np.column_stack((mid_x_data, mid_y_data))
+
+    #Set up an array for dot products
+    dot_prods = np.zeros(len(head_point_data))+1
+
+    #This is just chosen randomly based on what I've seen
+    offset = 20
+
+    for i in range(len(head_point_data)-offset-1):
+
+        vec1 = (head_point_data[i] - mid_point_data[i]) / calc_mag(head_point_data[i],mid_point_data[i])
+        vec2 = (head_point_data[i+offset] - mid_point_data[i+offset]) / calc_mag(head_point_data[i+offset],mid_point_data[i+offset])
+
+        dot_prods[i] = np.dot(vec1,vec2)
+
+        if np.isnan(np.dot(vec1,vec2)):
+            dot_prods[i] = 1
+
+    #Flip the dot products around so that higher more of a turn, not less
+    dot_prods = abs(dot_prods-1)
+
+    #Get the moving average. It's a window I just chose, but it works well I suppose
+    dot_prods = moving_average(dot_prods,10)
+
+    #Instead of setting an arbitray amount, look at ones that are more sificantly different from the rest. 
+    #Though I suppose that if they turned a lot this wouldn't work well...
+    #okay commenting it out for now and just picking a number
+
+    #peak_prom = np.std(dot_prods)*1.5
[…]

### 2022-11-10 Single Fish Turning Processor/new_turn_finder.py

@@ -33,7 +33,7 @@ scorerer = fish_data.keys()[0][0]
 
 #print(fish_data[scorerer]["individual1"])
 
-fish = "individual5"
+fish = "individual7"
 
 head_x_data = fish_data[scorerer][fish]["head"]["x"].to_numpy()
 head_y_data = fish_data[scorerer][fish]["head"]["y"].to_numpy()
@@ -107,11 +107,11 @@ for i in range(len(head_point_data)-offset-1):
 
 dot_prods = abs(dot_prods-1)
 
-dot_prods = moving_sum(dot_prods,10)
+dot_prods = moving_average(dot_prods,10)
 
 #print(dot_prods_windowed)
 
-peak_prom = np.std(dot_prods)*1.5
+peak_prom = 0.3 #np.std(dot_prods)*1.5
 
 print(peak_prom)
 

### 2022-11-16 Fish Data Analysis/Paper_Figures.qmd
Worked on figure details

@@
 allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")
+
+dot_binwidth = 0.015
 ```
@@
 only_still_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
-                 data = eight_fish_turning_data %>% filter(Flow == "Still Water"), 
+                 data = annushka_turning_data %>% filter(Flow == "Still Water"), 
                  family = binomial)
 
-eight_fish_still_model <- ggplot(eight_fish_turning_data %>% filter(Flow == "Still Water"),
+eight_fish_still_model <- ggplot(annushka_turning_data %>% filter(Flow == "Still Water"),
                            aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
@@
 only_flow_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
-                 data = eight_fish_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), 
+                 data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), 
                  family = binomial)
 
-eight_fish_flow_model <- ggplot(eight_fish_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+eight_fish_flow_model <- ggplot(annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                            aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
@@
            fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both") +
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
   geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
@@
            fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both") +
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
   geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
@@
            fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both") +
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
   geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
@@
 ```
+
+## Velocity Correlations
+
+```{r}
+raw_comp_data <- read.csv("Data/Fish_Raw_Comp_Values.csv")
+raw_comp_data <- na.omit(raw_comp_data)
+
+comp_data <- raw_comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           select(-X)
+
+velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10)
+```
+
+```{r}
+
+ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff)))+
+  #geom_point(alpha = 0.01)+
+  geom_violin() +
+  theme_classic()
+
+```

### 2022-11-21 Fish Data Analysis/Paper_Figures.qmd
Adding Velocity Dot Product

@@
 library(ggdist)
+library(emmeans)
 ```
@@
 ```{r}
-raw_comp_data <- read.csv("Data/Fish_Raw_Comp_Values.csv")
+raw_comp_data <- read.csv("Data/Fish_Comp_Values.csv")
 raw_comp_data <- na.omit(raw_comp_data)
@@
 
-velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10)
+velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10) %>% filter(Fish1_Speed < 5) %>% filter(Fish2_Speed < 5)  %>% filter(Flow == "Still Water")
+
+velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>% filter(round_Distance != 8)
+
+velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>%
+                                               filter(Flow == "Still Water") %>%
+                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
+                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
+                                                         sd_Speed_Diff = sd(abs(Speed_Diff))) %>%
+                                               ungroup()
+```
+
+```{r}
+ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
+  geom_point(alpha = 0.1)+
+  theme_classic()+ 
+  theme(legend.position = "none") +
+  ylab("Correlation Strength")+
+  xlab("Distance (BL)")
 ```
@@
 
-ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff)))+
-  #geom_point(alpha = 0.01)+
-  geom_violin() +
+ggplot(velocity_cor_data, aes(x = Fish1_Speed, y = Fish2_Speed))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(method = "lm")+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+ggplot(velocity_cor_data, aes(x = Distance, y = Fish1_Speed*Fish2_Speed))+
+  geom_point(alpha = 0.1)+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+cor.test(velocity_cor_data$Fish1_Speed,velocity_cor_data$Fish2_Speed)
+
+ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff), 
+                                                                color = Flow_Ablation_Darkness))+
+  geom_violin()+
   theme_classic()
 
+ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Speed_Diff, color = Flow_Ablation_Darkness))+
+  geom_point(position=position_dodge(width = 0.6))+
+  geom_errorbar(aes(ymin = mean_Speed_Diff-sd_Speed_Diff, ymax = mean_Speed_Diff+sd_Speed_Diff),
+                position=position_dodge(width = 0.6))+
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  theme_classic()
+
+speed_diff_glm <- glm(Speed_Diff ~ round_Distance * Flow_Ablation_Darkness, data = velocity_cor_data)
+Anova(speed_diff_glm)
+
+#emmeans(speed_diff_glm, specs = pairwise ~ Flow_Ablation_Darkness)
+#emmeans(speed_diff_glm, specs = pairwise ~ round_Distance)
+
 ```

### 2022-11-21 data_files_to_csv_4P.py

@@ -150,6 +150,8 @@ class fish_data:
         self.tailtip_y = data[scorer][name]["tailtip"]["y"].to_numpy()
         self.tailtip_perp = [] 
 
+        self.velocity_vec = []
+
         self.flow = flow
         
         #These are all blank and will be used for graphing
@@ -190,6 +192,8 @@ class fish_data:
         vec_x = head_x_next - self.head_x
         vec_y = head_y_next - self.head_y
 
+        self.velocity_vec = np.column_stack((vec_x[:-1], vec_y[:-1]))
+
         #Then we add the flow to the x value
         #Since (0,0) is in the upper left a positive vec_x value value means it is moving downstream
         #so I should subtract the flow value 
@@ -200,7 +204,6 @@ class fish_data:
         self.speed = np.sqrt(vec_x_flow**2+vec_y**2)[:-1]/fish_len * fps
 
     def calc_tailtip_perp(self):
-
         #First get the total number of frames
         total_frames = len(self.head_x)
 
@@ -251,6 +254,7 @@ class fish_data:
             #Now we append this here so that they all stay the same length. This basically extends the last tailbeat.
             self.tb_freq_reps = np.repeat(np.append(tb_freq,tb_freq[-1]),tailbeat_lengths) #[:len(tb_freq)])
 
+
     #Thsi function allows me to graph values for any fish without trying to cram it into a for loop somewhere
     def graph_values(self):
         fig = plt.figure(figsize=(8, 6))
@@ -296,12 +300,14 @@ class fish_comp:
         self.heading_diff = []
         self.speed_diff = []
         self.tailbeat_offset_reps = []
+        self.spatial_autocor = []
 
         self.calc_dist()
         self.calc_angle()
         self.calc_heading_diff()
         self.calc_speed_diff()
         self.calc_rayleigh_r()
+        self.calc_spatial_autocor()
 
         #self.graph_values()
 
@@ -486,6 +492,12 @@ class fish_comp:
 
         self.tailbeat_offset_reps = np.repeat(rayleigh_out,tailbeat_lengths[:len(rayleigh_out)])
 
+    def calc_spatial_autocor(self):
+
+        self.spatial_autocor = np.zeros(len(self.f1.velocity_vec))
+
+        for i in range(len(self.f1.velocity_vec)):
[…]

### 2022-11-24 Fish Data Analysis/Paper_Figures.qmd
Working on velocity cor graphs

@@
 
-velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>% filter(round_Distance != 8)
+velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,1))) %>% filter(round_Distance != 8)
 
@@
                                                summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
-                                                         sd_Speed_Diff = sd(abs(Speed_Diff))) %>%
+                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
+                                                         mean_Spatial_Auto = mean(abs(Spatial_Auto)),
+                                                         sd_Spatial_Auto = sd(abs(Spatial_Auto))) %>%
                                                ungroup()
@@
   xlab("Distance (BL)")
+
+ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
+  geom_point(position=position_dodge(width = 0.6))+
+  geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
+                position=position_dodge(width = 0.6))+
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  theme_classic()
 ```

### 2022-11-29 2Dto3D/Fish_Standardizer.py
Added V2 Data, working on aligning fish

@@ -1,0 +1,74 @@
+
+#The point of this code is to get the fish labled in the same order
+# Since if fish 1 in V1 and V2 isn't the same fish, it will all be a real mess
+#I will attempt to do this by getting x and y values from the head of the fish, and labeling them from 1 to 8
+# up to down and left to right. This will require finding a frame where all those fish are present, as I don't think
+# all these videos have a full first frames. But let's find out!
+
+import pandas as pd
+import numpy as np
+import os
+
+#Header list for reading the raw location CSVs
+header = list(range(4))
+
+#Get all te files
+v1_files = os.listdir("V1 CSVs")
+v2_files = os.listdir("V2 CSVs")
+
+num_fish = 8
+body_parts = ["head","midline2","tailbase","tailtip"]
+
+
+# We have more v1 files than v2, so we do this for every v2 file
+for v2f in v2_files:
+    if v2f.endswith(".csv"):
+
+        #Get a long ID for the matching V1, short ID for the DLT
+        file_id = v2f[0:22]
+        short_id = v2f[0:10]
+
+        print(file_id,short_id)
+
+        #Get the v1 file that matches, and the dlt coefs that go with them both
+        v1f = [f for f in v1_files if file_id in f][0]
+
+        #Add the filepath on here as well
+        v1f = "V1 CSVs/" + v1f
+        v2f = "V2 CSVs/" + v2f
+
+        print(v1f,v2f)
+
+        #Read in the raw data
+        v1_raw_data = pd.read_csv(v1f, index_col=0, header=header)
+        v2_raw_data = pd.read_csv(v2f, index_col=0, header=header)
+
+        v1_scorer = v1_raw_data.keys()[0][0]
+        v2_scorer = v2_raw_data.keys()[0][0]
+
+        data_length = len(v1_raw_data)
+
+        print(data_length)
+
+        both_all_fish_ind = -1
+
+        for i in range(1,data_length):
+            row_sum_v1 = np.sum(v1_raw_data.values[i-1:i])
+            row_sum_v2 = np.sum(v2_raw_data.values[i-1:i])
+
+            if not np.isnan(row_sum_v1+row_sum_v2):
+                both_all_fish_ind = i
+
+                break
+
+        print(both_all_fish_ind)
+
+        #Well... turns out that this might not work since there's not always a time when both have all fish for all data
+        # So I'll talk to Eric and we'll see
+        
+
+
+
+
+
+

### 2022-12-01 Fish Data Analysis/Paper_Figures.qmd
Wrote code to swap IDs in the CSVs

@@
 
-dot_binwidth = 0.015
+dot_binwidth = 0.0125
 ```
@@
   ylab("Probability of a Right Turn") +
-  ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
   scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
@@
   ylab("Probability of a Right Turn") +
-  ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
+  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
    ylim(0,1) +
@@
                      labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "Sensory Conditions")
 
@@
   ylim(0,1) +
-  ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
+  #ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
@@
 
-dark_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+dark_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark") %>%
+                                                  mutate(predicted = predict(dark_eight_and_single_model, type="response")) %>%
+                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                                  summarise(predicted = predicted, n = n()) %>%
+                                                  ungroup()
+
+dark_eight_and_single_graph <- ggplot(dark_eight_and_single_sum,
                            aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(dark_eight_and_single_model, type="response"), color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(dark_eight_and_single_model, type="response"), color = Type)) +
+  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
+  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
   theme_classic() +
@@
   ylim(0,1) +
-  ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
+  #ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
   scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
+  scale_size_continuous(breaks = c(25,50,75)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
                      labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
+                                "3:4","2:5","1:6","0:7")) + 
+  labs(size = "Number of Turns")
 
@@
 
-ablation_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
+ablation_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated")  %>%
+                                                  mutate(predicted = predict(ablation_eight_and_single_model, type="response")) %>%
+                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                                  summarise(predicted = predicted, n = n()) %>%
+                                                  ungroup()
+
+ablation_eight_and_single_graph <- ggplot(ablation_eight_and_single_sum,
                            aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(ablation_eight_and_single_model, type="response"), color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(ablation_eight_and_single_model, type="response"), color = Type)) +
+  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
+  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
   theme_classic() +
@@
   ylim(0,1) +
-  ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
+  #ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
   scale_colour_manual(values = c(sim_color,light_ab_color)) +
+  scale_size_continuous(breaks = c(25,50,75)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
                      labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(size = "Number of Turns")
 
@@
 
-light_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
+light_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light")  %>%
+                                                  mutate(predicted = predict(light_eight_and_single_model, type="response")) %>%
+                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                                  summarise(predicted = predicted, n = n()) %>%
+                                                  ungroup()
+
+light_eight_and_single_graph <- ggplot(light_eight_and_single_sum,
                            aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(light_eight_and_single_model, type="response"), color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(light_eight_and_single_model, type="response"), color = Type)) +
+  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
+  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
   theme_classic() +
@@
   ylim(0,1) +
-  ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
+  #ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
   scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
+  scale_size_continuous(breaks = c(25,50,75)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
   xlab("") +
@@
   theme(legend.position = "none") +
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)
+  ylim(0,3)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
   xlab("") +
@@
   theme(legend.position = "none") +
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)
+  ylim(0,3)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
 
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
-
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Polarization in Still Water") +
+  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
   xlab("") +
@@
   theme(legend.position = "none") +
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)
+  ylim(0,1.15)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
+  #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
   xlab("") +
@@
   theme(legend.position = "none") +
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)
+  ylim(0,1.15)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
 
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
   xlab("") +
@@
   theme(legend.position = "none") +
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)
+  ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
   xlab("") +
@@
   theme(legend.position = "none") +
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)
+  ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
 

### 2022-12-01 2Dto3D/Fish_Standardizer.py

@@ -12,12 +12,38 @@ import os
 #Header list for reading the raw location CSVs
 header = list(range(4))
 
-#Get all te files
+#Get all the files
 v1_files = os.listdir("V1 CSVs")
 v2_files = os.listdir("V2 CSVs")
 
+new_data_folder = "V2 CSVs Adjusted/"
+
 num_fish = 8
 body_parts = ["head","midline2","tailbase","tailtip"]
+
+def get_dist_np(x1s,y1s,x2s,y2s):
+    dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2)
+    return dist
+
+def create_index_col_old(indexes):
+    index_col = []
+
+    for ind in indexes:
+        index_col.append("individual"+str(ind))
+
+    index_col.append("single")
+
+    return(np.asarray(index_col))
+
+def create_index_col(v1_ind, v2_ind):
+    index_col = ["" for i in range(num_fish+1)]
+
+    for i in range(num_fish):
+        index_col[v1_ind[i]-1] = "individual"+str(v2_ind[i])
+
+    index_col[num_fish] = "single"
+
+    return(index_col)
 
 
 # We have more v1 files than v2, so we do this for every v2 file
@@ -53,18 +79,70 @@ for v2f in v2_files:
         both_all_fish_ind = -1
 
         for i in range(1,data_length):
-            row_sum_v1 = np.sum(v1_raw_data.values[i-1:i])
-            row_sum_v2 = np.sum(v2_raw_data.values[i-1:i])
+
+            #We only need there to always be head data, we don't need all the points, so this can still work
+            #Also this is how best to slice a multiindex that's just multicolumns, this data is weird
+            v1_raw_head_data = v1_raw_data.xs('head',axis=1,level=2)
+            v2_raw_head_data = v2_raw_data.xs('head',axis=1,level=2)
+
+            row_sum_v1 = np.sum(v1_raw_head_data.values[i-1:i])
+            row_sum_v2 = np.sum(v2_raw_head_data.values[i-1:i])
 
             if not np.isnan(row_sum_v1+row_sum_v2):
                 both_all_fish_ind = i
 
                 break
 
+        #Okay so now we have an index where all fish heads exist in both views, so we can then we can sort them 
+        # Based on distance to origin, and since they are only in one quadrent this should work to seperate them
         print(both_all_fish_ind)
 
[…]

### 2023-01-11 Fish Data Analysis/Paper_Figures.qmd
Adding group number finding
Also added the code that was used to make and test it to "Old Code"

@@
 
+eight_fish_all_cond_one_chart <- ggplot(turning_data_sum %>% filter(Flow == "Still Water") %>% filter(Type == "Eight Fish"),
+                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow_Ablation_Darkness))+
+  geom_point()+
+  geom_line(alpha = 0.25) +
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
+   ylim(0,1) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "Sensory Conditions")
+
 only_still_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
@@
 eight_fish_flow_model
+
+eight_fish_all_cond_one_chart
 ```
@@
   geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
+  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
   theme_classic() +
@@
   scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
-  scale_size_continuous(breaks = c(25,50,75)) +
+  #scale_size_continuous(breaks = c(25,50,75)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
   labs(size = "Number of Turns")
+
+dark_eight_and_single_graph_real <- ggplot(turning_data_sum %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
+                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
+  geom_point()+
+  geom_line(alpha = 0.25) +
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
+   ylim(0,1) +
+  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "Sensory Conditions")
 
@@
   scale_colour_manual(values = c(sim_color,light_ab_color)) +
-  scale_size_continuous(breaks = c(25,50,75)) +
+  #scale_size_continuous(breaks = c(25,50,75)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
   scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
-  scale_size_continuous(breaks = c(25,50,75)) +
+  #scale_size_continuous(breaks = c(25,50,75)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
 dark_eight_and_single_graph
+
+dark_eight_and_single_graph_real
 ```
@@
                                   Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
-                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed)) %>%
+                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
+                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
                            ungroup()
@@
   theme(legend.position = "none") +
-  ylim(0,8.5)+
+  ylim(-0.1,8.5)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 ```
+### Area
+
+```{r}
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+area_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Area,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Area_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Area_Mean_Val-Area_SD_Val, ymax=Area_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Area (BL^2)") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+area_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Area,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Area_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Area_Mean_Val-Area_SD_Val, ymax=Area_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Area (BL^2)") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+area_still
+area_flow
+```
+
+```{r}
+ggplot(school_data %>% filter(Flow == "Still Water"), 
+       aes(x = NND, y = Area, color = interaction(Ablation,Darkness,sep=", ")))+
+  geom_point()+
+  #geom_smooth(method = "glm", formula = 'y ~ poly(x, 2)', se = FALSE)+
+  geom_smooth(method = "gam", se = FALSE)+
+  theme_classic()+
+  guides(color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  xlab("NND (BL)")+
+  ylab("Area (BL^2)")
+
+```
+
 ### Now we combine them
@@
 
-velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>%
+velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,0.1))) %>%
                                                filter(Flow == "Still Water") %>%
@@
                                                          sd_Speed_Diff = sd(abs(Speed_Diff)),
-                                                         mean_Spatial_Auto = mean(abs(Spatial_Auto)),
-                                                         sd_Spatial_Auto = sd(abs(Spatial_Auto))) %>%
-                                               ungroup()
+                                                         mean_Spatial_Auto = mean(Spatial_Auto),
+                                                         sd_Spatial_Auto = sd(Spatial_Auto),
+                                                         count = n()) %>%
+                                               ungroup() %>%
+                                               mutate(round_Distance = as.numeric(levels(round_Distance))[round_Distance]) %>%
+                                               filter(count > 5)
 ```
@@
   geom_point(position=position_dodge(width = 0.6))+
-  geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
-                position=position_dodge(width = 0.6))+
+  geom_smooth(method = "glm", se = FALSE, color = "black")+
+  #geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
+  #              position=position_dodge(width = 0.6))+
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  facet_wrap(~Flow_Ablation_Darkness)+
   theme_classic()
@@
 ```
+
+## Startle Conditions
+```{r}
+
+startle_school_data <- read.csv("Data/Startle_First_Half_Fish_School_Values.csv")
+startle_school_data <- na.omit(startle_school_data)
+
+startle_school_data <- startle_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           filter(School_Speed < 7) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           group_by(Flow_Ablation_Darkness) %>%
+                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
+                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
+                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
+                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
+                           ungroup() %>% 
+                           mutate(Exp_Label = paste0("Darkness Pre-Startle ",Trial))
+
+startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
+                                             mutate(Exp_Label = "Light")
+
+startle_school_data <- rbind(startle_school_data_light,startle_school_data) %>% 
+                       mutate(Exp_Label = factor(Exp_Label)) %>%
+                       mutate(Exp_Label = fct_relevel(Exp_Label,c("Light",
+                                                                  "Darkness Pre-Startle 1",
+                                                                  "Darkness Pre-Startle 5",
+                                                                  "Darkness Pre-Startle 30")))
+
+```
+
+```{r}
+
+my_comparisons <- list(c("Light", "Darkness Pre-Startle 1"), c("Light", "Darkness Pre-Startle 5"), c("Light", "Darkness Pre-Startle 30"))
+
+nnd_startle <- ggplot(startle_school_data,
+       aes(x = Exp_Label, y = NND,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = NND_Mean_Val), size = 3, color = "Black") +
+  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
+  xlab("") +
+  ylab("NND (BL)") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,3)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+polar_startle <- ggplot(startle_school_data,
+       aes(x = Exp_Label, y = School_Polar,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
+  xlab("") +
+  ylab("Polarization") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,1.15)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+speed_startle <- ggplot(startle_school_data,
+       aes(x = Exp_Label, y = School_Speed,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Speed (BL/s)") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+nnd_startle
+polar_startle
+speed_startle
+
+ggsave("Paper Figures/startle_nnd.png", nnd_startle, width = 12, height = 7)
+
+```

### 2023-01-11 Single Fish Turning Processor/get_turn_bias_midline.py

@@ -41,6 +41,8 @@ def turn_frames(head_x_data,head_y_data,mid_x_data,mid_y_data):
 
         dot_prods[i] = np.dot(vec1,vec2)
 
+        print(vec1, vec2, dot_prods[i])
+
         if np.isnan(np.dot(vec1,vec2)):
             dot_prods[i] = 1
 

### 2023-01-11 data_files_to_csv_4P.py

@@ -13,6 +13,11 @@
 
 from scipy.signal import hilbert, savgol_filter
 from scipy.spatial import ConvexHull
+
+from scipy.spatial import distance_matrix
+import networkx as nx
+import pylab
+
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 from matplotlib import gridspec 
@@ -42,6 +47,10 @@ header = list(range(4))
 def get_dist_np(x1s,y1s,x2s,y2s):
     dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2)
     return dist
+
+def get_mag(vec):
+    mag = np.sqrt(vec[0]**2+vec[1]**2)
+    return mag
 
 def get_fish_length(fish):
     return get_dist_np(fish.head_x,fish.head_y,fish.midline_x,fish.midline_y) + get_dist_np(fish.midline_x,fish.midline_y,fish.tailbase_x,fish.tailbase_y) + get_dist_np(fish.tailbase_x,fish.tailbase_y,fish.tailtip_x,fish.tailtip_y)
@@ -497,7 +506,7 @@ class fish_comp:
         self.spatial_autocor = np.zeros(len(self.f1.velocity_vec))
 
         for i in range(len(self.f1.velocity_vec)):
-            self.spatial_autocor[i] = np.dot(self.f1.velocity_vec[i],self.f2.velocity_vec[i])
+            self.spatial_autocor[i] = np.dot(self.f1.velocity_vec[i],self.f2.velocity_vec[i]) / (get_mag(self.f1.velocity_vec[i])*get_mag(self.f2.velocity_vec[i]))
 
 
     def graph_values(self):
@@ -581,6 +590,7 @@ class school_comps:
         self.group_tailbeat_cor = []
 
         self.school_areas = []
+        self.school_groups = []
 
         self.calc_school_pos_stats()
         self.calc_school_speed()
@@ -589,6 +599,7 @@ class school_comps:
         self.calc_nnd()
         self.calc_tailbeat_cor()
         self.calc_school_area()
+        self.calc_school_groups()
 
     def calc_school_pos_stats(self):
         school_xs = [fish.head_x for fish in self.fishes]
@@ -688,6 +699,42 @@ class school_comps:
                 hull = ConvexHull(points)
 
                 self.school_areas[i] = hull.volume/fish_len**2
+
+    def calc_school_groups(self):
+        min_BL_for_groups = 2
+
+        school_xs = np.asarray([fish.head_x for fish in self.fishes])
[…]

### 2023-01-20 Fish Data Analysis/Final_Plots.Rmd
Ran code to make the 3D data files

@@
 ```
+
+```{r}
+ggplot(school_data %>% filter(Flow == "Still Water"), 
+       aes(x = NND, y = Area, color = interaction(Ablation,Darkness,sep=", ")))+
+  geom_point()+
+  #geom_smooth(method = "glm", formula = 'y ~ poly(x, 2)', se = FALSE)+
+  geom_smooth(method = "gam", se = FALSE)+
+  theme_classic()+
+  guides(color = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  xlab("NND (BL)")+
+  ylab("Area (BL^2)")
+
+```
+
+## Velocity Correlations
+
+```{r}
+raw_comp_data <- read.csv("Data/Fish_Comp_Values.csv")
+raw_comp_data <- na.omit(raw_comp_data)
+
+comp_data <- raw_comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           select(-X)
+
+velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10) %>% filter(Fish1_Speed < 5) %>% filter(Fish2_Speed < 5)  %>% filter(Flow == "Still Water")
+
+velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,1))) %>% filter(round_Distance != 8)
+
+velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,0.1))) %>%
+                                               filter(Flow == "Still Water") %>%
+                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
+                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
+                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
+                                                         mean_Spatial_Auto = mean(Spatial_Auto),
+                                                         sd_Spatial_Auto = sd(Spatial_Auto),
+                                                         count = n()) %>%
+                                               ungroup() %>%
+                                               mutate(round_Distance = as.numeric(levels(round_Distance))[round_Distance]) %>%
+                                               filter(count > 5)
+```
+
+```{r}
+ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
+  geom_point(alpha = 0.1)+
+  theme_classic()+ 
+  theme(legend.position = "none") +
+  ylab("Correlation Strength")+
+  xlab("Distance (BL)")
+
+ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
+  geom_point(position=position_dodge(width = 0.6))+
+  geom_smooth(method = "glm", se = FALSE, color = "black")+
+  #geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
+  #              position=position_dodge(width = 0.6))+
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  facet_wrap(~Flow_Ablation_Darkness)+
+  theme_classic()
+```
+
+```{r}
+
+ggplot(velocity_cor_data, aes(x = Fish1_Speed, y = Fish2_Speed))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(method = "lm")+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+ggplot(velocity_cor_data, aes(x = Distance, y = Fish1_Speed*Fish2_Speed))+
+  geom_point(alpha = 0.1)+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+cor.test(velocity_cor_data$Fish1_Speed,velocity_cor_data$Fish2_Speed)
+
+ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff), 
+                                                                color = Flow_Ablation_Darkness))+
+  geom_violin()+
+  theme_classic()
+
+ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Speed_Diff, color = Flow_Ablation_Darkness))+
+  geom_point(position=position_dodge(width = 0.6))+
+  geom_errorbar(aes(ymin = mean_Speed_Diff-sd_Speed_Diff, ymax = mean_Speed_Diff+sd_Speed_Diff),
+                position=position_dodge(width = 0.6))+
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  theme_classic()
+
+speed_diff_glm <- glm(Speed_Diff ~ round_Distance * Flow_Ablation_Darkness, data = velocity_cor_data)
+Anova(speed_diff_glm)
+
+#emmeans(speed_diff_glm, specs = pairwise ~ Flow_Ablation_Darkness)
+#emmeans(speed_diff_glm, specs = pairwise ~ round_Distance)
+
+```

### 2023-01-20 Fish Data Analysis/Paper_Figures.qmd
Ran code to make the 3D data files

@@
                                   Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
-                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
+                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
+                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups)) %>%
                            ungroup()
@@
 ```
+### Number of Groups
 
 ```{r}
-ggplot(school_data %>% filter(Flow == "Still Water"), 
-       aes(x = NND, y = Area, color = interaction(Ablation,Darkness,sep=", ")))+
-  geom_point()+
-  #geom_smooth(method = "glm", formula = 'y ~ poly(x, 2)', se = FALSE)+
-  geom_smooth(method = "gam", se = FALSE)+
-  theme_classic()+
-  guides(color = guide_legend(title = "Condition")) +
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Groups,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Groups_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Groups_Mean_Val-Area_SD_Val, ymax=Groups_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  xlab("NND (BL)")+
-  ylab("Area (BL^2)")
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Number of Groups") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
 
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+
+group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Groups,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Groups_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Groups_Mean_Val-Groups_SD_Val, ymax=Groups_Mean_Val+Groups_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Number of Groups") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+group_still
+group_flow
 ```
-
 ### Now we combine them
@@
                                     speed_still, speed_flow,
-          labels = c("A", "B", "C", "D", "E", "F"),
-          ncol = 2, nrow = 3)
+                                    group_still, group_flow,
+          labels = c("A", "B", "C", "D", "E", "F", "G", "H"),
+          ncol = 2, nrow = 4)
 
-ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 20)
-```
-
-## Velocity Correlations
-
-```{r}
-raw_comp_data <- read.csv("Data/Fish_Comp_Values.csv")
-raw_comp_data <- na.omit(raw_comp_data)
-
-comp_data <- raw_comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
-                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           select(-X)
-
-velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10) %>% filter(Fish1_Speed < 5) %>% filter(Fish2_Speed < 5)  %>% filter(Flow == "Still Water")
-
-velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,1))) %>% filter(round_Distance != 8)
-
-velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,0.1))) %>%
-                                               filter(Flow == "Still Water") %>%
-                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
-                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
-                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
-                                                         mean_Spatial_Auto = mean(Spatial_Auto),
-                                                         sd_Spatial_Auto = sd(Spatial_Auto),
-                                                         count = n()) %>%
-                                               ungroup() %>%
-                                               mutate(round_Distance = as.numeric(levels(round_Distance))[round_Distance]) %>%
-                                               filter(count > 5)
-```
-
-```{r}
-ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
-  geom_point(alpha = 0.1)+
-  theme_classic()+ 
-  theme(legend.position = "none") +
-  ylab("Correlation Strength")+
-  xlab("Distance (BL)")
-
-ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
-  geom_point(position=position_dodge(width = 0.6))+
-  geom_smooth(method = "glm", se = FALSE, color = "black")+
-  #geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
-  #              position=position_dodge(width = 0.6))+
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  facet_wrap(~Flow_Ablation_Darkness)+
-  theme_classic()
-```
-
-```{r}
-
-ggplot(velocity_cor_data, aes(x = Fish1_Speed, y = Fish2_Speed))+
-  geom_point(alpha = 0.1)+
-  geom_smooth(method = "lm")+
-  theme_classic()+ 
-  theme(legend.position = "none")
-
-ggplot(velocity_cor_data, aes(x = Distance, y = Fish1_Speed*Fish2_Speed))+
-  geom_point(alpha = 0.1)+
-  theme_classic()+ 
-  theme(legend.position = "none")
-
-cor.test(velocity_cor_data$Fish1_Speed,velocity_cor_data$Fish2_Speed)
-
-ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff), 
-                                                                color = Flow_Ablation_Darkness))+
-  geom_violin()+
-  theme_classic()
-
-ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Speed_Diff, color = Flow_Ablation_Darkness))+
-  geom_point(position=position_dodge(width = 0.6))+
-  geom_errorbar(aes(ymin = mean_Speed_Diff-sd_Speed_Diff, ymax = mean_Speed_Diff+sd_Speed_Diff),
-                position=position_dodge(width = 0.6))+
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  theme_classic()
-
-speed_diff_glm <- glm(Speed_Diff ~ round_Distance * Flow_Ablation_Darkness, data = velocity_cor_data)
-Anova(speed_diff_glm)
-
-#emmeans(speed_diff_glm, specs = pairwise ~ Flow_Ablation_Darkness)
-#emmeans(speed_diff_glm, specs = pairwise ~ round_Distance)
-
+ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 30)
 ```

### 2023-01-20 2Dto3D/DLT_Converter.py

@@ -2,7 +2,7 @@ import os
 import numpy as np
 import pandas as pd
 import math
-import plotly.express as px
+#import plotly.express as px
 from scipy import linalg
 
 #Header list for reading the raw location CSVs
@@ -10,7 +10,7 @@ header = list(range(4))
 
 #Get all te files
 v1_files = os.listdir("V1 CSVs")
-v2_files = os.listdir("V2 CSVs")
+v2_files = os.listdir("V2 CSVs Adjusted")
 dlt_coef_files = os.listdir("DLT Coefs")
 
 num_fish = 8
@@ -55,6 +55,8 @@ for v2f in v2_files:
         #Get a long ID for the matching V1, short ID for the DLT
         file_id = v2f[0:22]
         short_id = v2f[0:10]
+
+        print(short_id)
 
         #Get the v1 file that matches, and the dlt coefs that go with them both
         v1f = [f for f in v1_files if file_id in f][0]

### 2023-01-20 2Dto3D/DLT_Plotter.py

@@ -48,23 +48,23 @@ for file_name in three_d_files:
 
         #Now we graph it, nice and easy
 
-        print(df)
+        # print(df)
 
-        df.to_csv()
+        # df.to_csv()
 
-        sys.exit()
+        # sys.exit()
 
-        # #Though the axies keep shifting weirdly so not my fave
-        # fig = px.scatter_3d(df,x="x", y="y", z="z", color="Fish", animation_frame="Frame", hover_data = ["BodyPart"],
-        #                        range_x=[df["x"].min()-0.05,df["x"].max()+0.05],
-        #                        range_y=[df["y"].min()-0.05,df["y"].max()+0.05],
-        #                        range_z=[df["z"].min()-0.05,df["z"].max()+0.05],
-        #                        color_continuous_scale = "rainbow")
+        #Though the axies keep shifting weirdly so not my fave
+        fig = px.scatter_3d(df,x="x", y="y", z="z", color="Fish", animation_frame="Frame", hover_data = ["BodyPart"],
+                               range_x=[df["x"].min()-0.05,df["x"].max()+0.05],
+                               range_y=[df["y"].min()-0.05,df["y"].max()+0.05],
+                               range_z=[df["z"].min()-0.05,df["z"].max()+0.05],
+                               color_continuous_scale = "rainbow")
 
-        # fig.layout.scene.aspectratio = {'x':1, 'y':1, 'z':1}
+        fig.layout.scene.aspectratio = {'x':1, 'y':1, 'z':1}
 
-        # #fig.show()
+        #fig.show()
 
-        # file_id = file_name[0:22]
+        file_id = file_name[0:22]
 
-        # fig.write_html("Saved 3D Plots/{name}.html".format(name = file_id), auto_play=False)
+        fig.write_html("Saved 3D Plots/{name}.html".format(name = file_id), auto_play=False)

### 2023-01-26 Fish Data Analysis/Paper_Figures.qmd
Fixed Error with length calculation

@@
 ```{r}
-school_data <- read.csv("Data/Fish_School_Values.csv")
+school_data <- read.csv("Data/Fish_School_Values_3D.csv")
 school_data <- na.omit(school_data)
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
 
@@
   theme(legend.position = "none") +
-  ylim(0,3)+
+  #ylim(0,3)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
 
@@
 ```
+
 ### Polarization
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+
 polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
@@
   theme(legend.position = "none") +
-  ylim(0,1.15)+
+  #ylim(0,1.15)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
   theme(legend.position = "none") +
-  ylim(-0.1,8.5)+
+  #ylim(-0.1,8.5)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
   theme(legend.position = "none") +
-  ylim(0,8.5)+
+  #ylim(0,8.5)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 ```
+
 ### Area
@@
 ```
+
 ### Number of Groups
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+group_sum_data <- school_data %>% group_by(Flow, Ablation, Darkness, Groups) %>%
+                            summarise(count = n()) %>%
+                            ungroup() %>%
+                            mutate(Groups = as.factor(Groups),
+                                   Groups = fct_rev(Groups))
 
-group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Groups,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Groups_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Groups_Mean_Val-Area_SD_Val, ymax=Groups_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "),
+           y = count,
+           fill = Groups)) + 
+    geom_bar(position="fill", stat="identity")+
     xlab("") +
-  ylab("Number of Groups") +
+    ylab("Proportion of Time with this Many Groups") +
     theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+    scale_fill_manual(values=c("#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
     theme(axis.text.x = element_text(size = 15),
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
-
-group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Groups,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Groups_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Groups_Mean_Val-Groups_SD_Val, ymax=Groups_Mean_Val+Groups_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = interaction(Ablation,Darkness,sep=", "),
+           y = count,
+           fill = Groups)) + 
+    geom_bar(position="fill", stat="identity")+
     xlab("") +
-  ylab("Number of Groups") +
+    ylab("Proportion of Time with this Many Groups") +
     theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
     theme(axis.text.x = element_text(size = 15),
@@
 group_flow
+
 ```
+
 ### Now we combine them
@@
 
-ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 30)
+ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 14, height = 30)
 ```
@@
 ## Startle Conditions
+
 ```{r}
@@
 startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
-                                             mutate(Exp_Label = "Light")
+                                             mutate(Exp_Label = "Light") %>%
+                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))
 

### 2023-01-26 2D_3D_Compare_Plotter.py

@@ -13,7 +13,7 @@ num_fish = 8
 body_parts = ["head","midline2","tailbase","tailtip"]
 
 files_3D = os.listdir("3D_Finished_Fish_Data_4P_gaps")
-files_2D = os.listdir("Finished_Fish_Data_4P_gaps_Same_3D")
+files_2D = os.listdir("Finished_Fish_Data_4P_gaps")
 
 for file_3D in files_3D:
 
@@ -21,11 +21,13 @@ for file_3D in files_3D:
         file_id = file_3D[0:22]
         short_id = file_3D[0:10]
 
+        print(file_id)
+
         #Get the v1 file that matches, and the dlt coefs that go with them both
         file_2D = [f for f in files_2D if file_id in f][0]
 
         file_3D = "3D_Finished_Fish_Data_4P_gaps/" + file_3D
-        file_2D = "Finished_Fish_Data_4P_gaps_Same_3D/" + file_2D
+        file_2D = "Finished_Fish_Data_4P_gaps/" + file_2D
 
         files_to_do = [file_2D,file_3D]
 
@@ -35,6 +37,8 @@ for file_3D in files_3D:
             df = pd.melt(fish_raw_data)
 
             #Let's rename things to what they actually are
+            #It does it twice since the namming seems different between 2d and 3d
+            df = df.rename(columns={"scorer": "Scorer", "individuals": "Fish", "bodyparts": "BodyPart", "coords": "Point"})
             df = df.rename(columns={"variable_0": "Scorer", "variable_1": "Fish", "variable_2": "BodyPart", "variable_3": "Point"})
 
             #So now I add the Frame to this because I will need to group by that otherwise there is overlap between labels

### 2023-01-26 3D_data_files_to_csv_4P.py

@@ -15,6 +15,11 @@
 
 from scipy.signal import hilbert, savgol_filter
 from scipy.spatial import ConvexHull
+
+from scipy.spatial import distance_matrix
+import networkx as nx
+import pylab
+
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 from matplotlib import gridspec 
@@ -35,14 +40,22 @@ moving_average_n = 35
 #Tailbeat len is the median of all frame distances between tailbeats
 tailbeat_len = 19
 
+
 #Fish len is the median of all fish lengths in pixels
 #Scale is different becasue of calibration
-fish_len = 0.07195
+fish_len = 0.07862
+
+#Used to try and remove weird times where fish extend
+# Fish SD
+fish_sd = 0.39930
+
+# Fish Len Max?
+fish_max_len = fish_len + 3*fish_sd
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
 
-def get_dist_np(x1s,y1s,x2s,y2s):
+def get_dist_np_2D(x1s,y1s,x2s,y2s):
     dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2)
     return dist
 
@@ -51,7 +64,9 @@ def get_dist_np_3D(x1s,y1s,z1s,x2s,y2s,z2s):
     return dist
 
 def get_fish_length(fish):
-    return get_dist_np(fish.head_x,fish.head_y,fish.midline_x,fish.midline_y) + get_dist_np(fish.midline_x,fish.midline_y,fish.tailbase_x,fish.tailbase_y) + get_dist_np(fish.tailbase_x,fish.tailbase_y,fish.tailtip_x,fish.tailtip_y)
+    return (get_dist_np_3D(fish.head_x,fish.head_y,fish.head_z,fish.midline_x,fish.midline_y,fish.midline_z) + 
+            get_dist_np_3D(fish.midline_x,fish.midline_y,fish.midline_z,fish.tailbase_x,fish.tailbase_y,fish.tailbase_z) +
+            get_dist_np_3D(fish.tailbase_x,fish.tailbase_y,fish.tailbase_z,fish.tailtip_x,fish.tailtip_y,fish.tailtip_z))
 
 def moving_average(x, w):
     #Here I am using rolling instead of convolve in order to not have massive gaps from a single nan
@@ -73,7 +88,19 @@ def mean_tailbeat_chunk(data,tailbeat_len):
[…]

### 2023-01-26 data_files_to_csv_4P.py

@@ -173,12 +173,17 @@ class fish_data:
         self.speed = []
         self.zero_crossings = []
         self.tb_freq_reps = []
+        self.body_lengths = []
 
         #This calcualtes the summary stats
         self.calc_heading()
         self.calc_speed()
         self.calc_tailtip_perp()
         self.calc_tb_freq()
+        self.get_fish_BL()
+
+    def get_fish_BL(self):
+        self.body_lengths = get_dist_np(self.head_x,self.head_y,self.midline_x,self.midline_y) + get_dist_np(self.midline_x,self.midline_y,self.tailbase_x,self.tailbase_y) + get_dist_np(self.tailbase_x,self.tailbase_y,self.tailtip_x,self.tailtip_y)
 
     #This function calcualtes the pitch heading of the fish at each timepoint
     #We are using body heading now, so midline to head, not head to next head
@@ -796,6 +801,7 @@ class trial:
             chunked_headings = angular_mean_tailbeat_chunk(fish.heading,tailbeat_len)
             chunked_speeds = mean_tailbeat_chunk(fish.speed,tailbeat_len)
             chunked_tb_freqs = mean_tailbeat_chunk(fish.tb_freq_reps,tailbeat_len)
+            chunked_body_lengths = mean_tailbeat_chunk(fish.body_lengths,tailbeat_len)
             chunked_x = mean_tailbeat_chunk(fish.head_x,tailbeat_len)
             chunked_y = mean_tailbeat_chunk(fish.head_y,tailbeat_len)
 

### 2023-01-27 Fish Data Analysis/Paper_Figures.qmd
Moved around files

@@
                            mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           filter(School_Speed < 7) %>%
+                           #filter(School_Speed < 7) %>%
                            mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
@@
     theme_light()+ 
-    scale_fill_manual(values=c("#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
+    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
     theme(axis.text.x = element_text(size = 15),

### 2023-02-02 Fish Data Analysis/Paper_Figures.qmd
Testing 3D vs 2D graphs

@@
 startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
-                                             mutate(Exp_Label = "Light") %>%
-                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))
+                                             mutate(Exp_Label = "Light") #%>%
+                                             #select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))
 

### 2023-02-02 3D_data_files_to_csv_4P.py

@@ -13,7 +13,7 @@
 # nested for loops. Fish may be their own objects inside of the trial objects so that they can be quickly compared. Which may mean that I need to 
 # take apart fish_core_4P.py. In the end I think a lot of this will be easier to do with pandas and objects instead of reading line by line.
 
-from scipy.signal import hilbert, savgol_filter
+from scipy.signal import hilbert, savgol_filter, medfilt
 from scipy.spatial import ConvexHull
 
 from scipy.spatial import distance_matrix
@@ -88,7 +88,7 @@ def mean_tailbeat_chunk(data,tailbeat_len):
         start = k//tailbeat_len * tailbeat_len
         end = (k//tailbeat_len + 1) * tailbeat_len
 
-        mean_data[k] = np.nanmean(data[start:end])
+        mean_data[k] = np.mean(data[start:end])
 
     return mean_data[::tailbeat_len]
 
@@ -100,7 +100,7 @@ def median_tailbeat_chunk(data,tailbeat_len):
         start = k//tailbeat_len * tailbeat_len
         end = (k//tailbeat_len + 1) * tailbeat_len
 
-        mean_data[k] = np.nanmedian(data[start:end])
+        mean_data[k] = np.median(data[start:end])
 
     return mean_data[::tailbeat_len]
 
@@ -209,19 +209,21 @@ class fish_data:
         self.tb_freq_reps = []
         self.body_lengths = []
 
+
+        #Okay, so I want to remove data where fish are too long
+        # So I am going to just do that, and void it out here with nans
+        # Since all further functions draw from these positional values, I just null them here
+        self.get_fish_BL()
+        self.remove_long_fish()
+
         #This calcualtes the summary stats
         self.calc_yaw_heading()
         self.calc_pitch_heading()
         self.calc_speed()
         self.calc_tailtip_perp()
         self.calc_tb_freq()
-        self.get_fish_BL()
-
-        #Okay, so I want to remove data where fish are too long
-        # So I am going to just do that, and void it out here with nans
-        # Since all further functions draw from these positional values, I just null them here
-
-        self.remove_long_fish()
+        
+        
 
     def get_fish_BL(self):
         self.body_lengths = (get_dist_np_3D(self.head_x,self.head_y,self.head_z,self.midline_x,self.midline_y,self.midline_z) + 
@@ -691,6 +693,9 @@ class school_comps:
         self.school_groups = []
 
[…]

### 2023-02-02 data_files_to_csv_4P.py

@@ -39,7 +39,7 @@ moving_average_n = 35
 tailbeat_len = 19
 
 #Fish len is the median of all fish lengths in pixels
-fish_len = 193
+fish_len = 193 #0.07862 #
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
@@ -76,6 +76,18 @@ def mean_tailbeat_chunk(data,tailbeat_len):
         end = (k//tailbeat_len + 1) * tailbeat_len
 
         mean_data[k] = np.mean(data[start:end])
+
+    return mean_data[::tailbeat_len]
+
+def median_tailbeat_chunk(data,tailbeat_len):
+    max_tb_frame = len(data)-len(data)%tailbeat_len
+    mean_data = np.zeros(max_tb_frame)
+
+    for k in range(max_tb_frame):
+        start = k//tailbeat_len * tailbeat_len
+        end = (k//tailbeat_len + 1) * tailbeat_len
+
+        mean_data[k] = np.median(data[start:end])
 
     return mean_data[::tailbeat_len]
 
@@ -606,6 +618,8 @@ class school_comps:
         self.calc_school_area()
         self.calc_school_groups()
 
+        #self.graph_values()
+
     def calc_school_pos_stats(self):
         school_xs = [fish.head_x for fish in self.fishes]
         school_ys = [fish.head_y for fish in self.fishes]
@@ -654,9 +668,9 @@ class school_comps:
 
     def calc_nnd(self):
         #first we make an array to fill with the NNDs 
-        nnd_array = np.asarray([[[999 for j in range(self.n_fish)] for i in range(self.n_fish)] for t in range(len(self.school_center_x))])
+        #nnd_array = np.asarray([[[999 for j in range(self.n_fish)] for i in range(self.n_fish)] for t in range(len(self.school_center_x))])
 
-        nnd_array  = np.zeros((len(self.school_center_x),self.n_fish,self.n_fish)) + 999
+        nnd_array  = np.zeros((len(self.school_center_x),self.n_fish,self.n_fish)) + np.nan
 
         #now calculate all nnds
         for i in range(self.n_fish):
@@ -740,6 +754,44 @@ class school_comps:
             n_groups = len([len(c) for c in sorted(nx.connected_components(G), key=len, reverse=True)])
 
             self.school_groups[i] = n_groups
+
+    def graph_values(self):
+        fig = plt.figure(figsize=(16, 10))
[…]

### 2023-02-09 Fish Data Analysis/Paper_Figures.qmd
Fixed code not pulling from correct V2 files
Code was only pulling from the base V2 file as I had a hard coded link in the middle. Now it uses the correct data files each time

@@
 library(emmeans)
+
 ```
@@
     theme_light()+ 
-    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
+    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB","#FF0000")) +
     theme(axis.text.x = element_text(size = 15),

### 2023-02-09 Fish Data Analysis/Parallax Testing.qmd
Fixed code not pulling from correct V2 files
Code was only pulling from the base V2 file as I had a hard coded link in the middle. Now it uses the correct data files each time

---
title: "Parallax Testing"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(viridis)

```

## Functions and Variables

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.0125
```

```{r}
data_2d <- read.csv("Data/Fish_Comp_Values.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))

data_3d_xy <- read.csv("Data/Fish_Comp_Values_3D_xy.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))
```

```{r}

data_2d_still_sum <- data_2d %>% filter(Darkness == "Light" & Ablation == "No Ablation") %>%
                                  mutate(round_fish1_x = round_any(Fish1_X/193,0.25),
                                         round_fish1_y = round_any(Fish1_Y/193,0.25)) %>%
                                  group_by(round_fish1_x,round_fish1_y) %>%
                                  summarise(mean_dist_2d = mean(Distance, na.rm = TRUE)) %>%
                                  ungroup()

data_3d_xy_still_sum <- data_3d_xy %>% filter(Darkness == "Light" & Ablation == "No Ablation") %>%
                                  mutate(round_fish1_x = round_any(Fish1_X/0.07862,0.25),
                                         round_fish1_y = round_any(Fish1_Y/0.07862,0.25)) %>%
                                  group_by(round_fish1_x,round_fish1_y) %>%
                                  summarise(mean_dist_3d_xy = mean(Distance, na.rm = TRUE)) %>%
                                  ungroup()

data_both <- full_join(data_3d_xy_still_sum, data_2d_still_sum) %>% na.omit() %>%
                      mutate(dist_diff = abs(mean_dist_3d_xy - mean_dist_2d))

```

Graphing NND in 2D
```{r}
ggplot(data_2d_still_sum, aes(round_fish1_x,round_fish1_y, color = mean_dist_2d))+
  geom_point(size = 4, shape = 15)+
  scale_color_viridis() +
  theme_classic() +
  coord_fixed()

ggplot(data_3d_xy_still_sum, aes(round_fish1_x,round_fish1_y, color = mean_dist_3d_xy))+
  geom_point(size = 2, shape = 15)+
  scale_color_viridis() +
  theme_classic() +
  coord_fixed()

ggplot(data_both, aes(round_fish1_x,round_fish1_y, color = dist_diff))+
  geom_point(size = 8, shape = 15)+
  scale_color_viridis() +
  theme_classic() +
  coord_fixed()

ggplot(data_both, aes(round_fish1_x,dist_diff))+
  geom_point()+
  geom_smooth(method = "glm", formula = "y ~ poly(x,2)")+ 
  theme_classic()

ggplot(data_both, aes(round_fish1_y,dist_diff))+
  geom_point()+
  geom_smooth(method = "glm", formula = "y ~ poly(x,2)")+
  theme_classic()
```

```{r}

xy_glm <- glm(dist_diff ~ round_fish1_x + round_fish1_y, data = data_both)
x2y_glm <- glm(dist_diff ~ I(round_fish1_x^2) + round_fish1_y, data = data_both)
xy2_glm <- glm(dist_diff ~ round_fish1_x + I(round_fish1_y^2), data = data_both)
xx2y_glm <- glm(dist_diff ~ round_fish1_x + I(round_fish1_x^2) + round_fish1_y, data = data_both)
xyy2_glm <- glm(dist_diff ~ round_fish1_x + round_fish1_y + I(round_fish1_y^2), data = data_both)
x2y2_glm <- glm(dist_diff ~ I(round_fish1_x^2) + I(round_fish1_y^2), data = data_both)

xx2y_m_glm <- glm(dist_diff ~ (round_fish1_x + I(round_fish1_x^2)) * round_fish1_y, data = data_both)

ICtab(xy_glm,x2y_glm,xy2_glm,xx2y_glm,xyy2_glm,x2y2_glm,xx2y_m_glm)

Anova(xx2y_m_glm)

data_both <- data_both %>% mutate(modeled = predict(xx2y_m_glm))

ggplot(data_both, aes(round_fish1_x,round_fish1_y, color = modeled))+
  geom_point(size = 8, shape = 15)+
  scale_color_viridis() +
  theme_classic() +
  coord_fixed()

```

### 2023-02-09 2Dto3D/DLT_Converter.py

@@ -9,9 +9,13 @@ from scipy import linalg
 header = list(range(4))
 
 #Get all te files
-v1_files = os.listdir("V1 CSVs")
-v2_files = os.listdir("V2 CSVs Adjusted")
-dlt_coef_files = os.listdir("DLT Coefs")
+v1_filepath = "V1 CSVs/"
+v2_filepath = "V2 CSVs Adjusted/"
+dlt_coef_filepath = "DLT Coefs/"
+
+v1_files = os.listdir(v1_filepath)
+v2_files = os.listdir(v2_filepath)
+dlt_coef_files = os.listdir(dlt_coef_filepath)
 
 num_fish = 8
 body_parts = ["head","midline2","tailbase","tailtip"]
@@ -64,9 +68,9 @@ for v2f in v2_files:
         dlt_coefs_file = [f for f in dlt_coef_files if short_id in f][0]
 
         #Add the filepath on here as well
-        v1f = "V1 CSVs/" + v1f
-        v2f = "V2 CSVs/" + v2f
-        dlt_coefs_file = "DLT Coefs/" + dlt_coefs_file
+        v1f = v1_filepath + v1f
+        v2f = v2_filepath + v2f
+        dlt_coefs_file = dlt_coef_filepath + dlt_coefs_file
 
         print(v1f,v2f,dlt_coefs_file)
 
@@ -123,7 +127,7 @@ for v2f in v2_files:
 
         fish_out_df = pd.DataFrame.from_dict(fish_data_out_dict)
         #Replace to make new file name
-        new_file_name = v2f.replace("V2 CSVs/","").replace("V2","3D_")
+        new_file_name = v2f.replace(v2_filepath,"").replace("V2","3D_").replace("TN","LN")
         fish_out_df.to_csv("/Users/Ben/Desktop/Fish-Midline-Processer/2Dto3D/Final 3D/"+new_file_name)
 
 

### 2023-02-09 2Dto3D/DLT_Plotter.py

@@ -14,7 +14,7 @@ body_parts = ["head","midline2","tailbase","tailtip"]
 
 file_folder = "Final 3D/"
 
-three_d_files = os.listdir("Final 3D")
+three_d_files = os.listdir(file_folder)
 
 for file_name in three_d_files:
     if file_name.endswith(".csv"):

### 2023-02-09 3D_data_files_to_csv_4P.py

@@ -349,8 +349,13 @@ class fish_data:
         #Some fish are gone entirely, and this breaks if I call an index when the fish don't have any points
         if(len(self.zero_crossings) > 0):
             tailbeat_lengths[0] += self.zero_crossings[0]
-            #Now we append this here so that they all stay the same length. This basically extends the last tailbeat.
-            self.tb_freq_reps = np.repeat(np.append(tb_freq,tb_freq[-1]),tailbeat_lengths) #[:len(tb_freq)])
+
+            #Sometimes there are no zero crossings, which seems wrong but I'm going to catching for it anyways rn
+            if len(tailbeat_lengths) == 1:
+                self.tb_freq_reps = np.repeat(0,tailbeat_lengths)
+            else:
+                #Now we append this here so that they all stay the same length. This basically extends the last tailbeat.
+                self.tb_freq_reps = np.repeat(np.append(tb_freq,tb_freq[-1]),tailbeat_lengths) #[:len(tb_freq)])
 
     #Thsi function allows me to graph values for any fish without trying to cram it into a for loop somewhere
     def graph_values(self):

### 2023-02-09 data_files_to_csv_4P.py

@@ -39,7 +39,7 @@ moving_average_n = 35
 tailbeat_len = 19
 
 #Fish len is the median of all fish lengths in pixels
-fish_len = 193 #0.07862 #
+fish_len = 0.07862 #193 0.07862 #
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
@@ -277,8 +277,13 @@ class fish_data:
         #Some fish are gone entirely, and this breaks if I call an index when the fish don't have any points
         if(len(self.zero_crossings) > 0):
             tailbeat_lengths[0] += self.zero_crossings[0]
-            #Now we append this here so that they all stay the same length. This basically extends the last tailbeat.
-            self.tb_freq_reps = np.repeat(np.append(tb_freq,tb_freq[-1]),tailbeat_lengths) #[:len(tb_freq)])
+
+            #Sometimes there are no zero crossings, which seems wrong but I'm going to catching for it anyways rn
+            if len(tailbeat_lengths) == 1:
+                self.tb_freq_reps = np.repeat(0,tailbeat_lengths)
+            else:
+                #Now we append this here so that they all stay the same length. This basically extends the last tailbeat.
+                self.tb_freq_reps = np.repeat(np.append(tb_freq,tb_freq[-1]),tailbeat_lengths) #[:len(tb_freq)])
 
 
     #Thsi function allows me to graph values for any fish without trying to cram it into a for loop somewhere
@@ -891,6 +896,13 @@ class trial:
 
             current_comp = self.fish_comps[pair[0]][pair[1]]
 
+            chunked_f1_x = mean_tailbeat_chunk(current_comp.f1.head_x,tailbeat_len)
+            chunked_f1_y = mean_tailbeat_chunk(current_comp.f1.head_y,tailbeat_len)
+
+            chunked_f2_x = mean_tailbeat_chunk(current_comp.f2.head_x,tailbeat_len)
+            chunked_f2_y = mean_tailbeat_chunk(current_comp.f2.head_y,tailbeat_len)
+
+
             chunked_x_diffs = mean_tailbeat_chunk(current_comp.x_diff,tailbeat_len)
             chunked_y_diffs = mean_tailbeat_chunk(current_comp.y_diff,tailbeat_len)
[…]

### 2023-02-15 Charuco_DLT/rearrange_point_for_easywand.Rmd
Added Charuco Code

---
title: "R Notebook"
output: html_notebook
---

```{r setup}
library("tidyverse")
library("plotly")
library("imager")
library("here")
```

First step: Run `detect_charuco.ipynb` to detect the points in the videos of
the CHaRuCO boards.

Fill in the name of the output CSV file from `detect_charuco.ipynb`.
```{r}
detections <- read_csv("/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09/boards.csv") |> 
  select(-`...1`)
```

Fill in the directory that has the video files and the names of each video.
```{r}
videodir <- '/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09'
camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
camfiles <- map(camfiles, ~ file.path(videodir, .x))
```

NB: The code below uses `imager`, which won't load frames properly if there 
are any spaces in the path name anywhere

Make sure you set the video frame rate correctly.
```{r}
fps <- 20
```

This will show the 2D locations of each point for one camera.

```{r}
cam <- 2

detections |> 
  filter(camera == cam-1) |> 
  ggplot(aes(x = x, y = y, color = frame)) +
  geom_point()
```
This shows the range of x and y coordinates in the two cameras, just to check.
```{r}
detections |> 
  group_by(camera) |> 
  summarize(fr_hi = max(frame, na.rm = TRUE),
            across(c(x, y), 
                   list(lo = ~min(.x, na.rm = TRUE), hi = ~max(.x, na.rm = TRUE))))

```

This *should* load in a frame from one of the videos, but it doesn't always work, and I'm
not sure why.
```{r}
fr <- 10
cam <- 2

vidtime <- (fr-1) / fps

I1 <- imager::load.video(camfiles[[cam]], 
                         skip.to = vidtime,
                         frames = 1)
I1 <- as.data.frame(I1)
```

If the above block worked, then you should be able to plot the points and image
together here and check to make sure they look OK.
```{r}
detections |> 
  filter(frame == fr-1 & camera == cam-1) |> 
  ggplot(aes(x = x, y = y)) +
  geom_raster(data = I1, aes(x = x, y = y, fill = value)) +
  geom_point(aes(color = factor(id)))
```
# Set up points for EasyWand

To rearrange the points for EasyWand, we generate a fake "wand", which is any
pair of points that are separated by the same distance. This takes all of the pairs
that are separated by 1 grid square, which generates a *lot* of pairs. Not
every computer can process all of those points, so sometimes you want to generate
a smaller number. The "wand length" here is 1 grid square (=24.33 mm).
```{r}
pairs <- list(c(0,1), c(1,2), c(2,3), c(3,4),
              c(5,6), c(6,7), c(7,8), c(8,9),
              c(10,11), c(11,12), c(12,13), c(13,14),
              c(15,16), c(16,17), c(17,18), c(18,19),
              c(20,21), c(21,22), c(22,23), c(23,24),
              c(0,5), c(5,10), c(10,15), c(15,20),
              c(4,9), c(9,14), c(14,19), c(19,24))
```

This just gives the 4 pairs along the 4 edges of the grid. Then the "wand length" is
4 grid squares (=97.32mm).
```{r}
pairs <- list(c(0,4), c(4,24), c(24,20), c(20,0))
```

Generate all the pairs.
```{r}
mall <- list()
for (i in seq_along(pairs)) {
  p1 <- pairs[[i]]

  a1 <- detections |> filter(id == p1[1]) |> 
    rename(pt1_X = x, pt1_Y = y)
  a2 <- detections |> filter(id == p1[2]) |> 
    rename(pt2_X = x, pt2_Y = y)

  if (nrow(a1) > 0 & nrow(a2) > 0) {
    mall[[i]] = left_join(a1, a2, by = c('frame', 'camera')) |> 
      unite(id, c('id.x', 'id.y'))
  }
}

m <- bind_rows(mall)
```

Take a look at the beginning of the data frame, just to check.
```{r}
head(m)
```

Finish the reorganization.
```{r}
ptsforeasywand <-
  m |> 
  expand(camera, frame) |> 
  left_join(m, by = c('camera', 'frame')) |> 
  na.omit() |> 
  filter(!str_detect(id, 'NA')) |> 
  mutate(camera = camera+1) |> 
  pivot_wider(names_from = camera, values_from = starts_with('pt')) |> 
  rename_with(~str_replace(.x, '(pt\\d)_([X|Y])_(\\d)', '\\1_cam\\3_\\2')) |>
  select(pt1_cam1_X, pt1_cam1_Y,
         pt1_cam2_X, pt1_cam2_Y,
         pt2_cam1_X, pt2_cam1_Y,
         pt2_cam2_X, pt2_cam2_Y) |> 
  na.omit()

head(ptsforeasywand)
```

And save out the CSV.
```{r}
write_csv(ptsforeasywand, "/Users/Ben/Desktop/Charuco_DLT/2023_02_XX_calibrationcharuco_xypts.csv")
```

Final step: Load the CSV into EasyWand, punch in the correct fake "wand length",
add the camera parameters (resolution and focal length in pixels; check the SOPs
for 3D calibrations for these details for our cameras), and run the calibration.

### 2023-02-15 Fish Data Analysis/Paper_Figures.qmd
Added Charuco Code

@@
                                   Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
-                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups)) %>%
+                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
+                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                            ungroup()
@@
   xlab("") +
-  ylab("NND (BL)") +
+  ylab("School Height (BL)") +
   theme_light()+ 
@@
 nnd_flow
+```
+### Height Plot
+
+```{r}
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+
+height_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Height,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Height_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Height_Mean_Val-Height_SD_Val, ymax=Height_Mean_Val+Height_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
+  xlab("") +
+  ylab("NND (BL)") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,3)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+
+height_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Height,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Height_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Height_Mean_Val-Height_SD_Val, ymax=Height_Mean_Val+Height_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
+  xlab("") +
+  ylab("NND (BL)") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,3)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+height_still
+height_flow
 ```

### 2023-02-15 3D_data_files_to_csv_4P.py

@@ -697,6 +697,8 @@ class school_comps:
         self.school_areas = []
         self.school_groups = []
 
+        self.school_height = []
+
         self.calc_school_pos_stats()
 
         self.remove_and_smooth_points()
@@ -708,6 +710,7 @@ class school_comps:
         self.calc_tailbeat_cor()
         self.calc_school_area()
         self.calc_school_groups()
+        self.calc_school_height()
 
         #self.graph_values()
 
@@ -897,6 +900,12 @@ class school_comps:
             n_groups = len([len(c) for c in sorted(nx.connected_components(G), key=len, reverse=True)])
 
             self.school_groups[i] = n_groups
+
+    def calc_school_height(self):
+        school_zs = np.asarray([fish.head_z for fish in self.fishes])
+
+        self.school_height = np.nanmax(school_zs, axis = 0) - np.nanmin(school_zs, axis = 0)
+
 
     def graph_values(self):
         fig = plt.figure(figsize=(16, 10))
@@ -1159,10 +1168,11 @@ class trial:
         chunked_nnd = mean_tailbeat_chunk(self.school_comp.nearest_neighbor_distance,tailbeat_len)
         chunked_area = mean_tailbeat_chunk(self.school_comp.school_areas,tailbeat_len)
         chunked_groups = median_tailbeat_chunk(self.school_comp.school_groups,tailbeat_len)
+        chunked_height = mean_tailbeat_chunk(self.school_comp.school_height,tailbeat_len)
 
         short_data_length = min([len(chunked_x_center),len(chunked_y_center),len(chunked_x_sd),
                                  len(chunked_y_sd),len(chunked_group_speed),len(chunked_group_tb_freq),
-                                 len(chunked_nnd),len(chunked_area)])
+                                 len(chunked_nnd),len(chunked_area),len(chunked_groups),len(chunked_height)])
 
         d = {'Year': np.repeat(self.year,short_data_length),
              'Month': np.repeat(self.month,short_data_length),
@@ -1183,7 +1193,8 @@ class trial:
              'School_TB_Freq': chunked_group_tb_freq[:short_data_length], 
              'NND': chunked_nnd[:short_data_length],
              'Area': chunked_area[:short_data_length],
-             'Groups': chunked_groups[:short_data_length]}
+             'Groups': chunked_groups[:short_data_length],
+             'School_Height': chunked_height[:short_data_length]}
 
         out_data = pd.DataFrame(data=d)
 

### 2023-02-16 Fish Data Analysis/Paper_Figures.qmd
Marking place before grouping change
Working on groups in 3D, looking to see how hard it would be to look at all body part distances

@@
                            mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           #filter(School_Speed < 7) %>%
+                           filter(School_Speed <= 5) %>%
                            mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
@@
                                   Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
+                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                   Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 
@@
 nnd_flow
+
+nnd_glm <- glm(NND ~ Ablation:Darkness:Flow, data = school_data)
+emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)
+
 ```
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))
 
@@
 height_flow
+
+height_glm <- glm(School_Height ~ Ablation:Darkness:Flow, data = school_data)
+emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list()
 
@@
 polar_flow
+
+polar_glm <- glm(School_Polar ~ Ablation:Darkness:Flow, data = school_data)
+emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))
 
@@
 speed_flow
+
+speed_glm <- glm(School_Speed ~ Ablation:Darkness:Flow, data = school_data)
+emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
 area_flow
+
+area_glm <- glm(Area ~ Ablation:Darkness:Flow, data = school_data)
+emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
+```
+### Groups as Mean
+
+```{r}
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+
+mean_group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Mean Number of Groups") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+
+mean_group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
+  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
+  xlab("") +
+  ylab("Mean Number of Groups") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  #ylim(0,8.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.y = element_text(size = 15))
+
+mean_group_still
+mean_group_flow
+
 ```
@@
     theme_light()+ 
-    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB","#FF0000")) +
+    scale_fill_manual(values=c("#1D3557","#325A7C","#457B9D","#7BAFBF","#A8DADC","#D0EBE6","#F1FAEE","#e63946")) +
     theme(axis.text.x = element_text(size = 15),
@@
 group_flow
+
+groups_glm <- glm(Groups ~ Ablation:Darkness:Flow, data = school_data)
+emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 
@@
 startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
-                                             mutate(Exp_Label = "Light") #%>%
-                                             #select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))
+                                             mutate(Exp_Label = "Light") %>%
+                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val,
+                                                       School_Height, Height_Mean_Val, Height_SD_Val))
 

### 2023-02-16 2Dto3D/DLT_Converter.py

@@ -10,7 +10,7 @@ header = list(range(4))
 
 #Get all te files
 v1_filepath = "V1 CSVs/"
-v2_filepath = "V2 CSVs Adjusted/"
+v2_filepath = "V2 CSVs Adjusted Manual/"
 dlt_coef_filepath = "DLT Coefs/"
 
 v1_files = os.listdir(v1_filepath)
@@ -128,7 +128,7 @@ for v2f in v2_files:
         fish_out_df = pd.DataFrame.from_dict(fish_data_out_dict)
         #Replace to make new file name
         new_file_name = v2f.replace(v2_filepath,"").replace("V2","3D_").replace("TN","LN")
-        fish_out_df.to_csv("/Users/Ben/Desktop/Fish-Midline-Processer/2Dto3D/Final 3D/"+new_file_name)
+        fish_out_df.to_csv("/Users/Ben/Desktop/Fish-Midline-Processer/2Dto3D/Final 3D Manual/"+new_file_name)
 
 
 

### 2023-02-16 2Dto3D/DLT_Plotter.py

@@ -12,7 +12,7 @@ header = list(range(4))
 num_fish = 8
 body_parts = ["head","midline2","tailbase","tailtip"]
 
-file_folder = "Final 3D/"
+file_folder = "Final 3D Manual/"
 
 three_d_files = os.listdir(file_folder)
 
@@ -67,4 +67,4 @@ for file_name in three_d_files:
 
         file_id = file_name[0:22]
 
-        fig.write_html("Saved 3D Plots/{name}.html".format(name = file_id), auto_play=False)
+        fig.write_html("Saved 3D Plots Manual/{name}.html".format(name = file_id), auto_play=False)

### 2023-02-16 3D_data_files_to_csv_4P.py

@@ -43,11 +43,11 @@ tailbeat_len = 19
 
 #Fish len is the median of all fish lengths in pixels
 #Scale is different becasue of calibration
-fish_len = 0.07862
+fish_len = 0.083197
 
 #Used to try and remove weird times where fish extend
 # Fish SD
-fish_sd = 0.39930
+fish_sd = 0.62998
 
 # Fish Len Max?
 fish_max_len = fish_len + 3*fish_sd
@@ -889,9 +889,19 @@ class school_comps:
 
             dm = np.zeros((len(points),len(points)))
 
-            points = points/fish_len
+            print(points)
+
+            points = points
+
+            print(points)
 
             dm = distance_matrix(points,points)
+
+            print(dm)
+
+            dm = dm/fish_len
+
+            print(dm)
 
             dm_min = dm <= min_BL_for_groups
 
@@ -900,6 +910,12 @@ class school_comps:
             n_groups = len([len(c) for c in sorted(nx.connected_components(G), key=len, reverse=True)])
 
             self.school_groups[i] = n_groups
+
+            pos = nx.spring_layout(G)
+            nx.draw(G, pos, with_labels=True)
+            plt.show()
+
+            sys.exit()
 
     def calc_school_height(self):
         school_zs = np.asarray([fish.head_z for fish in self.fishes])
@@ -946,6 +962,10 @@ class school_comps:
         ax7 = plt.subplot(gs[1,3])
         ax7.plot(range(len(self.nearest_neighbor_distance)), self.nearest_neighbor_distance)
         ax7.set_title("School NND")
+
+        ax8 = plt.subplot(gs[2,3])
+        ax8.plot(range(len(self.school_groups)), self.school_groups)
+        ax8.set_title("School Groups")
 
         plt.show()
 
@@ -1168,6 +1188,7 @@ class trial:
         chunked_nnd = mean_tailbeat_chunk(self.school_comp.nearest_neighbor_distance,tailbeat_len)
         chunked_area = mean_tailbeat_chunk(self.school_comp.school_areas,tailbeat_len)
         chunked_groups = median_tailbeat_chunk(self.school_comp.school_groups,tailbeat_len)
[…]

### 2023-02-16 3D_data_files_to_csv_4P.py
Altered group detection to check tailtips
Also checks tailtip to tailtip, and head to tailtip, not just head to head

@@ -709,7 +709,10 @@ class school_comps:
         self.calc_nnd()
         self.calc_tailbeat_cor()
         self.calc_school_area()
-        self.calc_school_groups()
+
+        self.calc_school_groups_all_points()
+        #self.calc_school_groups()
+
         self.calc_school_height()
 
         #self.graph_values()
@@ -729,23 +732,6 @@ class school_comps:
 
     def remove_and_smooth_points(self):
         threshold = 0.01
-
-        #Removing the points leaves too many gaps to then fill in later
-        # median_school_center_x = medfilt(self.school_center_x, kernel_size = 11)
-        # median_school_center_y = medfilt(self.school_center_y, kernel_size = 11)
-        # median_school_center_z = medfilt(self.school_center_z, kernel_size = 11)
-
-        # difference_x = np.abs(self.school_center_x - median_school_center_x)
-        # difference_y = np.abs(self.school_center_y - median_school_center_y)
-        # difference_z = np.abs(self.school_center_z - median_school_center_z)
-
-        # outlier_id_x = difference_x > threshold
-        # outlier_id_y = difference_y > threshold
-        # outlier_id_z = difference_z > threshold
-
-        # self.school_center_x[outlier_id_x] = np.nan
-        # self.school_center_y[outlier_id_y] = np.nan
-        # self.school_center_z[outlier_id_z] = np.nan
 
         self.school_center_x = savgol_filter(self.school_center_x,31,1)
         self.school_center_y = savgol_filter(self.school_center_y,31,1)
@@ -861,7 +847,7 @@ class school_comps:
 
         self.school_groups = [np.nan for i in range(len(school_xs[0]))]
 
-        for i in range(len(school_xs[0])):
+        for i in range(87,len(school_xs[0])):
 
             x_row = school_xs[:,i]
             y_row = school_ys[:,i]
@@ -889,19 +875,11 @@ class school_comps:
 
             dm = np.zeros((len(points),len(points)))
 
-            print(points)
-
             points = points
-
-            print(points)
 
             dm = distance_matrix(points,points)
 
-            print(dm)
-
             dm = dm/fish_len
-
-            print(dm)
 
             dm_min = dm <= min_BL_for_groups
 
@@ -911,11 +889,77 @@ class school_comps:
 
             self.school_groups[i] = n_groups
 
-            pos = nx.spring_layout(G)
[…]

### 2023-02-27 Fish Data Analysis/Autocorrelation Testing.qmd
Paper Graphs and Analysis

---
title: "Autocorrelation Testing"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
```

```{r}
school_data <- read.csv("Data/Fish_School_Values_3D.csv")
school_data <- na.omit(school_data)

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_"),)
```

### NND Autocorrelation

```{r}

nnd_auto <- ggplot(school_data, aes(NND, lag(NND)))+
  geom_point()+
  geom_smooth(method = 'lm',formula='y ~ x',se =FALSE)+
  facet_wrap(~Date_Trial) +
  theme_classic()

ggsave("Autocorrelation Figures/NND_AutoCorreation_Test.png",nnd_auto, width = 12, height = 12)

```

### Polar Autocorrelation

```{r}

polar_auto <- ggplot(school_data, aes(School_Polar, lag(School_Polar)))+
  geom_point()+
  geom_smooth(method = 'lm',formula='y ~ x',se =FALSE)+
  facet_wrap(~Date_Trial) +
  theme_classic()

ggsave("Autocorrelation Figures/Polar_AutoCorreation_Test.png",polar_auto, width = 12, height = 12)

```

### Speed Autocorrelation

```{r}

speed_auto <- ggplot(school_data, aes(School_Speed, lag(School_Speed)))+
  geom_point()+
  geom_smooth(method = 'lm',formula='y ~ x',se =FALSE)+
  facet_wrap(~Date_Trial) +
  theme_classic()

ggsave("Autocorrelation Figures/Speed_AutoCorreation_Test.png",speed_auto, width = 12, height = 12)

```

### Groups Autocorrelation

```{r}

groups_auto <- ggplot(school_data, aes(Groups, lag(Groups)))+
  geom_point()+
  geom_smooth(method = 'lm',formula='y ~ x',se =FALSE)+
  facet_wrap(~Date_Trial) +
  theme_classic()

ggsave("Autocorrelation Figures/Groups_AutoCorreation_Test.png",groups_auto, width = 12, height = 12)

```

### Area Autocorrelation

```{r}

area_auto <- ggplot(school_data, aes(Area, lag(Area)))+
  geom_point()+
  geom_smooth(method = 'lm',formula='y ~ x',se =FALSE)+
  facet_wrap(~Date_Trial) +
  theme_classic()

ggsave("Autocorrelation Figures/Area_AutoCorreation_Test.png",area_auto, width = 12, height = 12)

```

### Height Autocorrelation

```{r}

height_auto <- ggplot(school_data, aes(School_Height, lag(School_Height)))+
  geom_point()+
  geom_smooth(method = 'lm',formula='y ~ x',se =FALSE)+
  facet_wrap(~Date_Trial) +
  theme_classic()

ggsave("Autocorrelation Figures/Height_AutoCorreation_Test.png",height_auto, width = 12, height = 12)

```

### Correlation Tests

```{r}

last_ind <- length(school_data$NND)

school_autocorrs <- school_data %>% group_by(Date_Trial) %>%
                    filter(Date_Trial != "2021_3_25_30") %>%
                    summarise(nnd_corr = cor.test(NND, lag(NND))$estimate,
                              nnd_p = cor.test(NND, lag(NND))$p.value,
                              polar_corr = cor.test(School_Polar, lag(School_Polar))$estimate,
                              polar_p = cor.test(School_Polar, lag(School_Polar))$p.value,
                              speed_corr = cor.test(School_Speed, lag(School_Speed))$estimate,
                              speed_p = cor.test(School_Speed, lag(School_Speed))$p.value,
                              groups_corr = cor.test(Groups, lag(Groups))$estimate,
                              groups_p = cor.test(Groups, lag(Groups))$p.value,
                              area_corr = cor.test(Area, lag(Area))$estimate,
                              area_p = cor.test(Area, lag(Area))$p.value,
                              height_corr = cor.test(School_Height, lag(School_Height))$estimate,
                              height_p = cor.test(School_Height, lag(School_Height))$p.value)

school_autocorrs

auto_cor_avgs <- school_autocorrs %>% summarise(nnd_CorAvg = mean(nnd_corr, na.rm = TRUE),
                                                nnd_SigPer = sum(nnd_p < 0.05,na.rm = TRUE)/n(),
                                                polar_CorAvg = mean(polar_corr, na.rm = TRUE),
                                                polar_SigPer = sum(polar_p < 0.05,na.rm = TRUE)/n(),
                                                speed_CorAvg = mean(speed_corr, na.rm = TRUE),
                                                speed_SigPer = sum(speed_p < 0.05,na.rm = TRUE)/n(),
                                                groups_CorAvg = mean(groups_corr, na.rm = TRUE),
                                                groups_SigPer = sum(groups_p < 0.05,na.rm = TRUE)/n(),
                                                area_CorAvg = mean(area_corr, na.rm = TRUE),
                                                area_SigPer = sum(area_p < 0.05,na.rm = TRUE)/n(),
                                                height_CorAvg = mean(height_corr, na.rm = TRUE),
                                                height_SigPer = sum(height_p < 0.05,na.rm = TRUE)/n())

auto_cor_avgs %>% pivot_longer(everything(), names_to = "Type", values_to = "Value") %>%
                  separate(Type, c("Type", "Stat")) %>%
                  pivot_wider(names_from = Stat, values_from = Value)

```

### 2023-02-27 Fish Data Analysis/Paper_Figures.qmd
Paper Graphs and Analysis

@@
 ```{r}
-eight_fish_all_cond <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish"),
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
+eight_fish_still <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Still Water"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point()+
-  geom_line(alpha = 0.25) +
-  facet_wrap(~ Darkness + Ablation) +
+  #geom_line(alpha = 0.25) +
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
+  #facet_wrap(~ Darkness + Ablation) +
   theme_classic() +
@@
   ylab("Probability of a Right Turn") +
+  ylim(0,1) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
                      labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "Sensory Conditions")
 
-eight_fish_all_cond_one_chart <- ggplot(turning_data_sum %>% filter(Flow == "Still Water") %>% filter(Type == "Eight Fish"),
-                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow_Ablation_Darkness))+
+eight_fish_flow <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point()+
-  geom_line(alpha = 0.25) +
+  #geom_line(alpha = 0.25) +
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
+  #facet_wrap(~ Darkness + Ablation) +
   theme_classic() +
@@
   ylab("Probability of a Right Turn") +
-  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
 
-eight_fish_still_model <- ggplot(annushka_turning_data %>% filter(Flow == "Still Water"),
-                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
-  #geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
-   ylim(0,1) +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory Conditions")
-
 only_flow_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
@@
 
-eight_fish_flow_model <- ggplot(annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
-                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
-  #geom_jitter(alpha = 0.1, height = 0.025)+
-  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  ylim(0,1) +
-  #ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory Conditions")
+eight_fish_still
+eight_fish_flow
 
-eight_fish_all_cond
-eight_fish_still_model
-eight_fish_flow_model
+turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
+                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
+Anova(turning_glm_still)
 
-eight_fish_all_cond_one_chart
+turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
+                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
+Anova(turning_glm_flow)
+
 ```
@@
 
-dark_eight_and_single_graph <- ggplot(dark_eight_and_single_sum,
-                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
-  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
+dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
+  geom_point()+
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
   theme_classic() +
@@
   ylim(0,1) +
-  #ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
   scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
-  #scale_size_continuous(breaks = c(25,50,75)) +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7")) + 
-  labs(size = "Number of Turns")
-
-dark_eight_and_single_graph_real <- ggplot(turning_data_sum %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
-                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
-  geom_point()+
-  geom_line(alpha = 0.25) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
-   ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
 
-ablation_eight_and_single_graph <- ggplot(ablation_eight_and_single_sum,
-                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
-  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
+ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
+  geom_point()+
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
   theme_classic() +
@@
   ylim(0,1) +
-  #ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
   scale_colour_manual(values = c(sim_color,light_ab_color)) +
-  #scale_size_continuous(breaks = c(25,50,75)) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
                                 "3:4","2:5","1:6","0:7"))+ 
-  labs(size = "Number of Turns")
+  labs(color = "Sensory Conditions")
 
@@
 
-light_eight_and_single_graph <- ggplot(light_eight_and_single_sum,
-                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
-  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
-  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
+light_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
+  geom_point()+
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
   theme_classic() +
@@
   ylim(0,1) +
-  #ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
   scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
-  #scale_size_continuous(breaks = c(25,50,75)) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
   scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
@@
 
-dark_eight_and_single_graph_real
+still_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
+                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
+                               family = binomial)
+Anova(still_light_turning_glm)
+
+ablated_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
+                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
+                               family = binomial)
+Anova(ablated_light_turning_glm)
+
+dark_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
+                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+                               family = binomial)
+Anova(dark_light_turning_glm)
+
+#Emmeans doesn't quite work since it makes it all into groups and not lines?
+real_vs_sim_turning_glm <- glm(turn_bool ~ 0+Fish_Num_Ratio*Ablation*Darkness*Flow*Type, data = all_turning_data, family = binomial)
+summary(real_vs_sim_turning_glm)
+Anova(real_vs_sim_turning_glm)
+emmeans(real_vs_sim_turning_glm, specs = pairwise ~ Type | Flow:Ablation:Darkness)
+
 ```
@@
 ```{r}
-turning_mega_plot <- ggarrange(eight_fish_all_cond, eight_fish_still_model, eight_fish_flow_model,
+# turning_mega_plot <- ggarrange(eight_fish_still, eight_fish_flow,ggplot() + theme_classic() + theme(axis.line=element_blank()),
+#           light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
+#           labels = c("A", "B", "", "C", "D", "E"),
+#           ncol = 3, nrow = 2)
+# 
+# ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)
+
+turning_both_plot <- ggarrange(eight_fish_still, eight_fish_flow,
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+
+ggsave("Paper Figures/turning_both_plot.png", turning_both_plot, width = 15, height = 7)
+
+turning_single_test_plot <- ggarrange(
           light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
-          labels = c("A", "B", "C", "D", "E", "F"),
-          ncol = 3, nrow = 2)
+          labels = c("A", "B", "C"),
+          ncol = 3, nrow = 1)
 
-ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)
+ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 22, height = 7)
+
 ```
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),  c("No Ablation, Light", "Ablated, Light"))
 
@@
   xlab("") +
-  ylab("School Height (BL)") +
+  ylab("School NND (BL)") +
   theme_light()+ 
@@
 
-nnd_glm <- glm(NND ~ Ablation:Darkness:Flow, data = school_data)
+nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+Anova(nnd_glm_still, test.statistic="F")
+length((school_data %>% filter(Flow == "Still Water"))$NND)
+
+nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+Anova(nnd_glm_flow, test.statistic="F")
+length((school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))$NND)
+
+nnd_glm <- glm(NND ~ Ablation*Darkness*Flow, data = school_data)
+Anova(nnd_glm)
 emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)
@@
 ```
+
 ### Height Plot
@@
 
-height_glm <- glm(School_Height ~ Ablation:Darkness:Flow, data = school_data)
+height_glm <- glm(School_Height ~ Ablation*Darkness*Flow, data = school_data)
+Anova(height_glm)
 emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
@@
 
-polar_glm <- glm(School_Polar ~ Ablation:Darkness:Flow, data = school_data)
+polar_glm <- glm(School_Polar ~ Ablation*Darkness*Flow, data = school_data)
+Anova(polar_glm)
 emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
+
+polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+Anova(polar_glm_still, test.statistic="F")
+
+polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+Anova(polar_glm_flow, test.statistic="F")
 ```
@@
 ```{r}
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
 
@@
 
-speed_glm <- glm(School_Speed ~ Ablation:Darkness:Flow, data = school_data)
+speed_glm <- glm(School_Speed ~ Ablation*Darkness*Flow, data = school_data)
+Anova(speed_glm)
 emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
+
+speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+Anova(speed_glm_still, test.statistic="F")
+
+speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+Anova(speed_glm_flow, test.statistic="F")
 ```
@@
 
-area_glm <- glm(Area ~ Ablation:Darkness:Flow, data = school_data)
+area_glm <- glm(Area ~ Ablation*Darkness*Flow, data = school_data)
+Anova(area_glm)
 emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
-```
-### Groups as Mean
-
-```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
-
-mean_group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
-  xlab("") +
-  ylab("Mean Number of Groups") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
-
-mean_group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
-  xlab("") +
-  ylab("Mean Number of Groups") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-mean_group_still
-mean_group_flow
-
 ```
@@
     theme_light()+ 
-    scale_fill_manual(values=c("#1D3557","#325A7C","#457B9D","#7BAFBF","#A8DADC","#D0EBE6","#F1FAEE","#e63946")) +
+    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
+                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
     theme(axis.text.x = element_text(size = 15),
@@
 
-groups_glm <- glm(Groups ~ Ablation:Darkness:Flow, data = school_data)
+groups_glm <- glm(Groups ~ Ablation*Darkness*Flow, data = school_data, family  = poisson)
+Anova(area_glm)
 emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
+
+groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"), family  = poisson)
+Anova(groups_glm_still, test.statistic="F")
+
+groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family  = poisson)
+Anova(groups_glm_flow, test.statistic="F")
 

### 2023-02-27 3D_data_files_to_csv_4P.py

@@ -710,6 +710,7 @@ class school_comps:
         self.calc_tailbeat_cor()
         self.calc_school_area()
 
+        #self.calc_school_groups_all_points_diff_xy_z()
         self.calc_school_groups_all_points()
         #self.calc_school_groups()
 
@@ -902,37 +903,45 @@ class school_comps:
 
         #Get all the fish head and tailtip points
         school_heads = np.asarray([[fish.head_x for fish in self.fishes],[fish.head_y for fish in self.fishes],[fish.head_z for fish in self.fishes]])
+        school_midlines = np.asarray([[fish.midline_x for fish in self.fishes],[fish.midline_y for fish in self.fishes],[fish.midline_z for fish in self.fishes]])
+        school_tailbases = np.asarray([[fish.tailbase_x for fish in self.fishes],[fish.tailbase_y for fish in self.fishes],[fish.tailbase_z for fish in self.fishes]])
         school_tailtips = np.asarray([[fish.tailtip_x for fish in self.fishes],[fish.tailtip_y for fish in self.fishes],[fish.tailtip_z for fish in self.fishes]])
 
         #Set up the final array to be filled in
         self.school_groups = [np.nan for i in range(len(school_xs[0]))]
 
-        for i in range(87,len(school_xs[0])):
+        for i in range(len(school_xs[0])):
 
             #Get just the points for the current frame
             head_points = np.asarray([item for item in zip(school_heads[0][:,i], school_heads[1][:,i], school_heads[2][:,i])])
+            midline_points = np.asarray([item for item in zip(school_midlines[0][:,i], school_midlines[1][:,i], school_midlines[2][:,i])])
+            tailbase_points = np.asarray([item for item in zip(school_tailbases[0][:,i], school_tailbases[1][:,i], school_tailbases[2][:,i])])
             tailtip_points = np.asarray([item for item in zip(school_tailtips[0][:,i], school_tailtips[1][:,i], school_tailtips[2][:,i])])
 
             #Remove NANs from head and tailtip so they aren't added as nodes later
-            mask = ~np.isnan(head_points) & ~np.isnan(tailtip_points)
+            mask = ~np.isnan(head_points) & ~np.isnan(midline_points) & ~np.isnan(tailbase_points) & ~np.isnan(tailtip_points)
 
             #Reshape to make them fit and remove NANs with mask
[…]

### 2023-02-27 Single Fish Turning Processor/get_turn_bias.py

@@ -125,7 +125,7 @@ def process_trial(folder,datafile):
                                       Fish_Left = num_LR[1],
                                       Fish_Right = num_LR[0]))
 
-f = open("eight_fish_turning.csv", "w")
+f = open("Single_Fish_Data.csv", "w")
 
 f.write("Year,Month,Day,Trial,Ablation,Darkness,Singles,Flow,Turn_Dir,Fish_Left,Fish_Right")
 

### 2023-03-01 Fish Data Analysis/Autocorrelation Testing.qmd
Finding data we need to skip for no correlations

@@
 
+```{r}
+n_to_lag = 4
+```
+
 ### NND Autocorrelation
@@
 
-nnd_auto <- ggplot(school_data, aes(NND, lag(NND)))+
+nnd_auto <- ggplot(school_data, aes(NND, lag(NND, n = n_to_lag)))+
   geom_point()+
@@
 
-polar_auto <- ggplot(school_data, aes(School_Polar, lag(School_Polar)))+
+polar_auto <- ggplot(school_data, aes(School_Polar, lag(School_Polar, n = n_to_lag)))+
   geom_point()+
@@
 
-speed_auto <- ggplot(school_data, aes(School_Speed, lag(School_Speed)))+
+speed_auto <- ggplot(school_data, aes(School_Speed, lag(School_Speed, n = n_to_lag)))+
   geom_point()+
@@
 
-groups_auto <- ggplot(school_data, aes(Groups, lag(Groups)))+
+groups_auto <- ggplot(school_data, aes(Groups, lag(Groups, n = n_to_lag)))+
   geom_point()+
@@
 
-area_auto <- ggplot(school_data, aes(Area, lag(Area)))+
+area_auto <- ggplot(school_data, aes(Area, lag(Area, n = n_to_lag)))+
   geom_point()+
@@
 
-height_auto <- ggplot(school_data, aes(School_Height, lag(School_Height)))+
+height_auto <- ggplot(school_data, aes(School_Height, lag(School_Height, n = n_to_lag)))+
   geom_point()+
@@
 
-last_ind <- length(school_data$NND)
-
 school_autocorrs <- school_data %>% group_by(Date_Trial) %>%
                     filter(Date_Trial != "2021_3_25_30") %>%
-                    summarise(nnd_corr = cor.test(NND, lag(NND))$estimate,
-                              nnd_p = cor.test(NND, lag(NND))$p.value,
-                              polar_corr = cor.test(School_Polar, lag(School_Polar))$estimate,
-                              polar_p = cor.test(School_Polar, lag(School_Polar))$p.value,
-                              speed_corr = cor.test(School_Speed, lag(School_Speed))$estimate,
-                              speed_p = cor.test(School_Speed, lag(School_Speed))$p.value,
-                              groups_corr = cor.test(Groups, lag(Groups))$estimate,
-                              groups_p = cor.test(Groups, lag(Groups))$p.value,
-                              area_corr = cor.test(Area, lag(Area))$estimate,
-                              area_p = cor.test(Area, lag(Area))$p.value,
-                              height_corr = cor.test(School_Height, lag(School_Height))$estimate,
-                              height_p = cor.test(School_Height, lag(School_Height))$p.value)
+                    summarise(nnd_corr = cor.test(NND, lag(NND, n = n_to_lag))$estimate,
+                              nnd_p = cor.test(NND, lag(NND, n = n_to_lag))$p.value,
+                              polar_corr = cor.test(School_Polar, lag(School_Polar, n = n_to_lag))$estimate,
+                              polar_p = cor.test(School_Polar, lag(School_Polar, n = n_to_lag))$p.value,
+                              speed_corr = cor.test(School_Speed, lag(School_Speed, n = n_to_lag))$estimate,
+                              speed_p = cor.test(School_Speed, lag(School_Speed, n = n_to_lag))$p.value,
+                              groups_corr = cor.test(Groups, lag(Groups, n = n_to_lag))$estimate,
+                              groups_p = cor.test(Groups, lag(Groups, n = n_to_lag))$p.value,
+                              area_corr = cor.test(Area, lag(Area, n = n_to_lag))$estimate,
+                              area_p = cor.test(Area, lag(Area, n = n_to_lag))$p.value,
+                              height_corr = cor.test(School_Height, lag(School_Height, n = n_to_lag))$estimate,
+                              height_p = cor.test(School_Height, lag(School_Height, n = n_to_lag))$p.value)
 
@@
 ```
+
+for loop lags
+```{r}
+
+for(i in seq(1:10)){
+  print(i)
+
+  new_autocorrs <- school_data %>% group_by(Date_Trial) %>%
+                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29","2021_7_7_16","2021_3_25_7","2021_10_6_34")) %>%
+                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
+                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
+                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
+                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
+                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
+                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
+                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
+                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
+                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
+                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
+                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
+                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
+                              lag = i)
+
+  if(i == 1){
+    school_autocorrs <- new_autocorrs
+  }
+  else{
+    school_autocorrs <- rbind(school_autocorrs,new_autocorrs) 
+  }
+
+}
+
+nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr, color = as.factor(lag)))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ggtitle("NND")+
+  theme_classic()
+
+polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr, color = as.factor(lag)))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ggtitle("Polar")+
+  theme_classic()
+
+speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr, color = as.factor(lag)))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ggtitle("Speed")+
+  theme_classic()
+
+groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr, color = as.factor(lag)))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ggtitle("Groups")+
+  theme_classic()
+
+area_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), area_corr, color = as.factor(lag)))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ggtitle("Area")+
+  theme_classic()
+
+height_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), height_corr, color = as.factor(lag)))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ggtitle("Area")+
+  theme_classic()
+
+lag_plots <- ggarrange(
+          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot, area_lag_plot, height_lag_plot,
+          ncol = 3, nrow = 2)
+
+ggsave("Autocorrelation Figures/Different_Lag_Figures.png", lag_plots, width = 22, height = 15)
+
+```

### 2023-03-01 Single Fish Turning Processor/get_turn_bias_midline.py

@@ -14,6 +14,9 @@ fish_names = ["individual1","individual2",
               "individual5","individual6",
               "individual7","individual8"]
 
+x_edges = [250,2250]
+y_edges = [200,900]
+
 csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Turn_Dir},{Fish_Left},{Fish_Right}\n"
 
 def calc_mag(p1,p2):
@@ -41,7 +44,7 @@ def turn_frames(head_x_data,head_y_data,mid_x_data,mid_y_data):
 
         dot_prods[i] = np.dot(vec1,vec2)
 
-        print(vec1, vec2, dot_prods[i])
+        #print(vec1, vec2, dot_prods[i])
 
         if np.isnan(np.dot(vec1,vec2)):
             dot_prods[i] = 1
@@ -72,6 +75,8 @@ def turn_frames(head_x_data,head_y_data,mid_x_data,mid_y_data):
     #But I can do it with is_point_LR() for each point, comparing one head to the next...
     turn_dirs = []
 
+    final_peaks = []
+
     for p in peaks:
         #mid to head and mid to next
         m2h = np.pad(head_point_data[p] - mid_point_data[p], (0, 1), 'constant')
@@ -82,9 +87,14 @@ def turn_frames(head_x_data,head_y_data,mid_x_data,mid_y_data):
         if turn_dir == None:
             print(m2h,m2n)
 
-        turn_dirs.append(turn_dir)
+        #Also we want to check that they aren't too close to the edge!
+        if((head_point_data[p][0] > x_edges[0]) and (head_point_data[p][0] < x_edges[1]) and (head_point_data[p][1] > y_edges[0]) and (head_point_data[p][1] < y_edges[1])):
+            turn_dirs.append(turn_dir)
+            final_peaks.append(p)
+        else:
+            print("Edge case!")
 
-    return(peaks,turn_dirs)
+    return(final_peaks,turn_dirs)
 
 def is_point_LR(mid_to_head,mid_to_other):
     #Get the cross product to see if they turned left or right
@@ -175,7 +185,7 @@ def process_trial(folder,datafile):
 
 f = open("single_fish_turning.csv", "w")
 
-f.write("Year,Month,Day,Trial,Ablation,Darkness,Singles,Flow,Turn_Dir,Fish_Left,Fish_Right")
[…]

### 2023-03-03 Fish Data Analysis/Paper_Figures.qmd
Adding Mixed Models

@@
 library(emmeans)
+library(lme4)
 
@@
 
-only_still_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
-                 data = annushka_turning_data %>% filter(Flow == "Still Water"), 
-                 family = binomial)
-
-only_flow_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
-                 data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), 
-                 family = binomial)
-
 eight_fish_still
 eight_fish_flow
-
-turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
-                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
-Anova(turning_glm_still)
-
-turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
-                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
-Anova(turning_glm_flow)
 
@@
 ```{r}
-
-dark_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
-                 data = all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark"), 
-                 family = binomial)
-
-dark_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark") %>%
-                                                  mutate(predicted = predict(dark_eight_and_single_model, type="response")) %>%
-                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
-                                                  summarise(predicted = predicted, n = n()) %>%
-                                                  ungroup()
 
@@
 
-ablation_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
-                 data = all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated"), 
-                 family = binomial)
-
-ablation_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated")  %>%
-                                                  mutate(predicted = predict(ablation_eight_and_single_model, type="response")) %>%
-                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
-                                                  summarise(predicted = predicted, n = n()) %>%
-                                                  ungroup()
-
 ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
@@
   labs(color = "Sensory Conditions")
-
-light_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
-                 data = all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"), 
-                 family = binomial)
-
-light_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light")  %>%
-                                                  mutate(predicted = predict(light_eight_and_single_model, type="response")) %>%
-                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
-                                                  summarise(predicted = predicted, n = n()) %>%
-                                                  ungroup()
 
@@
 dark_eight_and_single_graph
+```
 
-still_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
+### Turning Stats Table Here
+
+```{r}
+turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
+                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
+tgs_aov <- Anova(turning_glm_still)
+
+turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
+                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
+tgf_aov <- Anova(turning_glm_flow)
+
+turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
+       Factor = c("Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness",
+                  "Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness"),
+       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
+       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
+       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
+       Is_Sig = P_Val < 0.05)
+
+# Single vs Eight fish
+light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                                data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                                family = binomial)
-Anova(still_light_turning_glm)
+ltg_aov <- Anova(light_turning_glm)
 
-ablated_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
+ablated_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                                data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                                family = binomial)
-Anova(ablated_light_turning_glm)
+altg_aov <- Anova(ablated_turning_glm)
 
-dark_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
+dark_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                                data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                                family = binomial)
-Anova(dark_light_turning_glm)
+dtg_aov <- Anova(dark_turning_glm)
 
-#Emmeans doesn't quite work since it makes it all into groups and not lines?
-real_vs_sim_turning_glm <- glm(turn_bool ~ 0+Fish_Num_Ratio*Ablation*Darkness*Flow*Type, data = all_turning_data, family = binomial)
-summary(real_vs_sim_turning_glm)
-Anova(real_vs_sim_turning_glm)
-emmeans(real_vs_sim_turning_glm, specs = pairwise ~ Type | Flow:Ablation:Darkness)
+single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
+       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
+       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
+       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
+       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
+       Is_Sig = P_Val < 0.05)
+
+turning_results
+single_vs_eight_results
 
@@
                            mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+
+                           # ### Used to remove every third point to reduce autocorrelation
+                           mutate(Date = paste(Year,Month,Day,sep="_"),
+                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
+                           group_by(Date_Trial) %>%
+                           filter(row_number() %% 3 == 1) %>%
+                           ungroup() %>%
+                           # ###
+
                            group_by(Flow_Ablation_Darkness) %>%
@@
 nnd_flow
-
-nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-Anova(nnd_glm_still, test.statistic="F")
-length((school_data %>% filter(Flow == "Still Water"))$NND)
-
-nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-Anova(nnd_glm_flow, test.statistic="F")
-length((school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))$NND)
 
@@
 
+### School Stats Table Here
+
+```{r}
+
+nnd_glmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+nnd_s_aov_me <- Anova(nnd_glmer_still)
+
+nnd_glmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+nnd_f_aov_me <- Anova(nnd_glmer_flow)
+
+height_glmer_still <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+height_s_aov_me <- Anova(height_glmer_still)
+
+height_glmer_flow <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+height_f_aov_me <- Anova(height_glmer_flow)
+
+polar_glmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+polar_s_aov_me <- Anova(polar_glmer_still)
+
+polar_glmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+polar_f_aov_me <- Anova(polar_glmer_flow)
+
+speed_glmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+speed_s_aov_me <- Anova(speed_glmer_still)
+
+speed_glmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+speed_f_aov_me <- Anova(speed_glmer_flow)
+
+area_glmer_still <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+area_s_aov_me <- Anova(area_glmer_still)
+
+area_glmer_flow <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+area_f_aov_me <- Anova(area_glmer_flow)
+
+groups_glmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+groups_s_aov_me <- Anova(groups_glmer_still)
+
+groups_glmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+groups_f_aov_me <- Anova(groups_glmer_flow)
+
+glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
+       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
+       Condition = rep(c("Ablation","Darkness"), 12),
+       DF = rep(c(length(nnd_glmer_still@resp$y)-3,length(nnd_glmer_flow@resp$y)-3),12),
+       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
+                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
+                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
+                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
+                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
+                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),
+
+       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
+                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
+                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
+                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
+                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
+                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),
+
+       Is_Sig = P_Val < 0.05)
+
+glmm_school_stats_table
+
+nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+nnd_s_aov <- Anova(nnd_glm_still)
+
+nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+nnd_f_aov <- Anova(nnd_glm_flow)
+
+height_glm_still <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+height_s_aov <- Anova(height_glm_still)
+
+height_glm_flow <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+height_f_aov <- Anova(height_glm_flow)
+
+polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+polar_s_aov <- Anova(polar_glm_still)
+
+polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+polar_f_aov <- Anova(polar_glm_flow)
+
+speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+speed_s_aov <- Anova(speed_glm_still)
+
+speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+speed_f_aov <- Anova(speed_glm_flow)
+
+area_glm_still <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+area_s_aov <- Anova(area_glm_still)
+
+area_glm_flow <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+area_f_aov <- Anova(area_glm_flow)
+
+groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
+groups_s_aov <- Anova(groups_glm_still)
+
+groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+groups_f_aov <- Anova(groups_glm_flow)
+
+glm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
+       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
+       Condition = rep(c("Ablation","Darkness"), 12),
+       DF = rep(c(length(nnd_glm_still$y)-3,length(nnd_glm_flow$y)-3),12),
+       Chisq = c(nnd_s_aov$`LR Chisq`[1:2],nnd_f_aov$`LR Chisq`[1:2],
+                 height_s_aov$`LR Chisq`[1:2],height_f_aov$`LR Chisq`[1:2],
+                 polar_s_aov$`LR Chisq`[1:2],polar_f_aov$`LR Chisq`[1:2],
+                 speed_s_aov$`LR Chisq`[1:2],speed_f_aov$`LR Chisq`[1:2],
+                 area_s_aov$`LR Chisq`[1:2],area_f_aov$`LR Chisq`[1:2],
+                 groups_s_aov$`LR Chisq`[1:2],groups_f_aov$`LR Chisq`[1:2]),
+
+       P_Val = c(nnd_s_aov$`Pr(>Chisq)`[1:2],nnd_f_aov$`Pr(>Chisq)`[1:2],
+                 height_s_aov$`Pr(>Chisq)`[1:2],height_f_aov$`Pr(>Chisq)`[1:2],
+                 polar_s_aov$`Pr(>Chisq)`[1:2],polar_f_aov$`Pr(>Chisq)`[1:2],
+                 speed_s_aov$`Pr(>Chisq)`[1:2],speed_f_aov$`Pr(>Chisq)`[1:2],
+                 area_s_aov$`Pr(>Chisq)`[1:2],area_f_aov$`Pr(>Chisq)`[1:2],
+                 groups_s_aov$`Pr(>Chisq)`[1:2],groups_f_aov$`Pr(>Chisq)`[1:2]),
+
+       Is_Sig = P_Val < 0.05)
+
+glm_school_stats_table
+
+sum(glm_school_stats_table$Is_Sig == glmm_school_stats_table$Is_Sig)
+sum(glm_school_stats_table$Is_Sig == 1 & glmm_school_stats_table$Is_Sig == 1) / sum(glm_school_stats_table$Is_Sig == 1)
+
+```
+
 ### Now we combine them
@@
 ```
-
-## Startle Conditions
-
-```{r}
-
-startle_school_data <- read.csv("Data/Startle_First_Half_Fish_School_Values.csv")
-startle_school_data <- na.omit(startle_school_data)
-
-startle_school_data <- startle_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           filter(School_Speed < 7) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           group_by(Flow_Ablation_Darkness) %>%
-                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
-                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
-                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
-                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
-                           ungroup() %>% 
-                           mutate(Exp_Label = paste0("Darkness Pre-Startle ",Trial))
-
-startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
-                                             mutate(Exp_Label = "Light") %>%
-                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val,
-                                                       School_Height, Height_Mean_Val, Height_SD_Val))
-
-startle_school_data <- rbind(startle_school_data_light,startle_school_data) %>% 
-                       mutate(Exp_Label = factor(Exp_Label)) %>%
-                       mutate(Exp_Label = fct_relevel(Exp_Label,c("Light",
-                                                                  "Darkness Pre-Startle 1",
-                                                                  "Darkness Pre-Startle 5",
-                                                                  "Darkness Pre-Startle 30")))
-
-```
-
-```{r}
-
-my_comparisons <- list(c("Light", "Darkness Pre-Startle 1"), c("Light", "Darkness Pre-Startle 5"), c("Light", "Darkness Pre-Startle 30"))
-
-nnd_startle <- ggplot(startle_school_data,
-       aes(x = Exp_Label, y = NND,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = NND_Mean_Val), size = 3, color = "Black") +
-  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
-  xlab("") +
-  ylab("NND (BL)") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,3)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-polar_startle <- ggplot(startle_school_data,
-       aes(x = Exp_Label, y = School_Polar,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
-  xlab("") +
-  ylab("Polarization") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,1.15)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-speed_startle <- ggplot(startle_school_data,
-       aes(x = Exp_Label, y = School_Speed,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
-  xlab("") +
-  ylab("Speed (BL/s)") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-nnd_startle
-polar_startle
-speed_startle
-
-ggsave("Paper Figures/startle_nnd.png", nnd_startle, width = 12, height = 7)
-
-```

### 2023-03-03 Fish Data Analysis/Startle_Figure.qmd
Adding Mixed Models

---
title: "Startle Data"
format: html
editor: visual
---

## Loading in the Libraries for Everything

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)

```

## School Summary Stats

```{r}
school_data <- read.csv("Data/Fish_School_Values_3D.csv")
school_data <- na.omit(school_data)

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%

                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_"),) %>%
                           # group_by(Date_Trial) %>%
                           # filter(row_number() %% 3 != 1) %>%
                           # ungroup() %>%
                           # ###

                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

## Startle Conditions

```{r}

startle_school_data <- read.csv("Data/Startle_First_Half_Fish_School_Values.csv")
startle_school_data <- na.omit(startle_school_data)

startle_school_data <- startle_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
                           ungroup() %>% 
                           mutate(Exp_Label = paste0("Darkness Pre-Startle ",Trial))

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light") %>%
                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val,
                                                       School_Height, Height_Mean_Val, Height_SD_Val))

startle_school_data <- rbind(startle_school_data_light,startle_school_data) %>% 
                       mutate(Exp_Label = factor(Exp_Label)) %>%
                       mutate(Exp_Label = fct_relevel(Exp_Label,c("Light",
                                                                  "Darkness Pre-Startle 1",
                                                                  "Darkness Pre-Startle 5",
                                                                  "Darkness Pre-Startle 30")))

```

```{r}

my_comparisons <- list(c("Light", "Darkness Pre-Startle 1"), c("Light", "Darkness Pre-Startle 5"), c("Light", "Darkness Pre-Startle 30"))

nnd_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 3, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

polar_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

speed_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

nnd_startle
polar_startle
speed_startle

ggsave("Paper Figures/startle_nnd.png", nnd_startle, width = 12, height = 7)

```

### 2023-03-30 Fish Data Analysis/Paper_Figures.qmd
Updated paper figures and stats

@@
 
-dot_binwidth = 0.0125
+dot_binwidth = 0.03
+
+text_size = 16
 ```
@@
                                 "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
@@
   ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
+  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
                                 "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory\nConditions")+
+  theme(axis.text.x = element_text(size = text_size/2),
+        axis.text.y = element_text(size = text_size/2),
+        axis.title.y = element_text(size = text_size/2),
+        legend.position = "none")
 
@@
   ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,light_ab_color)) +
+  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
   ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
+  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
 
-ggsave("Paper Figures/turning_both_plot.png", turning_both_plot, width = 15, height = 7)
+ggsave("Paper Figures/turning_both_plot.png", turning_both_plot, width = 12, height = 6)
 
@@
 
-ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 22, height = 7)
+ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 9, height = 3)
 
@@
                            mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep="/n"))) %>%
 
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"),  c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
 
@@
   theme(legend.position = "none") +
-  #ylim(0,3)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  ylim(0,2)+
+  stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+my_comparisons <- list()
 
@@
   theme(legend.position = "none") +
-  #ylim(0,3)+
+  ylim(0,2)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
 ```{r}
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list()
 
@@
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list()
 
@@
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
   theme(legend.position = "none") +
-  #ylim(0,1.15)+
+  ylim(0,1.15)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list()
 
@@
   theme(legend.position = "none") +
-  #ylim(-0.1,8.5)+
+  ylim(0,6)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
   theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  ylim(0,6)+
+  stat_compare_means(comparisons = my_comparisons, label.y = c(5.5), label = "p.signif", hide.ns = TRUE) +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+my_comparisons <- list()
 
@@
     xlab("") +
-    ylab("Proportion of Time with this Many Groups") +
+    ylab("Proportion of Time") +
     theme_light()+ 
@@
                                "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
-    theme(axis.text.x = element_text(size = 15),
-          axis.text.y = element_text(size = 15),
-          axis.title.y = element_text(size = 15))
+    theme(axis.text.x = element_text(size = text_size),
+          axis.text.y = element_text(size = text_size),
+          axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
 
-ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 14, height = 30)
+ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 10, height = 17)
 ```
+
+Parallax
+
+```{r}
+para_vals <- read.csv("Data/Parallax_Distances.csv") %>% mutate(BLs = Distance / 200)
+
+breaks <- c("0.1")
+
+para_plot <- ggplot(para_vals, aes(X, Y, z = BLs))+
+  geom_contour_filled(bins = 5)+
+  scale_fill_viridis_d("Projection Error (BL)", 
+                       labels = c("< 0.1", "0.1 - 0.2", "0.2 - 0.3","0.3 - 0.4","0.4 - 0.5"))+
+  theme_classic()+
+  coord_fixed() +
+  ylab("Vertical Distance from Principal Point (pixels)")+
+  xlab("Hoizontal Distance from Principal Point (pixels)")+ 
+  theme(text = element_text(size = 20))
+
+ggsave("Paper Figures/parallax_model.png", para_plot, width = 14, height = 7)
+```

### 2023-03-30 Fish Data Analysis/Parallax Testing.qmd
Added Charuco Code
Updated paper figures and stats

@@
 ```{r}
+para_vals <- read.csv("Data/Parallax_Distances.csv") %>% mutate(BLs = Distance / 200)
+
+breaks <- c("0.1")
+
+ggplot(para_vals, aes(X, Y, z = BLs))+
+  geom_contour_filled(bins = 5, params = c(linewidth = 20))+
+  scale_fill_viridis_d("Projection Error (BL)", 
+                       labels = c("< 0.1", "0.1 - 0.2", "0.2 - 0.3","0.3 - 0.4","0.4 - 0.5"))+
+  theme_classic()+
+  coord_fixed() +
+  ylab("Vertical Distance from Principal Point (pixels)")+
+  xlab("Hoizontal Distance from Principal Point (pixels)")
+```
+
+Ignore everything below this, I'm just making a simple graph of predicted values
+
+```{r}
 data_2d <- read.csv("Data/Fish_Comp_Values.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
@@
                            mutate(Speed_Diff = abs(Speed_Diff)) %>%
-                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
-                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
-                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
-                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))
+                           mutate(Heading_Diff = abs(Heading_Diff))
 
@@
                            mutate(Speed_Diff = abs(Speed_Diff)) %>%
-                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
-                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
-                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
-                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))
+                           mutate(Heading_Diff = abs(Heading_Diff))
+
+data_3d <- read.csv("Data/Fish_Comp_Values_3D.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
+                           mutate(Heading_Diff = abs(Yaw.Heading_Diff))
 ```
@@
 data_both <- full_join(data_3d_xy_still_sum, data_2d_still_sum) %>% na.omit() %>%
-                      mutate(dist_diff = abs(mean_dist_3d_xy - mean_dist_2d))
+                      mutate(dist_diff = mean_dist_3d_xy - mean_dist_2d)
 
@@
 Graphing NND in 2D
+
 ```{r}
@@
 ```
+
+#Trying a full join for distances
+
+```{r}
+
+data_2d_merging <- data_2d %>% select(c(Year,Month,Day,Trial,Fish,Tailbeat_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y))
+data_3d_merging <- data_3d_xy %>% select(c(Year,Month,Day,Trial,Fish,Tailbeat_Num,Distance))
+
+data_2d_merging <- data_2d_merging %>% rename(Distance_2D = Distance)
+data_3d_merging <- data_3d_merging %>% rename(Distance_3D = Distance)
+
+merged_data <- inner_join(data_2d_merging,data_3d_merging) %>% mutate(Distance_Diff = Distance_2D - Distance_3D) %>% drop_na(Distance_Diff) %>% filter(Distance_Diff < 5)
+
+merged_data <- merged_data %>% mutate(Fish_Mid_X = (Fish1_X + Fish2_X)/2,
+                                      Fish_Mid_Y = (Fish1_Y + Fish2_Y)/2)
+```
+
+```{r}
+ggplot(merged_data, aes(x = Distance_Diff)) +
+  geom_histogram()+
+  theme_classic()
+
+ggplot(merged_data, aes(x = Fish_Mid_X, y = Fish_Mid_Y, color = Distance_Diff))+
+  geom_point()+
+  scale_color_viridis() +
+  theme_classic()
+
+ggplot(merged_data, aes(x = Fish_Mid_X, y = Fish_Mid_Y, z = Distance_Diff))+
+  stat_summary_2d(bins = 20, fun = mean) +
+  scale_fill_viridis() +
+  theme_classic()
+
+ggplot(merged_data, aes(x = Fish_Mid_X, y = Distance_Diff))+
+  geom_point()+
+  geom_smooth(se = F, method = "glm", formula = y ~ poly(x,2)) +
+  theme_classic()
+
+ggplot(merged_data, aes(x = Fish_Mid_Y, y = Distance_Diff))+
+  geom_point()+
+  geom_smooth(se = F, method = "glm", formula = y ~ poly(x,2)) +
+  theme_classic()
+```
+
+```{r}
+xy_glm <- glm(Distance_Diff ~ Fish_Mid_X + Fish_Mid_Y, data = merged_data)
+x2y_glm <- glm(Distance_Diff ~ I(Fish_Mid_X^2) + Fish_Mid_Y, data = merged_data)
+xy2_glm <- glm(Distance_Diff ~ Fish_Mid_X + I(Fish_Mid_Y^2), data = merged_data)
+xx2y_glm <- glm(Distance_Diff ~ Fish_Mid_X + I(Fish_Mid_X^2) + Fish_Mid_Y, data = merged_data)
+xyy2_glm <- glm(Distance_Diff ~ Fish_Mid_X + Fish_Mid_Y + I(Fish_Mid_Y^2), data = merged_data)
+x2y2_glm <- glm(Distance_Diff ~ I(Fish_Mid_X^2) + I(Fish_Mid_Y^2), data = merged_data)
+
+ICtab(xy_glm,x2y_glm,xy2_glm,xx2y_glm,xyy2_glm,x2y2_glm)
+```

### 2023-03-30 Fish Data Analysis/Results_Text.qmd
Updated paper figures and stats

---
title: "Results Text"
format: html
editor: visual
---

## Loading in the Libraries for Everything

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
```

## Functions and Variables

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03

text_size = 16
```

## School Summary Stats

```{r}
school_data <- read.csv("Data/Fish_School_Values_3D.csv")
school_data <- na.omit(school_data)

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep="/n"))) %>%

                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
                           group_by(Date_Trial) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup() %>%
                           # ###

                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

### School Stats Table Here

```{r}

nnd_glmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov_me <- Anova(nnd_glmer_still)

nnd_glmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov_me <- Anova(nnd_glmer_flow)

height_glmer_still <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
height_s_aov_me <- Anova(height_glmer_still)

height_glmer_flow <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
height_f_aov_me <- Anova(height_glmer_flow)

polar_glmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov_me <- Anova(polar_glmer_still)

polar_glmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov_me <- Anova(polar_glmer_flow)

speed_glmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov_me <- Anova(speed_glmer_still)

speed_glmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov_me <- Anova(speed_glmer_flow)

area_glmer_still <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
area_s_aov_me <- Anova(area_glmer_still)

area_glmer_flow <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
area_f_aov_me <- Anova(area_glmer_flow)

groups_glmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
groups_s_aov_me <- Anova(groups_glmer_still)

groups_glmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
groups_f_aov_me <- Anova(groups_glmer_flow)

glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(rep(length(nnd_glmer_still@resp$y)-3,2),
                  rep(length(nnd_glmer_flow@resp$y)-3,2)),times = 6),
       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),

       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),

       Is_Sig = P_Val < 0.05)

glmm_school_stats_table

```

```{r}

paste0("Placing the fish in darkness allowed us to understand the effect of swimming without vision on the schooling behavior of the giant danios. In still water, fish in darkness swam further from their neighbors ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
       ")",

       ", but with the same polarization ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
       ")",

       ", and in more groups ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
       ")",

       ", compared to fish in light. The average speed of the school was also the same ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
       ").",

       " In flowing water, the fish in darkness behaved more similarly to fish in light. The fish in darkness did not swim further apart from their neighbors ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
       ").",

       " They had the same polarization ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
       ")",

       ", and were not split into more groups ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
       ")",

       ", compared to fish in light in flowing water. The average speed of the school was also the same ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
       ").",

       " While polarity and speed were the same for fish in darkness, the fact that they broke up into many more subgroups and had a higher average NND shows that they were not one cohesive school. While these results were not the same when the fish were in flowing water, this may have been due to the influence of the flow as an outside orienting  force."
       )

```

```{r}

paste0("Manipulating the lateral line of the fish with gentamicin produced relatively few in the schooling kinematics of our fish. In still water, treated fish swam the same distance from neighbors ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
       ")",

       ", with the same polarization ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
       ")",

       ", and in the same number of groups ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
       ")",

       ", compared to fish in light. The average speed of the school was also the same ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
       ").",

       " In flowing water, the ablated behaved almost exactly the same as when they were in still water. They did not swim further apart from their neighbors ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Ablation"))$P_Val,3),
       ").",

       " They had the same polarization ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Ablation"))$P_Val,3),
       ")",

       ", and were not split into more groups ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Ablation"))$P_Val,3),
       ")",

       ", compared to fish in light in flowing water. However, the average speed of the school was lower ",

       "(F(1,",
       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow", Condition == "Ablation"))$DF,
       ") = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow", Condition == "Ablation"))$Chisq,3),
       ", p = ",
       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow", Condition == "Ablation"))$P_Val,3),
       ").",

       " While the speed of the treated school was different in flowing water, ablated fish preformed almost exactly the same as fish with their lateral lines intact, indicating that treated fish were still able to maintain a cohesive school."
       )

```

### Turning Results Text

```{r}
annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
                           #filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
                           rename("Turn_Dir" = "Turn.Direction")  %>%
                           rename("Fish_Left" = "No..Fish.Left")  %>%
                           rename("Fish_Right" = "No..Fish.Right")  %>%
                           mutate(Type = "Eight Fish")

single_fish_turning_data <- read.csv("Data/single_fish_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           select(-c("Singles")) %>%
                           mutate(Type = "Combined Single")

all_turning_data <- rbind(annushka_turning_data,single_fish_turning_data)
```

```{r}
turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
tgs_aov <- Anova(turning_glm_still)

turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
tgf_aov <- Anova(turning_glm_flow)

turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
       Factor = c("FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness",
                  "FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness"),
       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
       Is_Sig = P_Val < 0.05)

# Single vs Eight fish
light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                               family = binomial)
ltg_aov <- Anova(light_turning_glm)

ablated_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                               family = binomial)
altg_aov <- Anova(ablated_turning_glm)

dark_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                               family = binomial)
dtg_aov <- Anova(dark_turning_glm)

single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
       Is_Sig = P_Val < 0.05)

turning_results
single_vs_eight_results
```

```{r}
paste0("We found that there were significant differences between the turning behavior of the artificial “school” and the real group of eight fish under each sensory condition. Specifically, the probability of making a right turn, based on the ratio of fish on the left and right of the focal fish, was different when they were schooling in light with their lateral line intact ",

       "(F(1,",
       (single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Light"))$DF,
       ") = ",
       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Light"))$LR_Chisq,3),
       ", p = ",
       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Light"))$P_Val,3),
       ").",

       "when their lateral line was ablated ",

       "(F(1,",
       (single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Ablated"))$DF,
       ") = ",
       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Ablated"))$LR_Chisq,3),
       ", p = ",
       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Ablated"))$P_Val,5),
       ").",

       "and when the fish were in darkness ",

       "(F(1,",
       (single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Darkness"))$DF,
       ") = ",
       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Darkness"))$LR_Chisq,3),
       ", p = ",
       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Darkness"))$P_Val,3),
       ").",

       "(Figure XX). Therefore, the effects we saw were not because of the constraints of our tank, but because of actual changes in fish schooling behavior.")
```

```{r}
paste0("We found that fish were significantly more likely to turn towards where there were more fish, and that the likelihood of turning towards the majority of fish was similar even when fish had an ablated lateral line or were swimming in darkness. Overall, we found that fish in each experimental condition were more likely to turn towards other fish, in both still ",

       "(F(1,",
       (turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Still"))$DF,
       ") = ",
       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Still"))$LR_Chisq,3),
       ", p = ",
       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Still"))$P_Val,3),
       ")",

       " and flowing water ",

       "(F(1,",
       (turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Flow"))$DF,
       ") = ",
       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Flow"))$LR_Chisq,3),
       ", p = ",
       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Flow"))$P_Val,3),
       ")",

       " (Figure XX). We found that there was not a significant change in the turning behavior of fish in darkness ",

       "(F(1,",
       (turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Still"))$DF,
       ") = ",
       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Still"))$LR_Chisq,3),
       ", p = ",
       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Still"))$P_Val,3),
       ")",

       " or with an ablated lateral line ",

       "(F(1,",
       (turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Still"))$DF,
       ") = ",
       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Still"))$LR_Chisq,3),
       ", p = ",
       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Still"))$P_Val,3),
       ")",

       " in still water. In flowing water there was not a significant change from swimming in darkness ",

       "(F(1,",
       (turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Flow"))$DF,
       ") = ",
       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Flow"))$LR_Chisq,3),
       ", p = ",
       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Flow"))$P_Val,3),
       ")",

       ", but fish with ablated lateral lines were less influenced by the number of fish on either side of them when turning",

       "(F(1,",
       (turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Flow"))$DF,
       ") = ",
       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Flow"))$LR_Chisq,3),
       ", p = ",
       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Flow"))$P_Val,3),
       ")",

       ". These results suggest that turning fish were able to tell where the other fish around them were, even in darkness, because fish in darkness did not have a significantly different probability of turning left or right from those fish swimming in light."

)
```

### 2023-03-30 2Dto3D/DLT_Converter.py

@@ -4,6 +4,7 @@ import pandas as pd
 import math
 #import plotly.express as px
 from scipy import linalg
+import sys
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
@@ -23,6 +24,11 @@ body_parts = ["head","midline2","tailbase","tailtip"]
 def DLTdvRecon(Ls, uvs):
 
     #uvs are in format [[v1_xs,v1_ys],[v2_xs,v2_ys]]
+
+    print(Ls)
+    print(uvs)
+
+    sys.exit()
 
     Ls = np.array(Ls)
     uvs = np.array(uvs)

### 2023-04-07 Charuco_DLT/rearrange_point_for_easywand.Rmd
Doing charuco calibrations

@@
 ```{r}
-detections <- read_csv("/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09/boards.csv") |> 
+detections <- read_csv("/Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06/boards.csv") |> 
   select(-`...1`)
@@
 ```{r}
-videodir <- '/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09'
+videodir <- '//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06'
 camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
@@
 ```{r}
-write_csv(ptsforeasywand, "/Users/Ben/Desktop/Charuco_DLT/2023_02_XX_calibrationcharuco_xypts.csv")
+write_csv(ptsforeasywand, "//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06/2023_04_06_calibrationcharuco_xypts.csv")
 ```

### 2023-04-07 Charuco_DLT/detect_charuco.py

@@ -28,7 +28,7 @@ board = aniposelib.boards.CharucoBoard(squaresX=6, squaresY=6,
 # For paths on Windows machines, be careful not to remove the r at the beginning of the quote; 
 #  without it, all backslashes will be registered as special characters.
 
-videopath = r'/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09'
+videopath = r'//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06'
 videonames = ['checkerboard_V1.mp4','checkerboard_V2.mp4']
 
 #This will detect points in the first video, just for testing purposes.

### 2023-04-19 Fish Data Analysis/Autocorrelation Testing.qmd
Updated figures

@@
 
-for(i in seq(1:10)){
+for(i in seq(1:5)){
   print(i)
@@
   new_autocorrs <- school_data %>% group_by(Date_Trial) %>%
-                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29","2021_7_7_16","2021_3_25_7","2021_10_6_34")) %>%
+                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29")) %>%
                     summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
@@
   ylim(0,1)+
-  ggtitle("NND")+
-  theme_classic()
+  ylab("NND Autocorrelation")+
+  xlab("Lag Values")+
+  theme_classic()+ 
+  theme(legend.position = "none")
 
@@
   ylim(0,1)+
-  ggtitle("Polar")+
-  theme_classic()
+  ylab("Polarity Autocorrelation")+
+  xlab("Lag Values")+
+  theme_classic()+ 
+  theme(legend.position = "none")
 
@@
   ylim(0,1)+
-  ggtitle("Speed")+
-  theme_classic()
+  ylab("Speed Autocorrelation")+
+  xlab("Lag Values")+
+  theme_classic()+ 
+  theme(legend.position = "none")
 
@@
   ylim(0,1)+
-  ggtitle("Groups")+
-  theme_classic()
+  ylab("Groups Autocorrelation")+
+  xlab("Lag Values")+
+  theme_classic()+ 
+  theme(legend.position = "none")
 
@@
   ylim(0,1)+
-  ggtitle("Area")+
-  theme_classic()
+  ylab("Area Autocorrelation")+
+  xlab("Lag Values")+
+  theme_classic()+ 
+  theme(legend.position = "none")
 
@@
   ylim(0,1)+
-  ggtitle("Area")+
-  theme_classic()
+  ylab("School Height Autocorrelation")+
+  xlab("Lag Values")+
+  theme_classic()+ 
+  theme(legend.position = "none")
 
 lag_plots <- ggarrange(
-          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot, area_lag_plot, height_lag_plot,
-          ncol = 3, nrow = 2)
+          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot,
+          ncol = 2, nrow = 2,
+          labels = c("A", "B", "C", "D"))
 
-ggsave("Autocorrelation Figures/Different_Lag_Figures.png", lag_plots, width = 22, height = 15)
+ggsave("Paper Figures/Different_Lag_Figures.png", lag_plots, width = 7, height = 7)
 

### 2023-04-19 Fish Data Analysis/Paper_Figures.qmd
Updated figures

@@
 
+placeholder_tibble <- tibble("Fish_Ratio" = c("0:7","0:7","3:4"),
+                             "Fish_Num_Ratio" = c(0.875,0.875,0.5),
+                             "Flow" = c("Still Water","Still Water","Still Water"),
+                             "Ablation" = c("No Ablation","Ablated","Ablated"),
+                             "Darkness" = c("Light","Light","Light"),
+                             "Type" = c("Combined Single","Combined Single","Combined Single"),
+                             "n" = c(0,0,0))
+
+turning_data_sum <- turning_data_sum %>% ungroup()
+
+turning_data_sum <- full_join(turning_data_sum,placeholder_tibble)
+
 dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
@@
   geom_point()+
+  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
   geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
@@
   ylab("Probability of a Right Turn") +
-  ylim(0,1) +
   scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
                                 "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory\nConditions")+
+  labs(color = "School Type")+
   theme(axis.text.x = element_text(size = text_size/2),
         axis.text.y = element_text(size = text_size/2),
-        axis.title.y = element_text(size = text_size/2),
-        legend.position = "none")
+        axis.title.y = element_text(size = text_size/2))+
+  guides(fill = FALSE)+
+  scale_y_continuous("Probability of a Right Turn",
+                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
+                     limits = c(0, 1))
 
@@
   scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  scale_fill_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
   geom_point()+
+  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
   geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
@@
   xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
   ylim(0,1) +
   scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
 dark_eight_and_single_graph
-```
-
-### Turning Stats Table Here
-
-```{r}
-turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
-                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
-tgs_aov <- Anova(turning_glm_still)
-
-turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
-                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
-tgf_aov <- Anova(turning_glm_flow)
-
-turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
-       Factor = c("Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness",
-                  "Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness"),
-       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
-       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
-       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
-       Is_Sig = P_Val < 0.05)
-
-# Single vs Eight fish
-light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
-                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
-                               family = binomial)
-ltg_aov <- Anova(light_turning_glm)
-
-ablated_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
-                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
-                               family = binomial)
-altg_aov <- Anova(ablated_turning_glm)
-
-dark_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
-                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
-                               family = binomial)
-dtg_aov <- Anova(dark_turning_glm)
-
-single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
-       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
-       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
-       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
-       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
-       Is_Sig = P_Val < 0.05)
-
-turning_results
-single_vs_eight_results
-
 ```
@@
           labels = c("A", "B", "C"),
-          ncol = 3, nrow = 1)
+          ncol = 2, nrow = 2)
 
-ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 9, height = 3)
+ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 10, height = 7)
 
@@
   geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
+  geom_errorbar(aes(ymin=max(Speed_Mean_Val-Speed_SD_Val,0), ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
   guides(fill = guide_legend(title = "Condition")) +
@@
     scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
-                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
+                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
     theme(axis.text.x = element_text(size = text_size),
@@
 Anova(groups_glm_flow, test.statistic="F")
-
-```
-
-### School Stats Table Here
-
-```{r}
-
-nnd_glmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-nnd_s_aov_me <- Anova(nnd_glmer_still)
-
-nnd_glmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-nnd_f_aov_me <- Anova(nnd_glmer_flow)
-
-height_glmer_still <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-height_s_aov_me <- Anova(height_glmer_still)
-
-height_glmer_flow <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-height_f_aov_me <- Anova(height_glmer_flow)
-
-polar_glmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-polar_s_aov_me <- Anova(polar_glmer_still)
-
-polar_glmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-polar_f_aov_me <- Anova(polar_glmer_flow)
-
-speed_glmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-speed_s_aov_me <- Anova(speed_glmer_still)
-
-speed_glmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-speed_f_aov_me <- Anova(speed_glmer_flow)
-
-area_glmer_still <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-area_s_aov_me <- Anova(area_glmer_still)
-
-area_glmer_flow <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-area_f_aov_me <- Anova(area_glmer_flow)
-
-groups_glmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-groups_s_aov_me <- Anova(groups_glmer_still)
-
-groups_glmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-groups_f_aov_me <- Anova(groups_glmer_flow)
-
-glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
-       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
-       Condition = rep(c("Ablation","Darkness"), 12),
-       DF = rep(c(length(nnd_glmer_still@resp$y)-3,length(nnd_glmer_flow@resp$y)-3),12),
-       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
-                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
-                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
-                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
-                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
-                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),
-
-       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
-                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
-                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
-                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
-                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
-                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),
-
-       Is_Sig = P_Val < 0.05)
-
-glmm_school_stats_table
-
-nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-nnd_s_aov <- Anova(nnd_glm_still)
-
-nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-nnd_f_aov <- Anova(nnd_glm_flow)
-
-height_glm_still <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-height_s_aov <- Anova(height_glm_still)
-
-height_glm_flow <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-height_f_aov <- Anova(height_glm_flow)
-
-polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-polar_s_aov <- Anova(polar_glm_still)
-
-polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-polar_f_aov <- Anova(polar_glm_flow)
-
-speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-speed_s_aov <- Anova(speed_glm_still)
-
-speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-speed_f_aov <- Anova(speed_glm_flow)
-
-area_glm_still <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-area_s_aov <- Anova(area_glm_still)
-
-area_glm_flow <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-area_f_aov <- Anova(area_glm_flow)
-
-groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-groups_s_aov <- Anova(groups_glm_still)
-
-groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-groups_f_aov <- Anova(groups_glm_flow)
-
-glm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
-       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
-       Condition = rep(c("Ablation","Darkness"), 12),
-       DF = rep(c(length(nnd_glm_still$y)-3,length(nnd_glm_flow$y)-3),12),
-       Chisq = c(nnd_s_aov$`LR Chisq`[1:2],nnd_f_aov$`LR Chisq`[1:2],
-                 height_s_aov$`LR Chisq`[1:2],height_f_aov$`LR Chisq`[1:2],
-                 polar_s_aov$`LR Chisq`[1:2],polar_f_aov$`LR Chisq`[1:2],
-                 speed_s_aov$`LR Chisq`[1:2],speed_f_aov$`LR Chisq`[1:2],
-                 area_s_aov$`LR Chisq`[1:2],area_f_aov$`LR Chisq`[1:2],
-                 groups_s_aov$`LR Chisq`[1:2],groups_f_aov$`LR Chisq`[1:2]),
-
-       P_Val = c(nnd_s_aov$`Pr(>Chisq)`[1:2],nnd_f_aov$`Pr(>Chisq)`[1:2],
-                 height_s_aov$`Pr(>Chisq)`[1:2],height_f_aov$`Pr(>Chisq)`[1:2],
-                 polar_s_aov$`Pr(>Chisq)`[1:2],polar_f_aov$`Pr(>Chisq)`[1:2],
-                 speed_s_aov$`Pr(>Chisq)`[1:2],speed_f_aov$`Pr(>Chisq)`[1:2],
-                 area_s_aov$`Pr(>Chisq)`[1:2],area_f_aov$`Pr(>Chisq)`[1:2],
-                 groups_s_aov$`Pr(>Chisq)`[1:2],groups_f_aov$`Pr(>Chisq)`[1:2]),
-
-       Is_Sig = P_Val < 0.05)
-
-glm_school_stats_table
-
-sum(glm_school_stats_table$Is_Sig == glmm_school_stats_table$Is_Sig)
-sum(glm_school_stats_table$Is_Sig == 1 & glmm_school_stats_table$Is_Sig == 1) / sum(glm_school_stats_table$Is_Sig == 1)
 
@@
 ```
+
+Autocorrelation Figure
+
+```{r}
+
+school_data_no_removals <- read.csv("Data/Fish_School_Values_3D.csv")
+school_data_no_removals <- na.omit(school_data_no_removals)
+
+school_data_no_removals <- school_data_no_removals %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           filter(School_Speed <= 5) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           mutate(Date = paste(Year,Month,Day,sep="_"),
+                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_"),)
+
+for(i in seq(1:5)){
+  print(i)
+
+  new_autocorrs <- school_data_no_removals %>% group_by(Date_Trial) %>%
+                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29")) %>%
+                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
+                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
+                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
+                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
+                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
+                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
+                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
+                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
+                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
+                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
+                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
+                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
+                              lag = i)
+
+  if(i == 1){
+    school_autocorrs <- new_autocorrs
+  }
+  else{
+    school_autocorrs <- rbind(school_autocorrs,new_autocorrs) 
+  }
+
+}
+
+nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ylab("NND Autocorrelation")+
+  xlab("Offest")+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ylab("Polarity Autocorrelation")+
+  xlab("Offest")+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ylab("Speed Autocorrelation")+
+  xlab("Offest")+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr))+
+  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
+  stat_summary(fun.y=mean, geom="point", size = 3) +
+  ylim(0,1)+
+  ylab("Numebr of Groups Autocorrelation")+
+  xlab("Offest")+
+  theme_classic()+ 
+  theme(legend.position = "none")
+
+lag_plots <- ggarrange(
+          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot,
+          ncol = 2, nrow = 2,
+          labels = c("A", "B", "C", "D"))
+
+ggsave("Paper Figures/Different_Lag_Figures.png", lag_plots, width = 7, height = 7)
+
+```

### 2023-04-19 Fish Data Analysis/Results_Text.qmd
Updated figures

@@
 library(lme4)
+library(sjPlot)
 ```
@@
 
+tab_df(glmm_school_stats_table, file="sjt_des.doc")
 ```
@@
 single_vs_eight_results
+
+tab_df(single_vs_eight_results, file="sjt_des.doc")
 ```

### 2023-05-11 Fish Data Analysis/Raw Traces Figure.qmd
Working on summary example graph

---
title: "Raw Traces"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggplot2)
library(ggpubr)
```

This is to make sure that it's the smae size after I do supsmu
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

supsmu_right_length_y <- function(x_data,y_data){
  output <- rep(NA,length(y_data))

  smooth_x <- supsmu(x_data,y_data)$x
  smooth_y <- supsmu(x_data,y_data)$y

  for(i in 1:length(smooth_x)){
    output[smooth_x[i]] <- smooth_y[i]
  }

  return(output)
}

```

Load the Data

```{r}
comp_data <- read.csv("Data/Fish_Raw_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
```

```{r}
comp_data <- comp_data %>% filter(Data_ID == "2021_8_3_17")

comp_data_switch_fish <- comp_data %>% mutate(Fish3 = Fish1,
                                              Fish3_X = Fish1_X,
                                              Fish3_Y = Fish1_Y,
                                              Fish3_Z = Fish1_Z,
                                              Fish3_Yaw_Heading = Fish1_Yaw_Heading,
                                              Fish3_Pitch_Heading = Fish1_Pitch_Heading,
                                              Fish3_Speed = Fish1_Speed) %>%
                                       mutate(Fish1 = Fish2,
                                              Fish1_X = Fish2_X,
                                              Fish1_Y = Fish2_Y,
                                              Fish1_Z = Fish2_Z,
                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading,
                                              Fish1_Pitch_Heading = Fish2_Pitch_Heading,
                                              Fish1_Speed = Fish2_Speed) %>%
                                       mutate(Fish2 = Fish3,
                                              Fish2_X = Fish3_X,
                                              Fish2_Y = Fish3_Y,
                                              Fish2_Z = Fish3_Z,
                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading,
                                              Fish2_Pitch_Heading = Fish3_Pitch_Heading,
                                              Fish2_Speed = Fish3_Speed) %>%
                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Yaw_Heading,Fish3_Pitch_Heading,Fish3_Speed))

comp_data_two <- bind_rows(comp_data, comp_data_switch_fish)

comp_data_all <- comp_data_two %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                                   mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                                   mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                                   mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                                   mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                                   mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                                   mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                                   mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) #%>%
                                   # mutate(Fish1_X = ifelse(Fish1_Speed > 10, NA, Fish1_X),
                                   #        Fish1_Y = ifelse(Fish1_Speed > 10, NA, Fish1_Y),
                                   #        Fish1_Speed = ifelse(Fish1_Speed > 10, NA, Fish1_Speed),
                                   #        Fish1_Yaw_Heading = ifelse(Fish1_Speed > 10, NA, Fish1_Yaw_Heading))

```

```{r}

unique((comp_data_all %>% filter(Darkness == "Dark"))$Data_ID)

unique(comp_data_all$Data_ID)

```

```{r}

"2020_7_28_3"
"2021_3_25_1"

# "2021_10_6_36" 4/5
# "2021_8_3_7" 2/5
# "2021_8_3_17" 4/5
# "2021_10_8_15" 3/5

example_data <- comp_data_all %>% filter(Data_ID == "2021_8_3_17") #%>% filter(Fish1 == "individual1")

smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Speed = mean(Fish1_Speed),
                                         Fish1_Yaw_Heading = mean(Fish1_Yaw_Heading)) %>%
                               group_by(Fish1) %>%
                               mutate(sin_Heading_Smooth = supsmu_right_length_y(Frame_Num,sin(deg2rad(Fish1_Yaw_Heading))),
                                      cos_Heading_Smooth = supsmu_right_length_y(Frame_Num,cos(deg2rad(Fish1_Yaw_Heading))),
                                      Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
                                      Fish1_Yaw_Heading_Smooth = rad2deg(atan2(sin_Heading_Smooth,cos_Heading_Smooth)),
                                      Fish1_Speed_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Speed),
                                      Speed_Increasing_Smooth = ifelse(Fish1_Speed < lead(Fish1_Speed),1,0),
                                      Fish1_Yaw_Heading_First = Fish1_Yaw_Heading_Smooth[4],
                                      Fish1_Yaw_Heading_Change = ((Fish1_Yaw_Heading_Smooth-lag(Fish1_Yaw_Heading_Smooth)) + 180) %% 360 - 180,
                                      Fish1_Yaw_Heading_Total = Fish1_Yaw_Heading_Smooth[4] + cumsum(replace_na(Fish1_Yaw_Heading_Change, 0)),
                                      Fish1_Yaw_Heading_Min = min(Fish1_Yaw_Heading_Total),
                                      Fish1_Yaw_Heading_Max = min(Fish1_Yaw_Heading_Total),
                                      Fish1_Yaw_Heading_Total_Corrected = ifelse(Fish1_Yaw_Heading_Max > 360, Fish1_Yaw_Heading_Total - 360,
                                                                                 ifelse(Fish1_Yaw_Heading_Min < -360, Fish1_Yaw_Heading_Total + 360,
                                                                                        Fish1_Yaw_Heading_Total))) %>%
                               ungroup()

smooth_data_nnd <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    group_by(Fish1) %>%
                                    arrange(Frame_Num) %>%
                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance)) %>%
                                    ungroup()

nnd_summary <- smooth_data_nnd %>% group_by(Frame_Num) %>%
                                   summarise(meanNND = mean(nndDistance, na.rm = TRUE)) %>%
                                   ungroup() %>%
                                   mutate(meanNND_Smooth = supsmu_right_length_y(Frame_Num,meanNND))

nnd_points <- smooth_data_nnd %>% filter(Frame_Num %in% c(50, 150, 275)) %>% 
                                     mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
                                     select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
                                     pivot_longer(c(Fish1, Fish2),
                                                  names_to = "Useless",
                                                  values_to = "Fish1") %>%
                                     select(-c(Useless))

nnd_joined <- nnd_points %>% left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X, Fish1_Y))

smooth_data_looker <- smooth_data %>% filter(Frame_Num %in% c(50, 150, 275))

polar_summary <- example_data %>% select(Fish1,Frame_Num,Fish1_Yaw_Heading) %>%
                                  group_by(Fish1,Frame_Num) %>%
                                  summarise(Fish1_Yaw_Heading = mean(Fish1_Yaw_Heading)) %>%
                                  ungroup() %>%
                                  mutate(sinHeading = sin(deg2rad(Fish1_Yaw_Heading)),
                                         cosHeading = cos(deg2rad(Fish1_Yaw_Heading))) %>%
                                  group_by(Frame_Num) %>%
                                  summarise(n = n(),
                                            sumSin = sum(sinHeading, na.rm = TRUE),
                                            sumCos =sum(cosHeading, na.rm = TRUE)) %>%
                                  ungroup() %>%
                                  mutate(polar = 1/n * sqrt(sumSin**2 + sumCos**2),
                                         polar_Smooth = supsmu_right_length_y(Frame_Num,polar))

raw_movement_plot <- ggplot()+
  geom_path(data = smooth_data, aes(x = Fish1_X_Smooth, y = Fish1_Y_Smooth, color = Fish1), size = 1)+
  geom_point(data = nnd_joined, aes(x = Fish1_X, y = Fish1_Y, color = Fish1), alpha = 1, size = 3)+
  geom_line(data = nnd_joined, aes(x = Fish1_X, y = Fish1_Y, fill = Grouping), alpha = 1)+
  theme_classic()+
  theme(legend.position = "none")

raw_movement_plot

raw_speed_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Speed_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  theme_classic()+ 
  theme(legend.position = "none")

raw_heading_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Yaw_Heading_Total_Corrected, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  theme_classic()+ 
  theme(legend.position = "none")

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num, y = meanNND_Smooth), color = "black", size = 1.5)+
  theme_classic()+ 
  theme(legend.position = "none")

raw_polar_plot <- ggplot(polar_summary, aes(x = Frame_Num, y = polar_Smooth))+
  geom_line(color = "black", size = 1.5)+
  theme_classic()+ 
  theme(legend.position = "none")

raw_movement_plot
raw_speed_plot
raw_heading_plot
raw_nnd_plot
raw_polar_plot

raw_plots <- ggarrange(raw_movement_plot, raw_speed_plot, raw_heading_plot, raw_nnd_plot, raw_polar_plot,
          ncol = 1,
          labels = c("A","B","C","D","E"))

ggsave("Raw_Test.png", raw_plots, width = 7, height = 21)
```

## Now we try it with 2D data, see if that loosk better

Load the Data

```{r}
comp_data <- read.csv("Data/Fish_Raw_Comp_Values_2D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x")
```

```{r}

comp_data_switch_fish <- comp_data %>% mutate(Fish3 = Fish1,
                                              Fish3_X = Fish1_X,
                                              Fish3_Y = Fish1_Y,
                                              Fish3_Heading = Fish1_Heading,
                                              Fish3_Speed = Fish1_Speed) %>%
                                       mutate(Fish1 = Fish2,
                                              Fish1_X = Fish2_X,
                                              Fish1_Y = Fish2_Y,
                                              Fish1_Heading = Fish2_Heading,
                                              Fish1_Speed = Fish2_Speed) %>%
                                       mutate(Fish2 = Fish3,
                                              Fish2_X = Fish3_X,
                                              Fish2_Y = Fish3_Y,
                                              Fish2_Heading = Fish3_Heading,
                                              Fish2_Speed = Fish3_Speed) %>%
                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Heading,Fish3_Speed))

comp_data_two <- bind_rows(comp_data, comp_data_switch_fish)

comp_data_all <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                                   mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                                   mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                                   mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                                   mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                                   mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                                   mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                                   mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                                   mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))

```

```{r}

unique((comp_data_all %>% filter(Darkness == "Dark" & Flow == "Flowing Water (2 BL/s)"))$Data_ID) # "2021_7_7_18"

#unique(comp_data_all$Data_ID)

```

```{r}

example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_21")

smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Speed = mean(Fish1_Speed),
                                         Fish1_Heading = mean(Fish1_Heading)) %>%
                               group_by(Fish1) %>%
                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
                                      Fish1_Speed_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Speed),
                                      Fish1_Heading_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Heading),
                                      Speed_Increasing_Smooth = ifelse(Fish1_Speed < lead(Fish1_Speed),1,0)) %>%
                               ungroup()

smooth_data_nnd <- example_data %>% select(c(Fish1,Frame_Num,Distance,Fish1_X)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE)) %>%
                                    mutate(nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance)) %>%
                                    summarise(nndDistance = mean(nndDistance,na.rm = TRUE)) %>%
                                    ungroup() %>%
                                    group_by(Fish1) %>%
                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance)) %>%
                                    ungroup()

nnd_summary <- smooth_data_nnd %>% group_by(Frame_Num) %>%
                                   summarise(meanNND = mean(nndDistance, na.rm = TRUE)) %>%
                                   ungroup() %>%
                                   mutate(meanNND_Smooth = supsmu_right_length_y(Frame_Num,meanNND))

polar_summary <- example_data %>% select(Fish1,Frame_Num,Fish1_Heading) %>%
                                  group_by(Fish1,Frame_Num) %>%
                                  summarise(Fish1_Heading = mean(Fish1_Heading)) %>%
                                  ungroup() %>%
                                  mutate(sinHeading = sin(deg2rad(Fish1_Heading)),
                                         cosHeading = cos(deg2rad(Fish1_Heading))) %>%
                                  group_by(Frame_Num) %>%
                                  summarise(n = n(),
                                            sumSin = sum(sinHeading, na.rm = TRUE),
                                            sumCos =sum(cosHeading, na.rm = TRUE)) %>%
                                  ungroup() %>%
                                  mutate(polar = 1/n * sqrt(sumSin**2 + sumCos**2),
                                         polar_Smooth = supsmu_right_length_y(Frame_Num,polar))

raw_movement_plot <- ggplot(smooth_data, aes(x = Fish1_X, y = Fish1_Y, color = Fish1, alpha = Frame_Num))+
  geom_path(size = 1)+
  theme_classic()+
  coord_fixed()

raw_speed_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Speed_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  theme_classic()

raw_heading_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Heading_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  theme_classic()

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num, y = meanNND_Smooth), color = "black", size = 1.5)+
  theme_classic()

raw_polar_plot <- ggplot(polar_summary, aes(x = Frame_Num, y = polar_Smooth))+
  geom_line(color = "black", size = 1.5)+
  theme_classic()

raw_movement_plot
raw_speed_plot
raw_heading_plot
raw_nnd_plot
raw_polar_plot
```

### 2023-05-11 3D_data_files_to_csv_4P.py

@@ -1247,6 +1247,12 @@ class trial:
             chunked_pitch_heading_diffs = angular_mean_tailbeat_chunk(current_comp.pitch_heading_diff,tailbeat_len)
             chunked_f1_speed = mean_tailbeat_chunk(current_comp.f1.speed,tailbeat_len)
             chunked_f2_speed = mean_tailbeat_chunk(current_comp.f2.speed,tailbeat_len)
+            chunked_f1_X = mean_tailbeat_chunk(current_comp.f1.head_x,tailbeat_len)
+            chunked_f1_Y = mean_tailbeat_chunk(current_comp.f1.head_y,tailbeat_len)
+            chunked_f1_Z = mean_tailbeat_chunk(current_comp.f1.head_z,tailbeat_len)
+            chunked_f2_X = mean_tailbeat_chunk(current_comp.f2.head_x,tailbeat_len)
+            chunked_f2_Y = mean_tailbeat_chunk(current_comp.f2.head_y,tailbeat_len)
+            chunked_f2_Z = mean_tailbeat_chunk(current_comp.f2.head_z,tailbeat_len)
             chunked_speed_diffs = mean_tailbeat_chunk(current_comp.speed_diff,tailbeat_len)
             chunked_tailbeat_offsets = mean_tailbeat_chunk(current_comp.tailbeat_offset_reps,tailbeat_len)
 
@@ -1273,6 +1279,12 @@ class trial:
                  'Pitch Heading_Diff': chunked_pitch_heading_diffs[:short_data_length],
                  'Fish1_Speed': chunked_f1_speed[:short_data_length],
                  'Fish2_Speed': chunked_f2_speed[:short_data_length],
+                 'Fish1_X': chunked_f1_X[:short_data_length],
+                 'Fish1_Y': chunked_f1_Y[:short_data_length],
+                 'Fish1_Z': chunked_f1_Z[:short_data_length],
+                 'Fish2_X': chunked_f2_X[:short_data_length],
+                 'Fish2_Y': chunked_f2_Y[:short_data_length],
+                 'Fish2_Z': chunked_f2_Z[:short_data_length],
                  'Speed_Diff': chunked_speed_diffs[:short_data_length],
                  'Sync': chunked_tailbeat_offsets[:short_data_length]}
 
@@ -1295,7 +1307,7 @@ class trial:
 
             short_data_length = min([len(current_comp.x_diff),len(current_comp.y_diff),len(current_comp.z_diff),len(dists),
[…]

### 2023-05-11 data_files_to_csv_4P.py

@@ -39,7 +39,7 @@ moving_average_n = 35
 tailbeat_len = 19
 
 #Fish len is the median of all fish lengths in pixels
-fish_len = 0.07862 #193 0.07862 #
+fish_len = 193 #0.07862 #193 0.07862 #
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
@@ -764,35 +764,36 @@ class school_comps:
         fig = plt.figure(figsize=(16, 10))
         gs = gridspec.GridSpec(ncols = 5, nrows = 3) 
 
-        ax0 = plt.subplot(gs[:,0])
+        ax0 = plt.subplot(gs[:,:2])
+        ax0.set_aspect(1)
         for fish in self.fishes:
             ax0.scatter(fish.head_x, fish.head_y, c = np.linspace(0,1,num = len(fish.head_x)), s = 2)
 
-        ax1 = plt.subplot(gs[0,1])
+        ax1 = plt.subplot(gs[0,2])
         ax1.plot(range(len(self.school_center_x)), self.school_center_x)
         ax1.set_title("School X")
 
-        ax2 = plt.subplot(gs[1,1])
+        ax2 = plt.subplot(gs[1,2])
         ax2.plot(range(len(self.school_center_y)), self.school_center_y)
         ax2.set_title("School Y")
 
-        ax3 = plt.subplot(gs[0,2])
+        ax3 = plt.subplot(gs[0,3])
         ax3.plot(range(len(self.group_speed)), self.group_speed)
         ax3.set_title("School Speed")
 
-        ax4 = plt.subplot(gs[1,2])
+        ax4 = plt.subplot(gs[1,3])
         ax4.plot(range(len(self.group_tb_freq)), self.group_tb_freq)
         ax4.set_title("School TB Freq")
 
-        ax5 = plt.subplot(gs[2,2])
+        ax5 = plt.subplot(gs[2,3])
         ax5.plot(range(len(self.polarization)), self.polarization)
         ax5.set_title("School Polarization")
 
-        ax6 = plt.subplot(gs[0,3])
+        ax6 = plt.subplot(gs[0,4])
         ax6.plot(range(len(self.school_areas)), self.school_areas)
         ax6.set_title("School Area")
 
-        ax7 = plt.subplot(gs[1,3])
+        ax7 = plt.subplot(gs[1,4])
         ax7.plot(range(len(self.nearest_neighbor_distance)), self.nearest_neighbor_distance)
[…]

### 2023-05-15 Fish Data Analysis/Raw Traces Figure.qmd
Added 3D plotting

@@
 ```{r}
+library(gsignal)
 library(tidyverse)
@@
 library(ggpubr)
+library(plotly)
 ```
@@
 
+fish_len <- 0.083197
 ```
@@
 ```{r}
-comp_data <- comp_data %>% filter(Data_ID == "2021_8_3_17")
+#comp_data <- comp_data %>% filter(Data_ID == "2021_8_3_17")
 
@@
                                    mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                                   mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) #%>%
+                                   mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                                   mutate(Fish1_X = Fish1_X / fish_len,
+                                          Fish1_Y = Fish1_Y / fish_len,
+                                          Fish1_Z = Fish1_Z / fish_len,
+                                          Fish2_X = Fish2_X / fish_len,
+                                          Fish2_Y = Fish2_Y / fish_len,
+                                          Fish2_Z = Fish2_Z / fish_len) #%>%
                                    # mutate(Fish1_X = ifelse(Fish1_Speed > 10, NA, Fish1_X),
@@
 
-unique(comp_data_all$Data_ID)
+#unique(comp_data_all$Data_ID)
 
@@
 # "2021_8_3_17" 4/5
-# "2021_10_8_15" 3/5
 
-example_data <- comp_data_all %>% filter(Data_ID == "2021_8_3_17") #%>% filter(Fish1 == "individual1")
+# 2021_8_3_7:(206: 2 Groups)
+
+#2021_7_7_27 ?
+
+example_data <- comp_data_all %>% filter(Data_ID == "2021_7_7_14") #%>% filter(Fish1 == "individual1")
 
@@
                                          Fish1_Y = mean(Fish1_Y),
+                                         Fish1_Z = mean(Fish1_Z),
                                          Fish1_Speed = mean(Fish1_Speed),
@@
                                group_by(Fish1) %>%
-                               mutate(sin_Heading_Smooth = supsmu_right_length_y(Frame_Num,sin(deg2rad(Fish1_Yaw_Heading))),
-                                      cos_Heading_Smooth = supsmu_right_length_y(Frame_Num,cos(deg2rad(Fish1_Yaw_Heading))),
-                                      Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
+                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                       Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
-                                      Fish1_Yaw_Heading_Smooth = rad2deg(atan2(sin_Heading_Smooth,cos_Heading_Smooth)),
+                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
                                       Fish1_Speed_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Speed),
                                       Speed_Increasing_Smooth = ifelse(Fish1_Speed < lead(Fish1_Speed),1,0),
-                                      Fish1_Yaw_Heading_First = Fish1_Yaw_Heading_Smooth[4],
-                                      Fish1_Yaw_Heading_Change = ((Fish1_Yaw_Heading_Smooth-lag(Fish1_Yaw_Heading_Smooth)) + 180) %% 360 - 180,
-                                      Fish1_Yaw_Heading_Total = Fish1_Yaw_Heading_Smooth[4] + cumsum(replace_na(Fish1_Yaw_Heading_Change, 0)),
-                                      Fish1_Yaw_Heading_Min = min(Fish1_Yaw_Heading_Total),
-                                      Fish1_Yaw_Heading_Max = min(Fish1_Yaw_Heading_Total),
-                                      Fish1_Yaw_Heading_Total_Corrected = ifelse(Fish1_Yaw_Heading_Max > 360, Fish1_Yaw_Heading_Total - 360,
-                                                                                 ifelse(Fish1_Yaw_Heading_Min < -360, Fish1_Yaw_Heading_Total + 360,
-                                                                                        Fish1_Yaw_Heading_Total))) %>%
+                                      Fish1_Yaw_Heading_Max_Unwrap = rad2deg(supsmu_right_length_y(Frame_Num,unwrap(deg2rad(Fish1_Yaw_Heading))))) %>%
                                ungroup()
@@
 
-nnd_points <- smooth_data_nnd %>% filter(Frame_Num %in% c(50, 150, 275)) %>% 
+nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
+                                    group_by(Fish1,Frame_Num) %>%
+                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
+                                           all_nas = all(is.na(nndDistance))) %>%
+                                    filter(Distance < 2 | all_nas) %>%
+                                    mutate(row_n = row_number(),
+                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
+                                    filter(remove == "N") %>%
+                                    ungroup() %>%
+                                    filter(Frame_Num %in% c(10)) %>% 
                                     mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
@@
                                                   values_to = "Fish1") %>%
-                                     select(-c(Useless))
-
-nnd_joined <- nnd_points %>% left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X, Fish1_Y))
-
-smooth_data_looker <- smooth_data %>% filter(Frame_Num %in% c(50, 150, 275))
+                                    select(-c(Useless)) %>% 
+                                    left_join(., smooth_data %>% 
+                                    select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))
 
@@
   geom_path(data = smooth_data, aes(x = Fish1_X_Smooth, y = Fish1_Y_Smooth, color = Fish1), size = 1)+
-  geom_point(data = nnd_joined, aes(x = Fish1_X, y = Fish1_Y, color = Fish1), alpha = 1, size = 3)+
-  geom_line(data = nnd_joined, aes(x = Fish1_X, y = Fish1_Y, fill = Grouping), alpha = 1)+
+  geom_point(data = nnd_joined, aes(x = Fish1_X_Smooth, y = Fish1_Y_Smooth, color = Fish1), alpha = 1, size = 3)+
+  geom_line(data = nnd_joined, aes(x = Fish1_X_Smooth, y = Fish1_Y_Smooth, fill = Grouping), alpha = 1)+
   theme_classic()+
   theme(legend.position = "none")
-
-raw_movement_plot
 
@@
 
-raw_heading_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Yaw_Heading_Total_Corrected, color = Fish1))+
+raw_heading_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Yaw_Heading_Max_Unwrap, color = Fish1))+
   geom_line(size = 1, alpha = 0.5)+
@@
   theme_classic()+ 
+  ylim(0,1)+
   theme(legend.position = "none")
@@
 
-ggsave("Raw_Test.png", raw_plots, width = 7, height = 21)
-```
+ggsave("Raw_Test.png", raw_plots, width = 10, height = 14)
 
-## Now we try it with 2D data, see if that loosk better
+fig <- plot_ly() %>%
+       add_trace(x = smooth_data$Fish1_X_Smooth, y = smooth_data$Fish1_Y_Smooth, z = smooth_data$Fish1_Z_Smooth,
+               split = smooth_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
+               color = smooth_data$Fish1,
+               colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
 
-Load the Data
+       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth,
+                 split = nnd_joined$Fish1, type = 'scatter3d', mode = "markers",
+                 color = nnd_joined$Fish1,
+                 colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
 
-```{r}
-comp_data <- read.csv("Data/Fish_Raw_Comp_Values_2D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x")
-```
+       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth, 
+                 split = nnd_joined$Grouping, type = 'scatter3d', mode = "lines", color = I("black")) %>%
 
-```{r}
+       layout(showlegend = FALSE)
 
-comp_data_switch_fish <- comp_data %>% mutate(Fish3 = Fish1,
-                                              Fish3_X = Fish1_X,
-                                              Fish3_Y = Fish1_Y,
-                                              Fish3_Heading = Fish1_Heading,
-                                              Fish3_Speed = Fish1_Speed) %>%
-                                       mutate(Fish1 = Fish2,
-                                              Fish1_X = Fish2_X,
-                                              Fish1_Y = Fish2_Y,
-                                              Fish1_Heading = Fish2_Heading,
-                                              Fish1_Speed = Fish2_Speed) %>%
-                                       mutate(Fish2 = Fish3,
-                                              Fish2_X = Fish3_X,
-                                              Fish2_Y = Fish3_Y,
-                                              Fish2_Heading = Fish3_Heading,
-                                              Fish2_Speed = Fish3_Speed) %>%
-                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Heading,Fish3_Speed))
-
-comp_data_two <- bind_rows(comp_data, comp_data_switch_fish)
-
-comp_data_all <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                                   mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
-                                   mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                                   mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                                   mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                                   mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                                   mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                                   mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                                   mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
+fig
 
 ```
-
-```{r}
-
-unique((comp_data_all %>% filter(Darkness == "Dark" & Flow == "Flowing Water (2 BL/s)"))$Data_ID) # "2021_7_7_18"
-
-#unique(comp_data_all$Data_ID)
-
-```
-
-```{r}
-
-example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_21")
-
-smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
-                               summarise(Fish1_X = mean(Fish1_X),
-                                         Fish1_Y = mean(Fish1_Y),
-                                         Fish1_Speed = mean(Fish1_Speed),
-                                         Fish1_Heading = mean(Fish1_Heading)) %>%
-                               group_by(Fish1) %>%
-                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
-                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
-                                      Fish1_Speed_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Speed),
-                                      Fish1_Heading_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Heading),
-                                      Speed_Increasing_Smooth = ifelse(Fish1_Speed < lead(Fish1_Speed),1,0)) %>%
-                               ungroup()
-
-smooth_data_nnd <- example_data %>% select(c(Fish1,Frame_Num,Distance,Fish1_X)) %>%
-                                    group_by(Fish1,Frame_Num) %>%
-                                    mutate(nndDistance = min(Distance, na.rm = TRUE)) %>%
-                                    mutate(nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance)) %>%
-                                    summarise(nndDistance = mean(nndDistance,na.rm = TRUE)) %>%
-                                    ungroup() %>%
-                                    group_by(Fish1) %>%
-                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance)) %>%
-                                    ungroup()
-
-nnd_summary <- smooth_data_nnd %>% group_by(Frame_Num) %>%
-                                   summarise(meanNND = mean(nndDistance, na.rm = TRUE)) %>%
-                                   ungroup() %>%
-                                   mutate(meanNND_Smooth = supsmu_right_length_y(Frame_Num,meanNND))
-
-polar_summary <- example_data %>% select(Fish1,Frame_Num,Fish1_Heading) %>%
-                                  group_by(Fish1,Frame_Num) %>%
-                                  summarise(Fish1_Heading = mean(Fish1_Heading)) %>%
-                                  ungroup() %>%
-                                  mutate(sinHeading = sin(deg2rad(Fish1_Heading)),
-                                         cosHeading = cos(deg2rad(Fish1_Heading))) %>%
-                                  group_by(Frame_Num) %>%
-                                  summarise(n = n(),
-                                            sumSin = sum(sinHeading, na.rm = TRUE),
-                                            sumCos =sum(cosHeading, na.rm = TRUE)) %>%
-                                  ungroup() %>%
-                                  mutate(polar = 1/n * sqrt(sumSin**2 + sumCos**2),
-                                         polar_Smooth = supsmu_right_length_y(Frame_Num,polar))
-
-raw_movement_plot <- ggplot(smooth_data, aes(x = Fish1_X, y = Fish1_Y, color = Fish1, alpha = Frame_Num))+
-  geom_path(size = 1)+
-  theme_classic()+
-  coord_fixed()
-
-raw_speed_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Speed_Smooth, color = Fish1))+
-  geom_line(size = 1, alpha = 0.5)+
-  theme_classic()
-
-raw_heading_plot <- ggplot(smooth_data, aes(x = Frame_Num, y = Fish1_Heading_Smooth, color = Fish1))+
-  geom_line(size = 1, alpha = 0.5)+
-  theme_classic()
-
-raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num, y = Fish1_Distance_Smooth, color = Fish1))+
-  geom_line(size = 1, alpha = 0.5)+
-  geom_line(data = nnd_summary, aes(x = Frame_Num, y = meanNND_Smooth), color = "black", size = 1.5)+
-  theme_classic()
-
-raw_polar_plot <- ggplot(polar_summary, aes(x = Frame_Num, y = polar_Smooth))+
-  geom_line(color = "black", size = 1.5)+
-  theme_classic()
-
-raw_movement_plot
-raw_speed_plot
-raw_heading_plot
-raw_nnd_plot
-raw_polar_plot
-```

### 2023-05-17 Fish Data Analysis/Raw Traces Figure.qmd
Fixing 2021_10_08_17 Data

@@
 library(plotly)
+library(zoo)
 ```
@@
 
-#unique(comp_data_all$Data_ID)
+unique(comp_data_all$Data_ID)
 
@@
 
-example_data <- comp_data_all %>% filter(Data_ID == "2021_7_7_14") #%>% filter(Fish1 == "individual1")
+example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_27")
 
@@
                                       Fish1_Yaw_Heading_Max_Unwrap = rad2deg(supsmu_right_length_y(Frame_Num,unwrap(deg2rad(Fish1_Yaw_Heading))))) %>%
-                               ungroup()
+                               ungroup() %>% 
+                               filter(Fish1_Z_Smooth >= -0.1 & Fish1_Z_Smooth <= 5)
 
@@
 ```
+
+ Okay now we're going to try and replace all missing parts with a spline
+
+"2021_7_7_19"  "2021_7_7_27"  "2021_10_8_27" "2021_7_7_16"  "2021_7_7_17"  "2021_7_7_14"  "2021_10_8_21" "2021_10_8_26" "2021_7_7_6"   "2021_10_8_15"
+
+```{r}
+
+example_data_spline <- comp_data_all %>% filter(Data_ID == "2021_10_8_21")
+
+spline_data <- example_data_spline %>% group_by(Fish1,Frame_Num) %>%
+                               summarise(Fish1_X = mean(Fish1_X),
+                                         Fish1_Y = mean(Fish1_Y),
+                                         Fish1_Z = mean(Fish1_Z),
+                                         Fish1_Speed = mean(Fish1_Speed),
+                                         Fish1_Yaw_Heading = mean(Fish1_Yaw_Heading)) %>%
+                               group_by(Fish1) %>%
+                               mutate(Fish1_X_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_X,NA),
+                                      Fish1_Y_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Y,NA),
+                                      Fish1_Z_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Z,NA),
+                                      Fish1_Speed_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Speed,NA),
+                                      Fish1_Heading_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Yaw_Heading,NA)) %>%
+                               mutate(Fish1_X_Spline = na.spline(Fish1_X_IB) + 0*na.approx(Fish1_X_IB, na.rm = FALSE),
+                                      Fish1_Y_Spline = na.spline(Fish1_Y_IB) + 0*na.approx(Fish1_Y_IB, na.rm = FALSE),
+                                      Fish1_Z_Spline = na.spline(Fish1_Z_IB) + 0*na.approx(Fish1_Z_IB, na.rm = FALSE),
+                                      Fish1_Speed_Spline = na.spline(Fish1_Speed_IB) + 0*na.approx(Fish1_Speed_IB, na.rm = FALSE),
+                                      Fish1_Heading_Spline = na.spline(Fish1_Heading_IB) + 0*na.approx(Fish1_Heading_IB, na.rm = FALSE))%>%
+                               ungroup()
+
+fig <- plot_ly() %>%
+       add_trace(x = spline_data$Fish1_X_Spline, y = spline_data$Fish1_Y_Spline, z = spline_data$Fish1_Z_Spline,
+               split = spline_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
+               color = spline_data$Fish1,
+               colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
+       layout(showlegend = FALSE)
+
+fig
+
+```

### 2023-05-17 2Dto3D/DLT_Converter.py

@@ -25,11 +25,6 @@ def DLTdvRecon(Ls, uvs):
 
     #uvs are in format [[v1_xs,v1_ys],[v2_xs,v2_ys]]
 
-    print(Ls)
-    print(uvs)
-
-    sys.exit()
-
     Ls = np.array(Ls)
     uvs = np.array(uvs)
 

### 2023-05-17 2Dto3D/DLT_Plotter.py

@@ -67,4 +67,15 @@ for file_name in three_d_files:
 
         file_id = file_name[0:22]
 
-        fig.write_html("Saved 3D Plots Manual/{name}.html".format(name = file_id), auto_play=False)
+        fig.write_html("Saved 3D Plots Manual/{name}_animated.html".format(name = file_id), auto_play=False)
+
+
+        head_df = df[df['BodyPart'] == "head"] 
+
+        fig = px.line_3d(head_df,x="x", y="y", z="z", color="Fish", hover_data = ["BodyPart"])
+
+        fig.layout.scene.aspectratio = {'x':1, 'y':1, 'z':1}
+
+        #fig.show()
+
+        fig.write_html("Saved 3D Plots Manual/{name}_trace.html".format(name = file_id), auto_play=False)

### 2023-05-19 Fish Data Analysis/Raw Traces Figure.qmd
Finalizing plots before reorganization

@@
 This is to make sure that it's the smae size after I do supsmu
+
 ```{r}
@@
 
+nnd_frame <- 300
+
 example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_27")
@@
 
+select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
+                                          filter(Frame_Num %in% c(100, 200, 300)) %>% 
+                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
+                                          group_by(Fish1, Frame_Num) %>%
+                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
+                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
+                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))
+
 nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
@@
                                            all_nas = all(is.na(nndDistance))) %>%
-                                    filter(Distance < 2 | all_nas) %>%
+                                    filter(Distance < 1.9 | all_nas) %>%
                                     mutate(row_n = row_number(),
@@
                                     ungroup() %>%
-                                    filter(Frame_Num %in% c(10)) %>% 
+                                    filter(Frame_Num %in% c(nnd_frame)) %>% 
                                     mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
@@
                                     select(-c(Useless)) %>% 
-                                    left_join(., smooth_data %>% 
-                                    select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))
+                                    #rbind(., individual5_tib) %>%
+                                    left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))
 
@@
 
-       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth,
-                 split = nnd_joined$Fish1, type = 'scatter3d', mode = "markers",
-                 color = nnd_joined$Fish1,
+       add_trace(x = select_frames_labeled$Fish1_X_Smooth, y = select_frames_labeled$Fish1_Y_Smooth, z = select_frames_labeled$Fish1_Z_Smooth,
+                 split = select_frames_labeled$Fish1, type = 'scatter3d', mode = "markers",
+                 color = select_frames_labeled$Fish1,
                  colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
@@
 
+#make colors the same-ish for groups
+#do 2 3d figures and NND figure
 ```
@@
 
-"2021_7_7_19"  "2021_7_7_27"  "2021_10_8_27" "2021_7_7_16"  "2021_7_7_17"  "2021_7_7_14"  "2021_10_8_21" "2021_10_8_26" "2021_7_7_6"   "2021_10_8_15"
+"2021_7\_7_19" "2021_7\_7_27" "2021_10_8\_27" "2021_7\_7_16" "2021_7\_7_17" "2021_7\_7_14" "2021_10_8\_21" "2021_10_8\_26" "2021_7\_7_6" "2021_10_8\_15"
 
@@
 
-example_data_spline <- comp_data_all %>% filter(Data_ID == "2021_10_8_21")
+example_data_spline <- comp_data_all %>% filter(Data_ID == "2021_10_8_27")
 

### 2023-05-22 Fish Data Analysis/Raw Traces Figure.qmd
Reverting to old files, fixing 3d matching errors

@@
 
-unique(comp_data_all$Data_ID)
+```
+
+### Final Version Dark
+No flow
+
+```{r}
+
+nnd_frame <- 130
+
+example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_15")
+
+smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
+                               summarise(Fish1_X = mean(Fish1_X),
+                                         Fish1_Y = mean(Fish1_Y),
+                                         Fish1_Z = mean(Fish1_Z)) %>%
+                               group_by(Fish1) %>%
+                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
+                                      Fish1_X_Smooth = na.spline(Fish1_X_Smooth) + 0*na.approx(Fish1_X_Smooth, na.rm = FALSE),
+                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
+                                      Fish1_Y_Smooth = na.spline(Fish1_Y_Smooth) + 0*na.approx(Fish1_Y_Smooth, na.rm = FALSE),
+                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
+                                      Fish1_Z_Smooth = na.spline(Fish1_Z_Smooth) + 0*na.approx(Fish1_Z_Smooth, na.rm = FALSE)) %>%
+                               ungroup() #%>% 
+                               #filter(Fish1_Z_Smooth >= -0.5 & Fish1_Z_Smooth <= 5)
+
+smooth_data_nnd <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish1_Z,Fish2_X,Fish2_Y,Fish1_Z)) %>%
+                                    group_by(Fish1,Frame_Num) %>%
+                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
+                                           all_nas = all(is.na(nndDistance))) %>%
+                                    filter(Distance == nndDistance | all_nas) %>%
+                                    mutate(row_n = row_number()) %>%
+                                    filter(row_n == 1) %>%
+                                    ungroup() %>%
+                                    group_by(Fish1) %>%
+                                    arrange(Frame_Num) %>%
+                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance),
+                                           Fish1_Distance_Smooth = na.spline(Fish1_Distance_Smooth) + 0*na.approx(Fish1_Distance_Smooth, na.rm = FALSE)) %>%
+                                    ungroup() #%>% 
+                                    #filter(Fish1_Z >= -2 & Fish1_Z <= 5)
+
+nnd_summary <- smooth_data_nnd %>% group_by(Frame_Num) %>%
+                                   summarise(meanNND = mean(nndDistance, na.rm = TRUE)) %>%
+                                   ungroup() %>%
+                                   mutate(meanNND_Smooth = supsmu_right_length_y(Frame_Num,meanNND))
+
+select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
+                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
+                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
+                                          group_by(Fish1, Frame_Num) %>%
+                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
+                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
+                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))
+
+nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
+                                    group_by(Fish1,Frame_Num) %>%
+                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
+                                           all_nas = all(is.na(nndDistance))) %>%
+                                    filter(Distance <= 2 | all_nas) %>%
+                                    mutate(row_n = row_number(),
+                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
+                                    filter(remove == "N") %>%
+                                    ungroup() %>%
+                                    filter(Frame_Num %in% c(nnd_frame)) %>% 
+                                    mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
+                                    select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
+                                    pivot_longer(c(Fish1, Fish2),
+                                                  names_to = "Useless",
+                                                  values_to = "Fish1") %>%
+                                    select(-c(Useless)) %>% 
+                                    left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))
+
+raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
+  geom_line(size = 1, alpha = 0.5)+
+  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
+  scale_color_manual(values = c("#ea4747","#df4415","#ff7489","#4790ea","#47ea4b", "#15c9df", "#8574ff", "#09b326"))+
+  theme_classic()+ 
+  theme(legend.position = "none")+
+  xlab("Time (s)")+
+  ylab("NND (BL)")+
+  ylim(0,3)
+
+raw_nnd_plot
+
+axis_remove <- list(showaxeslabels  = FALSE,
+                    showgrid = FALSE,
+                    showline = FALSE,
+                    showticklabels = FALSE,
+                    showspikes = FALSE,
+                    showticklabels  = FALSE,
+                    visible = FALSE,
+                    zeroline = FALSE)
+
+fig <- plot_ly() %>%
+        #groups and colors
+        # 1, 2, 3: ea4747, df1574, fdbe6f
+        # 5, 8: 32CD32, 006400
+        # 4, 6, 7: 4790ea, 8115df, 45dfef
+        # Old: c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")
+        # New: c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")
+
+       add_trace(x = smooth_data$Fish1_X_Smooth, y = smooth_data$Fish1_Y_Smooth, z = smooth_data$Fish1_Z_Smooth,
+               split = smooth_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
+               color = smooth_data$Fish1,
+               colors = c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")) %>%
+
+       add_trace(x = select_frames_labeled$Fish1_X_Smooth, y = select_frames_labeled$Fish1_Y_Smooth, z = select_frames_labeled$Fish1_Z_Smooth,
+                 split = select_frames_labeled$Fish1, type = 'scatter3d', mode = "markers",
+                 color = select_frames_labeled$Fish1,
+                 colors = c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")) %>%
+
+       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth, 
+                 split = nnd_joined$Grouping, type = 'scatter3d', mode = "lines", color = I("black"), line = list(shape = "spline", width = 10)) %>%
+
+       layout(showlegend = FALSE, scene = list(aspectratio=list(x=2,y=1,z=1),
+              xaxis = axis_remove, 
+              yaxis = axis_remove,
+              zaxis = axis_remove))
+
+fig
+
+#make colors the same-ish for groups
+#do 2 3d figures and NND figure
+```
+
+## Non Darkness Figure
+
+```{r}
+
+unique((comp_data_all %>% filter(Darkness == "Light" & Flow == "Still Water"))$Data_ID)
 
 ```
+
+### Final Version
+
+```{r}
+
+#2021_8_3_7 !
+#2021_10_6_38 Not as good
+
+nnd_frame <- 120
+
+example_data <- comp_data_all %>% filter(Data_ID == "2021_8_3_7")
+
+smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
+                               summarise(Fish1_X = mean(Fish1_X),
+                                         Fish1_Y = mean(Fish1_Y),
+                                         Fish1_Z = mean(Fish1_Z)) %>%
+                               group_by(Fish1) %>%
+                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
+                                      Fish1_X_Smooth = na.spline(Fish1_X_Smooth) + 0*na.approx(Fish1_X_Smooth, na.rm = FALSE),
+                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
+                                      Fish1_Y_Smooth = na.spline(Fish1_Y_Smooth) + 0*na.approx(Fish1_Y_Smooth, na.rm = FALSE),
+                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
+                                      Fish1_Z_Smooth = na.spline(Fish1_Z_Smooth) + 0*na.approx(Fish1_Z_Smooth, na.rm = FALSE)) %>%
+                               ungroup() #%>% 
+                               #filter(Fish1_Z_Smooth >= -0.5 & Fish1_Z_Smooth <= 5)
+
+smooth_data_nnd <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish1_Z,Fish2_X,Fish2_Y,Fish1_Z)) %>%
+                                    group_by(Fish1,Frame_Num) %>%
+                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
+                                           all_nas = all(is.na(nndDistance))) %>%
+                                    filter(Distance == nndDistance | all_nas) %>%
+                                    mutate(row_n = row_number()) %>%
+                                    filter(row_n == 1) %>%
+                                    ungroup() %>%
+                                    group_by(Fish1) %>%
+                                    arrange(Frame_Num) %>%
+                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance),
+                                           Fish1_Distance_Smooth = na.spline(Fish1_Distance_Smooth) + 0*na.approx(Fish1_Distance_Smooth, na.rm = FALSE)) %>%
+                                    ungroup() #%>% 
+                                    #filter(Fish1_Z >= -2 & Fish1_Z <= 5)
+
+nnd_summary <- smooth_data_nnd %>% group_by(Frame_Num) %>%
+                                   summarise(meanNND = mean(nndDistance, na.rm = TRUE)) %>%
+                                   ungroup() %>%
+                                   mutate(meanNND_Smooth = supsmu_right_length_y(Frame_Num,meanNND))
+
+select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
+                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
+                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
+                                          group_by(Fish1, Frame_Num) %>%
+                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
+                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
+                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))
+
+nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
+                                    group_by(Fish1,Frame_Num) %>%
+                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
+                                           all_nas = all(is.na(nndDistance))) %>%
+                                    filter(Distance <= 2 | all_nas) %>%
+                                    mutate(row_n = row_number(),
+                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
+                                    filter(remove == "N") %>%
+                                    ungroup() %>%
+                                    filter(Frame_Num %in% c(nnd_frame)) %>% 
+                                    mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
+                                    select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
+                                    pivot_longer(c(Fish1, Fish2),
+                                                  names_to = "Useless",
+                                                  values_to = "Fish1") %>%
+                                    select(-c(Useless)) %>% 
+                                    left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))
+
+raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
+  geom_line(size = 1, alpha = 0.5)+
+  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
+  scale_color_manual(values = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC"))+
+  theme_classic()+ 
+  theme(legend.position = "none")+
+  xlab("Time (s)")+
+  ylab("NND (BL)")+
+  ylim(0,3)
+
+raw_nnd_plot
+
+axis_remove <- list(showaxeslabels  = FALSE,
+                    showgrid = FALSE,
+                    showline = FALSE,
+                    showticklabels = FALSE,
+                    showspikes = FALSE,
+                    showticklabels  = FALSE,
+                    visible = FALSE,
+                    zeroline = FALSE)
+
+fig <- plot_ly() %>%
+        #groups and colors
+        # 1, 2, 3: ea4747, df1574, fdbe6f
+        # 5, 8: 32CD32, 006400
+        # 4, 6, 7: 4790ea, 8115df, 45dfef
+        # Old: c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")
+        # New: c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")
+
+       add_trace(x = smooth_data$Fish1_X_Smooth, y = smooth_data$Fish1_Y_Smooth, z = smooth_data$Fish1_Z_Smooth,
+               split = smooth_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
+               color = smooth_data$Fish1,
+               colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
+
+       add_trace(x = select_frames_labeled$Fish1_X_Smooth, y = select_frames_labeled$Fish1_Y_Smooth, z = select_frames_labeled$Fish1_Z_Smooth,
+                 split = select_frames_labeled$Fish1, type = 'scatter3d', mode = "markers",
+                 color = select_frames_labeled$Fish1,
+                 colors =c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
+
+       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth, 
+                 split = nnd_joined$Grouping, type = 'scatter3d', mode = "lines", color = I("black"), line = list(shape = "spline", width = 10)) %>%
+
+       layout(showlegend = FALSE, scene = list(aspectratio=list(x=2,y=1,z=1),
+              xaxis = axis_remove, 
+              yaxis = axis_remove,
+              zaxis = axis_remove))
+
+fig
+
+#make colors the same-ish for groups
+#do 2 3d figures and NND figure
+```
+
+### Old Stuff
 

### 2023-05-22 2Dto3D/DLT_Plotter.py

@@ -17,7 +17,7 @@ file_folder = "Final 3D Manual/"
 three_d_files = os.listdir(file_folder)
 
 for file_name in three_d_files:
-    if file_name.endswith(".csv"):
+    if file_name.endswith(".csv"): #and "03_25_10" in file_name:
 
         print(file_name)
 

### 2023-05-22 3D_data_files_to_csv_4P.py

@@ -840,7 +840,7 @@ class school_comps:
                 self.school_areas[i] = hull.volume/fish_len**2
 
     def calc_school_groups(self):
-        min_BL_for_groups = 2
+        min_BL_for_groups = 1.5
 
         school_xs = np.asarray([fish.head_x for fish in self.fishes])
         school_ys = np.asarray([fish.head_y for fish in self.fishes])
@@ -848,7 +848,7 @@ class school_comps:
 
         self.school_groups = [np.nan for i in range(len(school_xs[0]))]
 
-        for i in range(87,len(school_xs[0])):
+        for i in range(0,len(school_xs[0])):
 
             x_row = school_xs[:,i]
             y_row = school_ys[:,i]

### 2023-05-23 Fish Data Analysis/Raw Traces Figure.qmd
Finished Figure 1

@@
 fish_len <- 0.083197
+text_size = 20
+
 ```
@@
 ```{r}
-comp_data <- read.csv("Data/Fish_Raw_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
+comp_data <- read.csv("Data/3D_Trace_Fish_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
 ```
@@
 ### Final Version Dark
+
 No flow
@@
 
+smooth_data_nnd_test_dark <- smooth_data_nnd %>% filter(Frame_Num %in% c(nnd_frame))
+
 nnd_summary <- smooth_data_nnd %>% group_by(Frame_Num) %>%
@@
 select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
-                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
+                                          filter(Frame_Num %in% c(240, nnd_frame)) %>% 
                                           left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
@@
   ylab("NND (BL)")+
-  ylim(0,3)
+  ylim(0,3)+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.x = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
@@
 
-axis_remove <- list(showaxeslabels  = FALSE,
-                    showgrid = FALSE,
+ggsave("Paper Figures/Dark_NND_Raw.png", raw_nnd_plot, width = 6, height = 4)
+
+axis_remove <- list(title = list(text = ""),
+                    showaxeslabels  = FALSE,
+                    showgrid = TRUE,
                     showline = FALSE,
@@
                     showticklabels  = FALSE,
-                    visible = FALSE,
+                    visible = TRUE,
                     zeroline = FALSE)
@@
 
+smooth_data_nnd_test_light <- smooth_data_nnd %>% filter(Frame_Num %in% c(nnd_frame))
+
 select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
-                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
+                                          filter(Frame_Num %in% c(240, nnd_frame)) %>% 
                                           left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
@@
 
-axis_remove <- list(showaxeslabels  = FALSE,
-                    showgrid = FALSE,
+ggsave("Paper Figures/Light_NND_Raw.png", raw_nnd_plot, width = 6, height = 4)
+
+axis_remove <- list(title = list(text = ""),
+                    showaxeslabels  = FALSE,
+                    showgrid = TRUE,
                     showline = FALSE,
@@
 #do 2 3d figures and NND figure
+```
+
+### Quick T Test
+
+```{r}
+
+t.test(smooth_data_nnd_test_dark$Distance, smooth_data_nnd_test_light$Distance)
+
 ```

### 2023-06-06 Fish Data Analysis/NN_Alignment.qmd
Before changing BL conversions

---
title: "NN Alignment Measure"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(circular)
```

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03
smaller_dot_binwidth = 0.01

text_size = 16
```

```{r}
fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv")  %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))

fish_comp_data <- na.omit(fish_comp_data)

fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
                                              Fish3_X = Fish1_X,
                                              Fish3_Y = Fish1_Y,
                                              Fish3_Z = Fish1_Z,
                                              Fish3_Speed = Fish1_Speed) %>%
                                       mutate(Fish1 = Fish2,
                                              Fish1_X = Fish2_X,
                                              Fish1_Y = Fish2_Y,
                                              Fish1_Z = Fish2_Z,
                                              Fish1_Speed = Fish2_Speed) %>%
                                       mutate(Fish2 = Fish3,
                                              Fish2_X = Fish3_X,
                                              Fish2_Y = Fish3_Y,
                                              Fish2_Z = Fish3_Z,
                                              Fish2_Speed = Fish3_Speed) %>%
                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed))

fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)

fish_comp_data_combo <- fish_comp_data_combo %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(Fish1_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep="/n")))

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    group_by(Flow_Ablation_Darkness) %>%
                                    mutate(Mean_Heading_Diff = mean(Yaw.Heading_Diff), SD_Heading_Diff = sd(Yaw.Heading_Diff)) %>%
                                    ungroup() %>%

                          # ### Used to remove every third point to reduce autocorrelation
                           mutate(Date_Trial_Fish = paste(Year,Month,Day,Trial,Fish1,sep="_")) %>%
                           group_by(Date_Trial_Fish) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()
                           # ###
```

```{r}

fish_data_nn_polar <- fish_data_nn %>% filter(Yaw.Heading_Diff <= 90) %>%
                                        mutate(Round_Yaw.Heading_Diff = round_any(Yaw.Heading_Diff,15)) %>%
                                       group_by(Round_Yaw.Heading_Diff, Flow, Ablation, Darkness) %>%
                                       summarise(count_headings = n()) %>%
                                       ungroup() %>%
                                       group_by(Flow, Ablation, Darkness) %>%
                                       mutate(sum_count = sum(count_headings),
                                              percent_dist = count_headings / sum_count) %>%
                                       ungroup()

ggplot(fish_data_nn_polar %>% filter(Flow == "Still Water"),
       aes(x = Round_Yaw.Heading_Diff, y = percent_dist, fill = interaction(Ablation,Darkness,sep=", "))) +
  geom_col() +
  facet_wrap(~interaction(Ablation,Darkness,sep=", "))+
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  coord_polar() +
  scale_x_continuous(limits = c(0,359),
                     breaks = seq(0, 360, by = 45),
                     minor_breaks = seq(0, 360, by = 15)) +
  theme_light()+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

ggplot(fish_data_nn_polar %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = Round_Yaw.Heading_Diff, y = percent_dist, fill = interaction(Ablation,Darkness,sep=", "))) +
  geom_col() +
  facet_wrap(~interaction(Ablation,Darkness,sep=", "))+
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  coord_polar() +
  scale_x_continuous(limits = c(0,359),
                     breaks = seq(0, 360, by = 45),
                     minor_breaks = seq(0, 360, by = 15)) +
  theme_light()+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

still_fish_data_nn <- fish_data_nn %>% filter(Flow == "Still Water")

#Non circular stats
heading_diff_glmer_still <- glmer(Yaw.Heading_Diff ~ Ablation*Darkness + (1|Data_ID), data = fish_data_nn %>% filter(Flow == "Still Water"), family = gaussian())
Anova(heading_diff_glmer_still)

heading_diff_glmer_flow <- glmer(Yaw.Heading_Diff ~ Ablation*Darkness + (1|Data_ID), data = fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"), family = gaussian())
Anova(heading_diff_glmer_flow)

```

```{r}

#Aligned where heading difference is less than 45 degrees

fish_aligned_2BL <- fish_comp_data_combo %>% filter(Distance <= 2 & Yaw.Heading_Diff <= 30) %>%
                    select(c(Data_ID, Year, Month, Day, Trial, Flow, Ablation, Darkness, Fish1, Fish2, Tailbeat_Num, Distance, Yaw.Heading_Diff)) %>%
                    arrange(Year, Month, Day, Trial, Fish1, Fish2, Tailbeat_Num) %>%
                    group_by(Data_ID, Year, Month, Day, Trial, Flow, Ablation, Darkness, Fish1, Fish2) %>%
                    mutate(Counter = 1,
                           Sum_Counter = cumsum(Counter),
                           Tailbeat_Diff = Tailbeat_Num - lag(Tailbeat_Num),
                           Tailbeat_Diff = ifelse(is.na(Tailbeat_Diff), 1, Tailbeat_Diff),
                           Sum_Tailbeat_Diff = cumsum(Tailbeat_Diff),
                           Alignment_Grouping = Sum_Tailbeat_Diff - Sum_Counter) %>%
                    ungroup() %>%
                    group_by(Data_ID, Year, Month, Day, Trial, Flow, Ablation, Darkness, Fish1, Fish2, Alignment_Grouping) %>%
                    summarise(Aligned_2BL_Dur = n()) %>%
                    ungroup() %>%
                    group_by(Flow, Ablation, Darkness) %>%
                    mutate(Mean_Aligned_2BL_Dur = mean(Aligned_2BL_Dur), SD_Aligned_2BL_Dur = sd(Aligned_2BL_Dur)) %>%
                    ungroup()

fish_aligned_2BL %>% group_by(Flow, Ablation, Darkness) %>% summarise(N = n())

```

```{r}
aligned_2BL_still <- ggplot(fish_aligned_2BL %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Aligned_2BL_Dur,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(smaller_dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Aligned_2BL_Dur), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Aligned_2BL_Dur-SD_Aligned_2BL_Dur, ymax=Mean_Aligned_2BL_Dur+SD_Aligned_2BL_Dur), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Number of Tailbeats Aligned") +
  theme_light()+ 
  theme(legend.position = "none") +
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

my_comparisons <- list()

aligned_2BL_flow <- ggplot(fish_aligned_2BL %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Aligned_2BL_Dur,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(smaller_dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Aligned_2BL_Dur), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Aligned_2BL_Dur-SD_Aligned_2BL_Dur, ymax=Mean_Aligned_2BL_Dur+SD_Aligned_2BL_Dur), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Number of Tailbeats Aligned") +
  theme_light()+ 
  theme(legend.position = "none") +
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

aligned_2BL_still
aligned_2BL_flow

aligned_2BL_glmer_still <- glmer(Aligned_2BL_Dur ~ Ablation*Darkness + (1|Data_ID),
                                 data = fish_aligned_2BL %>% filter(Flow == "Still Water"),
                                 family = poisson())
Anova(aligned_2BL_glmer_still)

aligned_2BL_glmer_flow <- glmer(Aligned_2BL_Dur ~ Ablation*Darkness + (1|Data_ID), 
                                data = fish_aligned_2BL %>% filter(Flow == "Flowing Water (2 BL/s)"),
                                family = poisson())
Anova(aligned_2BL_glmer_flow)

```

Okay so I think fish in darkness are paying attention to less fish
Only responding to turns when one or two other fish do, and more apart in time.

Look at delays in fish turning 
NN Heading might obscure some things as they pair up again soon after

```{r}

aligned_fish_comp <- fish_comp_data_combo %>% filter(Yaw.Heading_Diff <= 15) %>% filter(Flow == "Still Water") %>%
                    group_by(Flow, Ablation, Darkness) %>%
                    mutate(Mean_Distance = mean(Distance), SD_Distance = sd(Distance)) %>%
                    ungroup()

close_fish_comp <- fish_comp_data_combo %>% filter(Distance <= 2) %>% filter(Flow == "Still Water") %>%
                    group_by(Flow, Ablation, Darkness) %>%
                    mutate(Mean_Heading = mean(Yaw.Heading_Diff), SD_Heading = sd(Yaw.Heading_Diff)) %>%
                    ungroup()

ggplot(aligned_fish_comp %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Distance,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(smaller_dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Distance), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Distance-SD_Distance, ymax=Mean_Distance+SD_Distance), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Distance (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

Aligned_Distance_glmer_still <- lmer(Distance ~ Ablation*Darkness + (1|Data_ID),
                                 data = aligned_fish_comp %>% filter(Flow == "Still Water"))

Anova(Aligned_Distance_glmer_still)

ggplot(close_fish_comp %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Yaw.Heading_Diff,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(smaller_dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Heading), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Heading-SD_Heading, ymax=Mean_Heading+SD_Heading), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Distance (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

Close_Heading__glmer_still <- lmer(Yaw.Heading_Diff ~ Ablation*Darkness + (1|Data_ID),
                                 data = close_fish_comp %>% filter(Flow == "Still Water"))

Anova(Close_Heading__glmer_still)

```

### 2023-06-09 Fish Data Analysis/Heading Cross Corr.qmd
Attempted Models of Turning and Distance

---
title: "Heading Cross Corr"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
```

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03

text_size = 16
```

```{r}

x <- seq(0,2*pi,pi/10)
y1 <- sin(x)
y2 <- sin(x+pi)

plot(x,y1)
plot(x,y2)

ccf(y1, y2)

plot(ccf(1:10, 1:10)$lag,ccf(1:10, 1:10)$acf)

# plot(xcorr(1:10, 1:10, scale = "none")$lags,xcorr(1:10, 1:10, scale = "none")$R)
# plot(xcorr(1:10, 1:10, scale = "biased")$lags,xcorr(1:10, 1:10, scale = "biased")$R)
# plot(xcorr(1:10, 1:10, scale = "unbiased")$lags,xcorr(1:10, 1:10, scale = "unbiased")$R)
# plot(xcorr(1:10, 1:10, scale = "coeff")$lags,xcorr(1:10, 1:10, scale = "coeff")$R)

#let's try unbiased

```

```{r}

fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                                                               mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_")) %>%
                                                               select(Year, Month, Day, Data_ID, Trial, Tailbeat_Num,
                                                                      Ablation, Darkness, Flow, Fish1, Fish2,
                                                                      Distance, Fish1_Yaw_Heading, Fish2_Yaw_Heading)

#fish_comp_data <- na.omit(fish_comp_data)

fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
                                                        Fish3_Yaw_Heading = Fish1_Yaw_Heading) %>%
                                       mutate(Fish1 = Fish2,
                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading) %>%
                                       mutate(Fish2 = Fish3,
                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading) %>%
                                       select(-c(Fish3,Fish3_Yaw_Heading))

fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)

fish_comp_data_combo <- fish_comp_data_combo %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep="/n"))) %>%
                           arrange(Year,Month,Day,Trial,Fish1,Fish2,Tailbeat_Num)

```

I'm not 100% sure that the indexing and stuff is working exactly how I want it to so I'm going to 
just do it all via functions instead of trying to do mutate that cleanly

I think I only want lags starting at 0, no negative lags when we're matching up with distances

```{r}

get_corrs_lags <- function(f1_data, f2_data){

  output_len <- length(f1_data)

  output_vec <- rep(NA,output_len)

  saved_ccf <- ccf(f1_data, f2_data, na.action = na.pass, plot = F)
  corrs <- saved_ccf$acf
  lags <- saved_ccf$lag

  pos_lags <- lags >= 0

  pos_lag_corrs <- corrs[pos_lags]
  pos_lag_lags <- lags[pos_lags]

  output_corrs <- c(pos_lag_corrs, output_vec)[1:output_len]
  output_lags <- c(pos_lag_lags, output_vec)[1:output_len]

  return(list(output_corrs,output_lags))
}

```

Okay so we get the correlation for each time lag
And then have that to compare to the distances at that time
But how do you do a distance at a particular lag value? Do you just lag the coordinates and then calc the distances again?
That also doesn't seem right

```{r}

heading_corrs <- fish_comp_data_combo %>% group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
                                          mutate(len_run = sum(!is.na(Distance))) %>%
                                          ungroup() %>%
                                          filter(len_run > 2) %>%
                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
                                          mutate(corrs = get_corrs_lags(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[1]],
                                                 lags = get_corrs_lags(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[2]])

heading_corrs_sum <- heading_corrs %>% filter(lags >= 0) %>%
                                       group_by(Year,Month,Day,Trial,Fish1,Fish2, Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
                                       summarise(max_corr = max(corrs, na.rm = TRUE),
                                                 max_corr_lag = lags[na.omit(corrs == max_corr)],
                                                 lag_1_corr = corrs[lags == 1],
                                                 lag_1_distance = Distance[lags == 1],
                                                 max_corr_distance = Distance[na.omit(corrs == max_corr)]) %>%
                                       group_by(Flow, Ablation, Darkness) %>%
                                       mutate(Mean_Max_Corr = mean(max_corr, na.rm = T), SD_Max_Corr = sd(max_corr, na.rm = T),
                                              Mean_Max_Corr_Lag = mean(max_corr_lag, na.rm = T), SD_Max_Corr_Lag = sd(max_corr_lag, na.rm = T),
                                              Mean_Lag_1_Corr = mean(lag_1_corr, na.rm = T), SD_Lag_1_Corr = sd(lag_1_corr, na.rm = T),
                                              Mean_Lag_1_Distance = mean(lag_1_distance, na.rm = T), SD_Lag_1_Distance = sd(lag_1_distance, na.rm = T),
                                              Mean_Max_Corr_Distance = mean(max_corr_distance, na.rm = T), SD_Max_Corr_Distance = sd(max_corr_distance, na.rm = T)) %>%
                                       ungroup()
```

```{r}

ggplot(heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
  geom_point(aes(y = Mean_Max_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Max_Corr-SD_Max_Corr, ymax=Mean_Max_Corr+SD_Max_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr_lag,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
  geom_point(aes(y = Mean_Max_Corr_Lag), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Max_Corr_Lag-SD_Max_Corr_Lag, ymax=Mean_Max_Corr_Lag+SD_Max_Corr_Lag), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Lag at Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = lag_1_corr,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
  geom_point(aes(y = Mean_Lag_1_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Lag_1_Corr-SD_Lag_1_Corr, ymax=Mean_Lag_1_Corr+SD_Lag_1_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Correlation at 1 Lag") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = max_corr, y = max_corr_distance,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_point() +
  geom_smooth(se = F, method="glm") +
  guides(fill = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("Max Correlation") +
  ylab("Distance at Max Correlation") +
  xlim(0,1)+
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

```

### 2023-06-09 Fish Data Analysis/NN_Alignment.qmd
Attempted Models of Turning and Distance

@@
 
-Okay so I think fish in darkness are paying attention to less fish
-Only responding to turns when one or two other fish do, and more apart in time.
+Okay so I think fish in darkness are paying attention to less fish Only responding to turns when one or two other fish do, and more apart in time.
 
-Look at delays in fish turning 
-NN Heading might obscure some things as they pair up again soon after
+Look at delays in fish turning NN Heading might obscure some things as they pair up again soon after
 
@@
   xlab("") +
-  ylab("Distance (BL)") +
+  ylab("Heading Difference (Angle)") +
   theme_light()+ 
@@
 
+fish_comp_data_combo %>% group_by(Flow, Ablation, Darkness) %>% summarise(n = n())
+
 ```

### 2023-06-09 Fish Data Analysis/Paper_Figures.qmd
Reverting to old files, fixing 3d matching errors
Attempted Models of Turning and Distance

@@
 school_data <- read.csv("Data/Fish_School_Values_3D.csv")
+
 school_data <- na.omit(school_data)
@@
   theme(legend.position = "none") +
-  ylim(0,2)+
+  #ylim(0,2)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +

### 2023-06-09 Fish Data Analysis/Turning Latency.qmd
Attempted Models of Turning and Distance

---
title: "Turning Latency"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
```

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03

text_size = 16
```

```{r}
turning_data <- read.csv("Data/eight_fish_turning_latency.csv") %>%
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_")) %>% 
                           filter(Turn_Dir != "None") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           #0 is right, so this looks weird but it's fine
                           mutate(turn_bool = ifelse(Turn_Dir == "0",1,0),
                                  Turn_Dir = ifelse(Turn_Dir == "0","right","left")) %>%
                           arrange(Year, Month, Day, Trial, Frame)

latency_df <- turning_data %>% group_by(Data_ID,Turn_Dir) %>%
                               mutate(Latency = Frame - lag(Frame),
                                      Startler_Frame = lag(Frame),
                                      Startler_Fish = lag(Fish)) %>%
                               ungroup() %>%
                               filter(!is.na(Latency))

```

#Positional Data

```{r}
comp_data <- read.csv("Data/Fish_Raw_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_")) %>% select(c(Data_ID, Frame_Num, Fish1, Fish2, Distance))

comp_data_switch_fish <- comp_data %>% mutate(Fish3 = Fish1) %>%
                                       mutate(Fish1 = Fish2) %>%
                                       mutate(Fish2 = Fish3) %>%
                                       select(-c(Fish3))

comp_data_two <- bind_rows(comp_data, comp_data_switch_fish)
```

Now we combine them to get position and data

```{r}

latency_data_pos <- latency_df %>% left_join(comp_data_two, by = c("Data_ID" = "Data_ID", 
                                                                   "Startler_Frame" = "Frame_Num",
                                                                   "Startler_Fish" = "Fish1")) %>%
                                   na.omit()

```

Okay, so I want to be able to say something about how long it takes fish to respond to another fish's turn in the same direction

And I want to be able to talk about the distances between them when they turn

Actually what I *really* want is distance vs the probability of making a matching turn
  Within... let's say 50 frames

What I want is a data frame with 8 columns: 
Date ID, Condition, Frame Number, Fish Who Turned, Turn Direction, All Eight Other Fish, If Those Fish Turned Within X Frames, Distance

So let's start trying to build that

```{r}

max_diff = 60

#So here we try and find rows where the other fish turned within max_diff frames where Data_ID is the same as is the direction of the turn
#Also we remove rows where a fish just turned

did_match_turn <- function(all_data_df,data_id,turn_frame,main_fish,other_fish,turn_dir){
  turns_in_future <- all_data_df %>% filter(Data_ID == data_id & 
                                         Frame >= turn_frame & 
                                         Frame <= turn_frame + max_diff & 
                                         Turning_Fish == other_fish & 
                                         Turn_Dir == turn_dir)

  just_turned <- all_data_df %>% filter(Data_ID == data_id & 
                                         Frame <= turn_frame & 
                                         Frame >= turn_frame - max_diff & 
                                         Turning_Fish == other_fish & 
                                         Turn_Dir == turn_dir)

  if(length(turns_in_future$Data_ID) > 0){
    return(1)
  }
  else if(length(just_turned$Data_ID) > 0){
    return(NA)
  }
  else{
    return(0)
  }

}

```

Fist find out if the fish match

```{r}

all_fish <- c("individual1","individual2","individual3","individual4",
              "individual5","individual6","individual7","individual8")

base_late_data_df <- tibble(Data_ID = rep(turning_data$Data_ID, each = 8),
                         Flow = rep(turning_data$Flow, each = 8),
                         Ablation = rep(turning_data$Ablation, each = 8),
                         Darkness = rep(turning_data$Darkness, each = 8),
                         Flow_Ablation_Darkness = rep(turning_data$Flow_Ablation_Darkness, each = 8),
                         Frame = rep(turning_data$Frame, each = 8),
                         Turning_Fish = rep(turning_data$Fish, each = 8),
                         Turn_Dir = rep(turning_data$Turn_Dir, each = 8),
                         Other_Fish = rep(all_fish, length(turning_data$Fish)))

late_pairing_df <- base_late_data_df %>%
                   filter(Turning_Fish != Other_Fish) %>%
                   group_by(Data_ID,Frame,Turning_Fish,Other_Fish) %>% 
                   mutate(Also_Turned = did_match_turn(.,Data_ID,Frame,Turning_Fish,Other_Fish,Turn_Dir))

```

Now combine it

```{r}

dist_v_late_df <- late_pairing_df %>% left_join(comp_data_two, by = c("Data_ID" = "Data_ID", 
                                                                   "Frame" = "Frame_Num",
                                                                   "Turning_Fish" = "Fish1",
                                                                   "Other_Fish" = "Fish2")) %>% 
                                         filter(!is.na(Distance) & !is.na(Also_Turned) & Distance <= 10)

```

Now graph distance vs probabilty of turning!

```{r}

ggplot(dist_v_late_df %>% filter(Flow == "Still Water"),
       aes(x = Distance, y = Also_Turned, color = interaction(Ablation,Darkness,sep=", ")))+
  geom_point() +
  geom_smooth(se = F, method="glm", method.args=list(family="binomial")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_light() +
  theme(legend.position = "none")

dist_late_glmer_still <- glmer(Also_Turned ~ Distance*(Ablation+Darkness) + (1|Data_ID),
                               family ="binomial", data = dist_v_late_df %>% filter(Flow == "Still Water"))
Anova(dist_late_glmer_still)

```

```{r}

ggplot(latency_df %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Latency,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Latency), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Latency-SD_Latency, ymax=Mean_Latency+SD_Latency), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("") +
  ylab("Latency (Frames)") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(latency_data_pos %>% filter(Flow == "Still Water"),
       aes(x = Distance, y = Latency, color = interaction(Ablation,Darkness,sep=", "))) +
  geom_point()+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

latency_model <- lmer(Latency ~ Distance*(Ablation + Darkness) + (1|Data_ID), data = latency_data_pos)
model_sum <- summary(latency_model)

```

### 2023-06-09 2Dto3D/DLT_Plotter.py

@@ -9,6 +9,8 @@ import sys
 #Header list for reading the raw location CSVs
 header = list(range(4))
 
+fish_len = 0.083197
+
 num_fish = 8
 body_parts = ["head","midline2","tailbase","tailtip"]
 
@@ -70,7 +72,13 @@ for file_name in three_d_files:
         fig.write_html("Saved 3D Plots Manual/{name}_animated.html".format(name = file_id), auto_play=False)
 
 
+        fish_len
+
         head_df = df[df['BodyPart'] == "head"] 
+
+        head_df["x"] = head_df["x"]/fish_len
+        head_df["y"] = head_df["y"]/fish_len
+        head_df["z"] = head_df["z"]/fish_len
 
         fig = px.line_3d(head_df,x="x", y="y", z="z", color="Fish", hover_data = ["BodyPart"])
 

### 2023-06-09 3D_data_files_to_csv_4P.py

@@ -50,7 +50,8 @@ fish_len = 0.083197
 fish_sd = 0.62998
 
 # Fish Len Max?
-fish_max_len = fish_len + 3*fish_sd
+#Okay but now we need it in BL instead
+fish_max_len = (fish_len + 3*fish_sd) / fish_len
 
 #Header list for reading the raw location CSVs
 header = list(range(4))
@@ -171,21 +172,21 @@ class fish_data:
     def __init__(self, name, data, scorer, flow):
         #This sets up all of the datapoints that I will need from this fish
         self.name = name
-        self.head_x = data[scorer][name]["head"]["x"].to_numpy() 
-        self.head_y = data[scorer][name]["head"]["y"].to_numpy() 
-        self.head_z = data[scorer][name]["head"]["z"].to_numpy() 
+        self.head_x = data[scorer][name]["head"]["x"].to_numpy() / fish_len
+        self.head_y = data[scorer][name]["head"]["y"].to_numpy() / fish_len
+        self.head_z = data[scorer][name]["head"]["z"].to_numpy() / fish_len
 
-        self.midline_x = data[scorer][name]["midline2"]["x"].to_numpy() 
-        self.midline_y = data[scorer][name]["midline2"]["y"].to_numpy() 
-        self.midline_z = data[scorer][name]["midline2"]["z"].to_numpy() 
+        self.midline_x = data[scorer][name]["midline2"]["x"].to_numpy() / fish_len
+        self.midline_y = data[scorer][name]["midline2"]["y"].to_numpy() / fish_len
+        self.midline_z = data[scorer][name]["midline2"]["z"].to_numpy() / fish_len
 
-        self.tailbase_x = data[scorer][name]["tailbase"]["x"].to_numpy() 
-        self.tailbase_y = data[scorer][name]["tailbase"]["y"].to_numpy() 
-        self.tailbase_z = data[scorer][name]["tailbase"]["z"].to_numpy()
+        self.tailbase_x = data[scorer][name]["tailbase"]["x"].to_numpy() / fish_len
+        self.tailbase_y = data[scorer][name]["tailbase"]["y"].to_numpy() / fish_len
+        self.tailbase_z = data[scorer][name]["tailbase"]["z"].to_numpy() / fish_len
 
-        self.tailtip_x = data[scorer][name]["tailtip"]["x"].to_numpy() 
-        self.tailtip_y = data[scorer][name]["tailtip"]["y"].to_numpy()
[…]

### 2023-06-09 Single Fish Turning Processor/get_turn_bias_midline.py

@@ -17,7 +17,7 @@ fish_names = ["individual1","individual2",
 x_edges = [250,2250]
 y_edges = [200,900]
 
-csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Turn_Dir},{Fish_Left},{Fish_Right}\n"
+csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Frame},{Fish},{Turn_Dir},{Fish_Left},{Fish_Right}\n"
 
 def calc_mag(p1,p2):
     return math.sqrt((p1[0]-p2[0])**2 + (p1[1]-p2[1])**2)
@@ -179,13 +179,15 @@ def process_trial(folder,datafile):
                                       Darkness = darkness,
                                       Singles = "N",
                                       Flow = flow,
+                                      Frame = frame,
+                                      Fish = fish,
                                       Turn_Dir = turn_dirs[i],
                                       Fish_Left = num_LR[1],
                                       Fish_Right = num_LR[0]))
 
 f = open("single_fish_turning.csv", "w")
 
-f.write("Year,Month,Day,Trial,Ablation,Darkness,Singles,Flow,Turn_Dir,Fish_Left,Fish_Right\n")
+f.write("Year,Month,Day,Trial,Ablation,Darkness,Singles,Flow,Frame,Fish,Turn_Dir,Fish_Left,Fish_Right\n")
 
 folder = "Single_Fish_Data/"
 

### 2023-06-15 Fish Data Analysis/Heading Cross Corr.qmd
Working on heading Corrs

@@
 library(lme4)
+library(zoo)
+
+library(conflicted)
+conflict_prefer("filter", "dplyr")
 ```
@@
 ```
+Okay... let's try and get ccf to be flat wehn I'm coparing the same two things
+
+Also here's the C code that calculates acf
+Called from:
+
+acf <- .Call(C_acf, x, lag.max, type == "correlation")
+
+I think this translates it from R to C basically
+so this is the call that goes to the function:
+
+acf0(REAL(x), nx, ns, lagmax, cor, REAL(ans));
+
+SEXP acf(SEXP x, SEXP lmax, SEXP sCor)
+{
+    int nx = nrows(x), ns = ncols(x), lagmax = asInteger(lmax),
+	cor = asLogical(sCor);
+    x = PROTECT(coerceVector(x, REALSXP));
+    SEXP ans = PROTECT(allocVector(REALSXP, (lagmax + 1)*ns*ns));
+    acf0(REAL(x), nx, ns, lagmax, cor, REAL(ans));
+    SEXP d = PROTECT(allocVector(INTSXP, 3));
+    INTEGER(d)[0] = lagmax + 1;
+    INTEGER(d)[1] = INTEGER(d)[2] = ns;
+    setAttrib(ans, R_DimSymbol, d);
+    UNPROTECT(3);
+    return ans;
+}
+
+x is the vector, n is the rows, ns is the columns, nl is the lag, cor is a boolean, acf is the output vector (called ans in SEXP acf)
+
+static void
+acf0(double *x, int n, int ns, int nl, Rboolean correlation, double *acf)
+{
+    int d1 = nl+1, d2 = ns*d1;
+
+    for(int u = 0; u < ns; u++)
+	for(int v = 0; v < ns; v++)
+	    for(int lag = 0; lag <= nl; lag++) {
+		double sum = 0.0; int nu = 0;
+		for(int i = 0; i < n-lag; i++)
+		    if(!ISNAN(x[i + lag + n*u]) && !ISNAN(x[i + n*v])) {
+			nu++;
+			sum += x[i + lag + n*u] * x[i + n*v];
+		    }
+		acf[lag + d1*u + d2*v] = (nu > 0) ? sum/(nu + lag) : NA_REAL;
+	    }
+    if(correlation) {
+	if(n == 1) {
+	    for(int u = 0; u < ns; u++)
+		acf[0 + d1*u + d2*u] = 1.0;
+	} else {
+	    double *se = (double *) R_alloc(ns, sizeof(double));
+	    for(int u = 0; u < ns; u++)
+		se[u] = sqrt(acf[0 + d1*u + d2*u]);
+	    for(int u = 0; u < ns; u++)
+		for(int v = 0; v < ns; v++)
+		    for(int lag = 0; lag <= nl; lag++) { // ensure correlations remain in  [-1,1] :
+			double a = acf[lag + d1*u + d2*v] / (se[u]*se[v]);
+			acf[lag + d1*u + d2*v] = (a > 1.) ? 1. : ((a < -1.) ? -1. : a);
+		    }
+	}
+    }
+}
+
+I'm not 100% sure that the indexing and stuff is working exactly how I want it to so I'm going to 
+just do it all via functions instead of trying to do mutate that cleanly
+
+I think I only want lags starting at 0, no negative lags when we're matching up with distances
+
+```{r}
+
+get_corrs_lags <- function(f1_data, f2_data){
+
+  output_len <- length(f1_data)
+
+  output_vec <- rep(NA,output_len)
+
+  saved_ccf <- ccf(f1_data, f2_data, na.action = na.pass, plot = F, lag.max = output_len)
+  corrs <- saved_ccf$acf
+  lags <- saved_ccf$lag
+
+  pos_lags <- lags >= 0
+
+  pos_lag_corrs <- corrs[pos_lags]
+  pos_lag_lags <- lags[pos_lags]
+
+  output_corrs <- c(pos_lag_corrs, output_vec)[1:output_len]
+  output_lags <- c(pos_lag_lags, output_vec)[1:output_len]
+
+  return(list(output_corrs,output_lags))
+}
+
+```
 
@@
 
-```
-
-I'm not 100% sure that the indexing and stuff is working exactly how I want it to so I'm going to 
-just do it all via functions instead of trying to do mutate that cleanly
-
-I think I only want lags starting at 0, no negative lags when we're matching up with distances
-
-```{r}
-
-get_corrs_lags <- function(f1_data, f2_data){
-
-  output_len <- length(f1_data)
-
-  output_vec <- rep(NA,output_len)
-
-  saved_ccf <- ccf(f1_data, f2_data, na.action = na.pass, plot = F)
-  corrs <- saved_ccf$acf
-  lags <- saved_ccf$lag
-
-  pos_lags <- lags >= 0
-
-  pos_lag_corrs <- corrs[pos_lags]
-  pos_lag_lags <- lags[pos_lags]
-
-  output_corrs <- c(pos_lag_corrs, output_vec)[1:output_len]
-  output_lags <- c(pos_lag_lags, output_vec)[1:output_len]
-
-  return(list(output_corrs,output_lags))
-}
+fish_comp_data_combo <- fish_comp_data_combo %>% group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
+                         mutate(Fish1_Yaw_Heading_Wrapped = Fish1_Yaw_Heading,
+                                Fish2_Yaw_Heading_Wrapped = Fish2_Yaw_Heading,
+                                Fish1_Yaw_Heading = unwrap(Fish1_Yaw_Heading),
+                                Fish2_Yaw_Heading = unwrap(Fish2_Yaw_Heading))
 
@@
 heading_corrs_sum <- heading_corrs %>% filter(lags >= 0) %>%
-                                       group_by(Year,Month,Day,Trial,Fish1,Fish2, Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
+                                       group_by(Year,Month,Day,Trial,Data_ID,Fish1,Fish2, Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
                                        summarise(max_corr = max(corrs, na.rm = TRUE),
@@
 
+max_corr_vs_dist_glmer <- lmer(max_corr_distance ~ max_corr*(Ablation + Darkness) + (1|Data_ID), data = heading_corrs_sum %>% filter(Flow == "Still Water"))
+Anova(max_corr_vs_dist_glmer)
+
 ```
+
+# All the raw data
+
+```{r}
+
+raw_fish_comp_data <- read.csv("Data/Fish_Raw_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                                                               mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_")) %>%
+                                                               select(Year, Month, Day, Data_ID, Trial, Frame_Num,
+                                                                      Ablation, Darkness, Flow, Fish1, Fish2,
+                                                                      Distance, Fish1_Yaw_Heading, Fish2_Yaw_Heading)
+
+#fish_comp_data <- na.omit(fish_comp_data)
+
+raw_fish_comp_data_switch_fish <- raw_fish_comp_data %>% mutate(Fish3 = Fish1,
+                                                        Fish3_Yaw_Heading = Fish1_Yaw_Heading) %>%
+                                       mutate(Fish1 = Fish2,
+                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading) %>%
+                                       mutate(Fish2 = Fish3,
+                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading) %>%
+                                       select(-c(Fish3,Fish3_Yaw_Heading))
+
+raw_fish_comp_data_combo <- bind_rows(raw_fish_comp_data, raw_fish_comp_data_switch_fish)
+
+raw_fish_comp_data_combo <- raw_fish_comp_data_combo %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep="/n"))) %>%
+                           arrange(Year,Month,Day,Trial,Fish1,Fish2,Frame_Num)
+
+raw_fish_comp_data_combo <- raw_fish_comp_data_combo %>% group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
+                         mutate(Fish1_Yaw_Heading_Wrapped = Fish1_Yaw_Heading,
+                                Fish2_Yaw_Heading_Wrapped = Fish2_Yaw_Heading,
+                                Fish1_Yaw_Heading = unwrap(Fish1_Yaw_Heading),
+                                Fish2_Yaw_Heading = unwrap(Fish2_Yaw_Heading))
+
+```
+
+Testing things out, I think I just needed a much bigger lag
+
+```{r}
+
+data_subset <- raw_fish_comp_data_combo %>% filter(Data_ID == "2021_10_6_36", Fish1 == "individual5", Fish2 == "individual2")
+
+ggplot(data_subset, aes())+
+  geom_point(aes(Frame_Num, Fish1_Yaw_Heading), color = "red")+
+  geom_point(aes(Frame_Num, Fish2_Yaw_Heading), color = "blue")+
+  theme_light()
+
+ccf(data_subset$Fish1_Yaw_Heading, data_subset$Fish2_Yaw_Heading, na.action = na.pass, lag.max = length(data_subset$Fish1_Yaw_Heading))
+
+```
+
+So now we use a sliding window here instead of jsut the regular corr
+
+Now make it move by 10 frames instead of 1 for the window
+
+```{r}
+
+#I want this function to return the highest correaltion and the lag for that correlation for each 
+# window.
+
+windowed_correlation_finder <- function(x,y){
+  lag_max <- tailbeat_len
+  window_size <- tailbeat_len*3
+
+  window_step <- as.integer(tailbeat_len/2)
+
+  window_starts <- rep(NA,(length(x)-window_size-lag_max)*lag_max)
+  lags <- rep(NA,(length(x)-window_size-lag_max)*lag_max)
+  corr <- rep(NA,(length(x)-window_size-lag_max)*lag_max)
+
+  for (i in seq(1,length(x)-window_size-lag_max,window_step)) {
+
+    for (j in 1:lag_max) {
+
+      out_ind <- window_step*(i-1)+j
+
+      fish1_window <- x[i:(i+window_size)]
+      fish2_window <- y[(i+j):(i+j+window_size)]
+
+      if(sum(!is.na(fish1_window+fish2_window)) > window_step){
+        corr_val <- cor(fish1_window, fish2_window, method = "pearson", use = "complete.obs")
+
+        window_starts[out_ind] <- i
+        lags[out_ind] <- j
+        corr[out_ind] <- corr_val
+      }
+      else{
+        window_starts[out_ind] <- i
+        lags[out_ind] <- j
+        corr[out_ind] <- NA
+      }
+
+    }
+
+  }
+
+  all_data_frame <- tibble(window_start = window_starts,
+                           lag = lags,
+                           corr = corr)
+
+  out_df <- all_data_frame %>% group_by(window_start) %>% 
+                               mutate(isMax = (corr == max(corr, na.rm = TRUE))) %>% 
+                               filter(isMax) %>% 
+                               summarise(max_corr = first(corr), max_corr_lag = first(lag)) %>% 
+                               ungroup()
+
+  out_corrs <- out_df$max_corr
+  out_lags <- out_df$max_corr_lag
+
+  length(out_corrs) <- length(x)
+  length(out_lags) <- length(x)
+
+  output <- tibble(ccf = out_corrs, lags = out_lags)
+
+  return(output)
+}
+
+```
+
+Testing optimization
+```{r}
+
+x <- seq(0,2*pi,pi/10)
+y1 <- sin(x)
+y2 <- sin(x+pi/2 + rnorm(20,0,pi/4))
+
+plot(x,y1)
+plot(x,y2)
+
+tester_window_size <- 5
+
+y1_embed <- embed(y1,tester_window_size)
+y2_embed <- embed(y2,tester_window_size)
+
+list_embed <- data.frame(y1 = y1,y2 = y2)
+
+cor_vals <- rollapply(list_embed, width = tester_window_size,
+                      FUN = function(w) cor(list_embed[,1], list_embed[,2], method = "pearson", use = "complete.obs"),
+                      align = "right")
+
+cor_vals
+
+z2 <- zoo(rnorm(6))
+z2
+rollapply(1:6, 3, mean)
+
+```
+
+Okay so now a specific correaltion version
+
+```{r}
+get_corrs_lags_ben <- function(f1_data, f2_data){
+
+  output_len <- length(f1_data)
+
+  output_vec <- rep(NA,output_len)
+
+  saved_ccf <- windowed_correlation_finder(f1_data,f2_data)
+
+  corrs <- saved_ccf$ccf
+  lags <- saved_ccf$lags
+
+  pos_lags <- lags >= 0
+
+  pos_lag_corrs <- corrs[pos_lags]
+  pos_lag_lags <- lags[pos_lags]
+
+  output_corrs <- c(pos_lag_corrs, output_vec)[1:output_len]
+  output_lags <- c(pos_lag_lags, output_vec)[1:output_len]
+
+  return(list(output_corrs,output_lags))
+}
+```
+
+Okay so we get the correlation for each time lag
+And then have that to compare to the distances at that time
+But how do you do a distance at a particular lag value? Do you just lag the coordinates and then calc the distances again?
+That also doesn't seem right
+
+```{r}
+
+raw_heading_corrs <- raw_fish_comp_data_combo %>% #filter(Data_ID == "2021_8_3_11" & Fish1 == "individual8"  & Fish2 == "individual7") %>%
+                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
+                                          mutate(len_run = sum(!is.na(Distance))) %>%
+                                          ungroup() %>%
+                                          filter(len_run > 2) %>%
+                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
+                                          mutate(corrs = get_corrs_lags_ben(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[1]],
+                                                 lags = get_corrs_lags_ben(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[2]])
+
+raw_heading_corrs_sum <- raw_heading_corrs %>% filter(lags >= 0) %>%
+                                       group_by(Year,Month,Day,Trial,Data_ID,Fish1,Fish2, Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
+                                       summarise(max_corr = first(max(corrs, na.rm = TRUE)),
+                                                 max_corr_lag = first(lags[na.omit(corrs == max_corr)]),
+                                                 max_corr_distance = first(Distance[na.omit(corrs == max_corr)])) %>%
+                                       group_by(Flow, Ablation, Darkness) %>%
+                                       mutate(Mean_Max_Corr = mean(max_corr, na.rm = T), SD_Max_Corr = sd(max_corr, na.rm = T),
+                                              Mean_Max_Corr_Lag = mean(max_corr_lag, na.rm = T), SD_Max_Corr_Lag = sd(max_corr_lag, na.rm = T),
+                                              Mean_Max_Corr_Distance = mean(max_corr_distance, na.rm = T), SD_Max_Corr_Distance = sd(max_corr_distance, na.rm = T)) %>%
+                                       ungroup()
+```
+
+Okay so don't do a max of the time series, just plot all of the points, no mean and no max, just all distances and correlations
+
+#graphing raw data
+
+```{r}
+
+ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
+  geom_point(aes(y = Mean_Max_Corr), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Max_Corr-SD_Max_Corr, ymax=Mean_Max_Corr+SD_Max_Corr), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
+  xlab("") +
+  ylab("Max Correlation") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
+
+ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr_lag,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
+  geom_point(aes(y = Mean_Max_Corr_Lag), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Max_Corr_Lag-SD_Max_Corr_Lag, ymax=Mean_Max_Corr_Lag+SD_Max_Corr_Lag), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
+  xlab("") +
+  ylab("Lag at Max Correlation") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
+
+ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
+       aes(x = max_corr, y = max_corr_distance,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_point() +
+  geom_smooth(se = F, method="glm") +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  xlab("Max Correlation") +
+  ylab("Distance at Max Correlation") +
+  xlim(0,1)+
+  theme_light()+ 
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.x = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
+
+max_corr_glmer <- lmer(max_corr ~ Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
+Anova(max_corr_glmer)
+
+max_corr_vs_dist_glmer <- lmer(max_corr_distance ~ max_corr*(Ablation + Darkness) + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
+Anova(max_corr_vs_dist_glmer)
+
+```

### 2023-06-15 3D_data_files_to_csv_4P.py

@@ -215,8 +215,8 @@ class fish_data:
         # So I am going to just do that, and void it out here with nans
         # Since all further functions draw from these positional values, I just null them here
         self.get_fish_BL()
-        # self.remove_long_fish()
-        # self.remove_OOB_fish()
+        self.remove_long_fish()
+        self.remove_OOB_fish()
 
         #This calcualtes the summary stats
         self.calc_yaw_heading()

### 2023-06-27 Fish Data Analysis/Heading Cross Corr.qmd
Changing Cross Corr

@@
 
-  out_corrs <- out_df$max_corr
-  out_lags <- out_df$max_corr_lag
+  out_corrs <- rep(NA,length(x))
+  out_lags <- rep(NA,length(x))
 
-  length(out_corrs) <- length(x)
-  length(out_lags) <- length(x)
+  for (i in 1:length(out_df$window_start)) {
+    out_corrs[out_df$window_start[i]] <- out_df$max_corr[i]
+    out_lags[out_df$window_start[i]] <- out_df$max_corr_lag[i]
+  }
 
@@
 
-Okay so now a specific correaltion version
+Okay so now a specific correlation version
 
@@
                                           group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
-                                          mutate(corrs = get_corrs_lags_ben(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[1]],
-                                                 lags = get_corrs_lags_ben(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[2]])
+                                          mutate(corrs = windowed_correlation_finder(Fish1_Yaw_Heading,Fish2_Yaw_Heading)$ccf,
+                                                 lags = windowed_correlation_finder(Fish1_Yaw_Heading,Fish2_Yaw_Heading)$lags)
 
@@
                                        ungroup()
+
+raw_heading_corrs_graphing <- raw_heading_corrs %>% filter(!is.na(Distance) & !is.na(corrs))%>%
+                                       group_by(Flow, Ablation, Darkness) %>%
+                                       mutate(Mean_Corr = mean(corrs, na.rm = T), SD_Corr = sd(corrs, na.rm = T),
+                                              Mean_Lag = mean(lags, na.rm = T), SD_Lag = sd(lags, na.rm = T))
+
 ```
@@
 
-ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr,
+ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = corrs,
            color = interaction(Ablation,Darkness,sep=", "),
            fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
-  geom_point(aes(y = Mean_Max_Corr), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Mean_Max_Corr-SD_Max_Corr, ymax=Mean_Max_Corr+SD_Max_Corr), width=.2, color = "Black")+
+  geom_jitter(height = 0, alpha = 0.2)+
+  #stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
+  geom_point(aes(y = Mean_Corr), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Corr-SD_Corr, ymax=Mean_Corr+SD_Corr), width=.2, color = "Black")+
   guides(fill = guide_legend(title = "Condition")) +
@@
 
-ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr_lag,
+ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = lags,
            color = interaction(Ablation,Darkness,sep=", "),
            fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
-  geom_point(aes(y = Mean_Max_Corr_Lag), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Mean_Max_Corr_Lag-SD_Max_Corr_Lag, ymax=Mean_Max_Corr_Lag+SD_Max_Corr_Lag), width=.2, color = "Black")+
+  geom_jitter(height = 0, alpha = 0.2)+
+  #stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
+  geom_point(aes(y = Mean_Lag), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Lag-SD_Lag, ymax=Mean_Lag+SD_Lag), width=.2, color = "Black")+
   guides(fill = guide_legend(title = "Condition")) +
@@
 
-ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
-       aes(x = max_corr, y = max_corr_distance,
+ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
+       aes(x = Distance, y = corrs,
            color = interaction(Ablation,Darkness,sep=", "),
            fill = interaction(Ablation,Darkness,sep=", ")))+
-  geom_point() +
+  geom_point(alpha = 0.2) +
   geom_smooth(se = F, method="glm") +
@@
   scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  xlab("Max Correlation") +
-  ylab("Distance at Max Correlation") +
-  xlim(0,1)+
+  xlab("Distance") +
+  ylab("Correlation") +
+  #xlim(0,1)+
   theme_light()+ 
@@
 
-max_corr_glmer <- lmer(max_corr ~ Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
-Anova(max_corr_glmer)
+ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
+       aes(x = Distance, y = lags,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  geom_point(alpha = 0.2) +
+  geom_smooth(se = F, method="glm") +
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  xlab("Distance") +
+  ylab("Best Lag") +
+  #xlim(0,1)+
+  theme_light()+ 
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.x = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
-max_corr_vs_dist_glmer <- lmer(max_corr_distance ~ max_corr*(Ablation + Darkness) + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
-Anova(max_corr_vs_dist_glmer)
+corr_glmer <- lmer(corrs ~ 0+Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_graphing %>% filter(Flow == "Still Water"))
+summary(corr_glmer)
+Anova(corr_glmer)
+
+corr_vs_dist_glmer <- lmer(corrs ~ 0+Distance*(Ablation + Darkness) + (1|Data_ID), data = raw_heading_corrs_graphing %>% filter(Flow == "Still Water"))
+summary(corr_vs_dist_glmer)
+Anova(corr_vs_dist_glmer)
 

### 2023-07-20 Charuco_DLT/rearrange_point_for_easywand.Rmd
Adding more calibrations

--- 2023-02-15 Charuco_DLT/rearrange_point_for_easywand.Rmd
@@
 ```{r}
-detections <- read_csv("/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09/boards.csv") |> 
+detections <- read_csv("/Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29/boards.csv") |> 
   select(-`...1`)
@@
 ```{r}
-videodir <- '/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09'
+videodir <- '//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29'
 camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
@@
 ```{r}
-write_csv(ptsforeasywand, "/Users/Ben/Desktop/Charuco_DLT/2023_02_XX_calibrationcharuco_xypts.csv")
+write_csv(ptsforeasywand, "//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29/2023_06_29_calibrationcharuco_xypts.csv")
 ```

### 2023-07-20 Fish Data Analysis/Heading Cross Corr.qmd
Adding more calibrations

@@
 library(zoo)
+library(viridis)
 
@@
 ```
+
+# Bigger data
 
@@
 
-Testing optimization
-```{r}
-
-x <- seq(0,2*pi,pi/10)
-y1 <- sin(x)
-y2 <- sin(x+pi/2 + rnorm(20,0,pi/4))
-
-plot(x,y1)
-plot(x,y2)
-
-tester_window_size <- 5
-
-y1_embed <- embed(y1,tester_window_size)
-y2_embed <- embed(y2,tester_window_size)
-
-list_embed <- data.frame(y1 = y1,y2 = y2)
-
-cor_vals <- rollapply(list_embed, width = tester_window_size,
-                      FUN = function(w) cor(list_embed[,1], list_embed[,2], method = "pearson", use = "complete.obs"),
-                      align = "right")
-
-cor_vals
-
-z2 <- zoo(rnorm(6))
-z2
-rollapply(1:6, 3, mean)
-
-```
-
-Okay so now a specific correlation version
-
-```{r}
-get_corrs_lags_ben <- function(f1_data, f2_data){
-
-  output_len <- length(f1_data)
-
-  output_vec <- rep(NA,output_len)
-
-  saved_ccf <- windowed_correlation_finder(f1_data,f2_data)
-
-  corrs <- saved_ccf$ccf
-  lags <- saved_ccf$lags
-
-  pos_lags <- lags >= 0
-
-  pos_lag_corrs <- corrs[pos_lags]
-  pos_lag_lags <- lags[pos_lags]
-
-  output_corrs <- c(pos_lag_corrs, output_vec)[1:output_len]
-  output_lags <- c(pos_lag_lags, output_vec)[1:output_len]
-
-  return(list(output_corrs,output_lags))
-}
-```
-
 Okay so we get the correlation for each time lag
@@
 That also doesn't seem right
+
+# Raw Data processing
 
@@
   scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
+
+ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
+       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr,
+           color = interaction(Ablation,Darkness,sep=", "),
+           fill = interaction(Ablation,Darkness,sep=", ")))+
+  #geom_jitter(height = 0, alpha = 0.2)+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
+  geom_point(aes(y = Mean_Max_Corr), size = 5, color = "Black") +
+  geom_errorbar(aes(ymin=Mean_Max_Corr-SD_Max_Corr, ymax=Mean_Max_Corr+SD_Max_Corr), width=.2, color = "Black")+
+  guides(fill = guide_legend(title = "Condition")) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
+  xlab("") +
+  ylab("Max Correlation") +
+  theme_light()+ 
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
+
+max_corr_glmer <- lmer(max_corr ~ Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
+summary(max_corr_glmer)
+Anova(max_corr_glmer)
 
@@
 
+countour_lag_data <- raw_heading_corrs_graphing %>% mutate(round_corrs = round_any(corrs, 0.25),
+                                                           round_dists = round_any(Distance, 2))
+
+ggplot(countour_lag_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+       aes(x = Distance, y = corrs, color = lags))+
+  geom_point()+
+  scale_color_viridis()+
+  theme_classic()
+
+ggplot(countour_lag_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+       aes(x = Distance, y = lags))+
+  geom_point()+
+  theme_classic()
+
+ggplot(countour_lag_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+       aes(x = corrs, y = lags))+
+  geom_point()+
+  theme_classic()
+
 ```

### 2023-07-20 Fish Data Analysis/Paper_Figures.qmd
Adding more calibrations

@@
   new_autocorrs <- school_data_no_removals %>% group_by(Date_Trial) %>%
-                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29")) %>%
+                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29","2021_10_6_34",
+                                              "2021_7_7_16","2021_3_25_7","2021_3_25_22",
+                                              "2021_8_3_8")) %>%
                     summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),

### 2023-07-20 Fish Data Analysis/Results_Text.qmd
Reverting to old files, fixing 3d matching errors
Adding more calibrations

@@
                   rep(length(nnd_glmer_flow@resp$y)-3,2)),times = 6),
-       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
+       Chisq = round(c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
                  height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
@@
                  area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
-                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),
+                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),2),
 
-       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
+       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
                  height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
@@
                  area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
-                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),
+                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),2),
 
@@
        DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
-       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
-       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
+       LR_Chisq = round(c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),2),
+       P_Val = round(c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),2),
        Is_Sig = P_Val < 0.05)
@@
        DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
-       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
-       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
+       LR_Chisq = round(c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),3),
+       P_Val = round(c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),3),
        Is_Sig = P_Val < 0.05)

### 2023-07-20 Charuco_DLT/detect_charuco.py

@@ -28,7 +28,7 @@ board = aniposelib.boards.CharucoBoard(squaresX=6, squaresY=6,
 # For paths on Windows machines, be careful not to remove the r at the beginning of the quote; 
 #  without it, all backslashes will be registered as special characters.
 
-videopath = r'//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06'
+videopath = r'//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29'
 videonames = ['checkerboard_V1.mp4','checkerboard_V2.mp4']
 
 #This will detect points in the first video, just for testing purposes.
@@ -45,7 +45,7 @@ cap = cv2.VideoCapture(video1)
 
 #You can change it to look at a different frame
 
-i = 1000
+i = 100
 fr = rows[i]['framenum']
 
 cap.set(1, fr)

### 2024-02-20 Fish Data Analysis/Paper_Figures.qmd
Fixing file size commits

@@
 dark_no_ab_color = "#5e94d4"
+dark_ab_color = "#1E4371"
 sim_color = "#777777"
@@
 ```{r}
+
+abalated_dark_turning_data <- read.csv("Data/ablated_dark_data_turning.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
+                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
+                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
+                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
+                                                           c("7:0","6:1","5:2","4:3",
+                                                             "3:4","2:5","1:6","0:7"))) %>%
+                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
+                           select(-c("Singles","Frame","Fish")) %>%
+                           mutate(Type = "Eight Fish")
+
 annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
@@
 
-all_turning_data <- rbind(annushka_turning_data,single_fish_turning_data)
+eight_fish_turning_data <- rbind(annushka_turning_data,abalated_dark_turning_data)
+
+all_turning_data <- rbind(eight_fish_turning_data,single_fish_turning_data)
+
+eight_fish_data_sum  <- eight_fish_turning_data %>% na.omit %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                     summarize(mean_right_turn = mean(turn_bool),
+                                               sd_right_turn = sd(turn_bool),
+                                               se_right_turn = sd_right_turn/sqrt(n()),
+                                               n = n()) %>%
+                                     ungroup()
+
+single_fish_data_sum  <- single_fish_turning_data %>% na.omit %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                     summarize(mean_right_turn = mean(turn_bool),
+                                               sd_right_turn = sd(turn_bool),
+                                               se_right_turn = sd_right_turn/sqrt(n()),
+                                               n = n()) %>%
+                                     ungroup() %>%
+                                     filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation")
 
@@
   ylim(0,1) +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
 ```{r}
+placeholder_tibble <- tibble("Fish_Ratio" = c("0:7"),
+                             "Fish_Num_Ratio" = c(0.875),
+                             "Flow" = c("Still Water"),
+                             "Ablation" = c("No Ablation"),
+                             "Darkness" = c("Light"),
+                             "Type" = c("Combined Single"),
+                             "n" = c(0))
 
-placeholder_tibble <- tibble("Fish_Ratio" = c("0:7","0:7","3:4"),
-                             "Fish_Num_Ratio" = c(0.875,0.875,0.5),
-                             "Flow" = c("Still Water","Still Water","Still Water"),
-                             "Ablation" = c("No Ablation","Ablated","Ablated"),
-                             "Darkness" = c("Light","Light","Light"),
-                             "Type" = c("Combined Single","Combined Single","Combined Single"),
-                             "n" = c(0,0,0))
+light_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
+                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation") %>%
+                                      full_join(.,single_fish_data_sum) %>%
+                                      full_join(.,placeholder_tibble)
 
-turning_data_sum <- turning_data_sum %>% ungroup()
+light_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
+                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "Ablated") %>%
+                                      full_join(.,single_fish_data_sum) %>%
+                                      full_join(.,placeholder_tibble)
 
-turning_data_sum <- full_join(turning_data_sum,placeholder_tibble)
+dark_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
+                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "No Ablation") %>%
+                                      full_join(.,single_fish_data_sum) %>%
+                                      full_join(.,placeholder_tibble)
 
-dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
+dark_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
+                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "Ablated") %>%
+                                      full_join(.,single_fish_data_sum) %>%
+                                      full_join(.,placeholder_tibble)
+
+light_eight_and_single_graph <- ggplot(light_no_ab_eight_single_graph_data,
        aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
   geom_point()+
-  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
+  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
   geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
@@
   xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  ylim(0,1) +
+  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
 
-ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
+ablation_eight_and_single_graph <- ggplot(light_ab_eight_single_graph_data,
        aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
@@
 
-light_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
+dark_eight_and_single_graph <- ggplot(dark_no_ab_eight_single_graph_data,
        aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
   geom_point()+
-  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
+  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
   geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
@@
   xlab("# Fish on Left : # Fish on Right") +
-  ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  ylab("Probability of a Right Turn") +
+  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "School Type")+
+  theme(axis.text.x = element_text(size = text_size/2),
+        axis.text.y = element_text(size = text_size/2),
+        axis.title.y = element_text(size = text_size/2))+
+  guides(fill = FALSE)+
+  scale_y_continuous("Probability of a Right Turn",
+                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
+                     limits = c(0, 1))
+
+dark_ablation_eight_and_single_graph <- ggplot(dark_ab_eight_single_graph_data,
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
+  geom_point()+
+  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  scale_colour_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
+  scale_fill_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
   #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
@@
 dark_eight_and_single_graph
+dark_ablation_eight_and_single_graph
 ```
@@
 turning_single_test_plot <- ggarrange(
-          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
-          labels = c("A", "B", "C"),
+          light_eight_and_single_graph, ablation_eight_and_single_graph, 
+          dark_eight_and_single_graph, dark_ablation_eight_and_single_graph,
+          labels = c("A", "B", "C", "D"),
           ncol = 2, nrow = 2)
@@
 ```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
+
+my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
+                       c("No Ablation, Light", "Ablated, Dark"), 
+                       c("Ablated, Light", "No Ablation, Dark"),
+                       c("Ablated, Light", "Ablated, Dark"))
 
@@
   guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
   #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
@@
   theme(legend.position = "none") +
-  ylim(0,2)+
-  stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
+  ylim(0,2.5)+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
   theme(axis.text.x = element_text(size = text_size),
@@
 
-my_comparisons <- list()
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"), c("Ablated, Light", "Ablated, Dark"))
 
@@
   guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
   #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
@@
   theme(legend.position = "none") +
-  #ylim(0,2)+
+  ylim(0,2.5)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 
-```
-
-### Height Plot
-
-```{r}
-my_comparisons <- list()
-
-height_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Height,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Height_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Height_Mean_Val-Height_SD_Val, ymax=Height_Mean_Val+Height_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
-  xlab("") +
-  ylab("NND (BL)") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,3)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = text_size),
-        axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))+
-  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
-
-my_comparisons <- list()
-
-height_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Height,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Height_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Height_Mean_Val-Height_SD_Val, ymax=Height_Mean_Val+Height_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
-  xlab("") +
-  ylab("NND (BL)") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,3)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = text_size),
-        axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))+
-  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
-
-height_still
-height_flow
-
-height_glm <- glm(School_Height ~ Ablation*Darkness*Flow, data = school_data)
-Anova(height_glm)
-emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
   guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
   #ggtitle("Effect of Available Senses on Polarization in Still Water") +
@@
   guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
   #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
@@
   guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
   #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
@@
   guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
+  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
+  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
   #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
@@
 Anova(speed_glm_flow, test.statistic="F")
-```
-
-### Area
-
-```{r}
-my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
-
-area_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Area,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Area_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Area_Mean_Val-Area_SD_Val, ymax=Area_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
-  xlab("") +
-  ylab("Area (BL^2)") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = text_size),
-        axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))+
-  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
-
-my_comparisons <- list()
-
-area_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
-       aes(x = interaction(Ablation,Darkness,sep=", "), y = Area,
-           color = interaction(Ablation,Darkness,sep=", "),
-           fill = interaction(Ablation,Darkness,sep=", ")))+
-  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
-  geom_point(aes(y = Area_Mean_Val), size = 5, color = "Black") +
-  geom_errorbar(aes(ymin=Area_Mean_Val-Area_SD_Val, ymax=Area_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
-  guides(fill = guide_legend(title = "Condition")) +
-  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
-  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
-  xlab("") +
-  ylab("Area (BL^2)") +
-  theme_light()+ 
-  theme(legend.position = "none") +
-  #ylim(0,8.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
-  theme(axis.text.x = element_text(size = text_size),
-        axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))+
-  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
-
-area_still
-area_flow
-
-area_glm <- glm(Area ~ Ablation*Darkness*Flow, data = school_data)
-Anova(area_glm)
-emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
 groups_glm <- glm(Groups ~ Ablation*Darkness*Flow, data = school_data, family  = poisson)
-Anova(area_glm)
-emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
+Anova(groups_glm)
+emmeans(groups_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 
@@
 
-ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 10, height = 17)
+ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 17)
 ```

### 2024-02-20 Fish Data Analysis/Walls and LR Turns.qmd
Fixing file size commits

---
title: "Wall and LR Fish"
format: html
editor: visual
---

## Loading in the Libraries for Everything

```{r}
library(MASS)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
```

## Functions and Variables

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
dark_ab_color = "#1E4371"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03

text_size = 16
```

```{r}

eight_fish_turning_data <- read.csv("Data/eight_fish_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           dplyr::select(-c("Singles")) %>%
                           mutate(Type = "Eight Fish")

single_fish_turning_data <- read.csv("Data/single_fish_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           dplyr::select(-c("Singles")) %>%
                           mutate(Type = "Combined Single")
```

## Lets compare models for each of the different groups

Everything?

```{r}

eight_fish_turning_base <- glm(turn_bool ~ 1,
                               family = "binomial",
                               data = eight_fish_turning_data %>% filter(Flow == "Still Water"))

eight_fish_turning_step <- stepAIC(eight_fish_turning_base, 
                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio*Ablation*Darkness, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(eight_fish_turning_step)

single_fish_turning_base <- glm(turn_bool ~ 1,
                               family = "binomial",
                               data = single_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))

single_fish_turning_step <- stepAIC(single_fish_turning_base, 
                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(single_fish_turning_step)

```

### Light

```{r}

turning_glm_F0LNDN_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)

AIC(turning_glm_F0LNDN_B,turning_glm_F0LNDN_W,turning_glm_F0LNDN_F,turning_glm_F0LNDN_WF) %>% arrange(AIC)

Anova(turning_glm_F0LNDN_F)

```

### Abalated

```{r}

turning_glm_F0LYDN_B <- glm(turn_bool ~1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)

AIC(turning_glm_F0LYDN_B,turning_glm_F0LYDN_W,turning_glm_F0LYDN_F,turning_glm_F0LYDN_WF) %>% arrange(AIC)

Anova(turning_glm_F0LYDN_F)

```

### Dark

```{r}

turning_glm_F0LNDY_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)

AIC(turning_glm_F0LNDY_B,turning_glm_F0LNDY_W,turning_glm_F0LNDY_F,turning_glm_F0LNDY_WF) %>% arrange(AIC)

Anova(turning_glm_F0LNDY_F)

```

### Ablated Dark

```{r}

turning_glm_F0LYDY_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)

AIC(turning_glm_F0LYDY_B,turning_glm_F0LYDY_W,turning_glm_F0LYDY_F,turning_glm_F0LYDY_WF) %>% arrange(AIC)

Anova(turning_glm_F0LYDY_F)

```

### 2024-02-20 Fish Turning Processor/boundry_finder.py

@@ -1,0 +1,48 @@
+import matplotlib.pyplot as plt
+import pandas
+import os
+import numpy as np
+
+xs = []
+ys = []
+videos = []
+
+folder = "Eight_Fish_Data/"
+
+header = list(range(4))
+
+fish_names = ["individual1","individual2",
+              "individual3","individual4",
+              "individual5","individual6",
+              "individual7","individual8"]
+
+for file_name in os.listdir(folder):
+    if file_name.endswith(".csv"):
+        print(file_name)
+
+        fish_data = pandas.read_csv(folder+file_name,index_col=0, header=header)
+
+        year = file_name[0:4]
+        month = file_name[5:7]
+        day = file_name[8:10]
+        trial = file_name[11:13]
+        abalation = file_name[15:16]
+        darkness = file_name[18:19]
+        flow = file_name[21:22]
+
+        scorerer = fish_data.keys()[0][0]
+
+        for fish in fish_names:
+            head_x_data = fish_data[scorerer][fish]["head"]["x"].to_numpy()
+            head_y_data = fish_data[scorerer][fish]["head"]["y"].to_numpy()
+
+            xs = np.append(xs,head_x_data)
+            ys = np.append(ys,head_y_data)
+            videos = np.append(videos,np.repeat(file_name[0:10],len(head_x_data)))
+
+labels, index = np.unique(videos, return_inverse=True)
+        
+fig, ax = plt.subplots()
+sc = ax.scatter(xs, ys, marker = 'o', c = index, alpha = 0.8)
+ax.legend(sc.legend_elements()[0], labels)
+plt.show()

### 2024-02-20 Fish Turning Processor/distance to wall tester.py

@@ -1,0 +1,49 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+wall_lines = np.array([[[0,2],[6,2]],
+                       [[6,2],[6,0]],
+                       [[6,0],[0,0]],
+                       [[0,0],[0,2]]])
+
+def closest_right_distance_to_wall(headX, headY, midlineX, midlineY):
+
+    #find all the distances from every wall
+    distances = np.full([4], np.nan)
+    percents = np.full([4], np.nan)
+
+    for i,wall in enumerate(wall_lines):
+
+        #See math document from Eric 
+        #If you're not me, email me I guess?
+        #But this gives k and b 
+        # where k is the mutliplier of vector n that makes it intersect with vector w (wall)
+        # and where b is the mutliplier of vector w that makes it intersect with vector n (right perpendicular to fish)
+        nX = (headY - midlineY)
+        nY = -1*(headX - midlineX)
+
+        a = np.array([[wall[0][0] - headX],
+                      [wall[0][1] - headY]])
+
+        b = np.array([[nX , wall[0][0] - wall[1][0]],
+                      [nY , wall[0][1] - wall[1][1]]])
+
+        invB = np.linalg.inv(b)
+        answer = np.matmul(invB,a)
+
+        #This gives us the distance on the right the fish is from the wall
+        #And the percent along the wall that line intersects with
+        distances[i] = answer[0][0] * np.sqrt(nX**2 + nY**2)
+        percents[i] = answer[1][0]
+
+    #Then we only get the none negative distance snad percents (the real ones)
+    real_distances = (distances * (distances >= 0) * (percents >= 0))
+
+    #Then find the closest distance o those, and the percent that goes along with it
+    closest_real_dist = np.nanmin(np.where(real_distances == 0, np.nan, real_distances))
+    closest_real_percent = percents[np.where(distances == closest_real_dist)[0][0]]
+
+    return(closest_real_dist, closest_real_percent)
+
+print(closest_right_distance_to_wall(1.5,1.5,2,1))

### 2024-02-20 Fish Turning Processor/get_turn_bias_midline.py

@@ -1,0 +1,294 @@
+import matplotlib.pyplot as plt
+from matplotlib import gridspec 
+from scipy.signal import savgol_filter
+from scipy.signal import find_peaks
+import pandas
+import os
+import numpy as np
+import math
+
+header = list(range(4))
+
+fish_names = ["individual1","individual2",
+              "individual3","individual4",
+              "individual5","individual6",
+              "individual7","individual8"]
+
+# x_edges = [250,2250]
+# y_edges = [200,900]
+
+# x_edges = [-0.05,0.75]
+# y_edges = [-0.05,0.27]
+
+#For Real Fish
+# wall_lines = np.array([[[-0.05,0.27],[0.75,0.27]],
+#                        [[0.75,0.27],[0.75,-0.05]],
+#                        [[0.75,-0.05],[-0.05,-0.05]],
+#                        [[-0.05,-0.05],[-0.05,0.27]]])
+
+#For Single Fish
+wall_lines = np.array([[[0,1000],[2250,1000]],
+                       [[2250,1000],[2250,0]],
+                       [[2250,0],[0,0]],
+                       [[0,0],[0,1000]]])
+
+csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Frame},{Fish},{Turn_Dir},{Fish_Left},{Fish_Right},{Wall_Dist}\n"
+
+def calc_mag(p1,p2):
+    return math.sqrt((p1[0]-p2[0])**2 + (p1[1]-p2[1])**2)
+
+def moving_average(x, w):
+    return np.convolve(x, np.ones(w), 'valid') / w
+
+def moving_sum(x, w):
+    return np.convolve(x, np.ones(w), 'valid')
+
+def closest_right_distance_to_wall(headX, headY, midlineX, midlineY):
+
+    #find all the distances from every wall
+    distances = np.full([4], np.nan)
+    percents = np.full([4], np.nan)
+
+    for i,wall in enumerate(wall_lines):
+
+        #See math document from Eric 
+        #If you're not me, email me I guess?
+        #But this gives k and b 
+        # where k is the mutliplier of vector n that makes it intersect with vector w (wall)
+        # and where b is the mutliplier of vector w that makes it intersect with vector n (right perpendicular to fish)
+        nX = (headY - midlineY)
+        nY = -1*(headX - midlineX)
+
+        a = np.array([[wall[0][0] - headX],
[…]

### 2024-02-28 Fish Data Analysis/Walls and LR Turns.qmd
Cleaned up code around turns to a set angle
Instead of a rolling average, we now look at the change from the average heading 20 frames before and after a turn

@@
                                    trace = F)
-Anova(single_fish_turning_step)
+#Anova(single_fish_turning_step)
 

### 2024-02-28 Fish Turning Processor/get_turn_bias_midline.py

@@ -26,22 +26,38 @@ fish_names = ["individual1","individual2",
 #                        [[0.75,-0.05],[-0.05,-0.05]],
 #                        [[-0.05,-0.05],[-0.05,0.27]]])
 
-#For Single Fish
+# #For Single Fish
 wall_lines = np.array([[[0,1000],[2250,1000]],
                        [[2250,1000],[2250,0]],
                        [[2250,0],[0,0]],
                        [[0,0],[0,1000]]])
+
+#Tailbeat len is the median of all frame distances between tailbeats
+tailbeat_len = 19
+
+
+#calculate the dot product value needed to have the minimum turn
+min_turn_angle = 30
+min_turn_radian = min_turn_angle * np.pi / 180
+peak_prom = abs(np.dot((1,0),(np.cos(min_turn_radian), np.sin(min_turn_radian)))-1)/2
+
 
 csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Frame},{Fish},{Turn_Dir},{Fish_Left},{Fish_Right},{Wall_Dist}\n"
 
 def calc_mag(p1,p2):
     return math.sqrt((p1[0]-p2[0])**2 + (p1[1]-p2[1])**2)
 
+def calc_mag_multi(p1,p2):
+    return np.asarray([math.sqrt((p1[i][0]-p2[i][0])**2 + (p1[i][1]-p2[i][1])**2) for i in range(len(p1))])
+
+def calc_mag_vec(v1):
+    return math.sqrt((v1[0])**2 + (v1[1])**2)
+
 def moving_average(x, w):
-    return np.convolve(x, np.ones(w), 'valid') / w
+    return np.convolve(x, np.ones(w), 'same') / w
 
 def moving_sum(x, w):
-    return np.convolve(x, np.ones(w), 'valid')
+    return np.convolve(x, np.ones(w), 'same')
 
 def closest_right_distance_to_wall(headX, headY, midlineX, midlineY):
 
@@ -73,8 +89,8 @@ def closest_right_distance_to_wall(headX, headY, midlineX, midlineY):
         distances[i] = answer[0][0] * np.sqrt(nX**2 + nY**2)
         percents[i] = answer[1][0]
 
-    #Then we only get the none negative distance snad percents (the real ones)
-    real_distances = (distances * (distances >= 0) * (percents >= 0))
+    #Then we only get the none negative distances and percents (the real ones)
[…]

### 2024-03-01 Fish Data Analysis/Walls and LR Turns.qmd
Re graphing with new data

--- 2024-02-20 Fish Data Analysis/Walls and LR Turns.qmd
@@
                            dplyr::select(-c("Singles")) %>%
-                           mutate(Type = "Eight Fish")
+                           mutate(Type = "Eight Fish") %>%
+                           mutate(Min_Wall = pmin(Right_Wall_Dist,Left_Wall_Dist))
 
@@
                            mutate(Type = "Combined Single")
+
+eight_fish_data_sum  <- eight_fish_turning_data %>% na.omit %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                     summarize(mean_right_turn = mean(turn_bool),
+                                               sd_right_turn = sd(turn_bool),
+                                               se_right_turn = sd_right_turn/sqrt(n()),
+                                               n = n()) %>%
+                                     ungroup()
+
+eight_fish_data_sum_away  <- eight_fish_turning_data %>% na.omit %>% filter(Min_Wall >= 2) %>%
+                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                     summarize(mean_right_turn = mean(turn_bool),
+                                               sd_right_turn = sd(turn_bool),
+                                               se_right_turn = sd_right_turn/sqrt(n()),
+                                               n = n()) %>%
+                                     ungroup()
+```
+
+```{r}
+eight_fish_still <- ggplot(eight_fish_data_sum_away %>% filter(Flow == "Still Water"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
+  geom_point()+
+  #geom_line(alpha = 0.25) +
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
+  #facet_wrap(~ Darkness + Ablation) +
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  ylim(0,1) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
+
+eight_fish_flow <- ggplot(eight_fish_data_sum %>% filter(Flow == "Flowing Water (2 BL/s)"),
+       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
+  geom_point()+
+  #geom_line(alpha = 0.25) +
+  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
+  #facet_wrap(~ Darkness + Ablation) +
+  theme_classic() +
+  xlab("# Fish on Left : # Fish on Right") +
+  ylab("Probability of a Right Turn") +
+  ylim(0,1) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
+  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
+                                0.5,0.625,0.75,0.875),
+                     labels = c("7:0","6:1","5:2","4:3",
+                                "3:4","2:5","1:6","0:7"))+ 
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
+
+eight_fish_still
+eight_fish_flow
+
 ```
@@
                                family = "binomial",
-                               data = eight_fish_turning_data %>% filter(Flow == "Still Water"))
+                               data = eight_fish_turning_data %>% filter(Flow == "Still Water" & Min_Wall > 2))
 
 eight_fish_turning_step <- stepAIC(eight_fish_turning_base, 
-                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio*Ablation*Darkness, lower = ~1), 
+                                   list(upper = ~ Left_Wall_Dist*Right_Wall_Dist*Fish_Num_Ratio*Ablation*Darkness, lower = ~1), 
                                    direction = "both",
@@
 single_fish_turning_step <- stepAIC(single_fish_turning_base, 
-                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio, lower = ~1), 
+                                   list(upper = ~ Left_Wall_Dist*Right_Wall_Dist*Fish_Num_Ratio, lower = ~1), 
                                    direction = "both",

### 2024-03-01 3D_data_files_to_csv_4P.py

@@ -40,7 +40,6 @@ moving_average_n = 35
 #Tailbeat len is the median of all frame distances between tailbeats
 tailbeat_len = 19
 
-
 #Fish len is the median of all fish lengths in pixels
 #Scale is different becasue of calibration
 fish_len = 0.083197
@@ -1477,43 +1476,49 @@ for trial in trials:
 
 fish_sigular_dataframe.to_csv("Fish_Individual_Values_3D.csv")
 fish_comp_dataframe.to_csv("Fish_Comp_Values_3D.csv")
-fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_3D.csv")
+#fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_3D.csv")
 fish_school_dataframe.to_csv("Fish_School_Values_3D.csv")
 
-# #Recalculate when new data is added
-# all_trials_tailbeat_lens = []
-# all_trials_fish_lens = []
+#Recalculate when new data is added
+all_trials_tailbeat_lens = []
+all_trials_fish_lens = []
 
-# for trial in trials:
-#     all_trials_tailbeat_lens.extend(np.asarray(trial.return_tailbeat_lens()))
-#     all_trials_fish_lens.extend(np.asarray(trial.return_fish_lens()))
+for trial in trials:
+    all_trials_tailbeat_lens.extend(np.asarray(trial.return_tailbeat_lens()))
+    all_trials_fish_lens.extend(np.asarray(trial.return_fish_lens()))
 
-# all_trials_fish_lens = np.asarray(all_trials_fish_lens)
-# #all_trials_fish_lens = all_trials_fish_lens[all_trials_fish_lens < 1.25]
+all_trials_fish_lens = np.asarray(all_trials_fish_lens)*fish_len
+#all_trials_fish_lens = all_trials_fish_lens[all_trials_fish_lens < 1.25]
 
-# print("Tailbeat Len Median")
-# print(np.nanmedian(all_trials_tailbeat_lens)) #18
+print("Tailbeat Len Median")
+print(np.nanmedian(all_trials_tailbeat_lens)) #18
 
-# print("Fish Len Median")
-# print(np.nanmedian(all_trials_fish_lens))
+print("Fish Len Median")
+print(np.nanmedian(all_trials_fish_lens))
 
[…]

### 2024-03-01 Fish Turning Processor/get_turn_bias_midline.py

@@ -14,6 +14,9 @@ fish_names = ["individual1","individual2",
               "individual5","individual6",
               "individual7","individual8"]
 
+#Fish len is the median of all fish lengths 
+fish_len = 0.083197
+
 # x_edges = [250,2250]
 # y_edges = [200,900]
 
@@ -21,28 +24,28 @@ fish_names = ["individual1","individual2",
 # y_edges = [-0.05,0.27]
 
 #For Real Fish
-# wall_lines = np.array([[[-0.05,0.27],[0.75,0.27]],
-#                        [[0.75,0.27],[0.75,-0.05]],
-#                        [[0.75,-0.05],[-0.05,-0.05]],
-#                        [[-0.05,-0.05],[-0.05,0.27]]])
+wall_lines = np.array([[[-0.05,0.27],[0.75,0.27]],
+                       [[0.75,0.27],[0.75,-0.05]],
+                       [[0.75,-0.05],[-0.05,-0.05]],
+                       [[-0.05,-0.05],[-0.05,0.27]]])
 
 # #For Single Fish
-wall_lines = np.array([[[0,1000],[2250,1000]],
-                       [[2250,1000],[2250,0]],
-                       [[2250,0],[0,0]],
-                       [[0,0],[0,1000]]])
+# wall_lines = np.array([[[0,1000],[2250,1000]],
+#                        [[2250,1000],[2250,0]],
+#                        [[2250,0],[0,0]],
+#                        [[0,0],[0,1000]]])
 
 #Tailbeat len is the median of all frame distances between tailbeats
 tailbeat_len = 19
 
 
 #calculate the dot product value needed to have the minimum turn
-min_turn_angle = 30
+min_turn_angle = 15
 min_turn_radian = min_turn_angle * np.pi / 180
 peak_prom = abs(np.dot((1,0),(np.cos(min_turn_radian), np.sin(min_turn_radian)))-1)/2
 
 
-csv_output = "{Year},{Month},{Day},{Trial},{Ablation},{Darkness},{Singles},{Flow},{Frame},{Fish},{Turn_Dir},{Fish_Left},{Fish_Right},{Wall_Dist}\n"
[…]

### 2024-03-05 Fish Data Analysis/NN_Accel_Heading.qmd
Calculating NN Responses

---
title: "NN_Accel_Heading"
format: html
editor: visual
---

## Loading in the Libraries for Everything
```{r}
library(MASS)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
```

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
dark_ab_color = "#1E4371"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03

text_size = 16
```

Load in the data

```{r}

nn_accel_heading_df <- read.csv("Data/Fish_NN_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))

nn_heading_sum <- nn_accel_heading_df %>% mutate(angle_bins = round_any(Angle_to_NN,pi/4)) %>%
                                                #Limit to attraction zone
                                                #filter(Distance_to_NN <= 2) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Angle_PS, na.rm = T),
                                                          sd_turn = sd(Angle_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

nn_accel_sum <- nn_accel_heading_df %>% mutate(distance_bins = round_any(Distance_to_NN,0.5)) %>%
                                                group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_accel = mean(Acceleration, na.rm = T),
                                                          sd_accel = sd(Acceleration, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

```

```{r}

heading_base_lm <- lm(Angle_PS ~ Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
heading_lin_lm <- lm(Angle_PS ~ Angle_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
heading_cos_lm <- lm(Angle_PS ~ cos(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
heading_sin_lm <- lm(Angle_PS ~ sin(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))

AIC(heading_base_lm,heading_lin_lm,heading_cos_lm,heading_sin_lm) %>% arrange(AIC)

Anova(heading_sin_lm)

ggplot(nn_accel_heading_df %>% filter(Flow == "Still Water"),
       aes(x = Angle_to_NN, y = Angle_PS, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  theme_classic() +
  xlab("direction of neighbour (rad)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")

AIC(heading_sum_base_lm,heading_sum_lin_lm,heading_sum_cos_lm,heading_sum_sin_lm) %>% arrange(AIC)

ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = mean_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  theme_classic() +
  xlab("direction of neighbour (rad)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")

```

```{r}

accel_base_lm <- lm(Acceleration ~ Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water") %>% na.omit())
accel_lin_lm <- lm(Acceleration ~ Distance_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water") %>% na.omit())

AIC(accel_base_lm,accel_lin_lm) %>% arrange(AIC)

Anova(accel_lin_lm)

ggplot(nn_accel_heading_df %>% filter(Flow == "Still Water"),
       aes(x = Distance_to_NN, y = Acceleration, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_smooth(se = F, method = glm, formula = y ~ x)+
  theme_classic() +
  xlab("distance from neighbour (BL)") +
  ylab("focal fish acceleration (BL/s^2)") +
  ylim(-0.2, 0.2) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  labs(color = "Sensory Conditions")

ggplot(nn_accel_sum %>% filter(Flow == "Still Water"),
       aes(x = distance_bins, y = mean_accel, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ x)+
  theme_classic() +
  xlab("distance from neighbour (BL)") +
  ylab("focal fish acceleration (BL/s^2)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  labs(color = "Sensory Conditions")

```

### 2024-03-05 Fish Data Analysis/Walls and LR Turns.qmd
Calculating NN Responses

@@
   geom_point()+
-  #geom_line(alpha = 0.25) +
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
+  geom_line(alpha = 0.25) +
+  #geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
   #facet_wrap(~ Darkness + Ablation) +
@@
                          family = binomial)
-turning_glm_F0LNDN_W <- glm(turn_bool ~ Wall_Dist,
+turning_glm_F0LNDN_W <- glm(turn_bool ~ Left_Wall_Dist,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
@@
                          family = binomial)
-turning_glm_F0LNDN_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
+turning_glm_F0LNDN_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
@@
                          family = binomial)
-turning_glm_F0LYDN_W <- glm(turn_bool ~ Wall_Dist,
+turning_glm_F0LYDN_W <- glm(turn_bool ~ Left_Wall_Dist,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
@@
                          family = binomial)
-turning_glm_F0LYDN_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
+turning_glm_F0LYDN_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
@@
                          family = binomial)
-turning_glm_F0LNDY_W <- glm(turn_bool ~ Wall_Dist,
+turning_glm_F0LNDY_W <- glm(turn_bool ~ Left_Wall_Dist,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
@@
                          family = binomial)
-turning_glm_F0LNDY_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
+turning_glm_F0LNDY_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
@@
                          family = binomial)
-turning_glm_F0LYDY_W <- glm(turn_bool ~ Wall_Dist,
+turning_glm_F0LYDY_W <- glm(turn_bool ~ Left_Wall_Dist,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
@@
                          family = binomial)
-turning_glm_F0LYDY_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
+turning_glm_F0LYDY_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                          data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),

### 2024-03-05 3D_data_files_to_csv_4P.py

@@ -55,6 +55,9 @@ fish_max_len = (fish_len + 3*fish_sd) / fish_len
 #Header list for reading the raw location CSVs
 header = list(range(4))
 
+def calc_mag(p1,p2):
+    return math.sqrt((p1[0]-p2[0])**2 + (p1[1]-p2[1])**2)
+
 def get_dist_np_2D(x1s,y1s,x2s,y2s):
     dist = np.sqrt((x1s-x2s)**2+(y1s-y2s)**2)
     return dist
@@ -88,7 +91,7 @@ def mean_tailbeat_chunk(data,tailbeat_len):
         start = k//tailbeat_len * tailbeat_len
         end = (k//tailbeat_len + 1) * tailbeat_len
 
-        mean_data[k] = np.mean(data[start:end])
+        mean_data[k] = np.nanmean(data[start:end])
 
     return mean_data[::tailbeat_len]
 
@@ -100,7 +103,7 @@ def median_tailbeat_chunk(data,tailbeat_len):
         start = k//tailbeat_len * tailbeat_len
         end = (k//tailbeat_len + 1) * tailbeat_len
 
-        mean_data[k] = np.median(data[start:end])
+        mean_data[k] = np.nanmedian(data[start:end])
 
     return mean_data[::tailbeat_len]
 
@@ -116,8 +119,8 @@ def angular_mean_tailbeat_chunk(data,tailbeat_len):
 
         data_range = data[start:end]
 
-        cos_mean = np.mean(np.cos(data_range))
-        sin_mean = np.mean(np.sin(data_range))
+        cos_mean = np.nanmean(np.cos(data_range))
+        sin_mean = np.nanmean(np.sin(data_range))
 
         #SIN then COSINE
         angular_mean = np.rad2deg(np.arctan2(sin_mean,cos_mean))
@@ -133,7 +136,7 @@ def mean_tailbeat_chunk_sync(data,tailbeat_len):
         start = k//tailbeat_len * tailbeat_len
         end = (k//tailbeat_len + 1) * tailbeat_len
 
-        mean_data[k] = np.mean(data[start:end])
+        mean_data[k] = np.nanmean(data[start:end])
 
     return np.power(2,abs(mean_data[::tailbeat_len])*-1)
 
@@ -706,8 +709,6 @@ class fish_comp:
 
         plt.show()
 
-
-
 class school_comps:
     def __init__(self, fishes, n_fish, flow):
         self.fishes = fishes
[…]

### 2024-03-06 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before moving accel and heading code

@@
 library(lme4)
+library(viridis)
 ```
@@
                            mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           mutate(Distance_to_NN = ifelse(Relative_X < 1, Distance_to_NN*-1, Distance_to_NN))
 
-nn_heading_sum <- nn_accel_heading_df %>% mutate(angle_bins = round_any(Angle_to_NN,pi/4)) %>%
+nn_accel_heading_df_tb <- nn_accel_heading_df %>% group_by(Year,Month,Day,Trial,Individual,Tailbeat,
+                                                           Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                  summarise(Angle_to_NN = mean(Angle_to_NN, na.rm = T),
+                                                            Angle_PS = mean(Angle_PS, na.rm = T),
+                                                            Distance_to_NN = mean(Distance_to_NN, na.rm = T),
+                                                            Acceleration = mean(Acceleration, na.rm = T),
+                                                            Relative_X = mean(Relative_X, na.rm = T),
+                                                            Relative_Y = mean(Relative_Y, na.rm = T)) %>%
+                                                  ungroup() %>%
+                                                  na.omit()
+
+nn_heading_sum <- nn_accel_heading_df_tb %>% mutate(angle_bins = round_any(Angle_to_NN,pi/4)) %>%
                                                 #Limit to attraction zone
@@
 
-nn_accel_sum <- nn_accel_heading_df %>% mutate(distance_bins = round_any(Distance_to_NN,0.5)) %>%
+nn_accel_sum <- nn_accel_heading_df_tb %>% mutate(distance_bins = round_any(Distance_to_NN,0.5)) %>%
                                                 group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 
-heading_base_lm <- lm(Angle_PS ~ Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
-heading_lin_lm <- lm(Angle_PS ~ Angle_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
-heading_cos_lm <- lm(Angle_PS ~ cos(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
-heading_sin_lm <- lm(Angle_PS ~ sin(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
+heading_base_lm <- lm(Angle_PS ~ Flow_Ablation_Darkness, data = nn_accel_heading_df_tb %>% filter(Flow == "Still Water"))
+heading_lin_lm <- lm(Angle_PS ~ Angle_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df_tb %>% filter(Flow == "Still Water"))
+heading_cos_lm <- lm(Angle_PS ~ cos(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df_tb %>% filter(Flow == "Still Water"))
+heading_sin_lm <- lm(Angle_PS ~ sin(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df_tb %>% filter(Flow == "Still Water"))
 
@@
 
-Anova(heading_sin_lm)
+Anova(heading_cos_lm)
 
-ggplot(nn_accel_heading_df %>% filter(Flow == "Still Water"),
+ggplot(nn_accel_heading_df_tb %>% filter(Flow == "Still Water"),
        aes(x = Angle_to_NN, y = Angle_PS, color = interaction(Ablation, Darkness, sep =", ")))+
@@
   theme_classic() +
+  ylim(-0.1,0.1)+
   xlab("direction of neighbour (rad)") +
@@
   labs(color = "Sensory Conditions")
-
-AIC(heading_sum_base_lm,heading_sum_lin_lm,heading_sum_cos_lm,heading_sum_sin_lm) %>% arrange(AIC)
 
@@
 
-accel_base_lm <- lm(Acceleration ~ Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water") %>% na.omit())
-accel_lin_lm <- lm(Acceleration ~ Distance_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water") %>% na.omit())
+accel_base_lm <- lm(Acceleration ~ Flow_Ablation_Darkness, data = nn_accel_heading_df_tb %>% filter(Flow == "Still Water"))
+accel_lin_lm <- lm(Acceleration ~ Distance_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df_tb %>% filter(Flow == "Still Water"))
 
@@
 
-Anova(accel_lin_lm)
+Anova(accel_base_lm)
 
-ggplot(nn_accel_heading_df %>% filter(Flow == "Still Water"),
+ggplot(nn_accel_heading_df_tb %>% filter(Flow == "Still Water"),
        aes(x = Distance_to_NN, y = Acceleration, color = interaction(Ablation, Darkness, sep =", ")))+
@@
   ylab("focal fish acceleration (BL/s^2)") +
-  ylim(-0.2, 0.2) +
+  ylim(-0.01, 0.01) +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
@@
 ```
+
+```{r}
+
+directional_df <- nn_accel_heading_df_tb %>% mutate(round_X = round_any(Relative_X,0.5),
+                                                    round_Y = round_any(Relative_Y,0.5)) %>%
+                                                      group_by(round_X,round_Y,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                      summarise(mean_accel = mean(Acceleration),
+                                                                mean_turn = mean(Angle_PS)) %>%
+                                                      ungroup()
+
+ggplot(directional_df %>% filter(Flow == "Still Water"),
+       aes(round_X, round_Y, fill= mean_accel)) + 
+  geom_tile()+
+  facet_wrap(~Flow_Ablation_Darkness)+
+  scale_fill_viridis(option="magma")+
+  coord_fixed()+
+  theme_classic()
+
+ggplot(directional_df %>% filter(Flow == "Still Water"),
+       aes(round_X, round_Y, fill= mean_turn)) + 
+  geom_tile()+
+  facet_wrap(~Flow_Ablation_Darkness)+
+  scale_fill_viridis(option="magma")+
+  coord_fixed()+
+  theme_classic()
+
+```

### 2024-03-06 3D_data_files_to_csv_4P.py

@@ -208,6 +208,7 @@ class fish_data:
         self.yaw_heading = []
         self.pitch_heading = []
         self.speed = []
+        self.accel = []
         self.zero_crossings = []
         self.tb_freq_reps = []
         self.body_lengths = []
@@ -226,6 +227,8 @@ class fish_data:
         self.calc_speed()
         self.calc_tailtip_perp()
         self.calc_tb_freq()
+        self.calc_accel()
+        self.calc_yaw_heading_ps()
         
         
     def get_fish_BL(self):
@@ -840,8 +843,8 @@ class school_comps:
 
     def calc_angle_to_nn(self):
 
-        self.angle_to_nn_array = np.zeros((self.n_fish,int(len(self.school_center_x)/tailbeat_len))) + np.nan
-        self.heading_ps_array = np.zeros((self.n_fish,int(len(self.school_center_x)/tailbeat_len))) + np.nan
+        self.angle_to_nn_array = np.zeros((self.n_fish,len(self.school_center_x))) + np.nan
+        self.heading_ps_array = np.zeros((self.n_fish,len(self.school_center_x))) + np.nan
         
         #now calculate all nnds
         for i in range(self.n_fish):
@@ -852,13 +855,13 @@ class school_comps:
             #Get the vectors by chunks here
             #calculate the change in heading angle per second for the focal fish
 
-            fish_i_head_point_data = np.column_stack((mean_tailbeat_chunk(fish1.head_x,tailbeat_len), 
-                                                      mean_tailbeat_chunk(fish1.head_y,tailbeat_len)))
-            fish_i_mid_point_data = np.column_stack((mean_tailbeat_chunk(fish1.midline_x,tailbeat_len),
-                                                     mean_tailbeat_chunk(fish1.midline_y,tailbeat_len)))
+            # fish_i_head_point_data = np.column_stack((mean_tailbeat_chunk(fish1.head_x,tailbeat_len), 
+            #                                           mean_tailbeat_chunk(fish1.head_y,tailbeat_len)))
+            # fish_i_mid_point_data = np.column_stack((mean_tailbeat_chunk(fish1.midline_x,tailbeat_len),
+            #                                          mean_tailbeat_chunk(fish1.midline_y,tailbeat_len)))
 
[…]

### 2024-03-06 Fish Data Analysis/NN_Accel_Heading.qmd
Tied the code into school comps instead

--- 2024-03-05 Fish Data Analysis/NN_Accel_Heading.qmd
@@
 
-nn_accel_heading_df <- read.csv("Data/Fish_NN_Values_3D.csv") %>%
+fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                            mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
@@
                            mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
 
-nn_heading_sum <- nn_accel_heading_df %>% mutate(angle_bins = round_any(Angle_to_NN,pi/4)) %>%
-                                                #Limit to attraction zone
-                                                #filter(Distance_to_NN <= 2) %>%
+fish_comp_data <- na.omit(fish_comp_data)
+
+fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
+                                              Fish3_X = Fish1_X,
+                                              Fish3_Y = Fish1_Y,
+                                              Fish3_Z = Fish1_Z,
+                                              Fish3_Speed = Fish1_Speed,
+                                              Fish3_Accel = Fish1_Accel,
+                                              Fish3_Yaw_Heading = Fish1_Yaw_Heading,
+                                              Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
+                                              ) %>%
+                                       mutate(Fish1 = Fish2,
+                                              Fish1_X = Fish2_X,
+                                              Fish1_Y = Fish2_Y,
+                                              Fish1_Z = Fish2_Z,
+                                              Fish1_Speed = Fish2_Speed,
+                                              Fish1_Accel = Fish2_Accel,
+                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading,
+                                              Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
+                                       mutate(Fish2 = Fish3,
+                                              Fish2_X = Fish3_X,
+                                              Fish2_Y = Fish3_Y,
+                                              Fish2_Z = Fish3_Z,
+                                              Fish2_Speed = Fish3_Speed,
+                                              Fish2_Accel = Fish3_Accel,
+                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading,
+                                              Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
+                                       #Switch around angle when we switch focal fish
+                                       mutate(Angle = ifelse(Angle < 0, Angle + 180, Angle - 180)) %>%
+                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
+
+fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)
+
+fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
+                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
+                                           all_nas = all(is.na(nndDistance))) %>%
+                                    filter(Distance == nndDistance | all_nas) %>%
+                                    mutate(row_n = row_number()) %>%
+                                    filter(row_n == 1) %>%
+                                    ungroup() %>%
+                                    mutate(Angle_Rads = deg2rad(Angle),
+                                           RelativeX = Fish1_X - Fish2_X,
+                                           RelativeY = Fish1_Y - Fish2_Y,
+                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))
+
+nn_heading_sum <- fish_data_nn %>% mutate(angle_bins = round_any(Angle_Rads,pi/4)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                                summarise(mean_turn = mean(Angle_PS, na.rm = T),
-                                                          sd_turn = sd(Angle_PS, na.rm = T),
+                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                           n = n()) %>%
@@
 
-nn_accel_sum <- nn_accel_heading_df %>% mutate(distance_bins = round_any(Distance_to_NN,0.5)) %>%
+nn_accel_sum <- fish_data_nn %>% mutate(distance_bins = round_any(Distance,0.5)) %>%
                                                 group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                                summarise(mean_accel = mean(Acceleration, na.rm = T),
-                                                          sd_accel = sd(Acceleration, na.rm = T),
+                                                summarise(mean_accel = mean(Fish1_Accel, na.rm = T),
+                                                          sd_accel = sd(Fish1_Accel, na.rm = T),
                                                           n = n()) %>%
@@
 
-heading_base_lm <- lm(Angle_PS ~ Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
-heading_lin_lm <- lm(Angle_PS ~ Angle_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
-heading_cos_lm <- lm(Angle_PS ~ cos(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
-heading_sin_lm <- lm(Angle_PS ~ sin(Angle_to_NN)*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water"))
+heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn %>% filter(Flow == "Still Water"))
 
-AIC(heading_base_lm,heading_lin_lm,heading_cos_lm,heading_sin_lm) %>% arrange(AIC)
+heading_ps_angle_step <- stepAIC(heading_ps_angle_base, 
+                                   list(upper = ~ (Angle_Rads+cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness, lower = ~1), 
+                                   direction = "both",
+                                   trace = F)
 
-Anova(heading_sin_lm)
+Anova(heading_ps_angle_step)
 
-ggplot(nn_accel_heading_df %>% filter(Flow == "Still Water"),
-       aes(x = Angle_to_NN, y = Angle_PS, color = interaction(Ablation, Darkness, sep =", ")))+
+ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
+       aes(x = Angle_Rads, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point(alpha = 0.1)+
@@
   theme_classic() +
+  #ylim(-5,5)+
   xlab("direction of neighbour (rad)") +
@@
 
-accel_base_lm <- lm(Acceleration ~ Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water") %>% na.omit())
-accel_lin_lm <- lm(Acceleration ~ Distance_to_NN*Flow_Ablation_Darkness, data = nn_accel_heading_df %>% filter(Flow == "Still Water") %>% na.omit())
+accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
+accel_lin_lm <- lm(Fish1_Accel ~ Distance*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
 
@@
 
-Anova(accel_lin_lm)
+Anova(accel_base_lm)
 
-ggplot(nn_accel_heading_df %>% filter(Flow == "Still Water"),
-       aes(x = Distance_to_NN, y = Acceleration, color = interaction(Ablation, Darkness, sep =", ")))+
+ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
+       aes(x = Distance, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point(alpha = 0.1)+
@@
 
-ggplot(nn_accel_sum %>% filter(Flow == "Still Water"),
+ggplot(nn_accel_sum %>% filter(Flow == "Still Water" & distance_bins < 3),
        aes(x = distance_bins, y = mean_accel, color = interaction(Ablation, Darkness, sep =", ")))+
@@
 ```
+
+```{r}
+
+directional_df <- fish_data_nn %>% mutate(round_X = round_any(RelativeX,0.5),
+                                                    round_Y = round_any(RelativeY,0.5)) %>%
+                                                      group_by(round_X,round_Y,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                      summarise(mean_accel = mean(Fish1_Accel),
+                                                                mean_turn = mean(Fish1_Yaw_Heading_PS),
+                                                                n = n()) %>%
+                                                      ungroup()
+
+ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5 & mean_accel > -0.01 & mean_accel < 0.01),
+       aes(round_X, round_Y, fill= mean_accel)) + 
+  geom_tile()+
+  facet_wrap(~Flow_Ablation_Darkness)+
+  scale_fill_viridis(option="magma")+
+  coord_fixed()+
+  theme_classic()
+
+ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5),
+       aes(round_X, round_Y, fill= mean_turn)) + 
+  geom_tile()+
+  facet_wrap(~Flow_Ablation_Darkness)+
+  scale_fill_viridis(option="magma")+
+  coord_fixed()+
+  theme_classic()
+
+```

### 2024-03-06 3D_data_files_to_csv_4P.py

@@ -207,6 +207,7 @@ class fish_data:
         #These are the summary stats for the fish 
         self.yaw_heading = []
         self.pitch_heading = []
+        self.yaw_heading_ps = []
         self.speed = []
         self.accel = []
         self.zero_crossings = []
@@ -321,6 +322,46 @@ class fish_data:
         #Becasue of roll we don't want to the last value since it will be wrong
         self.pitch_heading = np.rad2deg(np.arctan2(self.vec_xy,self.vec_z))
 
+    #calcualtes the yaw heading change per second
+    def calc_yaw_heading_ps(self):
+
+        # chunked_yaw_cos = mean_tailbeat_chunk_sync(np.cos(np.deg2rad(self.yaw_heading)), tailbeat_len)
+        # chunked_yaw_sin = mean_tailbeat_chunk_sync(np.sin(np.deg2rad(self.yaw_heading)), tailbeat_len)
+
+        # self.yaw_heading_ps = np.arctan2(np.roll(chunked_yaw_sin,-1)-np.roll(chunked_yaw_sin,1),
+        #                                  np.roll(chunked_yaw_cos,-1)-np.roll(chunked_yaw_cos,1))[1:-1]
+
+        # self.yaw_heading_ps = np.rad2deg(self.yaw_heading_ps) * fps/2
+        
+
+        chunked_yaw_mean = angular_mean_tailbeat_chunk(np.deg2rad(self.yaw_heading), tailbeat_len)
+
+        self.yaw_heading_ps = np.rad2deg(np.arctan2(np.sin(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)),
+                                                    np.cos(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1))))[1:-1] * fps/2
+
+
+        # print(chunked_yaw_sin)
+        # print(np.sin(chunked_yaw_mean))
+        # print(np.roll(chunked_yaw_sin,-1)-np.roll(chunked_yaw_sin,1))
+        # print(np.sin(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)))
+
+        # print()
+
+        # print(chunked_yaw_cos)
+        # print(np.roll(chunked_yaw_cos,-1)-np.roll(chunked_yaw_cos,1))
+
+        # print()
+
+        # print(self.yaw_heading_ps)
+
[…]

### 2024-03-06 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before unchunking so early

@@
                                        #Switch around angle when we switch focal fish
-                                       mutate(Angle = ifelse(Angle < 0, Angle + 180, Angle - 180)) %>%
+                                       mutate(Angle = ifelse(Angle < 0, Angle + 180, Angle - 180),
+                                              Relative_X = -1*Relative_X) %>%
                                        select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
@@
                                     mutate(Angle_Rads = deg2rad(Angle),
-                                           RelativeX = Fish1_X - Fish2_X,
-                                           RelativeY = Fish1_Y - Fish2_Y,
                                            Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))
@@
 
-nn_accel_sum <- fish_data_nn %>% mutate(distance_bins = round_any(Distance,0.5)) %>%
+nn_accel_sum <- fish_data_nn %>% mutate(distance_bins = round_any(Relative_X,0.25)) %>%
                                                 group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
-accel_lin_lm <- lm(Fish1_Accel ~ Distance*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
+accel_lin_lm <- lm(Fish1_Accel ~ Relative_X*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
 
@@
 ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
-       aes(x = Distance, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
+       aes(x = Relative_X, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point(alpha = 0.1)+
@@
   ylab("focal fish acceleration (BL/s^2)") +
-  ylim(-0.01, 0.01) +
+  #ylim(-0.01, 0.01) +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
@@
   geom_point()+
-  geom_line(alpha = 0.75) +
-  #geom_smooth(se = F, method = glm, formula = y ~ x)+
+  #geom_line(alpha = 0.75) +
+  geom_smooth(se = F, method = glm, formula = y ~ 1)+
   theme_classic() +

### 2024-03-06 3D_data_files_to_csv_4P.py

@@ -332,7 +332,7 @@ class fish_data:
         #                                  np.roll(chunked_yaw_cos,-1)-np.roll(chunked_yaw_cos,1))[1:-1]
 
         # self.yaw_heading_ps = np.rad2deg(self.yaw_heading_ps) * fps/2
-        
+
 
         chunked_yaw_mean = angular_mean_tailbeat_chunk(np.deg2rad(self.yaw_heading), tailbeat_len)
 
@@ -501,6 +501,8 @@ class fish_comp:
         self.calc_speed_diff()
         self.calc_rayleigh_r()
 
+        self.calc_relative_x()
+
         #self.graph_values()
 
     def calc_dist(self):        
@@ -567,6 +569,25 @@ class fish_comp:
 
     def calc_speed_diff(self):
         self.speed_diff = self.f1.speed - self.f2.speed
+
+    def calc_relative_x(self):
+        x_diff = self.f2.head_x - self.f1.head_x
+        y_diff = self.f2.head_y - self.f1.head_y
+
+        diff_vec = np.column_stack((x_diff,y_diff))
+
+        heading_vec = np.column_stack((self.f1.vec_x,self.f1.vec_y))
+
+        self.relative_x = np.zeros(len(x_diff)) + np.nan
+
+        for i in range(len(x_diff)):
+            self.relative_x[i] = np.dot(diff_vec[i],heading_vec[i])
+
+        # relative_x_dot = np.sum(np.multiply(diff_vec, heading_vec), axis = 1)
+
+        # self.relative_x = np.arccos(relative_x_dot)
+
+        #print(self.relative_x)
 
     def calc_tailbeat_offset(self):
         #Setup an array to hold all the zero crossing differences
@@ -699,8 +720,6 @@ class fish_comp:
         tailbeat_lengths = abs(np.diff(np.append(self.f1.zero_crossings,len(self.f1.tailtip_zero_centered))))
 
         self.tailbeat_offset_reps = np.repeat(rayleigh_out,tailbeat_lengths[:len(rayleigh_out)])
-
-
 
     def graph_values(self):
         fig = plt.figure(figsize=(16, 10))
@@ -1340,6 +1359,7 @@ class trial:
             chunked_f2_X = mean_tailbeat_chunk(current_comp.f2.head_x,tailbeat_len)
[…]

### 2024-03-07 Fish Data Analysis/NN_Accel_Heading.qmd
Modeling angular data

@@
 
+Estimate the Wavelength
+
+```{r}
+# function to be minimized
+sum_squares <- function(lambda) {
+  lmfit <- lm(Fish1_Yaw_Heading_PS ~ (sin(2*pi/lambda*Fish1_Yaw_Heading_PS) + cos(2*pi/lambda*Fish1_Yaw_Heading_PS))*Ablation*Darkness,
+              data=fish_data_nn %>% filter(Flow == "Still Water"))
+  return(sum(lmfit$residuals^2))
+}
+
+lambda <- optimize(sum_squares,c(1,100))$minimum
+lambda
+
+#par 1 = amp
+#par 2 = freq
+#par 3 = phase
+
+min.RSS <- function(data, par) {
+             with(data, sum(par[1]*sin(par[2]*Angle_Rads+par[3]) - Fish1_Yaw_Heading_PS)^2)
+}
+
+result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
+result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
+result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
+result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))
+
+result_F0LNDN$par
+result_F0LYDN$par
+result_F0LNDY$par
+result_F0LYDY$par
+
+#par 4 & 5 = amp Ablation & Darkness
+#par 6 & 7 = freq Ablation & Darkness
+#par 8 & 9 = phase Ablation & Darkness
+
+fish_data_nn_optim <- fish_data_nn %>% filter(Flow == "Still Water") %>% mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
+                                                                                DarknessCat = ifelse(Darkness == "Dark",1,0))
+
+min.RSS_cat <- function(data, par) {
+             with(data, sum((par[1]+par[4]*AblationCat+par[5]*DarknessCat)*
+                              sin((par[2]+par[6]*AblationCat+par[7]*DarknessCat)*Angle_Rads+
+                                    (par[3]+par[8]*AblationCat+par[9]*DarknessCat)) - Fish1_Yaw_Heading_PS)^2)
+}
+
+result_F0_cat <- optim(par = c(1, 1, 0, 0, 0, 0, 0, 0, 0), fn = min.RSS_cat, data = fish_data_nn_optim)
+
+result_F0_cat
+
+nn_heading_sum <- nn_heading_sum %>% mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
+                                            DarknessCat = ifelse(Darkness == "Dark",1,0)) %>%
+                                     mutate(sin_pred = (result_F0_cat$par[1]+result_F0_cat$par[4]*AblationCat+result_F0_cat$par[5]*DarknessCat)*
+                                                        sin((result_F0_cat$par[2]+result_F0_cat$par[6]*AblationCat+result_F0_cat$par[7]*DarknessCat)*angle_bins+
+                                                        (result_F0_cat$par[3]+result_F0_cat$par[8]*AblationCat+result_F0_cat$par[9]*DarknessCat)))
+
+# #Now let's check the F0LNDN condition
+# heading_ps_F0LNDN_lm_base <- lm(Fish1_Yaw_Heading_PS ~ 1, 
+#                                 data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
+# heading_ps_F0LNDN_lm_lin <- lm(Fish1_Yaw_Heading_PS ~ Angle_Rads, 
+#                                 data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
+# heading_ps_F0LNDN_lm_sin <- lm(Fish1_Yaw_Heading_PS ~ sin(0.4444551*Angle_Rads+0.2544464), 
+#                                 data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
+# 
+# AIC(heading_ps_F0LNDN_lm_base,heading_ps_F0LNDN_lm_lin,heading_ps_F0LNDN_lm_sin) %>% arrange(AIC)
+# 
+# #Now let's check the F0LYDN condition
+# heading_ps_F0LYDN_lm_base <- lm(Fish1_Yaw_Heading_PS ~ 1, 
+#                                 data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
+# heading_ps_F0LYDN_lm_lin <- lm(Fish1_Yaw_Heading_PS ~ Angle_Rads, 
+#                                 data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
+# heading_ps_F0LYDN_lm_sin <- lm(Fish1_Yaw_Heading_PS ~ sin(1.11686351*Angle_Rads+-0.04623624), 
+#                                 data = fish_data_nn %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
+# 
+# AIC(heading_ps_F0LYDN_lm_base,heading_ps_F0LYDN_lm_lin,heading_ps_F0LYDN_lm_sin) %>% arrange(AIC)
+
+```
+
 ```{r}
 
-heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn %>% filter(Flow == "Still Water"))
+fish_data_nn_model <- fish_data_nn %>% filter(Flow == "Still Water") %>% 
+                                       mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
+                                              DarknessCat = ifelse(Darkness == "Dark",1,0))
+
+heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn_model)
 
 heading_ps_angle_step <- stepAIC(heading_ps_angle_base,
-                                   list(upper = ~ (Angle_Rads+cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness, lower = ~1), 
+                                   list(upper = ~ ((Angle_Rads+cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness), lower = ~1),
                                    direction = "both",
@@
 
+tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle_Rads):Ablation:Darkness, data = fish_data_nn_model)
+
 ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
@@
   facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
-  geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
+  geom_smooth(se = F)+
+  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
+  #geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
   theme_classic() +
@@
   geom_point()+
-  geom_line(alpha = 0.75) +
+  #geom_smooth(se = F)+
+  #geom_line(aes(y = sin_pred)) +
+  #geom_line(alpha = 0.75) +
   #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
+  geom_line(aes(y = predict(heading_ps_angle_step,
+                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins))), size = 1)+
   theme_classic() +

### 2024-03-07 3D_data_files_to_csv_4P.py

@@ -334,11 +334,29 @@ class fish_data:
         # self.yaw_heading_ps = np.rad2deg(self.yaw_heading_ps) * fps/2
 
 
-        chunked_yaw_mean = angular_mean_tailbeat_chunk(np.deg2rad(self.yaw_heading), tailbeat_len)
+        chunked_yaw_mean = np.deg2rad(angular_mean_tailbeat_chunk(self.yaw_heading, tailbeat_len))
 
         self.yaw_heading_ps = np.rad2deg(np.arctan2(np.sin(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)),
-                                                    np.cos(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1))))[1:-1] * fps/2
+                                                    np.cos(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1))))[1:-1] * fps/(2*tailbeat_len)
 
+        # print(repr(self.yaw_heading))
+        # print(repr(chunked_yaw_mean))
+        # print(repr(self.yaw_heading_ps))
+
+        #print(chunked_yaw_mean)
+
+        # fig = plt.figure(figsize=(8, 6))
+        # gs = gridspec.GridSpec(ncols = 2, nrows = 1) 
+
+        # ax0 = plt.subplot(gs[0,0])
+        # ax0.scatter(range(len(self.yaw_heading)), self.yaw_heading)
+        # ax0.scatter(np.linspace(0,len(chunked_yaw_mean),len(chunked_yaw_mean))*tailbeat_len, chunked_yaw_mean)
+        # ax0.plot(self.tailtip_x, self.tailtip_y)
+
+        # ax1 = plt.subplot(gs[0,1])
+        # ax1.scatter(range(len(self.yaw_heading_ps)), self.yaw_heading_ps / 60 * 2)
+
+        # plt.show()
 
         # print(chunked_yaw_sin)
         # print(np.sin(chunked_yaw_mean))
@@ -387,7 +405,7 @@ class fish_data:
         chunked_speed = mean_tailbeat_chunk_sync(self.speed,tailbeat_len)
 
         #remove the edge cases where rolling makes invalid values
[…]

### 2024-03-07 Fish Data Analysis/NN_Accel_Heading.qmd
changing angle calculation

@@
 
-tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle_Rads):Ablation:Darkness, data = fish_data_nn_model)
+tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Ablation+Darkness+Angle_Rads), data = fish_data_nn_model)
 
@@
   #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
-  geom_line(aes(y = predict(heading_ps_angle_step,
+  geom_line(aes(y = predict(tester_model,
                     newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins))), size = 1)+

### 2024-03-07 3D_data_files_to_csv_4P.py

@@ -55,6 +55,9 @@ fish_max_len = (fish_len + 3*fish_sd) / fish_len
 #Header list for reading the raw location CSVs
 header = list(range(4))
 
+def calc_mag_vec(p1):
+    return math.sqrt((p1[0])**2 + (p1[1])**2)
+
 def calc_mag(p1,p2):
     return math.sqrt((p1[0]-p2[0])**2 + (p1[1]-p2[1])**2)
 
@@ -534,14 +537,43 @@ class fish_comp:
 
     def calc_angle(self):
         #Calculate the angle of the x and y difference in degrees
-        angle_diff = np.rad2deg(np.arctan2(self.y_diff,self.x_diff))
+        #angle_diff = np.rad2deg(np.arctan2(self.y_diff,self.x_diff))
+
         #This makes it from 0 to 360
         #angle_diff_360 = np.mod(abs(angle_diff-360),360)
         #This rotates it so that 0 is at the top and 180 is below the fish for a sideways swimming fish model
         #self.angle = np.mod(angle_diff_360+90,360)
 
         #12/1/21: Back to making change notes. Now keeping it as the raw -180 to 180
-        self.angle = angle_diff
+
+        #3/7/24 Doing this with dot products to not run into issues with axes
+
+        f1_head = np.column_stack((self.f1.head_x, self.f1.head_y))
+        f1_midline = np.column_stack((self.f1.midline_x, self.f1.midline_y))
+        f2_head = np.column_stack((self.f2.head_x, self.f2.head_y))
+
+        dot_prods = np.zeros(len(self.f1.head_x)) + np.nan
+        cross_prods = np.zeros(len(self.f1.head_x)) + np.nan
+
+        for t in range(len(self.f1.head_x)):
+
+            unit_f1_body_vec = (f1_head[t] - f1_midline[t]) / calc_mag(f1_head[t],f1_midline[t])
+            unit_f1_f2_head_vec  = (f1_head[t] - f2_head[t]) / calc_mag(f1_head[t],f2_head[t])
+            unit_f1_body_vec_prep = [unit_f1_body_vec[1],-1*unit_f1_body_vec[0]]
+
+            dot_prods[t] = np.dot(unit_f1_body_vec,unit_f1_f2_head_vec)
+            cross_prods[t] = np.cross(unit_f1_f2_head_vec,unit_f1_body_vec_prep)
+
[…]

### 2024-03-07 Fish Data Analysis/NN_Accel_Heading.qmd
Save before I make it all radians for sanity

--- 2024-03-06 Fish Data Analysis/NN_Accel_Heading.qmd
@@
                                     mutate(Angle_Rads = deg2rad(Angle),
-                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))
+                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS)) %>%
+                                    filter(Distance <= 2)
 
-nn_heading_sum <- fish_data_nn %>% mutate(angle_bins = round_any(Angle_Rads,pi/4)) %>%
+nn_heading_sum <- fish_data_nn %>% mutate(angle_bins = round_any(Angle_Rads,pi/8)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 
-heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn %>% filter(Flow == "Still Water"))
+fish_data_nn_model <- fish_data_nn %>% filter(Flow == "Still Water") %>% 
+                                       mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
+                                              DarknessCat = ifelse(Darkness == "Dark",1,0))
+
+heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn_model)
 
 heading_ps_angle_step <- stepAIC(heading_ps_angle_base,
-                                   list(upper = ~ (Angle_Rads+cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness, lower = ~1), 
+                                   list(upper = ~ ((cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness), lower = ~1),
                                    direction = "both",
@@
 
+tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle_Rads)*Ablation*Darkness, data = fish_data_nn_model) 
+Anova(tester_model)
+
 ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
@@
   facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
-  geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
+  #geom_smooth(se = F)+
+  geom_smooth(se = F, method = glm, formula = y ~ 1)+
+  #geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
   theme_classic() +
   #ylim(-5,5)+
-  xlab("direction of neighbour (rad)") +
+  xlab("direction of neighbour (degrees)") +
   ylab("focal fish turning angle (rad/sec)") +
@@
   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
-                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
+                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
   labs(color = "Sensory Conditions")
@@
 ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
-       aes(x = angle_bins, y = mean_turn, color = interaction(Ablation, Darkness, sep =", ")))+
+       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point()+
-  geom_line(alpha = 0.75) +
+  #geom_smooth(se = F)+
+  #geom_line(aes(y = sin_pred)) +
+  #geom_line(alpha = 0.75) +
   #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
+  geom_line(aes(y = rad2deg(predict(heading_ps_angle_step,
+                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins)))), size = 1)+
   theme_classic() +
-  xlab("direction of neighbour (rad)") +
-  ylab("focal fish turning angle (rad/sec)") +
+  #ylim(-0.6,0.6)+
+  xlab("direction of neighbour (degrees)") +
+  ylab("focal fish turning angle (degrees/sec)") +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
-                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
+                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
+  # scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
+  #                    labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
   labs(color = "Sensory Conditions")

### 2024-03-07 3D_data_files_to_csv_4P.py

@@ -558,20 +558,21 @@ class fish_comp:
         for t in range(len(self.f1.head_x)):
 
             unit_f1_body_vec = (f1_head[t] - f1_midline[t]) / calc_mag(f1_head[t],f1_midline[t])
-            unit_f1_f2_head_vec  = (f1_head[t] - f2_head[t]) / calc_mag(f1_head[t],f2_head[t])
-            unit_f1_body_vec_prep = [unit_f1_body_vec[1],-1*unit_f1_body_vec[0]]
+            unit_f1_f2_head_vec  = (f2_head[t] - f1_head[t]) / calc_mag(f1_head[t],f2_head[t])
+            unit_f1_body_vec_perp = [-1*unit_f1_body_vec[1],unit_f1_body_vec[0]]
 
             dot_prods[t] = np.dot(unit_f1_body_vec,unit_f1_f2_head_vec)
-            cross_prods[t] = np.cross(unit_f1_f2_head_vec,unit_f1_body_vec_prep)
+            cross_prods[t] = np.dot(unit_f1_f2_head_vec,unit_f1_body_vec_perp)
 
             # if not np.isnan(dot_prods[t]):
+            #     print()
             #     print(t)
             #     print(f1_head[t], f1_midline[t], f2_head[t])
-            #     print(unit_f1_body_vec, unit_f1_f2_head_vec, unit_f1_body_vec_prep)
+            #     print(unit_f1_body_vec, unit_f1_f2_head_vec, unit_f1_body_vec_perp)
             #     print(dot_prods[t], cross_prods[t])
-            #     print(np.rad2deg(np.arccos(dot_prods[t])))
+            #     print(np.rad2deg(np.arccos(dot_prods[t]) * np.sign(cross_prods[t])))
 
-        self.angle = dot_prods * np.sign(cross_prods)
+        self.angle = np.rad2deg(np.arccos(dot_prods) * np.sign(cross_prods))
 
         #sys.exit()
 
@@ -1599,7 +1600,7 @@ data_folder = "3D_Finished_Fish_Data_4P_gaps/"
 
 trials = []
 
-single_file = "2020_07_28_11" # "2020_07_28_03_LN_DN_F2" #"2021_10_06_36_LY_DN_F2_3D_DLC_dlcrnetms5_DLC_2-2_4P_8F_Light_VentralMay10shuffle1_100000_el_filtered.csv"
[…]

### 2024-03-07 Fish Data Analysis/NN_Accel_Heading.qmd
Cleaned up rad and degrees, checked functions

@@
 ```{r}
+raw_new <- read.csv("Data/Fish_Comp_Values_3D.csv")
+raw_old <- read.csv("Data/older_Fish_Comp_Values_3D.csv") %>% mutate(Angle = deg2rad(Angle),
+                                                                     Fish1_Yaw_Heading = deg2rad(Fish1_Yaw_Heading),
+                                                                     Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))
+
+hist(raw_new$Angle - deg2rad(raw_old$Angle))
+hist(raw_new$Fish1_Yaw_Heading - deg2rad(raw_old$Fish1_Yaw_Heading))
+hist(raw_new$Fish1_Yaw_Heading_PS - deg2rad(raw_old$Fish1_Yaw_Heading_PS))
+
+```
+
+```{r}
 
@@
                                        #Switch around angle when we switch focal fish
-                                       mutate(Angle = ifelse(Angle < 0, Angle + 180, Angle - 180),
+                                       mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi),
                                               Relative_X = -1*Relative_X) %>%
@@
                                     ungroup() %>%
-                                    mutate(Angle_Rads = deg2rad(Angle),
-                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS)) %>%
+                                    mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
                                     filter(Distance <= 2)
 
-nn_heading_sum <- fish_data_nn %>% mutate(angle_bins = round_any(Angle_Rads,pi/8)) %>%
+fish_data_nn_normal <- fish_data_nn %>% group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+                                        ungroup()
+
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 
-nn_accel_sum <- fish_data_nn %>% mutate(distance_bins = round_any(Relative_X,0.25)) %>%
+nn_accel_sum <- fish_data_nn_normal %>% mutate(distance_bins = round_any(Relative_X,0.25)) %>%
                                                 group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 heading_ps_angle_step <- stepAIC(heading_ps_angle_base,
-                                   list(upper = ~ ((cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness), lower = ~1),
+                                   list(upper = ~ (sin(Angle)+Ablation:sin(Angle)+Darkness:sin(Angle)), lower = ~1),
                                    direction = "both",
@@
 
-tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle_Rads)*Ablation*Darkness, data = fish_data_nn_model) 
+tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle):Ablation:Darkness, data = fish_data_nn_model) 
 Anova(tester_model)
@@
 ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
-       aes(x = Angle_Rads, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
+       aes(x = Angle, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point(alpha = 0.1)+
@@
   #geom_smooth(se = F)+
-  geom_smooth(se = F, method = glm, formula = y ~ 1)+
-  #geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
+  #geom_smooth(se = F, method = glm, formula = y ~ 1)+
+  geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
   theme_classic() +
@@
   #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
-  geom_line(aes(y = rad2deg(predict(heading_ps_angle_step,
-                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins)))), size = 1)+
+  geom_line(aes(y = rad2deg(predict(tester_model,
+                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
   theme_classic() +
-  #ylim(-0.6,0.6)+
+  ylim(-50,50) +
   xlab("direction of neighbour (degrees)") +
@@
   labs(color = "Sensory Conditions")
+
+# emmeans(tester_model, ~ Ablation|Darkness, type = "response")
+# emmeans(tester_model, ~ Darkness|Ablation, type = "response")
 

### 2024-03-07 3D_data_files_to_csv_4P.py

@@ -111,7 +111,7 @@ def median_tailbeat_chunk(data,tailbeat_len):
     return mean_data[::tailbeat_len]
 
 def angular_mean_tailbeat_chunk(data,tailbeat_len):
-    data = np.deg2rad(data)
+    #data = np.deg2rad(data)
 
     max_tb_frame = len(data)-len(data)%tailbeat_len
     mean_data = np.zeros(max_tb_frame)
@@ -126,7 +126,8 @@ def angular_mean_tailbeat_chunk(data,tailbeat_len):
         sin_mean = np.nanmean(np.sin(data_range))
 
         #SIN then COSINE
-        angular_mean = np.rad2deg(np.arctan2(sin_mean,cos_mean))
+        #angular_mean = np.rad2deg(np.arctan2(sin_mean,cos_mean))
+        angular_mean = np.arctan2(sin_mean,cos_mean)
         mean_data[k] = angular_mean
 
     return mean_data[::tailbeat_len]
@@ -233,7 +234,8 @@ class fish_data:
         self.calc_tb_freq()
         self.calc_accel()
         self.calc_yaw_heading_ps()
-        
+
+        #self.graph_values()        
         
     def get_fish_BL(self):
         self.body_lengths = (get_dist_np_3D(self.head_x,self.head_y,self.head_z,self.midline_x,self.midline_y,self.midline_z) + 
@@ -303,7 +305,7 @@ class fish_data:
 
         #Then we use arctan to calculate the heading based on the x and y point vectors
         #Becasue of roll we don't want to the last value since it will be wrong
-        self.yaw_heading = np.rad2deg(np.arctan2(self.vec_y,self.vec_x))
+        self.yaw_heading = np.arctan2(self.vec_y,self.vec_x)
 
         # print(self.vec_x)
         # print(self.vec_y)
@@ -323,7 +325,7 @@ class fish_data:
 
         #Then we use arctan to calculate the heading based on the x and y point vectors
         #Becasue of roll we don't want to the last value since it will be wrong
-        self.pitch_heading = np.rad2deg(np.arctan2(self.vec_xy,self.vec_z))
+        self.pitch_heading = np.arctan2(self.vec_xy,self.vec_z)
 
     #calcualtes the yaw heading change per second
     def calc_yaw_heading_ps(self):
[…]

### 2024-03-08 Fish Data Analysis/NN_Accel_Heading.qmd
Saving here before more messing around

@@
 
+nth_min <- function(x,n){sort(na.omit(x))[n]}
+
 light_no_ab_color = "#d4d7dd"
@@
 Load in the data
-
-```{r}
-raw_new <- read.csv("Data/Fish_Comp_Values_3D.csv")
-raw_old <- read.csv("Data/older_Fish_Comp_Values_3D.csv") %>% mutate(Angle = deg2rad(Angle),
-                                                                     Fish1_Yaw_Heading = deg2rad(Fish1_Yaw_Heading),
-                                                                     Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))
-
-hist(raw_new$Angle - deg2rad(raw_old$Angle))
-hist(raw_new$Fish1_Yaw_Heading - deg2rad(raw_old$Fish1_Yaw_Heading))
-hist(raw_new$Fish1_Yaw_Heading_PS - deg2rad(raw_old$Fish1_Yaw_Heading_PS))
-
-```
 
@@
 fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
-                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
+                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
+                                           nndDistance = nth_min(Distance, 1),
                                            nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
@@
                                     mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
-                                    filter(Distance <= 2)
+                                    filter(Distance <= 1.5)
 
@@
 
-nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/5)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 
-nn_accel_sum <- fish_data_nn_normal %>% mutate(distance_bins = round_any(Relative_X,0.25)) %>%
+nn_accel_sum <- fish_data_nn_normal %>% mutate(distance_bins = round_any(Relative_X,0.2)) %>%
                                                 group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 
+```
+
+Estimating functions
+
+```{r}
+#par 1 = amp
+#par 2 = freq
+#par 3 = phase
+
+min.RSS <- function(data, par) {
+             with(data, sum(par[1]*sin(2*pi/par[2]*Angle+par[3]) - Fish1_Yaw_Heading_PS)^2)
+}
+
+result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
+result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
+result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
+result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))
+
+result_F0LNDN$par
+result_F0LYDN$par
+result_F0LNDY$par
+result_F0LYDY$par
 ```
@@
 
-tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle):Ablation:Darkness, data = fish_data_nn_model) 
-Anova(tester_model)
+manual_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
+                   data = fish_data_nn_model) 
+Anova(manual_model)
 
+#Raw data
 ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
@@
   facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
-  #geom_smooth(se = F)+
-  #geom_smooth(se = F, method = glm, formula = y ~ 1)+
   geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
   theme_classic() +
-  #ylim(-5,5)+
   xlab("direction of neighbour (degrees)") +
@@
 
+#Means graph
 ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
@@
   geom_point()+
-  #geom_smooth(se = F)+
-  #geom_line(aes(y = sin_pred)) +
-  #geom_line(alpha = 0.75) +
-  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
-  geom_line(aes(y = rad2deg(predict(tester_model,
+  geom_line(aes(y = rad2deg(predict(manual_model,
                     newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
@@
                      labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
-  # scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
-  #                    labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
   labs(color = "Sensory Conditions")
 
-# emmeans(tester_model, ~ Ablation|Darkness, type = "response")
-# emmeans(tester_model, ~ Darkness|Ablation, type = "response")
+test(emmeans(manual_model, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
 

### 2024-03-11 Fish Data Analysis/NN_Accel_Heading.qmd
Fully flipped fish pairs to do both

@@
                                        #Switch around angle when we switch focal fish
-                                       mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi),
+                                       mutate(Angle = -1*ifelse(Angle >= 0, Angle - pi, Angle + pi),
                                               Relative_X = -1*Relative_X) %>%
@@
 fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)
+
+min_dist <- 0.75
+max_dist <- 10
 
@@
                                            all_nas = all(is.na(nndDistance))) %>%
-                                    filter(Distance == nndDistance | all_nas) %>%
+                                    #filter(Distance == nndDistance | all_nas) %>%
                                     mutate(row_n = row_number()) %>%
-                                    filter(row_n == 1) %>%
+                                    #filter(row_n == 1) %>%
                                     ungroup() %>%
                                     mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
-                                    filter(Distance <= 1.5)
+                                    filter(Distance >= min_dist & Distance <= max_dist)
 
@@
 
-nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/5)) %>%
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          n = n()) %>%
+                                                ungroup() %>%
+                                                na.omit()
+
+nn_heading_dist_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6), distance_bins = round_any(Distance,0.25)) %>%
+                                                group_by(angle_bins,distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                 summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
@@
 
-fish_data_nn_model <- fish_data_nn %>% filter(Flow == "Still Water") %>% 
+fish_data_nn_model <- fish_data_nn_normal %>% filter(Flow == "Still Water") %>% 
                                        mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
@@
 heading_ps_angle_step <- stepAIC(heading_ps_angle_base,
-                                   list(upper = ~ (sin(Angle)+Ablation:sin(Angle)+Darkness:sin(Angle)), lower = ~1),
+                                   list(upper = ~ Angle*sin(Angle)*Ablation*Darkness, lower = ~1),
                                    direction = "both",
@@
 
+manual_model_2 <- lm(Fish2_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
+                   data = fish_data_nn_model %>% mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi))) 
+Anova(manual_model_2)
+
 #Raw data
 ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
-       aes(x = Angle, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
+       aes(x = Angle, y = rad2deg(Fish2_Yaw_Heading_PS), color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point(alpha = 0.1)+
@@
   geom_point()+
+  geom_line()+
+  # geom_line(aes(y = rad2deg(predict(manual_model,
+  #                   newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
   geom_line(aes(y = rad2deg(predict(manual_model,
@@
                      labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory Conditions")+
+  ggtitle(paste0("All Fish From ",min_dist," to ",max_dist))
 
 test(emmeans(manual_model, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
+
+# ggplot(nn_heading_dist_sum %>% filter(Flow == "Still Water"),
+#        aes(x = angle_bins, y = distance_bins, fill = mean_turn))+
+#   facet_wrap(~ Ablation + Darkness)+
+#   scale_fill_viridis(option="turbo",limits = c(-2,2))+
+#   geom_tile()+
+#   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
+#                      labels = round(unique(nn_heading_sum$angle_bins))) +
+#   coord_polar(start = -pi / 2)+
+#   theme_classic()
 
@@
 
-accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
-accel_lin_lm <- lm(Fish1_Accel ~ Relative_X*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
+accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"))
+accel_lin_lm <- lm(Fish1_Accel ~ Relative_X*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"))
 
@@
 
-ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
+ggplot(fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"),
        aes(x = Relative_X, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
@@
 
-ggplot(nn_accel_sum %>% filter(Flow == "Still Water" & distance_bins < 3),
+ggplot(nn_accel_sum %>% filter(Flow == "Flowing Water (2 BL/s)" & distance_bins < 3),
        aes(x = distance_bins, y = mean_accel, color = interaction(Ablation, Darkness, sep =", ")))+
@@
   #geom_line(alpha = 0.75) +
-  geom_smooth(se = F, method = glm, formula = y ~ 1)+
+  geom_smooth(se = F, method = glm, formula = y ~ x)+
   theme_classic() +
@@
 
-directional_df <- fish_data_nn %>% mutate(round_X = round_any(RelativeX,0.5),
-                                                    round_Y = round_any(RelativeY,0.5)) %>%
-                                                      group_by(round_X,round_Y,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                                      summarise(mean_accel = mean(Fish1_Accel),
-                                                                mean_turn = mean(Fish1_Yaw_Heading_PS),
-                                                                n = n()) %>%
-                                                      ungroup()
-
-ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5 & mean_accel > -0.01 & mean_accel < 0.01),
-       aes(round_X, round_Y, fill= mean_accel)) + 
-  geom_tile()+
-  facet_wrap(~Flow_Ablation_Darkness)+
-  scale_fill_viridis(option="magma")+
-  coord_fixed()+
-  theme_classic()
-
-ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5),
-       aes(round_X, round_Y, fill= mean_turn)) + 
-  geom_tile()+
-  facet_wrap(~Flow_Ablation_Darkness)+
-  scale_fill_viridis(option="magma")+
-  coord_fixed()+
-  theme_classic()
+# directional_df <- fish_data_nn %>% mutate(round_X = round_any(Relative_X,0.5),
+#                                                     round_Y = round_any(Relative_Y,0.5)) %>%
+#                                                       group_by(round_X,round_Y,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+#                                                       summarise(mean_accel = mean(Fish1_Accel),
+#                                                                 mean_turn = mean(Fish1_Yaw_Heading_PS),
+#                                                                 n = n()) %>%
+#                                                       ungroup()
+# 
+# ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5 & mean_accel > -0.01 & mean_accel < 0.01),
+#        aes(round_X, round_Y, fill= mean_accel)) + 
+#   geom_tile()+
+#   facet_wrap(~Flow_Ablation_Darkness)+
+#   scale_fill_viridis(option="magma")+
+#   coord_fixed()+
+#   theme_classic()
+# 
+# 
+# ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5),
+#        aes(round_X, round_Y, fill= mean_turn)) + 
+#   geom_tile()+
+#   facet_wrap(~Flow_Ablation_Darkness)+
+#   scale_fill_viridis(option="magma")+
+#   coord_fixed()+
+#   theme_classic()
 

### 2024-03-11 3D_data_files_to_csv_4P.py

@@ -341,8 +341,32 @@ class fish_data:
 
         chunked_yaw_mean = angular_mean_tailbeat_chunk(self.yaw_heading, tailbeat_len)
 
-        self.yaw_heading_ps = np.arctan2(np.sin(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)),
-                                         np.cos(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)))[1:-1] * fps/(2*tailbeat_len)
+        # self.yaw_heading_ps = np.arctan2(np.sin(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)),
+        #                                  np.cos(np.roll(chunked_yaw_mean,-1) - np.roll(chunked_yaw_mean,1)))[1:-1] * fps/(2*tailbeat_len)
+
+
+        chunked_yaw_heading_vec = np.column_stack((np.cos(chunked_yaw_mean), np.sin(chunked_yaw_mean)))
+        
+        dot_prods = np.zeros(len(chunked_yaw_heading_vec)) + np.nan
+        cross_prods = np.zeros(len(chunked_yaw_heading_vec)) + np.nan
+
+        for t in range(1,len(chunked_yaw_heading_vec)-1):
+
+            chunked_yaw_heading_vec_prev = chunked_yaw_heading_vec[t-1]
+            chunked_yaw_heading_vec_next = chunked_yaw_heading_vec[t+1]
+            chunked_yaw_heading_vec_prev_perp = [-1*chunked_yaw_heading_vec[t-1][1],chunked_yaw_heading_vec[t-1][0]]
+
+            dot_prods[t] = np.dot(chunked_yaw_heading_vec_prev,chunked_yaw_heading_vec_next)
+            cross_prods[t] = np.dot(chunked_yaw_heading_vec_next,chunked_yaw_heading_vec_prev_perp)
+
+        self.yaw_heading_ps = np.arccos(dot_prods) * np.sign(cross_prods) * fps/(2*tailbeat_len)
+        self.yaw_heading_ps = self.yaw_heading_ps[1:-1]
+
+        # print(chunked_yaw_heading_vec)
+        # print(self.yaw_heading_ps)
+        # print(dot_yaw_heading_angle)
+
+        # sys.exit()
 
 
         # print(repr(self.yaw_heading))
@@ -624,23 +648,29 @@ class fish_comp:
[…]

### 2024-03-11 Fish Data Analysis/NN_Accel_Heading.qmd
Save before undoing

@@
 
-fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
-                                              Fish3_X = Fish1_X,
-                                              Fish3_Y = Fish1_Y,
-                                              Fish3_Z = Fish1_Z,
-                                              Fish3_Speed = Fish1_Speed,
-                                              Fish3_Accel = Fish1_Accel,
-                                              Fish3_Yaw_Heading = Fish1_Yaw_Heading,
-                                              Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
-                                              ) %>%
-                                       mutate(Fish1 = Fish2,
-                                              Fish1_X = Fish2_X,
-                                              Fish1_Y = Fish2_Y,
-                                              Fish1_Z = Fish2_Z,
-                                              Fish1_Speed = Fish2_Speed,
-                                              Fish1_Accel = Fish2_Accel,
-                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading,
-                                              Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
-                                       mutate(Fish2 = Fish3,
-                                              Fish2_X = Fish3_X,
-                                              Fish2_Y = Fish3_Y,
-                                              Fish2_Z = Fish3_Z,
-                                              Fish2_Speed = Fish3_Speed,
-                                              Fish2_Accel = Fish3_Accel,
-                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading,
-                                              Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
-                                       #Switch around angle when we switch focal fish
-                                       mutate(Angle = -1*ifelse(Angle >= 0, Angle - pi, Angle + pi),
-                                              Relative_X = -1*Relative_X) %>%
-                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
+min_dist <- 0
+max_dist <- 0.75
 
-fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)
-
-min_dist <- 0.75
-max_dist <- 10
-
-fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
+fish_data_nn <- fish_comp_data %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                     mutate(#nndDistance = min(Distance, na.rm = TRUE),
@@
 
-Estimating functions
-
-```{r}
-#par 1 = amp
-#par 2 = freq
-#par 3 = phase
-
-min.RSS <- function(data, par) {
-             with(data, sum(par[1]*sin(2*pi/par[2]*Angle+par[3]) - Fish1_Yaw_Heading_PS)^2)
-}
-
-result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
-result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
-result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
-result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))
-
-result_F0LNDN$par
-result_F0LYDN$par
-result_F0LNDY$par
-result_F0LYDY$par
-```
-
 ```{r}
@@
 
-manual_model_2 <- lm(Fish2_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
-                   data = fish_data_nn_model %>% mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi))) 
-Anova(manual_model_2)
-
 #Raw data
@@
   geom_point()+
-  geom_line()+
-  # geom_line(aes(y = rad2deg(predict(manual_model,
-  #                   newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
+  #geom_line()+
   geom_line(aes(y = rad2deg(predict(manual_model,

### 2024-03-11 3D_data_files_to_csv_4P.py

@@ -1344,17 +1344,17 @@ class trial:
         # and so on and so forth
         
         #Now we're going to do all the fish both ways to make NND stuff easier
-        #self.fish_comp_indexes = [[i,j] for i in range(n_fish) for j in range(i+1,n_fish)]
+        self.fish_comp_indexes = [[i,j] for i in range(n_fish) for j in range(i+1,n_fish)]
 
-        # for pair in self.fish_comp_indexes:
-        #     random.shuffle(pair)
+        for pair in self.fish_comp_indexes:
+            random.shuffle(pair)
 
-        self.fish_comp_indexes = [[i,j] for i in range(n_fish) for j in range(n_fish)]
+        # self.fish_comp_indexes = [[i,j] for i in range(n_fish) for j in range(n_fish)]
 
-        #Remove matched pairs
-        matched_index = [0,9,18,27,36,45,56,63]
+        # #Remove matched pairs
+        # matched_index = [0,9,18,27,36,45,56,63]
 
-        self.fish_comp_indexes = np.delete(self.fish_comp_indexes, matched_index, axis = 0)
+        # self.fish_comp_indexes = np.delete(self.fish_comp_indexes, matched_index, axis = 0)
 
         self.fish_comps = [[0 for j in range(self.n_fish)] for i in range(self.n_fish)]
 

### 2024-03-12 Fish Data Analysis/NN_Accel_Heading.qmd
Adding Heading PS to the paper script

@@
 ## Loading in the Libraries for Everything
+
 ```{r}
@@
 library(viridis)
+library(lme4)
 ```
@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))
 
@@
 
+# fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
+#                                               Fish3_X = Fish1_X,
+#                                               Fish3_Y = Fish1_Y,
+#                                               Fish3_Z = Fish1_Z,
+#                                               Fish3_Speed = Fish1_Speed,
+#                                               Fish3_Accel = Fish1_Accel,
+#                                               Fish3_Yaw_Heading = Fish1_Yaw_Heading,
+#                                               Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
+#                                               ) %>%
+#                                        mutate(Fish1 = Fish2,
+#                                               Fish1_X = Fish2_X,
+#                                               Fish1_Y = Fish2_Y,
+#                                               Fish1_Z = Fish2_Z,
+#                                               Fish1_Speed = Fish2_Speed,
+#                                               Fish1_Accel = Fish2_Accel,
+#                                               Fish1_Yaw_Heading = Fish2_Yaw_Heading,
+#                                               Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
+#                                        mutate(Fish2 = Fish3,
+#                                               Fish2_X = Fish3_X,
+#                                               Fish2_Y = Fish3_Y,
+#                                               Fish2_Z = Fish3_Z,
+#                                               Fish2_Speed = Fish3_Speed,
+#                                               Fish2_Accel = Fish3_Accel,
+#                                               Fish2_Yaw_Heading = Fish3_Yaw_Heading,
+#                                               Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
+#                                        #Switch around angle when we switch focal fish
+#                                        mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi),
+#                                               Relative_X = -1*Relative_X) %>%
+#                                        select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
+# 
+# fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)
+
 min_dist <- 0
-max_dist <- 0.75
+max_dist <- 3
 
@@
                                     ungroup() %>%
-                                    mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
                                     filter(Distance >= min_dist & Distance <= max_dist)
@@
 
+Estimating functions
+
+```{r}
+#par 1 = amp
+#par 2 = freq
+#par 3 = phase
+
+min.RSS <- function(data, par) {
+             with(data, sum(par[1]*sin(2*pi/par[2]*Angle+par[3]) - Fish1_Yaw_Heading_PS)^2)
+}
+
+result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
+result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
+result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
+result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))
+
+result_F0LNDN$par
+result_F0LYDN$par
+result_F0LNDY$par
+result_F0LYDY$par
+```
+
 ```{r}
@@
 
-manual_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
+manual_model <- lm(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
                    data = fish_data_nn_model) 
@@
   xlab("direction of neighbour (degrees)") +
-  ylab("focal fish turning angle (degrees/sec)") +
+  ylab("focal fish turning angle speed (degrees/sec)") +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
@@
   labs(color = "Sensory Conditions")+
-  ggtitle(paste0("All Fish From ",min_dist," to ",max_dist))
+  ggtitle(paste0("Nearest Neighbor From ",min_dist," to ",max_dist))
 
@@
 
-```
-
-Estimating functions
-
-```{r}
-#par 1 = amp
-#par 2 = freq
-#par 3 = phase
-
-min.RSS <- function(data, par) {
-             with(data, sum(par[1]*sin(2*pi/par[2]*Angle+par[3]) - Fish1_Yaw_Heading_PS)^2)
-}
-
-result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
-result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
-result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
-result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))
-
-result_F0LNDN$par
-result_F0LYDN$par
-result_F0LNDY$par
-result_F0LYDY$par
 ```

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Re graphing with new data
Adding Heading PS to the paper script

@@
 
-## Fish Turning Graphs
+Heading Velocity graphs
 
 ```{r}
-
-abalated_dark_turning_data <- read.csv("Data/ablated_dark_data_turning.csv") %>%
+fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                            mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
@@
                            mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
-                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
-                           select(-c("Singles","Frame","Fish")) %>%
-                           mutate(Type = "Eight Fish")
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))
 
-annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
-                           #filter(Next.to.Wall == 0) %>%
-                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
-                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
-                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
-                           rename("Turn_Dir" = "Turn.Direction")  %>%
-                           rename("Fish_Left" = "No..Fish.Left")  %>%
-                           rename("Fish_Right" = "No..Fish.Right")  %>%
-                           mutate(Type = "Eight Fish")
+fish_comp_data <- na.omit(fish_comp_data)
 
-single_fish_turning_data <- read.csv("Data/single_fish_turning.csv") %>%
-                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
-                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
-                           select(-c("Singles")) %>%
-                           mutate(Type = "Combined Single")
+min_dist <- 0
+max_dist <- 2
 
-eight_fish_turning_data <- rbind(annushka_turning_data,abalated_dark_turning_data)
-
-all_turning_data <- rbind(eight_fish_turning_data,single_fish_turning_data)
-
-eight_fish_data_sum  <- eight_fish_turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               se_right_turn = sd_right_turn/sqrt(n()),
-                                               n = n()) %>%
+fish_data_nn_normal <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
+                                        group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                         ungroup()
 
-single_fish_data_sum  <- single_fish_turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               se_right_turn = sd_right_turn/sqrt(n()),
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                           n = n()) %>%
                                                 ungroup() %>%
-                                     filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation")
-
-turning_data_sum <- all_turning_data %>% na.omit %>%
-                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
-                                     summarize(mean_right_turn = mean(turn_bool),
-                                               sd_right_turn = sd(turn_bool),
-                                               se_right_turn = sd_right_turn/sqrt(n()),
-                                               n = n()) %>%
-                                     ungroup()
+                                                na.omit()
 ```
 
-### All the Plots of Eight Fish in Flow and Still, Raw and GLM
+Model and Graph
 
 ```{r}
-eight_fish_still <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Still Water"),
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
+
+heading_PS_model_still <- lm(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
+                   data = fish_data_nn_normal %>% filter(Flow == "Still Water")) 
+Anova(heading_PS_model_still)
+
+heading_PS_graph <- ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
+       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point()+
-  #geom_line(alpha = 0.25) +
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
-  #facet_wrap(~ Darkness + Ablation) +
+  geom_line(aes(y = rad2deg(predict(heading_PS_model_still,
+                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
   theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  ylim(0,1) +
+  ylim(-50,50) +
+  xlab("Direction of Neighbour (Degrees)") +
+  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
-  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory Conditions")+
-  theme(axis.text.x = element_text(size = text_size),
-        axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))
+  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
+                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
+  labs(color = "Sensory Conditions")
 
-eight_fish_flow <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Flowing Water (2 BL/s)"),
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point()+
-  #geom_line(alpha = 0.25) +
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
-  #facet_wrap(~ Darkness + Ablation) +
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  ylim(0,1) +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
-  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "Sensory Conditions")+
-  theme(axis.text.x = element_text(size = text_size),
-        axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))
+heading_PS_graph
 
-eight_fish_still
-eight_fish_flow
-
-```
-
-### All the Plots of Eight Fish vs Single in Still Water
-
-```{r}
-placeholder_tibble <- tibble("Fish_Ratio" = c("0:7"),
-                             "Fish_Num_Ratio" = c(0.875),
-                             "Flow" = c("Still Water"),
-                             "Ablation" = c("No Ablation"),
-                             "Darkness" = c("Light"),
-                             "Type" = c("Combined Single"),
-                             "n" = c(0))
-
-light_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
-                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation") %>%
-                                      full_join(.,single_fish_data_sum) %>%
-                                      full_join(.,placeholder_tibble)
-
-light_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
-                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "Ablated") %>%
-                                      full_join(.,single_fish_data_sum) %>%
-                                      full_join(.,placeholder_tibble)
-
-dark_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
-                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "No Ablation") %>%
-                                      full_join(.,single_fish_data_sum) %>%
-                                      full_join(.,placeholder_tibble)
-
-dark_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
-                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "Ablated") %>%
-                                      full_join(.,single_fish_data_sum) %>%
-                                      full_join(.,placeholder_tibble)
-
-light_eight_and_single_graph <- ggplot(light_no_ab_eight_single_graph_data,
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
-  geom_point()+
-  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "School Type")+
-  theme(axis.text.x = element_text(size = text_size/2),
-        axis.text.y = element_text(size = text_size/2),
-        axis.title.y = element_text(size = text_size/2))+
-  guides(fill = FALSE)+
-  scale_y_continuous("Probability of a Right Turn",
-                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
-                     limits = c(0, 1))
-
-ablation_eight_and_single_graph <- ggplot(light_ab_eight_single_graph_data,
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
-  geom_point()+
-  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  ylim(0,1) +
-  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  scale_fill_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "School Type")+
-  theme(axis.text.x = element_text(size = text_size/2),
-        axis.text.y = element_text(size = text_size/2),
-        axis.title.y = element_text(size = text_size/2))+
-  guides(fill = FALSE)+
-  scale_y_continuous("Probability of a Right Turn",
-                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
-                     limits = c(0, 1))
-
-dark_eight_and_single_graph <- ggplot(dark_no_ab_eight_single_graph_data,
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
-  geom_point()+
-  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "School Type")+
-  theme(axis.text.x = element_text(size = text_size/2),
-        axis.text.y = element_text(size = text_size/2),
-        axis.title.y = element_text(size = text_size/2))+
-  guides(fill = FALSE)+
-  scale_y_continuous("Probability of a Right Turn",
-                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
-                     limits = c(0, 1))
-
-dark_ablation_eight_and_single_graph <- ggplot(dark_ab_eight_single_graph_data,
-       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
-  geom_point()+
-  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
-  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
-  theme_classic() +
-  xlab("# Fish on Left : # Fish on Right") +
-  ylab("Probability of a Right Turn") +
-  scale_colour_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  scale_fill_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
-  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
-  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
-                                0.5,0.625,0.75,0.875),
-                     labels = c("7:0","6:1","5:2","4:3",
-                                "3:4","2:5","1:6","0:7"))+ 
-  labs(color = "School Type")+
-  theme(axis.text.x = element_text(size = text_size/2),
-        axis.text.y = element_text(size = text_size/2),
-        axis.title.y = element_text(size = text_size/2))+
-  guides(fill = FALSE)+
-  scale_y_continuous("Probability of a Right Turn",
-                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
-                     limits = c(0, 1))
-
-light_eight_and_single_graph
-ablation_eight_and_single_graph
-dark_eight_and_single_graph
-dark_ablation_eight_and_single_graph
-```
-
-### Now we combine it all
-
-```{r}
-# turning_mega_plot <- ggarrange(eight_fish_still, eight_fish_flow,ggplot() + theme_classic() + theme(axis.line=element_blank()),
-#           light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
-#           labels = c("A", "B", "", "C", "D", "E"),
-#           ncol = 3, nrow = 2)
-# 
-# ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)
-
-turning_both_plot <- ggarrange(eight_fish_still, eight_fish_flow,
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-
-ggsave("Paper Figures/turning_both_plot.png", turning_both_plot, width = 12, height = 6)
-
-turning_single_test_plot <- ggarrange(
-          light_eight_and_single_graph, ablation_eight_and_single_graph, 
-          dark_eight_and_single_graph, dark_ablation_eight_and_single_graph,
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-
-ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 10, height = 7)
+ggsave("Paper Figures/Heading_PS_Graph.jpg", heading_PS_graph, width = 7, height = 7)
 
@@
 
+school_stats_mega_plot
+
+school_stats_mega_plot <- annotate_figure(school_stats_mega_plot, 
+                top = text_grob("                 Still Water                                     Flowing Water (2 BL/s)",
+                                size = 24),
+                fig.lab.pos = "top")
+
 ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 17)

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Cleaning up paper code and colors

@@
 
-light_no_ab_color = "#d4d7dd"
+light_no_ab_color = "#9C9C9C"   #"#C62E65" #A1BAA4" #"#d4d7dd" 06D6A0
 light_ab_color = "#f5ba9e"
 dark_no_ab_color = "#5e94d4"
-dark_ab_color = "#1E4371"
+dark_ab_color = "#49A078"   #"#1E4371"
 sim_color = "#777777"
@@
 min_dist <- 0
-max_dist <- 2
+max_dist <- 3
 
@@
 
-school_data <- na.omit(school_data)
+#school_data <- na.omit(school_data)
 
@@
                            group_by(Flow_Ablation_Darkness) %>%
-                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
-                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
-                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
-                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
-                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
-                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
-                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
+                           mutate(NND_Mean_Val = mean(NND,na.rm = T), NND_SD_Val = sd(NND,na.rm = T),
+                                  Polar_Mean_Val = mean(School_Polar,na.rm = T), Polar_SD_Val = sd(School_Polar,na.rm = T),
+                                  Speed_Mean_Val = mean(School_Speed,na.rm = T), Speed_SD_Val = sd(School_Speed,na.rm = T),
+                                  Area_Mean_Val = mean(Area,na.rm = T), Area_SD_Val = sd(Area,na.rm = T),
+                                  Groups_Mean_Val = mean(Groups,na.rm = T), Groups_SD_Val = sd(Groups,na.rm = T),
+                                  Mean_Groups_Mean_Val = mean(Mean_Groups,na.rm = T), Mean_Groups_SD_Val = sd(Mean_Groups,na.rm = T),
+                                  Height_Mean_Val = mean(School_Height,na.rm = T), Height_SD_Val = sd(School_Height,na.rm = T)) %>%
                            ungroup()
@@
   theme(legend.position = "none") +
-  ylim(0,2.5)+
+  #ylim(0,2.5)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +

### 2024-03-12 Fish Data Analysis/Results_Text.qmd
Cleaning up paper code and colors

--- 2023-04-19 Fish Data Analysis/Results_Text.qmd
@@
                            filter(row_number() %% 3 == 1) %>%
-                           ungroup() %>%
-                           # ###
+                           ungroup()
 
-                           group_by(Flow_Ablation_Darkness) %>%
-                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
-                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
-                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
-                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
-                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
-                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
-                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
-                           ungroup()
+ggplot(school_data, aes(x = 1, y = NND, color = Flow_Ablation_Darkness))+
+  geom_point()+
+  facet_wrap(~Date_Trial)
 ```
@@
 
-nnd_glmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-nnd_s_aov_me <- Anova(nnd_glmer_still)
+nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+nnd_s_aov_me <- Anova(nnd_lmer_still)
 
-nnd_glmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-nnd_f_aov_me <- Anova(nnd_glmer_flow)
+nnd_lmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+nnd_f_aov_me <- Anova(nnd_lmer_flow)
 
-height_glmer_still <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-height_s_aov_me <- Anova(height_glmer_still)
+polar_lmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+polar_s_aov_me <- Anova(polar_lmer_still)
 
-height_glmer_flow <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-height_f_aov_me <- Anova(height_glmer_flow)
+polar_lmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+polar_f_aov_me <- Anova(polar_lmer_flow)
 
-polar_glmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-polar_s_aov_me <- Anova(polar_glmer_still)
+speed_lmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+speed_s_aov_me <- Anova(speed_lmer_still)
 
-polar_glmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-polar_f_aov_me <- Anova(polar_glmer_flow)
+speed_lmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+speed_f_aov_me <- Anova(speed_lmer_flow)
 
-speed_glmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-speed_s_aov_me <- Anova(speed_glmer_still)
+groups_lmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+groups_s_aov_me <- Anova(groups_lmer_still)
 
-speed_glmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-speed_f_aov_me <- Anova(speed_glmer_flow)
+groups_lmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+groups_f_aov_me <- Anova(groups_lmer_flow)
 
-area_glmer_still <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-area_s_aov_me <- Anova(area_glmer_still)
+glmm_school_stats_table <- tibble(Stat = c(rep("NND",6),rep("Polarization",6),rep("Speed",6),rep("Groups",6)),
+       Flow_or_Still = rep(c(rep("Still",3) , rep("Flow",3)), 4),
+       Condition = rep(c("Ablation","Darkness","Ablation:Darkness"), 8),
+       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,3),
+                  rep(length(nnd_lmer_flow@resp$y)-3,3)),times = 4),
+       Chisq = round(c(nnd_s_aov_me$Chisq[1:3],nnd_f_aov_me$Chisq[1:3],
+                 polar_s_aov_me$Chisq[1:3],polar_f_aov_me$Chisq[1:3],
+                 speed_s_aov_me$Chisq[1:3],speed_f_aov_me$Chisq[1:3],
+                 groups_s_aov_me$Chisq[1:3],groups_f_aov_me$Chisq[1:3]),2),
 
-area_glmer_flow <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-area_f_aov_me <- Anova(area_glmer_flow)
-
-groups_glmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-groups_s_aov_me <- Anova(groups_glmer_still)
-
-groups_glmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-groups_f_aov_me <- Anova(groups_glmer_flow)
-
-glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
-       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
-       Condition = rep(c("Ablation","Darkness"), 12),
-       DF = rep(c(rep(length(nnd_glmer_still@resp$y)-3,2),
-                  rep(length(nnd_glmer_flow@resp$y)-3,2)),times = 6),
-       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
-                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
-                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
-                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
-                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
-                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),
-
-       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
-                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
-                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
-                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
-                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
-                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),
+       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[1:3],nnd_f_aov_me$`Pr(>Chisq)`[1:3],
+                 polar_s_aov_me$`Pr(>Chisq)`[1:3],polar_f_aov_me$`Pr(>Chisq)`[1:3],
+                 speed_s_aov_me$`Pr(>Chisq)`[1:3],speed_f_aov_me$`Pr(>Chisq)`[1:3],
+                 groups_s_aov_me$`Pr(>Chisq)`[1:3],groups_f_aov_me$`Pr(>Chisq)`[1:3]),2),
 
@@
 
-paste0("Placing the fish in darkness allowed us to understand the effect of swimming without vision on the schooling behavior of the giant danios.
-In still water, fish in darkness swam further from their neighbors ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
-       ")",
-
-       ", but with the same polarization ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
-       ")",
-
-       ", and in more groups ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
-       ")",
-
-       ", compared to fish in light. The average speed of the school was also the same ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Darkness"))$P_Val,3),
-       ").",
-
-       " In flowing water, the fish in darkness behaved more similarly to fish in light. The fish in darkness did not swim further apart from their neighbors ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
-       ").",
-
-       " They had the same polarization ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
-       ")",
-
-       ", and were not split into more groups ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
-       ")",
-
-       ", compared to fish in light in flowing water. The average speed of the school was also the same ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow" & Condition == "Darkness"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow" & Condition == "Darkness"))$P_Val,3),
-       ").",
-
-       " While polarity and speed were the same for fish in darkness, the fact that they broke up into many more subgroups and had a higher average NND shows that they were not one cohesive school.
-While these results were not the same when the fish were in flowing water, this may have been due to the influence of the flow as an outside orienting  force."
-       )
-
-```
-
-```{r}
-
-paste0("Manipulating the lateral line of the fish with gentamicin produced relatively few in the schooling kinematics of our fish. In still water, treated fish swam the same distance from neighbors ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
-       ")",
-
-       ", with the same polarization ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
-       ")",
-
-       ", and in the same number of groups ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
-       ")",
-
-       ", compared to fish in light. The average speed of the school was also the same ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Still" & Condition == "Ablation"))$P_Val,3),
-       ").",
-
-       " In flowing water, the ablated behaved almost exactly the same as when they were in still water. They did not swim further apart from their neighbors ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "NND" & Flow_or_Still == "Flow" & Condition == "Ablation"))$P_Val,3),
-       ").",
-
-       " They had the same polarization ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Polarization" & Flow_or_Still == "Flow" & Condition == "Ablation"))$P_Val,3),
-       ")",
-
-       ", and were not split into more groups ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Groups" & Flow_or_Still == "Flow" & Condition == "Ablation"))$P_Val,3),
-       ")",
-
-       ", compared to fish in light in flowing water. However, the average speed of the school was lower ",
-
-       "(F(1,",
-       (glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow", Condition == "Ablation"))$DF,
-       ") = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow", Condition == "Ablation"))$Chisq,3),
-       ", p = ",
-       round((glmm_school_stats_table %>% filter(Stat == "Speed" & Flow_or_Still == "Flow", Condition == "Ablation"))$P_Val,3),
-       ").",
-
-       " While the speed of the treated school was different in flowing water, ablated fish preformed almost exactly the same as fish with their lateral lines intact, indicating that treated fish were still able to maintain a cohesive school."
-       )
-
 ```
@@
 ```{r}
-annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
-                           #filter(Next.to.Wall == 0) %>%
-                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
-                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
-                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
-                           rename("Turn_Dir" = "Turn.Direction")  %>%
-                           rename("Fish_Left" = "No..Fish.Left")  %>%
-                           rename("Fish_Right" = "No..Fish.Right")  %>%
-                           mutate(Type = "Eight Fish")
 
-single_fish_turning_data <- read.csv("Data/single_fish_turning.csv") %>%
-                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
-                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
-                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
-                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
-                                                           c("7:0","6:1","5:2","4:3",
-                                                             "3:4","2:5","1:6","0:7"))) %>%
-                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
-                           select(-c("Singles")) %>%
-                           mutate(Type = "Combined Single")
-
-all_turning_data <- rbind(annushka_turning_data,single_fish_turning_data)
 ```
-
-```{r}
-turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
-                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
-tgs_aov <- Anova(turning_glm_still)
-
-turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
-                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
-tgf_aov <- Anova(turning_glm_flow)
-
-turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
-       Factor = c("FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness",
-                  "FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness"),
-       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
-       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
-       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
-       Is_Sig = P_Val < 0.05)
-
-# Single vs Eight fish
-light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
-                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
-                               family = binomial)
-ltg_aov <- Anova(light_turning_glm)
-
-ablated_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
-                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
-                               family = binomial)
-altg_aov <- Anova(ablated_turning_glm)
-
-dark_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
-                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
-                               family = binomial)
-dtg_aov <- Anova(dark_turning_glm)
-
-single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
-       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
-       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
-       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
-       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
-       Is_Sig = P_Val < 0.05)
-
-turning_results
-single_vs_eight_results
-
-tab_df(single_vs_eight_results, file="sjt_des.doc")
-```
-
-```{r}
-paste0("We found that there were significant differences between the turning behavior of the artificial “school” and the real group of eight fish under each sensory condition.
-Specifically, the probability of making a right turn, based on the ratio of fish on the left and right of the focal fish, was different when they were schooling in light with their lateral line intact ",
-
-       "(F(1,",
-       (single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Light"))$DF,
-       ") = ",
-       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Light"))$LR_Chisq,3),
-       ", p = ",
-       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Light"))$P_Val,3),
-       ").",
-
-       "when their lateral line was ablated ",
-
-       "(F(1,",
-       (single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Ablated"))$DF,
-       ") = ",
-       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Ablated"))$LR_Chisq,3),
-       ", p = ",
-       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Ablated"))$P_Val,5),
-       ").",
-
-       "and when the fish were in darkness ",
-
-       "(F(1,",
-       (single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Darkness"))$DF,
-       ") = ",
-       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Darkness"))$LR_Chisq,3),
-       ", p = ",
-       round((single_vs_eight_results %>% filter(Factor == "FNR:Type" & Condition == "Darkness"))$P_Val,3),
-       ").",
-
-       "(Figure XX). Therefore, the effects we saw were not because of the constraints of our tank, but because of actual changes in fish schooling behavior.")
-```
-
-```{r}
-paste0("We found that fish were significantly more likely to turn towards where there were more fish, and that the likelihood of turning towards the majority of fish was similar even when fish had an ablated lateral line or were swimming in darkness.
-Overall, we found that fish in each experimental condition were more likely to turn towards other fish, in both still ",
-
-       "(F(1,",
-       (turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Still"))$DF,
-       ") = ",
-       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Still"))$LR_Chisq,3),
-       ", p = ",
-       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Still"))$P_Val,3),
-       ")",
-
-       " and flowing water ",
-
-       "(F(1,",
-       (turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Flow"))$DF,
-       ") = ",
-       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Flow"))$LR_Chisq,3),
-       ", p = ",
-       round((turning_results %>% filter(Factor == "FNR" & Flow_or_Still == "Flow"))$P_Val,3),
-       ")",
-
-       " (Figure XX). We found that there was not a significant change in the turning behavior of fish in darkness ",
-
-       "(F(1,",
-       (turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Still"))$DF,
-       ") = ",
-       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Still"))$LR_Chisq,3),
-       ", p = ",
-       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Still"))$P_Val,3),
-       ")",
-
-       " or with an ablated lateral line ",
-
-       "(F(1,",
-       (turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Still"))$DF,
-       ") = ",
-       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Still"))$LR_Chisq,3),
-       ", p = ",
-       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Still"))$P_Val,3),
-       ")",
-
-       " in still water. In flowing water there was not a significant change from swimming in darkness ",
-
-       "(F(1,",
-       (turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Flow"))$DF,
-       ") = ",
-       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Flow"))$LR_Chisq,3),
-       ", p = ",
-       round((turning_results %>% filter(Factor == "FNR:Darkness" & Flow_or_Still == "Flow"))$P_Val,3),
-       ")",
-
-       ", but fish with ablated lateral lines were less influenced by the number of fish on either side of them when turning",
-
-       "(F(1,",
-       (turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Flow"))$DF,
-       ") = ",
-       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Flow"))$LR_Chisq,3),
-       ", p = ",
-       round((turning_results %>% filter(Factor == "FNR:Ablation" & Flow_or_Still == "Flow"))$P_Val,3),
-       ")",
-
-       ".
-These results suggest that turning fish were able to tell where the other fish around them were, even in darkness, because fish in darkness did not have a significantly different probability of turning left or right from those fish swimming in light."
-
-)
-```

### 2024-03-12 3D_data_files_to_csv_4P.py

@@ -986,7 +986,15 @@ class school_comps:
 
         #Then we get the mins of each row (or column, they are the same), and then get the mean for the mean
         # NND for that timepoint
-        self.nearest_neighbor_distance = np.nanmean(np.nanmin(nnd_array,axis = 1),axis = 1)
+
+        min_array = np.nanmin(nnd_array,axis = 1)
+
+        #We then NAN out all timepoints where we don't have at least 4 fish to make up the school at that time
+        num_nans = np.count_nonzero(np.isnan(min_array), axis=1).astype(np.float) 
+        num_nans[num_nans > 4] = np.nan
+        num_nans[num_nans <= 4] = 1
+
+        self.nearest_neighbor_distance = np.nanmean(np.nanmin(nnd_array,axis = 1), axis = 1)*num_nans
         
     def calc_tailbeat_cor(self):
         pass
@@ -1658,21 +1666,21 @@ print("Creating CSVs...")
 
 for trial in trials:
     if first_trial:
-        # fish_sigular_dataframe = trial.return_fish_vals()
-        fish_comp_dataframe = trial.return_comp_vals()
-        # fish_raw_comp_dataframe = trial.return_raw_comp_vals()
-        # fish_school_dataframe = trial.return_school_vals()
+        #fish_sigular_dataframe = trial.return_fish_vals()
+        #fish_comp_dataframe = trial.return_comp_vals()
+        #fish_raw_comp_dataframe = trial.return_raw_comp_vals()
+        fish_school_dataframe = trial.return_school_vals()
         first_trial = False
     else:
-        # fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
-        fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
-        # fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
-        # fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
+        #fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
+        #fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
+        #fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
[…]

### 2024-03-12 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before writing, final graphs

@@
 
-# fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
-#                                               Fish3_X = Fish1_X,
-#                                               Fish3_Y = Fish1_Y,
-#                                               Fish3_Z = Fish1_Z,
-#                                               Fish3_Speed = Fish1_Speed,
-#                                               Fish3_Accel = Fish1_Accel,
-#                                               Fish3_Yaw_Heading = Fish1_Yaw_Heading,
-#                                               Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
-#                                               ) %>%
-#                                        mutate(Fish1 = Fish2,
-#                                               Fish1_X = Fish2_X,
-#                                               Fish1_Y = Fish2_Y,
-#                                               Fish1_Z = Fish2_Z,
-#                                               Fish1_Speed = Fish2_Speed,
-#                                               Fish1_Accel = Fish2_Accel,
-#                                               Fish1_Yaw_Heading = Fish2_Yaw_Heading,
-#                                               Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
-#                                        mutate(Fish2 = Fish3,
-#                                               Fish2_X = Fish3_X,
-#                                               Fish2_Y = Fish3_Y,
-#                                               Fish2_Z = Fish3_Z,
-#                                               Fish2_Speed = Fish3_Speed,
-#                                               Fish2_Accel = Fish3_Accel,
-#                                               Fish2_Yaw_Heading = Fish3_Yaw_Heading,
-#                                               Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
-#                                        #Switch around angle when we switch focal fish
-#                                        mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi),
-#                                               Relative_X = -1*Relative_X) %>%
-#                                        select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
-# 
-# fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)
+single_fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "???")) %>%
+                           mutate(Darkness = ifelse(Darkness == "S", "Single", "???")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))
 
-min_dist <- 0
-max_dist <- 3
+single_fish_comp_data <- na.omit(single_fish_comp_data)
 
-fish_data_nn <- fish_comp_data %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
+all_fish_comp <- rbind(fish_comp_data,single_fish_comp_data)
+
+min_dist <- 4
+max_dist <- 10
+
+fish_data_nn <- all_fish_comp %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                     mutate(#nndDistance = min(Distance, na.rm = TRUE),
@@
 fish_data_nn_normal <- fish_data_nn %>% group_by(Flow_Ablation_Darkness) %>%
-                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T)) %>%
                                         ungroup()
@@
 ```
+
+Load in Single Fish
 
@@
   ylab("focal fish turning angle (rad/sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
@@
   theme_classic() +
-  ylim(-50,50) +
+  #ylim(-50,50) +
   xlab("direction of neighbour (degrees)") +
   ylab("focal fish turning angle speed (degrees/sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Commit before writing, final graphs

@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>%
+
+                           # ### Used to remove every third point to reduce autocorrelation
                            mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                   Date = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
+                           group_by(Comp_ID) %>%
+                           filter(row_number() %% 3 == 1) %>%
+                           ungroup()
 
@@
 
-min_dist <- 0
-max_dist <- 3
+close_min_dist <- 0
+close_max_dist <- 3
 
-fish_data_nn_normal <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
+far_min_dist <- 3
+far_max_dist <- 100
+
+fish_data_nn_normal_close <- fish_comp_data %>% filter(Distance >= close_min_dist & Distance <= close_max_dist) %>%
                                         group_by(Flow_Ablation_Darkness) %>%
@@
 
-nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
+nn_heading_sum_close <- fish_data_nn_normal_close %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          n = n()) %>%
+                                                ungroup() %>%
+                                                na.omit()
+
+fish_data_nn_normal_far <- fish_comp_data %>% filter(Distance >= far_min_dist & Distance <= far_max_dist) %>%
+                                        group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+                                        ungroup()
+
+nn_heading_sum_far <- fish_data_nn_normal_far %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
 
-heading_PS_model_still <- lm(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
-                   data = fish_data_nn_normal %>% filter(Flow == "Still Water")) 
-Anova(heading_PS_model_still)
+heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
+                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
+Anova(heading_PS_model_close)
 
-heading_PS_graph <- ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
+heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
+                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
+Anova(heading_PS_model_far)
+
+heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
        aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
   geom_point()+
-  geom_line(aes(y = rad2deg(predict(heading_PS_model_still,
-                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
+  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
+                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
+                    re.form = NA))), size = 1)+
   theme_classic() +
-  ylim(-50,50) +
+  ylim(-75,75) +
   xlab("Direction of Neighbour (Degrees)") +
@@
   scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
-  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
-                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
+  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
+                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
   labs(color = "Sensory Conditions")
 
-heading_PS_graph
+heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
+       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
+  geom_point()+
+  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
+                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
+                    re.form = NA))), size = 1)+
+  theme_classic() +
+  ylim(-75,75) +
+  xlab("Direction of Neighbour (Degrees)") +
+  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
+                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
+  labs(color = "Sensory Conditions")
 
-ggsave("Paper Figures/Heading_PS_Graph.jpg", heading_PS_graph, width = 7, height = 7)
+heading_PS_graph_close
+heading_PS_graph_far
+
+heading_PS_mega_plot <- ggarrange(heading_PS_graph_close, heading_PS_graph_far, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1, common.legend = TRUE, legend="right")
+
+heading_PS_mega_plot
+
+ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)
 

### 2024-03-12 Fish Data Analysis/Results_Text.qmd
Commit before writing, final graphs

@@
                             # ### Used to remove every third point to reduce autocorrelation
-                           mutate(Date = paste(Year,Month,Day,sep="_"),
-                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
-                           group_by(Date_Trial) %>%
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
+                           group_by(Comp_ID) %>%
                            filter(row_number() %% 3 == 1) %>%
                            ungroup()
-
-ggplot(school_data, aes(x = 1, y = NND, color = Flow_Ablation_Darkness))+
-  geom_point()+
-  facet_wrap(~Date_Trial)
 ```
@@
        Flow_or_Still = rep(c(rep("Still",3) , rep("Flow",3)), 4),
-       Condition = rep(c("Ablation","Darkness","Ablation:Darkness"), 8),
+       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 8),
        DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,3),
@@
 
-```{r}
-
-```
-
 ### Turning Results Text
@@
 
+fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_")) %>%
+
+                           # ### Used to remove every third point to reduce autocorrelation
+                           mutate(Date = paste(Year,Month,Day,sep="_"),
+                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
+                           group_by(Date_Trial) %>%
+                           filter(row_number() %% 3 == 1) %>%
+                           ungroup()
+
+fish_comp_data <- na.omit(fish_comp_data)
+
+close_min_dist <- 0
+close_max_dist <- 3
+
+far_min_dist <- 3
+far_max_dist <- 10
+
+fish_data_nn_normal_close <- fish_comp_data %>% filter(Distance >= close_min_dist & Distance <= close_max_dist) %>%
+                                        group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+                                        ungroup()
+
+fish_data_nn_normal_far <- fish_comp_data %>% filter(Distance >= far_min_dist & Distance <= far_max_dist) %>%
+                                        group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+                                        ungroup()
+
 ```
+
+```{r}
+
+heading_PS_model_close <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
+                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
+aov_heading_PS_model_close <- Anova(heading_PS_model_close)
+
+test(emmeans(heading_PS_model_close, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
+
+heading_PS_model_far <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
+                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
+aov_heading_PS_model_far <- Anova(heading_PS_model_far)
+
+test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
+
+turning_school_stats_table <- tibble(
+       Near_or_Far = rep(c(rep("Near",4) , rep("Far",4)), 1),
+       Condition = rep(c("Angle","Angle x Ablation","Angle x Darkness","Angle x Ablation x Darkness"), 2),
+       DF = c(rep(length(heading_PS_model_close@resp$y)-4,4),
+                  rep(length(heading_PS_model_far@resp$y)-4,4)),
+       Chisq = round(c(aov_heading_PS_model_close$Chisq[1:4],aov_heading_PS_model_far$Chisq[1:4]),3),
+       P_Val = round(c(aov_heading_PS_model_close$`Pr(>Chisq)`[1:4],aov_heading_PS_model_far$`Pr(>Chisq)`[1:4]),3),
+       Is_Sig = P_Val < 0.05)
+
+turning_school_stats_table
+
+tab_df(turning_school_stats_table, file="turning_stats.doc")
+
+```

### 2024-03-12 3D_data_files_to_csv_4P.py

@@ -897,7 +897,7 @@ class school_comps:
         self.calc_school_polarization()
         self.calc_nnd()
         self.calc_tailbeat_cor()
-        self.calc_school_area()
+        #self.calc_school_area()
 
         #self.calc_school_groups_all_points_diff_xy_z()
         self.calc_school_groups_all_points()
@@ -1645,7 +1645,9 @@ class trial:
         return(out_data)
 
 
-data_folder = "3D_Finished_Fish_Data_4P_gaps/"
+#data_folder = "3D_Finished_Fish_Data_4P_gaps/"
+
+data_folder = "Single Fish Combiner/Multi Data/"
 
 trials = []
 
@@ -1667,20 +1669,20 @@ print("Creating CSVs...")
 for trial in trials:
     if first_trial:
         #fish_sigular_dataframe = trial.return_fish_vals()
-        #fish_comp_dataframe = trial.return_comp_vals()
+        fish_comp_dataframe = trial.return_comp_vals()
         #fish_raw_comp_dataframe = trial.return_raw_comp_vals()
-        fish_school_dataframe = trial.return_school_vals()
+        #fish_school_dataframe = trial.return_school_vals()
         first_trial = False
     else:
         #fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
-        #fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
+        fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
         #fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
-        fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
+        #fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
 
 #fish_sigular_dataframe.to_csv("Fish_Individual_Values_3D.csv")
-#fish_comp_dataframe.to_csv("Fish_Comp_Values_3D.csv")
+fish_comp_dataframe.to_csv("Fish_Comp_Values_3D_Single.csv")
 #fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_3D.csv")
-fish_school_dataframe.to_csv("Fish_School_Values_3D.csv")
+#fish_school_dataframe.to_csv("Fish_School_Values_3D.csv")
 
 # #Recalculate when new data is added
 # all_trials_tailbeat_lens = []

### 2024-03-12 Single Fish Combiner/Fish_Combiner.py

@@ -3,13 +3,17 @@ import numpy as np
 from random import *
 import os
 
+ruler_tip = [388, 294]
+ruler_base = [369, 976]
+ruler_length_pix = np.sqrt((ruler_tip[0]-ruler_base[0])**2+(ruler_tip[1]-ruler_base[1])**2)
+
+ruler_length_m = 0.181
+
 #Header list for reading the raw location CSVs
 header_3 = list(range(3))
 header_4 = list(range(4))
 
-data_folders = ["Good Single Fish/light/still/","Good Single Fish/light/flow/",
-                "Good Single Fish/dark/still/","Good Single Fish/dark/flow/",
-                "Good Single Fish/ablation/still/","Good Single Fish/ablation/flow/"]
+data_folders = ["Good Single Fish/light/still/"]
 
 for data_folder in data_folders:
 
@@ -25,12 +29,13 @@ for data_folder in data_folders:
     # Make 10 combo files
 
     # The smallest number of data files for a condition is 13, which still gives us 1287 combinations for that 
-    for x in range(10):
+    # Match number of trials to real data
+    for x in range(5):
         shuffle(data_files)
         all_data_arr = [pd.read_csv(data_folder+f, index_col=0, header=header_3) for f in data_files]
 
         date = data_files[0][0:10]
-        conds = data_files[0][14:22]
+        conds = "LS_DS_F0" #data_files[0][14:22]
 
         #Store and reset the file numbers
         file_numbers = []
@@ -40,6 +45,14 @@ for data_folder in data_folders:
             file_numbers.append(data_files[i][11:13])
 
             data_to_fill.iloc[: ,i*12:(i+1)*12] = all_data_arr[i].iloc[: ,0:13]
+
+        #Make all the zs into 0s
+        data_to_fill.iloc[:,2:96:3] = 0
+
+        #Turn Everything into meters
+        data_to_fill.iloc[:,:] = data_to_fill.iloc[:,:] / ruler_length_pix * ruler_length_m
+
+        data_to_fill.columns.set_levels(['z', 'x', 'y'],level=3,inplace=True)
 
         # Sort the numbers first to make sure we don't get any duplicates
         file_numbers.sort()

### 2024-03-12 Fish Data Analysis/Results_Text.qmd
Small type fix

@@
                            # ### Used to remove every third point to reduce autocorrelation
-                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
-                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
-                           group_by(Comp_ID) %>%
+                           mutate(Date = paste(Year,Month,Day,sep="_"),
+                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
+                           group_by(Date_Trial) %>%
                            filter(row_number() %% 3 == 1) %>%
@@
                             # ### Used to remove every third point to reduce autocorrelation
-                           mutate(Date = paste(Year,Month,Day,sep="_"),
-                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
-                           group_by(Date_Trial) %>%
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
+                           group_by(Comp_ID) %>%
                            filter(row_number() %% 3 == 1) %>%
@@
 far_min_dist <- 3
-far_max_dist <- 10
+far_max_dist <- 100
 

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Graph formatting

@@
        aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point()+
+  geom_point(size = 3)+
   geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                     newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
-                    re.form = NA))), size = 1)+
+                    re.form = NA))), size = 2)+
   theme_classic() +
@@
                      labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
@@
        aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point()+
+  geom_point(size = 3)+
   geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
                     newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
-                    re.form = NA))), size = 1)+
+                    re.form = NA))), size = 2)+
   theme_classic() +
@@
                      labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
@@
 heading_PS_mega_plot
+
+heading_PS_mega_plot <- annotate_figure(heading_PS_mega_plot, 
+                top = text_grob("Near (< 3 BL)                                          Far (> 3 BL)",
+                                size = 24),
+                fig.lab.pos = "top")
 

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Trial Single Fish

--- 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Type = "Eight") %>%
 
@@
 fish_comp_data <- na.omit(fish_comp_data)
+
+fish_comp_data_single <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "S", "No Ablation")) %>%
+                           mutate(Darkness = ifelse(Darkness == "S", "Light")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Type = "Single") %>%
+
+                           # ### Used to remove every third point to reduce autocorrelation
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
+                           group_by(Comp_ID) %>%
+                           filter(row_number() %% 3 == 1) %>%
+                           ungroup()
+
+fish_comp_data_single <- na.omit(fish_comp_data_single)
+
+fish_comp_data <- rbind(fish_comp_data,fish_comp_data_single)
 
@@
 nn_heading_sum_close <- fish_data_nn_normal_close %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
-                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness) %>%
                                                 summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
@@
 nn_heading_sum_far <- fish_data_nn_normal_far %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
-                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness) %>%
                                                 summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
@@
 
-heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
+heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                    data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
@@
 
-heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
+heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                    data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
@@
 heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
-       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point()+
+       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ", line = Type)))+
+  geom_point(size = 3)+
   geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                     newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
-                    re.form = NA))), size = 1)+
+                    re.form = NA))), size = 2)+
   theme_classic() +
@@
   ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
                      labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
@@
   ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
                      labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
-  labs(color = "Sensory Conditions")
+  labs(color = "Sensory Conditions")+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 
@@
 
+heading_PS_mega_plot <- annotate_figure(heading_PS_mega_plot, 
+                top = text_grob("Near (< 3 BL)                                          Far (> 3 BL)",
+                                size = 24),
+                fig.lab.pos = "top")
+
 ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)
+
+test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness*Type | Angle, at = list(Angle = c(pi/2))))
 

### 2024-03-13 Fish Data Analysis/Paper_Figures.qmd
Edits for paper

--- 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
@@
 my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
-                       c("No Ablation, Light", "Ablated, Dark"), 
                        c("Ablated, Light", "No Ablation, Dark"),
@@
 
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"), c("Ablated, Light", "Ablated, Dark"))
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"),
+                       #c("No Ablation, Light", "Ablated, Dark"),
+                       c("Ablated, Light", "No Ablation, Dark"))
 
@@
   theme(legend.position = "none") +
-  #ylim(0,2.5)+
+  #ylim(0,5)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 
-my_comparisons <- list()
+my_comparisons <- list(c("No Ablation, Light","Ablated, Dark"),
+                       c("Ablated, Light","Ablated, Dark"),
+                       c("No Ablation, Dark","Ablated, Dark"))
 
@@
   theme(legend.position = "none") +
-  ylim(0,1.15)+
+  #ylim(0,2)+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
-
-polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-Anova(polar_glm_still, test.statistic="F")
-
-polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-Anova(polar_glm_flow, test.statistic="F")
 ```
@@
 ```{r}
-my_comparisons <- list()
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"),
+                       c("No Ablation, Dark", "Ablated, Dark"))
 
@@
 
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"))
 
@@
 emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
-
-speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
-Anova(speed_glm_still, test.statistic="F")
-
-speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-Anova(speed_glm_flow, test.statistic="F")
 ```

### 2024-03-13 Fish Data Analysis/Results_Text.qmd
Edits for paper

@@
 
+plot(nnd_lmer_still)
+qqnorm(resid(nnd_lmer_still))
+qqline(resid(nnd_lmer_still))
+
 nnd_lmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
 nnd_f_aov_me <- Anova(nnd_lmer_flow)
+
+plot(nnd_lmer_flow)
+qqnorm(resid(nnd_lmer_flow))
+qqline(resid(nnd_lmer_flow))
 
@@
 
+plot(polar_lmer_still)
+qqnorm(resid(polar_lmer_still))
+qqline(resid(polar_lmer_still))
+
 polar_lmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
 polar_f_aov_me <- Anova(polar_lmer_flow)
+
+plot(polar_lmer_flow)
+qqnorm(resid(polar_lmer_flow))
+qqline(resid(polar_lmer_flow))
 
@@
 
+plot(speed_lmer_still)
+qqnorm(resid(speed_lmer_still))
+qqline(resid(speed_lmer_still))
+
 speed_lmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
@@
 
-groups_lmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+plot(speed_lmer_flow)
+qqnorm(resid(speed_lmer_flow))
+qqline(resid(speed_lmer_flow))
+
+groups_lmer_still <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"),
+                           family = poisson)
 groups_s_aov_me <- Anova(groups_lmer_still)
 
-groups_lmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+plot(groups_lmer_still)
+qqnorm(resid(groups_lmer_still))
+qqline(resid(groups_lmer_still))
+
+groups_lmer_flow <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+                           family = poisson)
 groups_f_aov_me <- Anova(groups_lmer_flow)
+
+plot(groups_lmer_flow)
+qqnorm(resid(groups_lmer_flow))
+qqline(resid(groups_lmer_flow))
 
@@
 
-heading_PS_model_close <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
+heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                    data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
@@
 
+plot(heading_PS_model_close)
+qqnorm(resid(heading_PS_model_close))
+qqline(resid(heading_PS_model_close))
+
 test(emmeans(heading_PS_model_close, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
 
-heading_PS_model_far <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
+heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
                    data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
 aov_heading_PS_model_far <- Anova(heading_PS_model_far)
+
+plot(heading_PS_model_far)
+qqnorm(resid(heading_PS_model_far))
+qqline(resid(heading_PS_model_far))
 

### 2024-03-13 Fish Data Analysis/Paper_Figures.qmd
Small graph fixes

@@
 my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
+                       c("No Ablation, Light", "Ablated, Dark"),
                        c("Ablated, Light", "No Ablation, Dark"),
@@
 
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"),
-                       #c("No Ablation, Light", "Ablated, Dark"),
-                       c("Ablated, Light", "No Ablation, Dark"))
+my_comparisons <- list(c("Ablated, Light", "No Ablation, Dark"))
 
@@
   theme(legend.position = "none") +
-  #ylim(0,1.15)+
+  ylim(0,1)+
+  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 
-my_comparisons <- list(c("No Ablation, Light","Ablated, Dark"),
-                       c("Ablated, Light","Ablated, Dark"),
-                       c("No Ablation, Dark","Ablated, Dark"))
+my_comparisons <- list()
 
@@
   theme(legend.position = "none") +
-  #ylim(0,2)+
+  ylim(0,1)+
+  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
@@
 ```{r}
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"),
-                       c("No Ablation, Dark", "Ablated, Dark"))
+my_comparisons <- list()
 
@@
 
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"))
+my_comparisons <- list()
 
@@
 ```{r}
-group_sum_data <- school_data %>% group_by(Flow, Ablation, Darkness, Groups) %>%
+group_sum_data <- school_data %>% filter(Groups > 0) %>% group_by(Flow, Ablation, Darkness, Groups) %>%
                             summarise(count = n()) %>%

### 2024-03-13 3D_data_files_to_csv_4P.py

@@ -897,7 +897,7 @@ class school_comps:
         self.calc_school_polarization()
         self.calc_nnd()
         self.calc_tailbeat_cor()
-        #self.calc_school_area()
+        self.calc_school_area()
 
         #self.calc_school_groups_all_points_diff_xy_z()
         self.calc_school_groups_all_points()
@@ -928,26 +928,32 @@ class school_comps:
         self.school_center_z = savgol_filter(self.school_center_z,31,1)
 
     def calc_school_speed(self):
-        #Based on the movement of the center of the school, not the mean of all the fish speeds
+        # #Based on the movement of the center of the school, not the mean of all the fish speeds
 
-        #First we get the next points for the group
-        group_x_next = np.roll(self.school_center_x, -1)
-        group_y_next = np.roll(self.school_center_y, -1)
-        group_z_next = np.roll(self.school_center_z, -1)
+        # #First we get the next points for the group
+        # group_x_next = np.roll(self.school_center_x, -1)
+        # group_y_next = np.roll(self.school_center_y, -1)
+        # group_z_next = np.roll(self.school_center_z, -1)
 
-        #Then we create a vector of the future point minus the last one
-        vec_x = group_x_next - self.school_center_x
-        vec_y = group_y_next - self.school_center_y
-        vec_z = group_z_next - self.school_center_z
+        # #Then we create a vector of the future point minus the last one
+        # vec_x = group_x_next - self.school_center_x
+        # vec_y = group_y_next - self.school_center_y
+        # vec_z = group_z_next - self.school_center_z
 
-        #Then we add the flow to the x value
-        #Since (0,0) is in the upper left a positive vec_x value value means it is moving downstream
-        #so I should subtract the flow value 
-        #The flow value is mutliplied by the fish length since the vec_x values are in pixels, but it is in BLS so divide by fps
-        vec_x_flow = vec_x - (self.flow)/fps
+        # #Then we add the flow to the x value
+        # #Since (0,0) is in the upper left a positive vec_x value value means it is moving downstream
+        # #so I should subtract the flow value 
[…]

### 2024-03-13 Fish Data Analysis/NN_Accel_Heading.qmd
Added single fish to processing and graphs. Also made it an angle ring

--- 2024-03-11 Fish Data Analysis/NN_Accel_Heading.qmd
@@
 library(viridis)
+library(lme4)
+
 ```
@@
 round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
-ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}
+
+deg_ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}
+rad_ang_mean <- function(x){atan2(mean(sin(x)),mean(cos(x)))}
 
@@
 
+single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "S", "Single","Jingle")) %>%
+                           mutate(Darkness = ifelse(Darkness == "S", "Single","Jingle")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           # ### Used to remove every third point to reduce autocorrelation
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
+                           group_by(Comp_ID) %>%
+                           filter(row_number() %% 3 == 1) %>%
+                           ungroup()
+
+single_comp_data <- na.omit(single_comp_data)
+
 fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
+                           # ### Used to remove every third point to reduce autocorrelation
+                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
+                           group_by(Comp_ID) %>%
+                           filter(row_number() %% 3 == 1) %>%
+                           ungroup()
 
@@
 
-min_dist <- 0
-max_dist <- 0.75
+fish_comp_data <- rbind(fish_comp_data,single_comp_data)
 
-fish_data_nn <- fish_comp_data %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
-                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
-                                           nndDistance = nth_min(Distance, 1),
-                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
-                                           all_nas = all(is.na(nndDistance))) %>%
-                                    #filter(Distance == nndDistance | all_nas) %>%
-                                    mutate(row_n = row_number()) %>%
-                                    #filter(row_n == 1) %>%
-                                    ungroup() %>%
-                                    mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
-                                    filter(Distance >= min_dist & Distance <= max_dist)
+min_dist <- 1
+max_dist <- 3
 
-fish_data_nn_normal <- fish_data_nn %>% group_by(Flow_Ablation_Darkness) %>%
-                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+#calculate average angle to all other fish in that range
+fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
+                                                 group_by(Date,Year,Month,Day,Trial,
+                                                          Flow,Ablation,Darkness,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
+                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
+                                                           #Should be the same number each time
+                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T)) %>%
                                                  ungroup()
 
-nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
+fish_data_nn_normal <- fish_comp_data_ring_angles %>% group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T)) %>%
+                                        ungroup()
+
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Mean_Angle,pi/6)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
@@
                                                           sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          se = sd(Fish1_Yaw_Heading_PS, na.rm = T) / sqrt(n()),
                                                           n = n()) %>%
                                                 ungroup() %>%
-                                                na.omit()
+                                                na.omit() %>%
+                                                group_by(Flow_Ablation_Darkness) %>%
+                                                mutate(se = mean(se)) %>%
+                                                ungroup()
+```
 
-nn_heading_dist_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6), distance_bins = round_any(Distance,0.25)) %>%
-                                                group_by(angle_bins,distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
-                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
-                                                          n = n()) %>%
-                                                ungroup() %>%
-                                                na.omit()
+Load in Single Fish
 
-nn_accel_sum <- fish_data_nn_normal %>% mutate(distance_bins = round_any(Relative_X,0.2)) %>%
-                                                group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-                                                summarise(mean_accel = mean(Fish1_Accel, na.rm = T),
-                                                          sd_accel = sd(Fish1_Accel, na.rm = T),
-                                                          n = n()) %>%
-                                                ungroup() %>%
-                                                na.omit()
-
-```
+Estimating functions
 
@@
 heading_ps_angle_step <- stepAIC(heading_ps_angle_base,
-                                   list(upper = ~ Angle*sin(Angle)*Ablation*Darkness, lower = ~1),
+                                   list(upper = ~ Mean_Angle*sin(Mean_Angle)*Ablation*Darkness, lower = ~1),
                                    direction = "both",
@@
 
-manual_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
+manual_model <- lmer(Fish1_Yaw_Heading_PS ~ sin(Mean_Angle) + sin(Mean_Angle):Ablation + sin(Mean_Angle):Darkness + sin(Mean_Angle):Ablation:Darkness + (1|Date), 
                    data = fish_data_nn_model) 
@@
 #Raw data
-ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
-       aes(x = Angle, y = rad2deg(Fish2_Yaw_Heading_PS), color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point(alpha = 0.1)+
+ggplot(fish_data_nn_model,
+       aes(x = Mean_Angle, y = rad2deg(Fish1_Yaw_Heading_PS), color = interaction(Ablation, Darkness, sep =", ")))+
+  geom_point(alpha = 0.5)+
   facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
-  geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
+  geom_line(aes(y = predict(manual_model)), size = 1)+
   theme_classic() +
@@
   labs(color = "Sensory Conditions")
+
+graph_model_data = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Mean_Angle = angle_bins)
 
@@
   geom_point()+
-  #geom_line()+
-  geom_line(aes(y = rad2deg(predict(manual_model,
-                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
+  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
+  geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
+                  ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
+                  fill = interaction(Ablation, Darkness, sep =", ")),
+              alpha = 0.25, colour = NA)+
   theme_classic() +
-  ylim(-50,50) +
+  ylim(-75,75) +
   xlab("direction of neighbour (degrees)") +
-  ylab("focal fish turning angle (degrees/sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  ylab("focal fish turning angle speed (degrees/sec)") +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
+  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
@@
   labs(color = "Sensory Conditions")+
-  ggtitle(paste0("All Fish From ",min_dist," to ",max_dist))
+  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
+  guides(fill = FALSE)
 
-test(emmeans(manual_model, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
-
-# ggplot(nn_heading_dist_sum %>% filter(Flow == "Still Water"),
-#        aes(x = angle_bins, y = distance_bins, fill = mean_turn))+
-#   facet_wrap(~ Ablation + Darkness)+
-#   scale_fill_viridis(option="turbo",limits = c(-2,2))+
-#   geom_tile()+
-#   scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
-#                      labels = round(unique(nn_heading_sum$angle_bins))) +
-#   coord_polar(start = -pi / 2)+
-#   theme_classic()
+test(emmeans(manual_model, trt.vs.ctrlk ~ Ablation*Darkness | Mean_Angle,
+             at = list(Mean_Angle = c(pi/2))))
 
 ```
-
-Estimating functions
-
-```{r}
-#par 1 = amp
-#par 2 = freq
-#par 3 = phase
-
-min.RSS <- function(data, par) {
-             with(data, sum(par[1]*sin(2*pi/par[2]*Angle+par[3]) - Fish1_Yaw_Heading_PS)^2)
-}
-
-result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
-result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
-result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
-result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))
-
-result_F0LNDN$par
-result_F0LYDN$par
-result_F0LNDY$par
-result_F0LYDY$par
-```
-
-```{r}
-
-accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"))
-accel_lin_lm <- lm(Fish1_Accel ~ Relative_X*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"))
-
-AIC(accel_base_lm,accel_lin_lm) %>% arrange(AIC)
-
-Anova(accel_base_lm)
-
-ggplot(fish_data_nn %>% filter(Flow == "Flowing Water (2 BL/s)"),
-       aes(x = Relative_X, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point(alpha = 0.1)+
-  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
-  geom_smooth(se = F, method = glm, formula = y ~ x)+
-  theme_classic() +
-  xlab("distance from neighbour (BL)") +
-  ylab("focal fish acceleration (BL/s^2)") +
-  #ylim(-0.01, 0.01) +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
-  labs(color = "Sensory Conditions")
-
-ggplot(nn_accel_sum %>% filter(Flow == "Flowing Water (2 BL/s)" & distance_bins < 3),
-       aes(x = distance_bins, y = mean_accel, color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point()+
-  #geom_line(alpha = 0.75) +
-  geom_smooth(se = F, method = glm, formula = y ~ x)+
-  theme_classic() +
-  xlab("distance from neighbour (BL)") +
-  ylab("focal fish acceleration (BL/s^2)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
-  labs(color = "Sensory Conditions")
-
-```
-
-```{r}
-
-# directional_df <- fish_data_nn %>% mutate(round_X = round_any(Relative_X,0.5),
-#                                                     round_Y = round_any(Relative_Y,0.5)) %>%
-#                                                       group_by(round_X,round_Y,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
-#                                                       summarise(mean_accel = mean(Fish1_Accel),
-#                                                                 mean_turn = mean(Fish1_Yaw_Heading_PS),
-#                                                                 n = n()) %>%
-#                                                       ungroup()
-# 
-# ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5 & mean_accel > -0.01 & mean_accel < 0.01),
-#        aes(round_X, round_Y, fill= mean_accel)) + 
-#   geom_tile()+
-#   facet_wrap(~Flow_Ablation_Darkness)+
-#   scale_fill_viridis(option="magma")+
-#   coord_fixed()+
-#   theme_classic()
-# 
-# 
-# ggplot(directional_df %>% filter(Flow == "Still Water" & n > 5),
-#        aes(round_X, round_Y, fill= mean_turn)) + 
-#   geom_tile()+
-#   facet_wrap(~Flow_Ablation_Darkness)+
-#   scale_fill_viridis(option="magma")+
-#   coord_fixed()+
-#   theme_classic()
-
-```

### 2024-03-13 3D_data_files_to_csv_4P.py

@@ -897,7 +897,7 @@ class school_comps:
         self.calc_school_polarization()
         self.calc_nnd()
         self.calc_tailbeat_cor()
-        self.calc_school_area()
+        #self.calc_school_area()
 
         #self.calc_school_groups_all_points_diff_xy_z()
         self.calc_school_groups_all_points()
@@ -1652,7 +1652,7 @@ class trial:
         return(out_data)
 
 
-data_folder = "3D_Finished_Fish_Data_4P_gaps/"
+data_folder = "Single Fish Combiner/Multi Data/"
 
 trials = []
 
@@ -1673,21 +1673,24 @@ print("Creating CSVs...")
 
 for trial in trials:
     if first_trial:
-        fish_sigular_dataframe = trial.return_fish_vals()
+        # fish_sigular_dataframe = trial.return_fish_vals()
         fish_comp_dataframe = trial.return_comp_vals()
-        fish_raw_comp_dataframe = trial.return_raw_comp_vals()
-        fish_school_dataframe = trial.return_school_vals()
+        # fish_raw_comp_dataframe = trial.return_raw_comp_vals()
+        # fish_school_dataframe = trial.return_school_vals()
         first_trial = False
     else:
-        fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
+        # fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
         fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
-        fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
-        fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
+        # fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
+        # fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
 
-fish_sigular_dataframe.to_csv("Fish_Individual_Values_3D.csv")
+# fish_sigular_dataframe.to_csv("Fish_Individual_Values_3D.csv")
+#fish_comp_dataframe.to_csv("Fish_Comp_Values_3D.csv")
+# fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_3D.csv")
[…]

### 2024-03-14 Fish Data Analysis/NN_Accel_Heading.qmd
Single fish in one model
Post chat with Perry

@@
                            mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation  == "S", "Single","Jingle")) %>%
-                           mutate(Darkness = ifelse(Darkness == "S", "Single","Jingle")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
+                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                            mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                            mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
@@
                            filter(row_number() %% 3 == 1) %>%
-                           ungroup()
+                           ungroup() %>% mutate(Type = "Single")
 
@@
                            filter(row_number() %% 3 == 1) %>%
-                           ungroup()
+                           ungroup() %>% mutate(Type = "Eight")
 
@@
 
-min_dist <- 1
-max_dist <- 3
+min_dist <- 3
+max_dist <- 100
 
@@
                                                  group_by(Date,Year,Month,Day,Trial,
-                                                          Flow,Ablation,Darkness,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
+                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
                                                  summarise(Mean_Angle = rad_ang_mean(Angle),
@@
 nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Mean_Angle,pi/6)) %>%
-                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                 summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
@@
   geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
-  geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
-                  ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
-                  fill = interaction(Ablation, Darkness, sep =", ")),
-              alpha = 0.25, colour = NA)+
+  # geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
+  #                 ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
+  #                 fill = interaction(Ablation, Darkness, sep =", ")),
+  #             alpha = 0.25, colour = NA)+
   theme_classic() +
@@
 
+test(emmeans(manual_model, trt.vs.ctrlk ~ Ablation*Darkness | Mean_Angle,
+             at = list(Mean_Angle = c(pi/2))))
+
 ```

### 2024-03-14 Single Fish Combiner/Fish_Combiner.py

@@ -13,7 +13,7 @@ ruler_length_m = 0.181
 header_3 = list(range(3))
 header_4 = list(range(4))
 
-data_folders = ["Good Single Fish/light/still/"]
+data_folders = ["Good Single Fish/light/still/","Good Single Fish/dark/still/","Good Single Fish/ablation/still/"]
 
 for data_folder in data_folders:
 
@@ -35,7 +35,7 @@ for data_folder in data_folders:
         all_data_arr = [pd.read_csv(data_folder+f, index_col=0, header=header_3) for f in data_files]
 
         date = data_files[0][0:10]
-        conds = "LS_DS_F0" #data_files[0][14:22]
+        conds = data_files[0][14:22]
 
         #Store and reset the file numbers
         file_numbers = []

### 2024-03-14 Fish Data Analysis/NN_Accel_Heading.qmd
Playing around with using SD as limits

@@
                            mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
-                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "Jingle")) %>%
+                           mutate(Darkness = ifelse(Darkness == "S", "Single", "Jingle")) %>%
                            mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
                            mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
@@
 
-min_dist <- 3
-max_dist <- 100
+sd <- 1.77
+
+min_dist <- sd*0.5
+max_dist <- sd*1.5
 
@@
   theme_classic() +
-  ylim(-75,75) +
+  ylim(-100,100) +
   xlab("direction of neighbour (degrees)") +

### 2024-03-15 Fish Data Analysis/NN_Accel_Heading.qmd
Single fish plotting works

@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           # ### Used to remove every third point to reduce autocorrelation
+                           # # ### Used to remove every third point to reduce autocorrelation
                            mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
@@
                            group_by(Comp_ID) %>%
-                           filter(row_number() %% 3 == 1) %>%
-                           ungroup() %>% mutate(Type = "Single")
+                           #filter(row_number() %% 3 == 1) %>%
+                           ungroup() %>%
+                           mutate(Type = "Single")
 
@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           # ### Used to remove every third point to reduce autocorrelation
+                           ### Used to remove every third point to reduce autocorrelation
                            mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
@@
                            group_by(Comp_ID) %>%
-                           filter(row_number() %% 3 == 1) %>%
-                           ungroup() %>% mutate(Type = "Eight")
+                           #filter(row_number() %% 3 == 1) %>%
+                           ungroup() %>%
+                           mutate(Type = "Eight")
 
@@
 
+ggplot(fish_comp_data, aes(x = Angle))+
+  geom_histogram()+
+  facet_wrap(~Flow_Ablation_Darkness)
+
 sd <- 1.77
 
-min_dist <- sd*0.5
-max_dist <- sd*1.5
+min_dist <- 0.75 #sd*0.5
+max_dist <- 3 #sd*1.5
 
@@
 ```
+
+Distribution of turning velocities at say 90 degrees
+just make a Kolmogorov–Smirnov to compare distribution. See if distribution is different
+  Not larger or smaller?
+Also maybe just do a t test 
+trim the edge points
+
+too much variance, not significant
 
@@
   geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
-  # geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
-  #                 ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
-  #                 fill = interaction(Ablation, Darkness, sep =", ")),
-  #             alpha = 0.25, colour = NA)+
+  geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
+                  ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
+                  fill = interaction(Ablation, Darkness, sep =", ")),
+              alpha = 0.25, colour = NA)+
   theme_classic() +
@@
 
+plot(manual_model)
+qqnorm(resid(manual_model))
+#qqline(resid(groups_lmer_flow))
+
 ```
+
+Removing underlying variation to the data?
+
+```{r}
+
+tank_data <- fish_comp_data %>% filter(Flow == "Still Water") %>% 
+                                mutate(Round_X = round_any(Fish1_X,1),
+                                       Round_Y = round_any(Fish1_Y,1)) %>%
+                                group_by(Flow_Ablation_Darkness, Round_X, Round_Y) %>%
+                                summarise(Mean_HPS = mean(Fish1_Yaw_Heading_PS)) %>%
+                                ungroup()
+
+ggplot(tank_data , aes(Round_X, Round_Y, fill = Mean_HPS))+
+  facet_wrap(~ Flow_Ablation_Darkness)+
+  geom_tile()+
+  theme_classic()
+
+```

### 2024-03-15 Fish Data Analysis/NN_Accel_Heading.qmd
Working on subset of angles

@@
 
-single_comp_data <- na.omit(single_comp_data)
-
 fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
@@
 
-fish_comp_data <- na.omit(fish_comp_data)
-
 fish_comp_data <- rbind(fish_comp_data,single_comp_data)
@@
 
-min_dist <- 0.75 #sd*0.5
-max_dist <- 3 #sd*1.5
+min_dist <- 3 #sd*0.5
+max_dist <- 100 #sd*1.5
 
@@
 Estimating functions
+
+Kolmogorov–Smirnov around 90 degrees
+
+```{r}
+
+perp_angle_df <- fish_comp_data %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105)) %>% filter(Distance >= 2 & Distance <= 100) %>% filter(Flow == "Still Water")
+
+single_fish_df <- perp_angle_df %>% filter(Darkness == "Single" & Ablation == "Single")
+LNDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "No Ablation")
+LYDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "Ablated")
+LNDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "No Ablation")
+LYDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "Ablated")
+
+LNDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDN_fish_df$Fish1_Yaw_Heading_PS)
+LYDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDN_fish_df$Fish1_Yaw_Heading_PS)
+LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDY_fish_df$Fish1_Yaw_Heading_PS)
+LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDY_fish_df$Fish1_Yaw_Heading_PS)
+
+p.adjust(c(LNDN_KS$p.value,LYDN_KS$p.value,LNDY_KS$p.value,LNDY_KS$p.value))
+
+# perp_model <- aov(Fish1_Yaw_Heading_PS ~ Darkness*Ablation, data = perp_angle_df)
+# Anova(perp_model)
+# TukeyHSD(perp_model)
+
+ggplot(perp_angle_df, aes(x = Flow_Ablation_Darkness, y = Fish1_Yaw_Heading_PS,
+                          fill = Flow_Ablation_Darkness, color = Flow_Ablation_Darkness))+
+  stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
+  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
+  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
+  theme_classic()+
+  ggtitle("Heading per Second, 2 to 100 BL, 75 to 100 Degrees")
+
+```
 

### 2024-03-15 Single Fish Combiner/Fish_Combiner.py

@@ -13,7 +13,7 @@ ruler_length_m = 0.181
 header_3 = list(range(3))
 header_4 = list(range(4))
 
-data_folders = ["Good Single Fish/light/still/","Good Single Fish/dark/still/","Good Single Fish/ablation/still/"]
+data_folders = ["Good Single Fish/light/still/"] #,"Good Single Fish/dark/still/","Good Single Fish/ablation/still/"]
 
 for data_folder in data_folders:
 
@@ -30,12 +30,12 @@ for data_folder in data_folders:
 
     # The smallest number of data files for a condition is 13, which still gives us 1287 combinations for that 
     # Match number of trials to real data
-    for x in range(10):
+    for x in range(5):
         shuffle(data_files)
         all_data_arr = [pd.read_csv(data_folder+f, index_col=0, header=header_3) for f in data_files]
 
         date = data_files[0][0:10]
-        conds = data_files[0][14:22]
+        conds = "LS_DS_F0" #data_files[0][14:22]
 
         #Store and reset the file numbers
         file_numbers = []

### 2024-03-18 Fish Data Analysis/Paper_Figures.qmd
Changed graph text, removed parallax figure

@@
   xlab("") +
-  ylab("Speed (BL/s)") +
+  ylab("Mean Speed of Fish (BL/s)") +
   theme_light()+ 
@@
 ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 17)
-```
-
-Parallax
-
-```{r}
-para_vals <- read.csv("Data/Parallax_Distances.csv") %>% mutate(BLs = Distance / 200)
-
-breaks <- c("0.1")
-
-para_plot <- ggplot(para_vals, aes(X, Y, z = BLs))+
-  geom_contour_filled(bins = 5)+
-  scale_fill_viridis_d("Projection Error (BL)", 
-                       labels = c("< 0.1", "0.1 - 0.2", "0.2 - 0.3","0.3 - 0.4","0.4 - 0.5"))+
-  theme_classic()+
-  coord_fixed() +
-  ylab("Vertical Distance from Principal Point (pixels)")+
-  xlab("Hoizontal Distance from Principal Point (pixels)")+ 
-  theme(text = element_text(size = 20))
-
-ggsave("Paper Figures/parallax_model.png", para_plot, width = 14, height = 7)
 ```

### 2024-03-19 Fish Data Analysis/NN_Accel_Heading.qmd
Working through single fish normalization

@@
 library(lme4)
-
 ```
@@
 deg2rad <- function(deg) {(deg * pi) / (180)}
-round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
+round_any <- function(x, accuracy, f=round){f(x / accuracy) * accuracy}
 
@@
 
-fish_comp_data <- rbind(fish_comp_data,single_comp_data)
+#fish_comp_data <- rbind(fish_comp_data,single_comp_data)
 
@@
 
-min_dist <- 3 #sd*0.5
-max_dist <- 100 #sd*1.5
+min_dist <- 0.5 #sd*0.5
+max_dist <- 3 #sd*1.5
+
+offset <- 1.5
+
+top_edge <- 3 - offset 
+bottom_edge <- 0# + offset
+left_edge <- 0 + offset
+right_edge <- 7 - offset
 
@@
 
-perp_angle_df <- fish_comp_data %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105)) %>% filter(Distance >= 2 & Distance <= 100) %>% filter(Flow == "Still Water")
+perp_angle_df <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(80) & Mean_Angle <= deg2rad(100)) %>% filter(Flow == "Still Water")#%>% filter(Distance >= 0 & Distance <= 3) %>% filter(Flow == "Still Water")
 
-single_fish_df <- perp_angle_df %>% filter(Darkness == "Single" & Ablation == "Single")
+perp_angle_df_neg <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(-100) & Mean_Angle <= deg2rad(-80)) %>% filter(Flow == "Still Water") %>% mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
+
+perp_angle_df <- rbind(perp_angle_df,perp_angle_df_neg)
+
+perp_angle_df <- perp_angle_df %>% group_by(Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
+                                                mutate(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                       sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                       n = n()) %>%
+                                                ungroup()
+
+#single_fish_df <- perp_angle_df %>% filter(Darkness == "Single" & Ablation == "Single")
 LNDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "No Ablation")
@@
 
-LNDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDN_fish_df$Fish1_Yaw_Heading_PS)
-LYDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDN_fish_df$Fish1_Yaw_Heading_PS)
-LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDY_fish_df$Fish1_Yaw_Heading_PS)
-LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDY_fish_df$Fish1_Yaw_Heading_PS)
+# LNDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDN_fish_df$Fish1_Yaw_Heading_PS)
+# LYDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDN_fish_df$Fish1_Yaw_Heading_PS)
+# LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDY_fish_df$Fish1_Yaw_Heading_PS)
+# LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDY_fish_df$Fish1_Yaw_Heading_PS)
 
-p.adjust(c(LNDN_KS$p.value,LYDN_KS$p.value,LNDY_KS$p.value,LNDY_KS$p.value))
+#p.adjust(c(LNDN_KS$p.value,LYDN_KS$p.value,LNDY_KS$p.value,LNDY_KS$p.value))
 
-# perp_model <- aov(Fish1_Yaw_Heading_PS ~ Darkness*Ablation, data = perp_angle_df)
-# Anova(perp_model)
-# TukeyHSD(perp_model)
+perp_model <- aov(Fish1_Yaw_Heading_PS ~ Darkness*Ablation, data = perp_angle_df)
+Anova(perp_model)
+qqnorm(resid(perp_model))
+TukeyHSD(perp_model)
 
-ggplot(perp_angle_df, aes(x = Flow_Ablation_Darkness, y = Fish1_Yaw_Heading_PS,
-                          fill = Flow_Ablation_Darkness, color = Flow_Ablation_Darkness))+
+ggplot(perp_angle_df, aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
+                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
   stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
-  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
-  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
+  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
+  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
   theme_classic()+
-  ggtitle("Heading per Second, 2 to 100 BL, 75 to 100 Degrees")
+  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+
+  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color))
 
@@
                                        mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
-                                              DarknessCat = ifelse(Darkness == "Dark",1,0))
+                                              DarknessCat = ifelse(Darkness == "Dark",1,0)) %>% na.omit()
 
@@
 ```
+
+When are single fish flat?
+```{r}
+
+offset <- 2
+
+top_edge <- 3 - offset 
+bottom_edge <- 0# + offset
+left_edge <- 0 + offset
+right_edge <- 7 - offset
+
+#calculate average angle to all other fish in that range
+single_fish_mean_angles <- single_comp_data %>%   #filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light") %>%
+                                                filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
+                                                filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge) %>%
+                                                #filter(Distance >= min_dist & Distance <= max_dist) %>%
+                                                group_by(Date,Year,Month,Day,Trial,
+                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
+                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
+                                                           #Should be the same number each time
+                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T),
+                                                           Fish1_X = mean(Fish1_X, rm.na = T),
+                                                           Fish1_Y = mean(Fish1_Y, rm.na = T)) %>%
+                                                 ungroup() %>%
+                                                 #normalize
+                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))
+
+single_flat_lm <- lm(Fish1_Yaw_Heading_PS ~ 1, data = single_fish_mean_angles)
+single_lin_lm <- lm(Fish1_Yaw_Heading_PS ~ Mean_Angle, data = single_fish_mean_angles)
+single_sin_lm <- lm(Fish1_Yaw_Heading_PS ~ sin(Mean_Angle), data = single_fish_mean_angles)
+
+AIC(single_flat_lm,single_lin_lm,single_sin_lm) %>% arrange(AIC)
+
+single_perp_angle_df <- single_fish_mean_angles %>% filter(Mean_Angle >= deg2rad(80) & Mean_Angle <= deg2rad(100)) %>% filter(Flow == "Still Water")
+
+single_perp_angle_df_neg <- single_fish_mean_angles %>% filter(Mean_Angle >= deg2rad(-100) & Mean_Angle <= deg2rad(-80)) %>% filter(Flow == "Still Water") %>% mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
+
+single_perp_angle_df <- rbind(single_perp_angle_df,single_perp_angle_df)
+
+t.test(single_perp_angle_df$Fish1_Yaw_Heading_PS)
+
+effect_size <- mean(single_perp_angle_df$Fish1_Yaw_Heading_PS) / sd(single_perp_angle_df$Fish1_Yaw_Heading_PS)
+
+ggplot(single_perp_angle_df, aes(x = Fish1_Yaw_Heading_PS))+
+  geom_histogram(color = "black", fill = "red")+
+  theme_classic()
+
+ggplot(single_fish_mean_angles, aes(x = Mean_Angle, y = Fish1_Yaw_Heading_PS))+
+  geom_point(color = "red")+
+  # geom_smooth(method = "glm", formula = y ~ 1, color = "black")+
+  # geom_smooth(method = "glm", formula = y ~ x, color = "green")+
+  # geom_smooth(method = "glm", formula = y ~ sin(x), color = "blue")+
+  theme_classic()
+
+single_fish_mean_angles_heatmap <- single_fish_mean_angles %>% mutate(RoundX = round_any(Fish1_X, -0.5),
+                                                                      RoundY = round_any(Fish1_Y, -0.5)) %>%
+                                                               group_by(RoundX,RoundY) %>%
+                                                               summarise(mean_turn = mean(Mean_Angle)) %>%
+                                                               ungroup()
+
+ggplot(single_fish_mean_angles_heatmap, aes(x = RoundX, y = RoundY, fill = mean_turn))+
+  geom_tile()+
+  coord_equal()+
+  scale_fill_gradient2(low = "blue", mid = "white", high = "red")+
+  theme_classic()
+
+```

### 2024-03-19 Single Fish Combiner/Fish_Combiner.py

@@ -13,7 +13,7 @@ ruler_length_m = 0.181
 header_3 = list(range(3))
 header_4 = list(range(4))
 
-data_folders = ["Good Single Fish/light/still/"] #,"Good Single Fish/dark/still/","Good Single Fish/ablation/still/"]
+data_folders = ["Good Single Fish/light/still/"] #["Good Single Fish/light/still/"] #,"Good Single Fish/dark/still/","Good Single Fish/ablation/still/"]
 
 for data_folder in data_folders:
 

### 2024-03-19 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before merge

@@
 
+x_offset <- 1.5
+y_offset <- 0.75
+
+max_x <- ceiling(max(fish_comp_data$Fish1_X)) - 1.5
+min_x <- floor(min(fish_comp_data$Fish1_X)) - 1.5
+max_y <- ceiling(max(fish_comp_data$Fish1_Y)) - 0.75
+min_y <- floor(max(fish_comp_data$Fish1_Y)) - 0.75
+
+#Limit away from the edge
+fish_comp_data <- fish_comp_data %>% filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
+                                     filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge)
+
 ggplot(fish_comp_data, aes(x = Angle))+
@@
 min_dist <- 0.5 #sd*0.5
-max_dist <- 3 #sd*1.5
-
-offset <- 1.5
-
-top_edge <- 3 - offset 
-bottom_edge <- 0# + offset
-left_edge <- 0 + offset
-right_edge <- 7 - offset
+max_dist <- 2 #sd*1.5
 
@@
 fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
+                                                 #mutate(Mean_Angle = Angle)
                                                  group_by(Date,Year,Month,Day,Trial,
@@
                           fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
-  stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
+  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
   geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
@@
   scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
-  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color))
+  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  theme(legend.position = "none")+
+  xlab("")+
+  ylab("Turning Angle (Degrees / s)")
 
@@
 
-offset <- 2
+x_offset <- 1.5
+y_offset <- 0.75
 
-top_edge <- 3 - offset 
-bottom_edge <- 0# + offset
-left_edge <- 0 + offset
-right_edge <- 7 - offset
+top_edge <- 3 - y_offset 
+bottom_edge <- 0 + y_offset
+left_edge <- 0 + x_offset
+right_edge <- 7 - x_offset
 
@@
                                                           Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
-                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
-                                                           #Should be the same number each time
-                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T),
-                                                           Fish1_X = mean(Fish1_X, rm.na = T),
-                                                           Fish1_Y = mean(Fish1_Y, rm.na = T)) %>%
+                                                 # summarise(Mean_Angle = rad_ang_mean(Angle),
+                                                 #           #Should be the same number each time
+                                                 #           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T),
+                                                 #           Fish1_X = mean(Fish1_X, rm.na = T),
+                                                 #           Fish1_Y = mean(Fish1_Y, rm.na = T)) %>%
                                                  ungroup() %>%
                                                  #normalize
-                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))
+                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                        Mean_Angle = Angle)
 
@@
 
-single_perp_angle_df <- rbind(single_perp_angle_df,single_perp_angle_df)
+single_perp_angle_df <- rbind(single_perp_angle_df,single_perp_angle_df_neg)
 
@@
 effect_size <- mean(single_perp_angle_df$Fish1_Yaw_Heading_PS) / sd(single_perp_angle_df$Fish1_Yaw_Heading_PS)
+effect_size
 
 ggplot(single_perp_angle_df, aes(x = Fish1_Yaw_Heading_PS))+
-  geom_histogram(color = "black", fill = "red")+
+  geom_histogram(color = "black", fill = "red", binwidth = 1)+
   theme_classic()
@@
   # geom_smooth(method = "glm", formula = y ~ x, color = "green")+
-  # geom_smooth(method = "glm", formula = y ~ sin(x), color = "blue")+
+  geom_smooth(method = "glm", formula = y ~ sin(x), color = "blue")+
   theme_classic()
 
-single_fish_mean_angles_heatmap <- single_fish_mean_angles %>% mutate(RoundX = round_any(Fish1_X, -0.5),
-                                                                      RoundY = round_any(Fish1_Y, -0.5)) %>%
+single_fish_mean_angles_heatmap <- single_fish_mean_angles %>% mutate(RoundX = round_any(Fish1_X, 0.5),
+                                                                      RoundY = round_any(Fish1_Y, 0.5)) %>%
                                                                group_by(RoundX,RoundY) %>%
-                                                               summarise(mean_turn = mean(Mean_Angle)) %>%
+                                                               summarise(mean_turn = mean(Mean_Angle),
+                                                                         n = n()) %>%
                                                                ungroup()
@@
 
+possible_offsets <- expand_grid(x = seq(0,2,0.25), y = seq(0,1.25,0.25))
+
+offset_return <- function(x,y){
+  te <- 3 - y 
+  be <- 0 + y
+  le <- 0 + x
+  re <- 7 - x
+
+  tester_data <- single_comp_data %>%  filter(Fish1_X >= le & Fish1_X <= re) %>%
+                                        filter(Fish1_Y >= be & Fish1_Y <= te) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))
+
+  tester_perp_df <- tester_data %>% filter(Angle >= deg2rad(80) & Angle <= deg2rad(100)) %>%
+                                                      filter(Flow == "Still Water")
+
+  tester_perp_df_neg <- tester_data %>% filter(Angle >= deg2rad(-100) & Angle <= deg2rad(-80)) %>% 
+                                                        filter(Flow == "Still Water") %>% 
+                                                        mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
+
+  tester_perp_df <- rbind(tester_perp_df,tester_perp_df_neg)
+
+  t_test_out <- t.test(tester_perp_df$Fish1_Yaw_Heading_PS)
+
+  return(t_test_out$p.val)
+}
+
+for(x in seq(0,2,0.25)){
+  for (y in seq(0,1.25,0.25)) {
+    print(paste(x,y))
+    print(offset_return(x,y))
+  }
+}
+
 ```

### 2024-03-19 Single Fish Combiner/Fish_Combiner.py

@@ -30,7 +30,7 @@ for data_folder in data_folders:
 
     # The smallest number of data files for a condition is 13, which still gives us 1287 combinations for that 
     # Match number of trials to real data
-    for x in range(5):
+    for x in range(10):
         shuffle(data_files)
         all_data_arr = [pd.read_csv(data_folder+f, index_col=0, header=header_3) for f in data_files]
 

### 2024-03-19 Fish Data Analysis/Paper_Figures.qmd

@@
 heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
-       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
+       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ", line = Type)))+
   geom_point(size = 3)+
@@
   ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
@@
   ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
   scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
@@
 ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)
+
+test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness*Type | Angle, at = list(Angle = c(pi/2))))
 

### 2024-03-19 Fish Data Analysis/Paper_Figures.qmd
Single Fish example made

@@
 text_size = 16
+
+# for turning data
+x_offset <- 1.95
+y_offset <- 1.15
 ```
@@
 ```
+
+Single Fish Figure
+
+```{r}
+
+single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
+                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
+                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "Jingle")) %>%
+                           mutate(Darkness = ifelse(Darkness == "S", "Single", "Jingle")) %>%
+                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
+                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
+                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
+                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
+                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
+                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
+                           mutate(Type = "Single")
+
+top_edge <- ceiling(max(single_comp_data$Fish1_Y)) - y_offset 
+bottom_edge <- floor(min(single_comp_data$Fish1_Y)) + y_offset
+left_edge <- floor(min(single_comp_data$Fish1_X)) + x_offset
+right_edge <- ceiling(max(single_comp_data$Fish1_X)) - x_offset
+
+single_fish_mean_angles_middle <- single_comp_data %>% filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
+                                                filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge) %>%
+                                                 #normalize
+                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))
+
+#Combine -75 to -105 with 75 to 105
+single_perp_angle_df_middle <- single_fish_mean_angles_middle %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105))
+single_perp_angle_df_neg_middle <- single_fish_mean_angles_middle %>% filter(Angle >= deg2rad(-105) & Angle <= deg2rad(-75)) %>%
+                                                                 mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
+single_perp_angle_df_middle <- rbind(single_perp_angle_df_middle,single_perp_angle_df_neg_middle) %>% mutate(Label = "Edges Removed")
+
+single_fish_mean_angles_all <- single_comp_data %>% mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))
+
+single_perp_angle_df_all <- single_fish_mean_angles_all %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105))
+single_perp_angle_df_neg_all <- single_fish_mean_angles_all %>% filter(Angle >= deg2rad(-105) & Angle <= deg2rad(-75)) %>%
+                                                                mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
+single_perp_angle_df_all <- rbind(single_perp_angle_df_all,single_perp_angle_df_neg_all) %>% mutate(Label = "All Data")
+
+single_perp_angle_graphing <- rbind(single_perp_angle_df_middle,single_perp_angle_df_all)
+
+t.test(single_perp_angle_df_middle$Fish1_Yaw_Heading_PS)
+
+single_plot <- ggplot(single_perp_angle_graphing, aes(x = Fish1_Yaw_Heading_PS, fill = Label))+
+  geom_histogram(aes(y=0.5*..density..),binwidth=1,position='identity', alpha = 0.5)+
+  theme_classic()+
+  scale_fill_manual(values = c("#CE2414","#138EC2"))+
+  ylab("Proportion of Values")+
+  xlab("Turning Angle (Degrees / s)")+
+  xlim(-5,5)
+
+single_plot
+
+ggsave("Paper Figures/Edge_Removal_Single_Fish.png", single_plot, width = 7, height = 7)
+
+```

### 2024-03-19 Fish Data Analysis/NN_Accel_Heading.qmd
Commit with final graphs

@@
 
-x_offset <- 1.5
-y_offset <- 0.75
+x_offset <- 1.95
+y_offset <- 1.15
 
-max_x <- ceiling(max(fish_comp_data$Fish1_X)) - 1.5
-min_x <- floor(min(fish_comp_data$Fish1_X)) - 1.5
-max_y <- ceiling(max(fish_comp_data$Fish1_Y)) - 0.75
-min_y <- floor(max(fish_comp_data$Fish1_Y)) - 0.75
+max_x <- ceiling(max(fish_comp_data$Fish1_X, na.rm = T)) - 1.5
+min_x <- floor(min(fish_comp_data$Fish1_X, na.rm = T)) - 1.5
+max_y <- ceiling(max(fish_comp_data$Fish1_Y, na.rm = T)) - 0.75
+min_y <- floor(max(fish_comp_data$Fish1_Y, na.rm = T)) - 0.75
 
 #Limit away from the edge
-fish_comp_data <- fish_comp_data %>% filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
-                                     filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge)
+fish_comp_data <- fish_comp_data %>% filter(Fish1_X >= min_x & Fish1_X <= max_x) %>%
+                                     filter(Fish1_Y >= min_y & Fish1_Y <= max_y)
 
@@
 
-min_dist <- 0.5 #sd*0.5
+min_dist <- 0 #sd*0.5
 max_dist <- 2 #sd*1.5
@@
 
-perp_angle_df <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(80) & Mean_Angle <= deg2rad(100)) %>% filter(Flow == "Still Water")#%>% filter(Distance >= 0 & Distance <= 3) %>% filter(Flow == "Still Water")
+perp_angle_df <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(75) & Mean_Angle <= deg2rad(105)) %>% filter(Flow == "Still Water")#%>% filter(Distance >= 0 & Distance <= 3) %>% filter(Flow == "Still Water")
 
-perp_angle_df_neg <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(-100) & Mean_Angle <= deg2rad(-80)) %>% filter(Flow == "Still Water") %>% mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
+perp_angle_df_neg <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(-105) & Mean_Angle <= deg2rad(-75)) %>% filter(Flow == "Still Water") %>% mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
 

### 2024-03-19 Fish Data Analysis/Paper_Figures.qmd
Commit with final graphs

@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           mutate(Type = "Eight") %>%
-
-                           # ### Used to remove every third point to reduce autocorrelation
+                           ### Used to remove every third point to reduce autocorrelation
                            mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
@@
                            group_by(Comp_ID) %>%
-                           filter(row_number() %% 3 == 1) %>%
+                           #filter(row_number() %% 3 == 1) %>%
                            ungroup()
 
-fish_comp_data <- na.omit(fish_comp_data)
+min_x <- floor(min(fish_comp_data$Fish1_X, na.rm = T)) + x_offset
+max_x <- ceiling(max(fish_comp_data$Fish1_X, na.rm = T)) - x_offset
+min_y <- floor(min(fish_comp_data$Fish1_Y, na.rm = T)) + y_offset
+max_y <- ceiling(max(fish_comp_data$Fish1_Y, na.rm = T)) - y_offset
 
-fish_comp_data_single <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
-                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
-                           mutate(Ablation = ifelse(Ablation  == "S", "No Ablation")) %>%
-                           mutate(Darkness = ifelse(Darkness == "S", "Light")) %>%
-                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
-                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
-                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation"))) %>%
-                           mutate(Darkness = fct_relevel(Darkness, c("Light"))) %>%
-                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
-                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           mutate(Type = "Single") %>%
+print(paste(min_x,max_x,min_y,max_y))
 
-                           # ### Used to remove every third point to reduce autocorrelation
-                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
-                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
-                           group_by(Comp_ID) %>%
-                           filter(row_number() %% 3 == 1) %>%
-                           ungroup()
+min_dist <- 0
+middle_dist <- 2.5
+max_dist <- 100
 
-fish_comp_data_single <- na.omit(fish_comp_data_single)
+#Limit away from the edge
+fish_comp_data <- fish_comp_data %>% filter(Fish1_X >= min_x & Fish1_X <= max_x) %>%
+                                     filter(Fish1_Y >= min_y & Fish1_Y <= max_y)
 
-fish_comp_data <- rbind(fish_comp_data,fish_comp_data_single)
+#close
+fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
+                                                 mutate(Dist_Cat = ifelse(Distance <= middle_dist, "Close", "Far")) %>%
+                                                 # group_by(Date,Year,Month,Day,Trial,
+                                                 #          Flow,Ablation,Darkness,Dist_Cat,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
+                                                 # summarise(Mean_Angle = rad_ang_mean(Angle),
+                                                 #           #Should be the same number each time
+                                                 #           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T)) %>%
+                                                 # ungroup()
+                                                   mutate(Mean_Angle = Angle)
 
-close_min_dist <- 0
-close_max_dist <- 3
+fish_data_nn_normal <- fish_comp_data_ring_angles %>% group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T)) %>%
+                                        ungroup() %>% 
+                                        filter(Flow == "Still Water")
 
-far_min_dist <- 3
-far_max_dist <- 100
-
-fish_data_nn_normal_close <- fish_comp_data %>% filter(Distance >= close_min_dist & Distance <= close_max_dist) %>%
-                                        group_by(Flow_Ablation_Darkness) %>%
-                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
-                                        ungroup()
-
-nn_heading_sum_close <- fish_data_nn_normal_close %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
-                                                group_by(angle_bins,Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness) %>%
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Mean_Angle,pi/6)) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Dist_Cat) %>%
                                                 summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
@@
                                                           n = n()) %>%
-                                                ungroup() %>%
-                                                na.omit()
-
-fish_data_nn_normal_far <- fish_comp_data %>% filter(Distance >= far_min_dist & Distance <= far_max_dist) %>%
-                                        group_by(Flow_Ablation_Darkness) %>%
-                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                                 ungroup() 
-
-nn_heading_sum_far <- fish_data_nn_normal_far %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
-                                                group_by(angle_bins,Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness) %>%
-                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
-                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
-                                                          n = n()) %>%
-                                                ungroup() %>%
-                                                na.omit()
 ```
@@
 
-heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
-                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
-Anova(heading_PS_model_close)
+perp_angle_df <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(75) & Mean_Angle <= deg2rad(105))
 
-heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
-                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
-Anova(heading_PS_model_far)
+perp_angle_df_neg <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(-105) & Mean_Angle <= deg2rad(-75)) %>% 
+                                                   mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
 
-heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
-       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ", line = Type)))+
-  geom_point(size = 3)+
-  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
-                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
-                    re.form = NA))), size = 2)+
-  theme_classic() +
-  ylim(-75,75) +
-  xlab("Direction of Neighbour (Degrees)") +
-  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
-  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
-                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
-  labs(color = "Sensory Conditions")+
+perp_angle_df <- rbind(perp_angle_df,perp_angle_df_neg)
+
+perp_angle_df <- perp_angle_df %>% group_by(Flow,Ablation,Darkness,Flow_Ablation_Darkness,Dist_Cat) %>%
+                                                mutate(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                       sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                       n = n()) %>%
+                                                ungroup()
+
+perp_angle_lm_close <- lm(Fish1_Yaw_Heading_PS ~ Ablation*Darkness, data = perp_angle_df %>% filter(Dist_Cat == "Close"))
+Anova(perp_angle_lm_close)
+emmeans(perp_angle_lm_close, specs = pairwise ~ Ablation:Darkness)
+
+my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"),
+                       c("No Ablation, Dark", "Ablated, Dark"))
+
+heading_PS_graph_close <- ggplot(perp_angle_df %>% filter(Dist_Cat == "Close"),
+                                 aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
+                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth*0.375, "npc")) +
+  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
+  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
+  theme_light()+
+  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  theme(legend.position = "none")+
+  xlab("")+
+  ylab("Turning Angle (Degrees / s)")+
+  scale_y_continuous(breaks = seq(-180,180, 60))+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
   theme(axis.text.x = element_text(size = text_size),
         axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
-heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
-       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
-  geom_point(size = 3)+
-  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
-                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
-                    re.form = NA))), size = 2)+
-  theme_classic() +
-  ylim(-75,75) +
-  xlab("Direction of Neighbour (Degrees)") +
-  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
-  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
-  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
-                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
-  labs(color = "Sensory Conditions")+
+perp_angle_lm_far <- lm(Fish1_Yaw_Heading_PS ~ Ablation*Darkness, data = perp_angle_df %>% filter(Dist_Cat == "Far"))
+Anova(perp_angle_lm_far)
+emmeans(perp_angle_lm_far, specs = pairwise ~ Ablation:Darkness)
+
+my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
+                       c("No Ablation, Light", "Ablated, Dark"))
+
+heading_PS_graph_far <- ggplot(perp_angle_df %>% filter(Dist_Cat == "Far"),
+                                 aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
+                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
+  stat_dots(side = "both", binwidth = unit(dot_binwidth*0.375, "npc")) +
+  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
+  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
+  theme_light()+
+  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
+  theme(legend.position = "none")+
+  xlab("")+
+  ylab("Turning Angle (Degrees / s)")+
+  scale_y_continuous(breaks = seq(-180,180, 60))+
+  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
   theme(axis.text.x = element_text(size = text_size),
         axis.text.y = element_text(size = text_size),
-        axis.title.y = element_text(size = text_size))
+        axis.title.y = element_text(size = text_size))+
+  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
 
@@
           labels = c("A", "B"),
-          ncol = 2, nrow = 1, common.legend = TRUE, legend="right")
+          ncol = 2, nrow = 1)
 
@@
 heading_PS_mega_plot <- annotate_figure(heading_PS_mega_plot, 
-                top = text_grob("Near (< 3 BL)                                          Far (> 3 BL)",
-                                size = 24),
-                fig.lab.pos = "top")
+                top = text_grob("Near (< 2.5 BL)                                          Far (> 2.5 BL)",
+                                size = 24))
 
 ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)
-
-test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness*Type | Angle, at = list(Angle = c(pi/2))))
 

### 2024-03-19 Fish Data Analysis/Paper_Figures.qmd
Formatting fixes and table

@@
                            separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
-                           ### Used to remove every third point to reduce autocorrelation
                            mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
@@
                                   Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
-                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
-                           group_by(Comp_ID) %>%
-                           #filter(row_number() %% 3 == 1) %>%
-                           ungroup()
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_"))
 
@@
 fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
-                                                 mutate(Dist_Cat = ifelse(Distance <= middle_dist, "Close", "Far")) %>%
-                                                 # group_by(Date,Year,Month,Day,Trial,
-                                                 #          Flow,Ablation,Darkness,Dist_Cat,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
-                                                 # summarise(Mean_Angle = rad_ang_mean(Angle),
-                                                 #           #Should be the same number each time
-                                                 #           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T)) %>%
-                                                 # ungroup()
-                                                   mutate(Mean_Angle = Angle)
+                                                 mutate(Dist_Cat = ifelse(Distance <= middle_dist, "Close", "Far"))
 
@@
 
-nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Mean_Angle,pi/6)) %>%
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                 group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Dist_Cat) %>%
@@
 
-perp_angle_df <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(75) & Mean_Angle <= deg2rad(105))
+perp_angle_df <- fish_data_nn_normal %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105))
 
-perp_angle_df_neg <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(-105) & Mean_Angle <= deg2rad(-75)) %>% 
+perp_angle_df_neg <- fish_data_nn_normal %>% filter(Angle >= deg2rad(-105) & Angle <= deg2rad(-75)) %>% 
                                                    mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
@@
   geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
+  geom_line(aes(y = rad2deg(mean_turn), group = 1), size = 1, color = "black") +
   geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
@@
   xlab("")+
-  ylab("Turning Angle (Degrees / s)")+
+  ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
   scale_y_continuous(breaks = seq(-180,180, 60))+
@@
   geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
+   geom_line(aes(y = rad2deg(mean_turn), group = 1), size = 1, color = "black") +
   geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
@@
 heading_PS_mega_plot <- annotate_figure(heading_PS_mega_plot, 
-                top = text_grob("Near (< 2.5 BL)                                          Far (> 2.5 BL)",
+                top = text_grob("  Near (< 2.5 BL)                                                Far (> 2.5 BL)",
                                 size = 24))
@@
 
-single_plot <- ggplot(single_perp_angle_graphing, aes(x = Fish1_Yaw_Heading_PS, fill = Label))+
-  geom_histogram(aes(y=0.5*..density..),binwidth=1,position='identity', alpha = 0.5)+
+single_plot <- ggplot(single_perp_angle_graphing, aes(x = rad2deg(Fish1_Yaw_Heading_PS), fill = Label))+
+  geom_histogram(aes(y=0.5*..density..),binwidth=45,position='identity', alpha = 0.5)+
   theme_classic()+
@@
   xlab("Turning Angle (Degrees / s)")+
-  xlim(-5,5)
+  xlim(-200,200)
 

### 2024-03-19 Fish Data Analysis/Results_Text.qmd
Formatting fixes and table

@@
 
-light_no_ab_color = "#d4d7dd"
+light_no_ab_color = "#9C9C9C"   #"#C62E65" #A1BAA4" #"#d4d7dd" 06D6A0
 light_ab_color = "#f5ba9e"
 dark_no_ab_color = "#5e94d4"
+dark_ab_color = "#49A078"   #"#1E4371"
 sim_color = "#777777"
@@
                                   Date = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_")) %>%
+                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
+                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_"))
 
-                            # ### Used to remove every third point to reduce autocorrelation
-                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
-                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
-                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
-                           group_by(Comp_ID) %>%
-                           filter(row_number() %% 3 == 1) %>%
-                           ungroup()
+min_x <- floor(min(fish_comp_data$Fish1_X, na.rm = T)) + x_offset
+max_x <- ceiling(max(fish_comp_data$Fish1_X, na.rm = T)) - x_offset
+min_y <- floor(min(fish_comp_data$Fish1_Y, na.rm = T)) + y_offset
+max_y <- ceiling(max(fish_comp_data$Fish1_Y, na.rm = T)) - y_offset
 
-fish_comp_data <- na.omit(fish_comp_data)
+print(paste(min_x,max_x,min_y,max_y))
 
-close_min_dist <- 0
-close_max_dist <- 3
+min_dist <- 0
+middle_dist <- 2.5
+max_dist <- 100
 
-far_min_dist <- 3
-far_max_dist <- 100
+#Limit away from the edge
+fish_comp_data <- fish_comp_data %>% filter(Fish1_X >= min_x & Fish1_X <= max_x) %>%
+                                     filter(Fish1_Y >= min_y & Fish1_Y <= max_y)
 
-fish_data_nn_normal_close <- fish_comp_data %>% filter(Distance >= close_min_dist & Distance <= close_max_dist) %>%
-                                        group_by(Flow_Ablation_Darkness) %>%
-                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
-                                        ungroup()
+#close
+fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
+                                                 mutate(Dist_Cat = ifelse(Distance <= middle_dist, "Close", "Far"))
 
-fish_data_nn_normal_far <- fish_comp_data %>% filter(Distance >= far_min_dist & Distance <= far_max_dist) %>%
-                                        group_by(Flow_Ablation_Darkness) %>%
-                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
+fish_data_nn_normal <- fish_comp_data_ring_angles %>% group_by(Flow_Ablation_Darkness) %>%
+                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T)) %>%
+                                        ungroup() %>% 
+                                        filter(Flow == "Still Water")
+
+nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
+                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Dist_Cat) %>%
+                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                          n = n()) %>%
                                                 ungroup()
@@
 
-heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
-                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
-aov_heading_PS_model_close <- Anova(heading_PS_model_close)
+perp_angle_df <- fish_data_nn_normal %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105))
 
-plot(heading_PS_model_close)
-qqnorm(resid(heading_PS_model_close))
-qqline(resid(heading_PS_model_close))
+perp_angle_df_neg <- fish_data_nn_normal %>% filter(Angle >= deg2rad(-105) & Angle <= deg2rad(-75)) %>% 
+                                                   mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
 
-test(emmeans(heading_PS_model_close, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
+perp_angle_df <- rbind(perp_angle_df,perp_angle_df_neg)
 
-heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
-                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
-aov_heading_PS_model_far <- Anova(heading_PS_model_far)
+perp_angle_df <- perp_angle_df %>% group_by(Flow,Ablation,Darkness,Flow_Ablation_Darkness,Dist_Cat) %>%
+                                                mutate(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                       sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
+                                                       n = n()) %>%
+                                                ungroup()
 
-plot(heading_PS_model_far)
-qqnorm(resid(heading_PS_model_far))
-qqline(resid(heading_PS_model_far))
+perp_angle_lmer_close <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Close"))
+perp_angle_aov_me_close <- Anova(perp_angle_lmer_close)
 
-test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
+plot(perp_angle_lmer_close)
+qqnorm(resid(perp_angle_lmer_close))
+qqline(resid(perp_angle_lmer_close))
+
+perp_angle_lmer_far <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Far"))
+perp_angle_aov_me_far <- Anova(perp_angle_lmer_far)
+
+plot(perp_angle_lmer_far)
+qqnorm(resid(perp_angle_lmer_far))
+qqline(resid(perp_angle_lmer_far))
 
 turning_school_stats_table <- tibble(
-       Near_or_Far = rep(c(rep("Near",4) , rep("Far",4)), 1),
-       Condition = rep(c("Angle","Angle x Ablation","Angle x Darkness","Angle x Ablation x Darkness"), 2),
-       DF = c(rep(length(heading_PS_model_close@resp$y)-4,4),
-                  rep(length(heading_PS_model_far@resp$y)-4,4)),
-       Chisq = round(c(aov_heading_PS_model_close$Chisq[1:4],aov_heading_PS_model_far$Chisq[1:4]),3),
-       P_Val = round(c(aov_heading_PS_model_close$`Pr(>Chisq)`[1:4],aov_heading_PS_model_far$`Pr(>Chisq)`[1:4]),3),
+       Near_or_Far = rep(c(rep("Near",3) , rep("Far",3)), 1),
+       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 2),
+       DF = c(rep(length(perp_angle_lmer_close@resp$y)-3,3),
+                  rep(length(perp_angle_lmer_far@resp$y)-3,3)),
+       Chisq = round(c(perp_angle_aov_me_close$Chisq[1:3],perp_angle_aov_me_far$Chisq[1:3]),3),
+       P_Val = round(c(perp_angle_aov_me_close$`Pr(>Chisq)`[1:3],perp_angle_aov_me_far$`Pr(>Chisq)`[1:3]),3),
        Is_Sig = P_Val < 0.05)

### 2024-03-20 Fish Data Analysis/Paper_Figures.qmd
Small graph fixes

@@
   ylab("NND Autocorrelation")+
-  xlab("Offest")+
+  xlab("Offset")+
   theme_classic()+ 
@@
   ylab("Polarity Autocorrelation")+
-  xlab("Offest")+
+  xlab("Offset")+
   theme_classic()+ 
@@
   ylab("Speed Autocorrelation")+
-  xlab("Offest")+
+  xlab("Offset")+
   theme_classic()+ 
@@
   ylab("Numebr of Groups Autocorrelation")+
-  xlab("Offest")+
+  xlab("Offset")+
   theme_classic()+ 
@@
 
-single_perp_angle_graphing <- rbind(single_perp_angle_df_middle,single_perp_angle_df_all)
+single_perp_angle_graphing <- rbind(single_perp_angle_df_middle,single_perp_angle_df_all) %>%
+                              mutate(Rounded_Turning = round_any(Fish1_Yaw_Heading_PS, pi/6)) %>%
+                              group_by(Label) %>%
+                              mutate(group_n = n()) %>%
+                              ungroup() %>%
+                              group_by(Label,Rounded_Turning,group_n) %>%
+                              summarise(perc = mean(n()/group_n*100)) %>%
+                              ungroup()
 
+t.test(single_perp_angle_df_all$Fish1_Yaw_Heading_PS)
 t.test(single_perp_angle_df_middle$Fish1_Yaw_Heading_PS)
 
-single_plot <- ggplot(single_perp_angle_graphing, aes(x = rad2deg(Fish1_Yaw_Heading_PS), fill = Label))+
-  geom_histogram(aes(y=0.5*..density..),binwidth=45,position='identity', alpha = 0.5)+
+single_plot <- ggplot(single_perp_angle_graphing, aes(x = rad2deg(Rounded_Turning), y = perc, fill = Label))+
+  #geom_histogram(aes(y=0.5*..density..*100),binwidth=45,position='identity', alpha = 0.5)+
+  geom_col(position='identity',alpha = 0.5)+
   theme_classic()+
   scale_fill_manual(values = c("#CE2414","#138EC2"))+
-  ylab("Proportion of Values")+
-  xlab("Turning Angle (Degrees / s)")+
-  xlim(-200,200)
+  ylab("Percentage of Values")+
+  xlab("Turning Angle Rate (Degrees / s)")+
+  xlim(-200,200)+
+  theme(axis.text.x = element_text(size = text_size),
+        axis.text.y = element_text(size = text_size),
+        axis.title.x = element_text(size = text_size),
+        axis.title.y = element_text(size = text_size))
 

### 2024-03-21 3D_data_files_to_csv_4P.py
Cleaning up Code and Data Folder

@@ -1652,7 +1652,7 @@ class trial:
         return(out_data)
 
 
-data_folder = "Single Fish Combiner/Multi Data/"
+data_folder = "3D_Finished_Fish_Data_4P_gaps/"
 
 trials = []
 
@@ -1673,23 +1673,23 @@ print("Creating CSVs...")
 
 for trial in trials:
     if first_trial:
-        # fish_sigular_dataframe = trial.return_fish_vals()
+        fish_sigular_dataframe = trial.return_fish_vals()
         fish_comp_dataframe = trial.return_comp_vals()
-        # fish_raw_comp_dataframe = trial.return_raw_comp_vals()
-        # fish_school_dataframe = trial.return_school_vals()
+        fish_raw_comp_dataframe = trial.return_raw_comp_vals()
+        fish_school_dataframe = trial.return_school_vals()
         first_trial = False
     else:
-        # fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
+        fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
         fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
-        # fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
-        # fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
+        fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
+        fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
 
-# fish_sigular_dataframe.to_csv("Fish_Individual_Values_3D.csv")
-#fish_comp_dataframe.to_csv("Fish_Comp_Values_3D.csv")
-# fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_3D.csv")
-# fish_school_dataframe.to_csv("Fish_School_Values_3D.csv")
+fish_sigular_dataframe.to_csv("Fish_Individual_Values_3D.csv")
+fish_comp_dataframe.to_csv("Fish_Comp_Values_3D.csv")
+fish_raw_comp_dataframe.to_csv("Fish_Raw_Comp_Values_3D.csv")
+fish_school_dataframe.to_csv("Fish_School_Values_3D.csv")
 
[…]

### 2024-04-22 Fish Data Analysis/Paper_Figures.qmd
Text changes

@@
 text_size = 16
+sig_text_size = 6
 
@@
 
-perp_angle_lm_close <- lm(Fish1_Yaw_Heading_PS ~ Ablation*Darkness, data = perp_angle_df %>% filter(Dist_Cat == "Close"))
-Anova(perp_angle_lm_close)
-emmeans(perp_angle_lm_close, specs = pairwise ~ Ablation:Darkness)
-
-my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"),
-                       c("No Ablation, Dark", "Ablated, Dark"))
+sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "B","No Ablation, Dark" = "A", "Ablated, Dark" = "B")
+perp_angle_df$sig_letters <- unlist(sig_dict[interaction(perp_angle_df$Ablation, perp_angle_df$Darkness, sep =", ")])
 
@@
   ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
-  scale_y_continuous(breaks = seq(-180,180, 60))+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  scale_y_continuous(breaks = seq(-180,180, 60), limits = c(-180,300))+
+  geom_text(aes(label = sig_letters, y = 300), color = "black", size = sig_text_size) +
   theme(axis.text.x = element_text(size = text_size),
@@
 
-perp_angle_lm_far <- lm(Fish1_Yaw_Heading_PS ~ Ablation*Darkness, data = perp_angle_df %>% filter(Dist_Cat == "Far"))
-Anova(perp_angle_lm_far)
-emmeans(perp_angle_lm_far, specs = pairwise ~ Ablation:Darkness)
-
 my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
                        c("No Ablation, Light", "Ablated, Dark"))
+
+sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "B", "Ablated, Dark" = "B")
+perp_angle_df$sig_letters <- unlist(sig_dict[interaction(perp_angle_df$Ablation, perp_angle_df$Darkness, sep =", ")])
 
@@
   geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
+  geom_text(aes(label = sig_letters, y = 300), color = "black", size = sig_text_size) +
   theme_light()+
@@
   ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
-  scale_y_continuous(breaks = seq(-180,180, 60))+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  scale_y_continuous(breaks = seq(-180,180, 60), limits = c(-180,300))+
   theme(axis.text.x = element_text(size = text_size),
@@
 
-ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)
+ggsave("Paper Figures/Figure 3.png", heading_PS_mega_plot, width = 14, height = 7)
 
@@
 
-my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
-                       c("No Ablation, Light", "Ablated, Dark"),
-                       c("Ablated, Light", "No Ablation, Dark"),
-                       c("Ablated, Light", "Ablated, Dark"))
+sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "B", "Ablated, Dark" = "B")
+school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])
 
@@
   #ylim(0,2.5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  geom_text(aes(label = sig_letters, y = 4), color = "black", size = sig_text_size) +
   theme(axis.text.x = element_text(size = text_size),
@@
 
-my_comparisons <- list(c("Ablated, Light", "No Ablation, Dark"))
+sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
+school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])
 
@@
   #ylim(0,5)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  geom_text(aes(label = sig_letters, y = 4), color = "black", size = sig_text_size) +
   theme(axis.text.x = element_text(size = text_size),
@@
 nnd_flow
-
-nnd_glm <- glm(NND ~ Ablation*Darkness*Flow, data = school_data)
-Anova(nnd_glm)
-emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)
-
 ```
@@
 
-my_comparisons <- list()
+sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
+school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])
 
@@
   scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
   theme(axis.text.x = element_text(size = text_size),
@@
 
-my_comparisons <- list()
+sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "A", "Ablated, Dark" = "B")
+school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])
 
@@
 polar_flow
-
-polar_glm <- glm(School_Polar ~ Ablation*Darkness*Flow, data = school_data)
-Anova(polar_glm)
-emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
 ```{r}
-my_comparisons <- list()
+sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
+school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])
 
@@
   ylim(0,6)+
-  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
+  geom_text(aes(label = sig_letters, y = 5.5), color = "black", size = sig_text_size) +
   theme(axis.text.x = element_text(size = text_size),
@@
   ylim(0,6)+
-  stat_compare_means(comparisons = my_comparisons, label.y = c(5.5), label = "p.signif", hide.ns = TRUE) +
+  geom_text(aes(label = sig_letters, y = 5.5), color = "black", size = sig_text_size) +
   theme(axis.text.x = element_text(size = text_size),
@@
 speed_flow
-
-speed_glm <- glm(School_Speed ~ Ablation*Darkness*Flow, data = school_data)
-Anova(speed_glm)
-emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
 ```
@@
 
+sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "B", "Ablated, Dark" = "B")
+group_sum_data$sig_letters <- unlist(sig_dict[interaction(group_sum_data$Ablation, group_sum_data$Darkness, sep =", ")])
+
 group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
@@
                                "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
+    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
     theme(axis.text.x = element_text(size = text_size),
@@
   scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
+
+sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
+group_sum_data$sig_letters <- unlist(sig_dict[interaction(group_sum_data$Ablation, group_sum_data$Darkness, sep =", ")])
 
@@
 group_flow
-
-groups_glm <- glm(Groups ~ Ablation*Darkness*Flow, data = school_data, family  = poisson)
-Anova(groups_glm)
-emmeans(groups_glm, specs = pairwise ~ Ablation:Darkness | Flow)
-
-groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"), family  = poisson)
-Anova(groups_glm_still, test.statistic="F")
-
-groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family  = poisson)
-Anova(groups_glm_flow, test.statistic="F")
-
 ```
@@
 
-ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 17)
+ggsave("Paper Figures/Figure 2.png", school_stats_mega_plot, width = 12, height = 17)
 ```

### 2024-04-22 Fish Data Analysis/Results_Text.qmd
Text changes

@@
 ```{r}
+library(marginaleffects)
 library(tidyverse)
@@
 
+```{r}
+still_school <- school_data %>% filter(Flow == "Still Water")
+
+nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = still_school)
+nnd_s_aov_me <- Anova(nnd_lmer_still, type=c("III"))
+
+m1 <- lmer(NND ~ Ablation*Darkness + (1|Date), data = still_school)
+m2 <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = still_school)
+m3 <- lmer(NND ~ Ablation*Darkness + Trial + (0 + Trial|Date), data = still_school)
+m4 <- lmer(NND ~ Ablation*Darkness + Trial+ (0 + Trial|Date) + (1|Date), data = still_school)
+m5 <- lmer(NND ~ Ablation*Darkness + (1|Date/Trial) + (1|Date), data = still_school)
+
+AIC(m1,m2,m3,m4,m5) %>% arrange(AIC)
+
+summary(nnd_lmer_still)
+nnd_s_aov_me
+
+Anova(m5, type=c("III"))
+
+emmeans(nnd_lmer_still, specs = pairwise ~ Ablation:Darkness)
+
+NND_pred <- predictions(m3, newdata = datagrid(Ablation = c("No Ablation","Ablated"),
+         Darkness = c("Light","Dark"),
+         Date = unique(still_school$Date),
+         Trial = seq(1:max(still_school$Trial)),
+         model = nnd_lmer_still))
+
+ggplot(NND_pred, aes(x = Trial, y = estimate, color = Date))+
+  geom_line()+
+  geom_point(data = still_school, aes(x = Trial, y = NND, color = Date))+
+  facet_wrap(~ Ablation+Darkness)+
+  theme_light()
+```
+
 ### School Stats Table Here
@@
 
-nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-nnd_s_aov_me <- Anova(nnd_lmer_still)
+nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+nnd_s_aov_me <- Anova(nnd_lmer_still, type=c("III"))
+nnd_s_aov_me
 
@@
 
-nnd_lmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-nnd_f_aov_me <- Anova(nnd_lmer_flow)
+nnd_lmer_flow <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+nnd_f_aov_me <- Anova(nnd_lmer_flow, type=c("III"))
 
@@
 
-polar_lmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-polar_s_aov_me <- Anova(polar_lmer_still)
+polar_lmer_still <- lmer(School_Polar ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+polar_s_aov_me <- Anova(polar_lmer_still, type=c("III"))
 
@@
 
-polar_lmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-polar_f_aov_me <- Anova(polar_lmer_flow)
+polar_lmer_flow <- lmer(School_Polar ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+polar_f_aov_me <- Anova(polar_lmer_flow, type=c("III"))
 
@@
 
-speed_lmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
-speed_s_aov_me <- Anova(speed_lmer_still)
+speed_lmer_still <- lmer(School_Speed ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
+speed_s_aov_me <- Anova(speed_lmer_still, type=c("III"))
 
@@
 
-speed_lmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
-speed_f_aov_me <- Anova(speed_lmer_flow)
+speed_lmer_flow <- lmer(School_Speed ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
+speed_f_aov_me <- Anova(speed_lmer_flow, type=c("III"))
 
@@
 
-groups_lmer_still <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"),
+groups_lmer_still <- glmer(Groups ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"),
                            family = poisson)
-groups_s_aov_me <- Anova(groups_lmer_still)
+groups_s_aov_me <- Anova(groups_lmer_still, type=c("III"))
 
@@
 
-groups_lmer_flow <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
+groups_lmer_flow <- glmer(Groups ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                            family = poisson)
-groups_f_aov_me <- Anova(groups_lmer_flow)
+groups_f_aov_me <- Anova(groups_lmer_flow, type=c("III"))
 
@@
 
-glmm_school_stats_table <- tibble(Stat = c(rep("NND",6),rep("Polarization",6),rep("Speed",6),rep("Groups",6)),
-       Flow_or_Still = rep(c(rep("Still",3) , rep("Flow",3)), 4),
-       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 8),
-       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,3),
-                  rep(length(nnd_lmer_flow@resp$y)-3,3)),times = 4),
-       Chisq = round(c(nnd_s_aov_me$Chisq[1:3],nnd_f_aov_me$Chisq[1:3],
-                 polar_s_aov_me$Chisq[1:3],polar_f_aov_me$Chisq[1:3],
-                 speed_s_aov_me$Chisq[1:3],speed_f_aov_me$Chisq[1:3],
-                 groups_s_aov_me$Chisq[1:3],groups_f_aov_me$Chisq[1:3]),2),
+values_to_grab <- c(2,3,4,5)
 
-       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[1:3],nnd_f_aov_me$`Pr(>Chisq)`[1:3],
-                 polar_s_aov_me$`Pr(>Chisq)`[1:3],polar_f_aov_me$`Pr(>Chisq)`[1:3],
-                 speed_s_aov_me$`Pr(>Chisq)`[1:3],speed_f_aov_me$`Pr(>Chisq)`[1:3],
-                 groups_s_aov_me$`Pr(>Chisq)`[1:3],groups_f_aov_me$`Pr(>Chisq)`[1:3]),2),
+glmm_school_stats_table <- tibble(Stat = c(rep("NND",8),rep("Polarization",8),rep("Speed",8),rep("Groups",8)),
+       Flow_or_Still = rep(c(rep("Still",4) , rep("Flow",4)), 4),
+       Condition = rep(c("Ablation","Darkness","Trial","Ablation x Darkness"), 8),
+       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,4),
+                  rep(length(nnd_lmer_flow@resp$y)-3,4)),times = 4),
+       Chisq = round(c(nnd_s_aov_me$Chisq[values_to_grab],nnd_f_aov_me$Chisq[values_to_grab],
+                 polar_s_aov_me$Chisq[values_to_grab],polar_f_aov_me$Chisq[values_to_grab],
+                 speed_s_aov_me$Chisq[values_to_grab],speed_f_aov_me$Chisq[values_to_grab],
+                 groups_s_aov_me$Chisq[values_to_grab],groups_f_aov_me$Chisq[values_to_grab]),2),
+
+       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[values_to_grab],nnd_f_aov_me$`Pr(>Chisq)`[values_to_grab],
+                 polar_s_aov_me$`Pr(>Chisq)`[values_to_grab],polar_f_aov_me$`Pr(>Chisq)`[values_to_grab],
+                 speed_s_aov_me$`Pr(>Chisq)`[values_to_grab],speed_f_aov_me$`Pr(>Chisq)`[values_to_grab],
+                 groups_s_aov_me$`Pr(>Chisq)`[values_to_grab],groups_f_aov_me$`Pr(>Chisq)`[values_to_grab]),2),
 
@@
 
-perp_angle_lmer_close <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Close"))
+perp_angle_lmer_close <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + Trial + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Close"))
 perp_angle_aov_me_close <- Anova(perp_angle_lmer_close)
@@
 
-perp_angle_lmer_far <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Far"))
+perp_angle_lmer_far <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + Trial + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Far"))
 perp_angle_aov_me_far <- Anova(perp_angle_lmer_far)
@@
 
+shapiro.test(resid(perp_angle_lmer_far))
+
 turning_school_stats_table <- tibble(
-       Near_or_Far = rep(c(rep("Near",3) , rep("Far",3)), 1),
-       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 2),
-       DF = c(rep(length(perp_angle_lmer_close@resp$y)-3,3),
-                  rep(length(perp_angle_lmer_far@resp$y)-3,3)),
-       Chisq = round(c(perp_angle_aov_me_close$Chisq[1:3],perp_angle_aov_me_far$Chisq[1:3]),3),
-       P_Val = round(c(perp_angle_aov_me_close$`Pr(>Chisq)`[1:3],perp_angle_aov_me_far$`Pr(>Chisq)`[1:3]),3),
+       Near_or_Far = rep(c(rep("Near",4) , rep("Far",4)), 1),
+       Condition = rep(c("Ablation","Darkness","Trial","Ablation x Darkness"), 2),
+       DF = c(rep(length(perp_angle_lmer_close@resp$y)-3,4),
+                  rep(length(perp_angle_lmer_far@resp$y)-3,4)),
+       Chisq = round(c(perp_angle_aov_me_close$Chisq[1:4],perp_angle_aov_me_far$Chisq[1:4]),2),
+       P_Val = round(c(perp_angle_aov_me_close$`Pr(>Chisq)`[1:4],perp_angle_aov_me_far$`Pr(>Chisq)`[1:4]),2),
        Is_Sig = P_Val < 0.05)
@@
 tab_df(turning_school_stats_table, file="turning_stats.doc")
-
 ```

### 2024-06-18 2Dto3D/DLT_Plotter.py
Changing plotting, saving tables

@@ -69,16 +69,16 @@ for file_name in three_d_files:
 
         file_id = file_name[0:22]
 
-        fig.write_html("Saved 3D Plots Manual/{name}_animated.html".format(name = file_id), auto_play=False)
+        #fig.write_html("Saved 3D Plots Manual/{name}_animated.html".format(name = file_id), auto_play=False)
 
 
         fish_len
 
         head_df = df[df['BodyPart'] == "head"] 
 
-        head_df["x"] = head_df["x"]/fish_len
-        head_df["y"] = head_df["y"]/fish_len
-        head_df["z"] = head_df["z"]/fish_len
+        head_df["x"] = head_df["x"]
+        head_df["y"] = head_df["y"]
+        head_df["z"] = head_df["z"]
 
         fig = px.line_3d(head_df,x="x", y="y", z="z", color="Fish", hover_data = ["BodyPart"])
 

### 2025-08-22 Fish Data Analysis/Paper_Figures.qmd
Small updates

@@
     theme_light()+ 
+    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
     scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",

### 2025-08-22 Fish Data Analysis/groups.qmd
Small updates

---
title: "Groups with lines!"
format: html
editor: visual
---

## Loading in the Libraries for Everything

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(pracma)
library(igraph)

```

## Functions and Variables

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}

deg_ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}
rad_ang_mean <- function(x){atan2(mean(sin(x)),mean(cos(x)))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}

fold_angle_neg_180_180_to_neg_90_90 <- function(x){ifelse(x > 90,90-abs(90-x),ifelse(x < -90, -90+abs(-90-x), x))}

min_n <- function(x,n){sort(x)[1:n]}
max_n <- function(x,n){sort(x,decreasing = TRUE)[1:n]}

light_no_ab_color = "#9C9C9C"   #"#C62E65" #A1BAA4" #"#d4d7dd" 06D6A0
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
dark_ab_color = "#49A078"   #"#1E4371"
sim_color = "#777777"

flow_split_still = "#F59DE2"
flow_split_flow = "#5DD492"

dark_split_light = "#5e94d4"
dark_split_dark = "#011627"

tailbeat_len = 19

allowed_flow_type = c("Still Water","Flowing Water (2 BL/s)")

dot_binwidth = 0.03

text_size = 16
sig_text_size = 6

# for turning data
x_offset <- 1.95
y_offset <- 1.15

fish_len <- 0.083197
```

```{r}
get_n_groups <- function(HeadX, HeadY, HeadZ, gDist){

  HeadX <- na.omit(HeadX)
  HeadY <- na.omit(HeadY)
  HeadZ <- na.omit(HeadZ)

  #Need at least 5 fish for this
  if(length(HeadX) < 5){
    return(NA)
  }

  A <- matrix(c(HeadX, HeadY, HeadZ), nrow =  length(HeadX), ncol = 3)
  B <- matrix(c(HeadX, HeadY,HeadZ), nrow =  length(HeadX), ncol = 3)

  X <- (distmat(A, B) <= max(gDist))

  #print(X)

  g <- graph_from_adjacency_matrix(X, mode = "lower", weighted = "weight")

  return(components(g)$no)
}
```

### Number of Groups

```{r}
all_fish_comp <- read.csv("Data/Fish_Raw_Values_3D.csv") %>% 
                           filter(Flow == "0") %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Ablation_Darkness = factor(paste(Ablation,Darkness,sep=", ")))

#Uncomment with new data, takes a long time to run just for graph edits
all_fish_comp_groups <- all_fish_comp %>% expand_grid(Group_Dist = seq(10,25,1)) %>%
                                          group_by(Darkness, Ablation, Ablation_Darkness,
                                                   Year, Month, Day, Trial, Tailbeat, Frame, Group_Dist) %>%
                                          summarize(n_groups = get_n_groups(Head_X,Head_Y,Head_Z,Group_Dist)) %>%
                                          ungroup() %>%
                                          group_by(Darkness, Ablation, Ablation_Darkness,
                                                   Year, Month, Day, Trial, Tailbeat, Group_Dist) %>%
                                          summarize(Groups = as.integer(mean(n_groups, na.rm = TRUE))) %>%
                                          ungroup() %>%

                                           # ### Used to remove every third point to reduce autocorrelation
                                           filter(Tailbeat %% 3 == 1) %>%
                                          na.omit()

saveRDS(all_fish_comp_groups, "all_fish_comp_groups.RDS")

all_fish_comp_groups <- readRDS("all_fish_comp_groups.RDS")

group_sum_data <- all_fish_comp_groups %>% 
                            filter(Groups > 0) %>% group_by(Ablation, Darkness, Groups, Group_Dist) %>%
                            summarise(count = n()) %>%
                            ungroup() %>%
                            mutate(Groups = as.factor(Groups),
                                   Groups = fct_rev(Groups))

group_sum_data_1 <- group_sum_data %>% complete(Darkness,Ablation,Group_Dist,Groups,fill=list(count=0)) %>%
                                       group_by(Darkness,Ablation,Group_Dist) %>%
                                       mutate(total = sum(count),
                                              Percent_Group = count / total) %>%
                                       ungroup() %>%
                                       filter(Groups == 1)

group_sum_data_1_binom <- all_fish_comp_groups %>% mutate(Is_One = ifelse(Groups == 1, 1, 0)) %>%
                                                   mutate(Date = paste(Year,Month,Day,sep="_"))

group_1_glm <- glm(Is_One ~ Ablation*Darkness*Group_Dist, data = group_sum_data_1_binom, family = "binomial")
group_1_aov <- Anova(group_1_glm, type=c("III"))
group_1_aov

# group_1_glmer <- glmer(Is_One ~ Ablation*Darkness*Group_Dist + Trial + (1|Date), data = group_sum_data_1_binom, family = "binomial")
# group_1_aov <- Anova(group_1_glmer, type=c("III"))
# group_1_aov

group_still <- ggplot(group_sum_data_1, aes(Group_Dist / fish_len / 100, Percent_Group, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(data = group_sum_data_1_binom, aes(x = Group_Dist / fish_len / 100, y = predict(group_1_glm, type="response")), size = 1) + 
  xlab("Maximum Distance to Connect Group (BL)")+
  ylab("Proportion of Time in 1 Group")+
  scale_y_continuous(breaks = seq(0,1,0.25), limits = c(0,1))+
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color),
                     name = "Condition") +
  theme_light()+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size),
        strip.text.x = element_text(size = text_size))

group_still

#ggsave("Paper Figures/Subgroup_Graphs.png", group_still, width = 10, height = 7)

```

### 2025-08-22 3D_data_files_to_csv_4P.py

@@ -1441,6 +1441,38 @@ class trial:
 
         return(out_data)
 
+    def return_raw_points(self):
+        firstfish = True
+
+        for fish in self.fishes:
+
+            data_len = len(fish.head_x)
+
+            d = {'Year': np.repeat(self.year,data_len),
+                 'Month': np.repeat(self.month,data_len),
+                 'Day': np.repeat(self.day,data_len),
+                 'Trial': np.repeat(self.trial,data_len), 
+                 'Tailbeat': np.linspace(1,data_len,data_len) // tailbeat_len,
+                 'Frame': np.linspace(1,data_len,data_len),
+                 'Ablation': np.repeat(self.abalation,data_len), 
+                 'Darkness': np.repeat(self.darkness,data_len), 
+                 'Flow': np.repeat(self.flow,data_len), 
+                 #get into cm, not BL or meters
+                 'Head_X': fish.head_x * fish_len*100,
+                 'Head_Y': fish.head_y * fish_len*100,
+                 'Head_Z': fish.head_z * fish_len*100,
+                 'Midline_X': fish.head_x * fish_len*100,
+                 'Midline_Y': fish.head_y * fish_len*100,
+                 'Midline_Z': fish.head_z * fish_len*100} #,
+
+            if firstfish:
+                out_data = pd.DataFrame(data=d)
+                firstfish = False
+            else:
+                out_data = out_data.append(pd.DataFrame(data=d))
+
+        return(out_data)
+
     def return_comp_vals(self):
         firstfish = True
 
@@ -1677,17 +1709,20 @@ for trial in trials:
         fish_comp_dataframe = trial.return_comp_vals()
         fish_raw_comp_dataframe = trial.return_raw_comp_vals()
         fish_school_dataframe = trial.return_school_vals()
+        fish_raw_dataframe = trial.return_raw_points()
         first_trial = False
     else:
         fish_sigular_dataframe = fish_sigular_dataframe.append(trial.return_fish_vals())
         fish_comp_dataframe = fish_comp_dataframe.append(trial.return_comp_vals())
         fish_raw_comp_dataframe = fish_raw_comp_dataframe.append(trial.return_raw_comp_vals())
         fish_school_dataframe = fish_school_dataframe.append(trial.return_school_vals())
[…]
